### 2018-10-22 Thesis_Latex/Preliminary Report/Preliminary_Report.tex
third commit

\documentclass[11pt]{IEEEtran}

\usepackage{algorithm}
\usepackage{algpseudocode}
\usepackage{multirow}
\usepackage{multicol}
\usepackage{siunitx}
\usepackage{booktabs}
\usepackage{listings}
\usepackage{stfloats}
\usepackage{midfloat}
\usepackage{color}
\usepackage[table]{xcolor}
\usepackage{lipsum}
\usepackage[utf8x]{inputenc}
\usepackage{hyperref}
\usepackage{bbm}

\newtheorem{thm}{Theorem}[section]
\newtheorem{defn}[thm]{Def.}
\newtheorem{propen}[thm]{Prop.}
\newtheorem{cor}[thm]{Cor.}

\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
		T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}

\title{ATLASCAR2 - Path Planning and Tracking with Moving Obstacle Avoidance based on MPC}
\author{\IEEEauthorblockN{Alberto Franco}\\
\IEEEauthorblockA{Department of Information Engineering\\
Università degli Studi di Padova\\ \href{mailto:alberto.franco.3@studenti.unipd.it}{alberto.franco.3@studenti.unipd.it}}}

\begin{document}
\maketitle
\begin{abstract}
This preliminary report presents the proposal of my master thesis. The aim of this project is to study and implement a path planning and tracking framework in order to prevent ATLASCAR2 collision with a moving obstacle vehicle. The proposed algorithm, based on the Model Predictive Control paradigm, solves an optimal problem formulated in terms of cost minimization under constraints.
\end{abstract}
\vspace{-1em}
\section{Introduction}
In robotic research, the problem of navigation is among the most important. Basically all autonomous mobile robots need some kind of navigation to fulfill the mobile term.
We understand navigation as a process of planning a path of a mobile robot from its current position to a desired goal location, following the planned path, and avoiding any discovered obstacles along the way. The desired paths have to
fulfill several conditions to ensure safety and feasibility of the navigation. Moreover, the paths can be also compared in terms of desirability for example short or smooth paths are usually more desirable than long and curved ones. Such paths should therefore be preferred in the navigation process. Beyond the path planning, the navigation problem also involves reacting to changes of the environment model. Robots are required to move towards target in a short time and avoid either static or dynamic obstacles observed by their sensors, which involves efficient path planning and valid obstacle avoidance. Though these two topics have been well researched, currently, there is no ideal solution to handling the navigation problem within cluttered dynamic environments.

\section{Context of the Problem}
Dynamic environments pose several added difficulties to the motion planning problem. The dynamics of the ATLASCAR2 must be taken into account, and there are limitations due to the sensors range and uncertainty in measurements, that must be reflected on the motion plan. Besides it, a motion plan must incorporate time restrictions, meaning the vehicle will require a certain amount of time to accomplish a task. For example, when crossing a road, the ATLASCAR2 must do it fast enough to avoid incoming cars.

\section{Proposed Solution}
The idea is to develop a path-planning approach based on the
theory of virtual potential field and a path-tracking framework using multiconstrained MPC (MMPC) for autonomous vehicles, which seeks to minimize the incidence for collision on roads. By receiving information about vehicle position, road parameters, and obstacles surrounding the vehicle, this framework provides a vehicle trajectory for a collision avoidance system based on a 3-D virtual dangerous potential field, which seeks to minimize risk to the vehicle through evasive maneuvering. A MMPC-based path-tracking system, considering the geometric constraints of road and dynamic constraints of the vehicle, calculates the steering wheel angle to track the planned trajectory and to avoid obstacles.

\section{Phases and Objectives}
The main phases/objectives include the following:
\begin{itemize}
	\item Create the state of the art for this problem and associated techniques, and get acquainted with the existing setup and previous related works;
	\item Introduce the problem and overall framework of the collision avoidance system;
	\item Implement the path-planning algorithm that determines a collision-free trajectory based on the 3-D dangerous potential field;
	\item Develop the augmented vehicle dynamic model used for path tracking;
	\item Design and implement of multiconstrained Model Predictive Control
	\item Simulations of path-planning and path-tracking with ATLASCAR2 to verify the effectiveness of the proposed framework;
	\item Write the thesis and other documentation.
\end{itemize}

\begin{thebibliography}{00}
	\bibitem{MMPC}J. Ji, A. Khajepour, W. W. Melek and Y. Huang, "Path Planning and Tracking for Vehicle Collision Avoidance Based on Model Predictive Control With Multiconstraints," in IEEE Transactions on Vehicular Technology, vol. 66, no. 2, pp. 952-964, Feb. 2017.

	\bibitem{onlineMPC}M. Werling and D. Liccardo, "Automatic collision avoidance using model-predictive online optimization," 2012 IEEE 51st IEEE Conference on Decision and Control (CDC), Maui, HI, 2012, pp. 6309-6314.

	\bibitem{swarms}Wei Xi and J. S. Baras, "MPC based motion control of car-like vehicle swarms," 2007 Mediterranean Conference on Control \& Automation, Athens, 2007, pp. 1-6.

	\bibitem{autoMPC}J. V. Frasch et al., "An auto-generated nonlinear MPC algorithm for real-time obstacle avoidance of ground vehicles," 2013 European Control Conference (ECC), Zurich, 2013, pp. 4136-4141.

	\bibitem{safety}T. Xu and H. Yuan, "Autonomous vehicle active safety system based on path planning and predictive control," 2016 35th Chinese Control Conference (CCC), Chengdu, 2016, pp. 8889-8895.

	\bibitem{matsumoto}N. Wada and T. Matsumoto, "Driver assistance for collision avoidance by constrained MPC," 2017 56th Annual Conference of the Society of Instrument and Control Engineers of Japan (SICE), Kanazawa, 2017, pp. 90-93.

	\bibitem{fuzzyMPC}Y. Nishio, K. Nonaka and K. Sekiguchi, "Moving obstacle avoidance control by fuzzy potential method and model predictive control," 2017 11th Asian Control Conference (ASCC), Gold Coast, QLD, 2017, pp. 1298-1303.

	\bibitem{NONMPC}Yu, S., Li, X., Chen, H. and Allgöwer, F. (2015), "Nonlinear model predictive control for path following problems". Int. J. Robust Nonlinear Control, 25: 1168–1182. 
\end{thebibliography}

\end{document}

### 2018-10-23 Thesis_Latex/Preliminary Report/Preliminary_Report.tex
Preliminary Report

@@
 \section{Proposed Solution}
-The idea is to develop a path-planning approach based on the
-theory of virtual potential field and a path-tracking framework using multiconstrained MPC (MMPC) for autonomous vehicles, which seeks to minimize the incidence for collision on roads.
-By receiving information about vehicle position, road parameters, and obstacles surrounding the vehicle, this framework provides a vehicle trajectory for a collision avoidance system based on a 3-D virtual dangerous potential field, which seeks to minimize risk to the vehicle through evasive maneuvering.
-A MMPC-based path-tracking system, considering the geometric constraints of road and dynamic constraints of the vehicle, calculates the steering wheel angle to track the planned trajectory and to avoid obstacles.
+The idea is to develop a path planning approach based on the
+theory of virtual potential field and a path tracking framework using multiconstrained MPC (MMPC) for autonomous vehicles, which seeks to minimize the incidence for collision on roads.
+By receiving information about vehicle position, road parameters, and obstacles surrounding the vehicle, this framework provides a vehicle trajectory for a collision avoidance system based on a 3D virtual dangerous potential field, which seeks to minimize risk to the vehicle through evasive maneuvering.
+A MMPC-based path tracking system, considering the geometric constraints of road and dynamic constraints of the vehicle, calculates the steering wheel angle to track the planned trajectory and to avoid obstacles.
 
 \section{Phases and Objectives}
-The main phases/objectives include the following:
+The main phases/objectives are the following:
 \begin{itemize}
 	\item Create the state of the art for this problem and associated techniques, and get acquainted with the existing setup and previous related works;
-	\item Introduce the problem and overall framework of the collision avoidance system;
-	\item Implement the path-planning algorithm that determines a collision-free trajectory based on the 3-D dangerous potential field;
+	\item Introduce the problem in the context of ATLASCAR2 and overall framework of the collision avoidance system;
+	\item Implement the path planning algorithm that determines a collision-free trajectory based on the 3D dangerous potential field;
 	\item Develop the augmented vehicle dynamic model used for path tracking;
 	\item Design and implement of multiconstrained Model Predictive Control
-	\item Simulations of path-planning and path-tracking with ATLASCAR2 to verify the effectiveness of the proposed framework;
+	\item Simulations of path planning and path tracking with ATLASCAR2 to verify the effectiveness of the proposed framework;
 	\item Write the thesis and other documentation.

### 2018-12-13 Thesis_Latex/Paper/Paper.tex
update Paper

\documentclass[conference, 11pt]{IEEEtran}
\IEEEoverridecommandlockouts

\usepackage{algorithm}
\usepackage{algpseudocode}
\usepackage{multirow}
\usepackage{multicol}
\usepackage{siunitx}
\usepackage{booktabs}
\usepackage{listings}
\usepackage{stfloats}
\usepackage{midfloat}
\usepackage{color}
\usepackage[table]{xcolor}
\usepackage{lipsum}
\usepackage[utf8x]{inputenc}

\usepackage{bbm}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage[colorlinks=true,linkcolor=black,anchorcolor=black,citecolor=black,filecolor=black,menucolor=black,runcolor=black,urlcolor=black]{hyperref}

\newtheorem{thm}{Theorem}[section]
\newtheorem{defn}[thm]{Def.}
\newtheorem{propen}[thm]{Prop.}
\newtheorem{cor}[thm]{Cor.}

\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
		T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}

\title{Advanced Methods for Autonomous Driving based on Adaptive Model Predictive Control}
\author{\IEEEauthorblockN{Alberto Franco}\\
\IEEEauthorblockA{Department of Information Engineering\\
Università degli Studi di Padova\\ \href{mailto:alberto.franco.3@studenti.unipd.it}{alberto.franco.3@studenti.unipd.it}}}

\begin{document}
\maketitle
\begin{abstract}
	In this paper we present two different strategies for a self-driving car. The aim of this project is to study and implement a path tracking framework in order to prevent ATLASCAR2 collision with moving obstacle vehicles. The proposed algorithms, based on the Model Predictive Control paradigm, solve optimal problems formulated in terms of cost minimization under constraints.
\end{abstract}

\section{Introduction}
In robotic research, the problem of navigation is among the most important. Basically all autonomous mobile robots need some kind of navigation to fulfill the mobile term.
We understand navigation as a process of planning a path of a mobile robot from its current position to a desired goal location, following the planned path, and avoiding any discovered obstacles along the way. The desired paths have to
fulfill several conditions to ensure safety and feasibility of the navigation. Moreover, the paths can be also compared in terms of desirability for example short or smooth paths are usually more desirable than long and curved ones. Such paths should therefore be preferred in the navigation process. Beyond the path planning, the navigation problem also involves reacting to changes of the environment model. Robots are required to move towards target in a short time and avoid either static or dynamic obstacles observed by their sensors, which involves efficient path planning and valid obstacle avoidance. Though these two topics have been well researched, currently, there is no ideal solution to handling the navigation problem within cluttered dynamic environments.

\section{Context of the Problem and \\  Proposed Solution}
The ATLACAR2 has a sensor, such as lidar, that measures the distance to an obstacle in front of the vehicle and in the same lane. The obstacle can be static, such as a large pothole, or moving, such as a slow-moving vehicle. The most common maneuver from the driver is to temporarily move to another lane, drive past the obstacle, and move back to the original lane afterward
In this case, we want to design an obstacle avoidance system that moves the ATLASCAR2 around a moving obstacle in the lane using throttle and steering angle. This system uses an adaptive Model Predictive Controller that updates both the predictive model and the mixed input/output constraints at each control interval. Moreover this vehicle is also 
equipped with a lane-keeping assist system: it has a sensor, such as camera, that measures the lateral deviation and relative yaw angle between the centerline of a lane and the ATLASCAR2. The sensor also measures the current lane curvature and curvature derivative. Depending on the curve length that the sensor can view, the curvature in front of the vehicle can be calculated from the current curvature and curvature derivative. This system keeps the autonomous car travelling along the centerline of the lanes on the road by adjusting the front steering angle. The goal for lane keeping control is to drive both lateral deviation and relative yaw angle close to zero.

TO DO THEORETICAL BACKGROUND ADAPTIVE MPC

\section{Obstacle Avoidance}
\subsection{Problem Formulation}
The collision avoidance problem is very dependent on the vehicle modeling since it is a requirement for  adaptive MPC law design. 
\begin{figure}[!h]
	\centering
	\includegraphics[width=1\columnwidth]{./figure/obstacleAvoidance.pdf}
	\caption{Problem description of collision avoidance on road.}
	\label{fig:obstacleAvoidance}
\end{figure}

The model used in this paper should take into account the kinematic and dynamic aspects of the vehicle. Here, we present a non linear mathematical model of a vehicle used for the development of a collision avoidance system.
The model has four states and two inputs:
\[ 
\textbf{x}=\begin{bmatrix}
   x&y&\theta&v 
  \end{bmatrix}^{T}
\qquad 
\textbf{u}=\begin{bmatrix}
T&\delta 
\end{bmatrix}^{T}
\]
where $(x,y)$ are the global coordinates of the center point of the car, $\theta$ is the heading angle of the car body with respect to the $x$-axis and $v$ is the speed of the car (positive). The manipulated variables are $T$ the throttle (positive when accelerating/negative when decelerating) and $\delta$ the steering angle ($0$ when aligned with car, counterclockwise positive).

The simple non-linear model to describe the dynamics of the ATLASCAR2 is the following
\begin{equation*}
	\label{eqn:dynamics_model_obstacle_avoidance}
	\left \{ \begin{array}{llll}
	\dot{x} = -v\sin(\theta)\cdot\theta+\cos(\theta)\cdot v\\
	\dot{y} = v\cos(\theta)\cdot\theta+\sin(\theta)\cdot v\\
	\dot{\theta} =(\tan(\delta)/C_L)\cdot v+ \bigg(v\bigg(\tan(\delta)^2+1\bigg)/C_L\bigg)\cdot \delta\\
	\dot{v} =0.5\cdot T
	\end{array} 
	\right .
\end{equation*}
where $C_L$ is the car length. The state equations can be re-written in more compact form as follows:
\begin{equation}
	\label{eqn:dynamics_ss_obstacle_avoidance_con}
	\begin{array}{ll}
	\dot{\textbf{x}} =A_c \textbf{x}+ B_c \textbf{u}\\
	\textbf{y} =C_c \textbf{x} + D_c \textbf{u}
	\end{array}
\end{equation}
where
\[ 
A_c=\begin{bmatrix}
0&0&-v\sin(\theta)&\cos(\theta)\\
0&0&v\cos(\theta)&\sin(\theta)\\
0&0&0&\tan(\delta)/C_L\\
0&0&0&0
\end{bmatrix},
\]
\[
B_c=\begin{bmatrix}
0&0\\
0&0\\
0&v\bigg(\tan(\delta)^2+1\bigg)/C_L\\
0.5&0
\end{bmatrix},
\]
\[
C_c=\begin{bmatrix}
1&0&0&0\\
0&1&0&0\\
0&0&1&0\\
0&0&0&1
\end{bmatrix} = \textbf{I}_4, 
\qquad
D_c=\begin{bmatrix}
0&0\\
0&0\\
0&0\\
0&0
\end{bmatrix} = \textbf{0}_{4\times2}. 
\]
The system to be controlled is usually modeled by a discrete state-space model in the MPC literature. Therefore, (\ref{eqn:dynamics_ss_obstacle_avoidance_con})
is transformed into a discrete state-space model to be used by the model predictive controller:
\begin{equation}
\label{eqn:dynamics_ss_obstacle_avoidance_dis}
	\begin{array}{rr}
	{\textbf{x}}(k+1) =A_d \textbf{x}(k)+ B_d \textbf{u}(k)\\
	\textbf{y}(k) =C_d \textbf{x}(k) + D_d \textbf{u}(k)
	\end{array}
\end{equation}
where $A_d$ and $B d$ are the state and control matrices for the discrete state-space equation, respectively, which can be calculated with the Euler method as
\[
A_d = e^{A_cT_s},\qquad B_d = \int_{kT_s}^{(k+1)T_s} e^{A_c[(k+1)T_s-\eta]}B_c d\eta
\]
where $T_s$ is the sampling interval for the discrete state-space model. The matrices $C_d$ and $D_d$ are equivalent to those in the continuous case. For simplicity, we assume that all the states are measurable and the ATLASCAR2 drives east with a constant speed at the nominal operating point. In the scenario we are going to consider, the road is straight and our vehicle stays in the middle of the center lane when not passing. Without losing generality, the ATLASCAR2 passes an obstacle both to the right and to the left lane depending on where it is placed on the road. We create also a safe zone around the obstacles so that the vehicle does not get too close the osbtacle when passing it.

\subsection{Design of Adaptive Model Predictive Control}

We designed a model predictive controller that can make the ATLASCAR2 mantain a desired velocity and stay in the middle of center lane. We used an Adaptive MPC controller because it handles the nonlinear vehicle dynamics more effectively than a traditional MPC controller in fact the latter uses a constant plant model, however, the former allows us to provide a new plant model at each control interval. Because the new model describes the plant dynamics more accurately at the new operating condition, an adaptive MPC controller performs better than a traditional MPC controller. In practice at each control interval, the adaptive MPC controller updates the plant model and the nominal conditions. Once updated, the model and the conditions remain constant over the prediction horizon. At the beginning, we specified the constraints for the manipulated variables: to prevent the ATLASCAR2 from accelerating or decelerating too quickly, we added an hard constraint on the throttle rate of change and another one on the steering angle rate of change. We used an approach that takes advantage of the ability of MPC to handle constraint explicitly. When an obstacle is detected, it defines an area on the road (in terms of constraints) that the ATLASCAR2 must not enter during the prediction horizon. At the next control interval the area is redefined based on the new positions of the vehicle and the obstacle until passing is completed.
To define the area to avoid, we used the following mixed Input/Output constraints:
\begin{equation*}
	\label{eqn:mixed_IO_constraints}
	E\textbf{u}+F\textbf{y}\leq G
\end{equation*}
where $\textbf{u}$ and $\textbf{y}$ are respectively the manipulated variable vector and the output variable vector, while $E,F,G$ are the matrices that can be updated when the controller is running:
\begin{itemize}
	\item the first constraint is an upper bound on the $y$-coordinate (right boundary of the road);
	\item the second constraint is a lower bound on the $y$-coordinate (left boundary of the road);
	\item the third constraint is for the obstacle avoidance; even though no obstacle is detected at the nominal condition, we must add this fake constraint here because we cannot change the dimensions of the constraint matrices at run time (it has the same form as the second one).ù
\end{itemize}
The matrices for the above inequality are the following:
\[
E= 
\begin{bmatrix}
0&0\\
0&0\\
0&0\\
0&0
\end{bmatrix},
\quad
F=\begin{bmatrix}
0&1&0&0\\
0&-1&0&0\\
cS&-1&0&0
\end{bmatrix},\quad
G=
\begin{bmatrix}
W/2\\W/2\\-cI
\end{bmatrix}
\]
where $W$ is the width of the road and $cI$ and $cS$ are the required parameters such that the ATLASCAR2 must be above the line formed from the vehicle to safe zone corner for left/right passing.

\subsection{Simulation Results}
TO DO

\section{Lane Following}
\subsection{Problem Formulation}
A lane-following system is a control system that keeps the vehicle traveling along the centerline of a highway lane, while maintaining a user-set velocity. The lane-following scenario is depicted in the following figure:
\begin{figure}[!h]
	\centering
	\includegraphics[width=1\columnwidth]{./figure/laneFollowing.pdf}
	\caption{Problem description of a lane following system.}
	\label{fig:laneFollowing}
\end{figure}

In a classic lane keeping assist, it is assumed that the longitudinal velocity is constant. This restriction is relaxed in this model because the longitudinal acceleration varies in this MIMO control system. This lane-following system manipulates both the longitudinal acceleration and the front steering angle of the vehicle to keep the lateral deviation and the relative yaw angle small and the longitudinal velocity close to a driver set velocity. If these two goals cannot be met at the same moment, the system tries to balance them.

The model that we are considering, contains a lot of parameters. The first fundamental block describes the vehicle dynamics: we have applied the bicycle model of lateral vehicle dynamics and approximate the longitudinal dynamics using a time constant:
\subsubsection{Longitudinal dynamics}
\begin{equation}
	\label{eqn:longi_dynamics_simple_model}
	G(s)=\frac{1}{\tau s^2+s} \quad \text{where $\tau$ is a time constant}
\end{equation}

\subsubsection{Lateral dynamics}
Local function: we have a continuous vehicle lateral model from parameters
\begin{equation}
\label{eqn:lateral_dynamics_simple_model}
\begin{array}{ll}
\dot{\textbf{x}}_{\text{lat}} =A_g \textbf{x}_{\text{lat}}+ B_g \textbf{u}_{\text{lat}}\\
\textbf{y}_{\text{lat}} =C_g \textbf{x}_{\text{lat}} + D_g \textbf{u}_{\text{lat}}
\end{array}
\end{equation}
where the input is the steering angle in radians, and the outputs are the lateral velocity in meters per second and yaw angle rate in radians per second.
\begin{equation*}
\textbf{x}_{\text{lat}} = \begin{bmatrix}
V_y&\dot{\psi}
\end{bmatrix}^T
\qquad
\textbf{u}_{\text{lat}} = \delta
\end{equation*}
and
\[ 
A_g=\begin{bmatrix}
-\frac{2C_F+2C_R}{mV_x}&-\frac{2C_Fl_F-2C_Rl_R}{mV_x} - V_x\\
-\frac{2C_Fl_F-2C_Rl_R}{I_ZV_x}&-\frac{2C_Fl_F^2+2C_Rl_R^2}{I_ZV_x}
\end{bmatrix},
\]
\[
B_g=\begin{bmatrix}
2C_F/m\\
2C_Fl_F/I_Z
\end{bmatrix},
\quad
C_g=\textbf{I}_2, 
\quad
D_g=\textbf{0}_{2\times1}.
\]
The parameters that we are considering are the following ones:
\begin{itemize}
	\item $V_x$ is the longitudinal velocity of the car;	
	\item $m$ is the total mass parameter; 
	\item $I_Z$ is the yaw moment of inertia parameter;
	\item $l_F$ and $l_R$ are the longitudinal distances from center of gravity to front and rear tires parameters;
	\item $C_F$ and $C_R$ are the cornering stiffnesses of front and rear tires parameters.
\end{itemize}
The goal for the driver steering model is to keep the vehicle in its lane and follow the curved road by controlling the front steering angle . This goal is achieved by driving the yaw angle error $e_2 = \psi -\psi_{\text{des}}$ and lateral displacement error $e_1$ to zero ($\dot{e}_1 = V_xe_2+V_y$). We can incorporate these two paramenters in the augmented model:
\begin{equation}
\label{eqn:lateral_dynamics_augmented_model}
\begin{array}{ll}
\dot{\textbf{x}}_{\text{aug}} =A_a \textbf{x}_{\text{aug}}+ B_a \textbf{u}_{\text{aug}}\\
\textbf{y}_{\text{aug}} =C_a \textbf{x}_{\text{aug}} + D_a \textbf{u}_{\text{aug}}
\end{array}
\end{equation}
where
\begin{equation*}
\textbf{x}_{\text{aug}} = \begin{bmatrix}
V_y&\dot{\psi}&e_1&e_2
\end{bmatrix}^T,
\qquad
\textbf{u}_{\text{aug}} = 
\begin{bmatrix}
\delta&\dot{\psi}_{\text{des}}
\end{bmatrix}^T
\end{equation*}
and
\[ 
A_a=\begin{bmatrix}
A_g&\textbf{0}_{2\times2}\\
\textbf{I}_2&\begin{matrix}
0&V_x\\
0&0
\end{matrix}
\end{bmatrix},
\quad
B_a=\begin{bmatrix}
B_g&\textbf{0}_{2\times1}\\
0&0\\
0&-1
\end{bmatrix},
\]
\[
C_a=\begin{bmatrix}
\textbf{0}_{2\times2}&\textbf{I}_2
\end{bmatrix}, 
\quad
D_a=
\textbf{0}_{2\times2}. 
\]
Combining (\ref{eqn:longi_dynamics_simple_model}) with (\ref{eqn:lateral_dynamics_augmented_model}) yields the state-space model that characterizes the model predictive controller:
\begin{equation}
\label{eqn:full_dynamics_model}
\begin{array}{ll}
\dot{\textbf{x}}_{\text{tot}} =A_f \textbf{x}_{\text{tot}}+ B_f \textbf{u}_{\text{tot}}\\
\textbf{y}_{\text{tot}} =C_f \textbf{x}_{\text{tot}} + D_f \textbf{u}_{\text{tot}}
\end{array}
\end{equation}
where
\begin{equation*}
\textbf{x}_{\text{tot}} = \begin{bmatrix}
V_x\\\dot{V}_x\\V_y\\\dot{\psi}\\e_1\\e_2
\end{bmatrix},
\qquad
\textbf{u}_{\text{tot}} = 
\begin{bmatrix}
a\\\delta\\\dot{\psi}_{\text{des}}
\end{bmatrix}
\end{equation*}
and

\[ 
A_f=\begin{bmatrix}
\begin{matrix}-2&0\\1&0\end{matrix}&\textbf{0}_{2\times4}\\
\textbf{0}_{4\times2}&A_a
\end{bmatrix},
\quad
B_f=\begin{bmatrix}\begin{matrix}2\\0\end{matrix}&\textbf{0}_{2\times2}\\
\textbf{0}_{4\times1}&B_a
\end{bmatrix},
\]
\[
C_f=\begin{bmatrix}
\begin{matrix}0&1\end{matrix}&\textbf{0}_{1\times4}\\
\textbf{0}_{2\times2}&C_a
\end{bmatrix}, 
\quad
D_f=\textbf{0}_{3\times3}. 
\]

However the system to be controlled is usually modeled by a discrete state-space model:
\begin{equation}
\label{eqn:full_dynamics_model_disc}
\begin{array}{rr}
{\textbf{x}}_{\text{tot}}(k+1) =A \textbf{x}_{\text{tot}}(k)+ B \textbf{u}_{\text{tot}}(k)\\
\textbf{y}_{\text{tot}}(k) =C\textbf{x}_{\text{tot}}(k) + D \textbf{u}_{\text{tot}}(k)
\end{array}
\end{equation}
where $A$ and $B$ are the state and control matrices for the discrete state-space equation, respectively, which can be calculated, also in this case, with the Euler method as:
\[
A = e^{A_fT_s},\qquad B = \int_{kT_s}^{(k+1)T_s} e^{A_f[(k+1)T_s-\eta]}B_f d\eta
\]
where $T_s$ is the sampling interval for the discrete state-space model. The matrices $C$ and $D$ are equivalent to those in the continuous case.

\subsection{Design of Adaptive Model Predictive Control}
We created an Adaptive MPC controller with a prediction model that has six states, three outputs (longitudinal velocity, lateral deviation, relative yaw angle), and two inputs. The model has two manipulated signals: acceleration and steering. The product of the road curvature and the longitudinal velocity is modeled as a measured disturbance. We have set the constraints for manipulated variables and the scale factors. Moreover we have specified the weights in the standard MPC cost function. The third output, yaw angle, is allowed to float because there are only two manipulated variables to make it a square system. In this controller, there is no steady-state error in the yaw angle as long as the second output, lateral deviation, reaches 0 at steady state. Finally we have also penalized acceleration change more for smooth driving experience. This controller uses a linear model for the vehicle dynamics and updates the model online as the longitudinal velocity varies.

\subsection{Simulation Results}

TO DO

At the start of the simulation, this velocity is equal to the Initial condition for longitudinal velocity parameter. At run time, this velocity is equal to the Longitudinal velocity input signal.

\section{Conclusions and Future Work}
In this work we proposed two advanced methods for the ATLASCAR2 based on adaptive Model Predictive Control. In the first case we analyzed an obstacle avoidance system that moves the vehicle around different moving obstacles in the lane using throttle and steering angle. This system updates both the predictive model and the mixed input/output constraints at each control interval. Instead, in the second scenario  we have developted a lane following system that keeps the ATLASCAR2 travelling along the centerline of the lanes on the road by adjusting the front steering angle of the car. The flexibility of the concepts used in these methods allows a multitude of refinements and extensions to this project. For example the next possible work cuold be to combine the two previous control strategies in a way that they can operate simultaneously. Moreover the final method could be tested in a real autonomous driving scenario.

\begin{thebibliography}{00}
	\bibitem{MMPC}J. Ji, A. Khajepour, W. W. Melek and Y. Huang, "Path Planning and Tracking for Vehicle Collision Avoidance Based on Model Predictive Control With Multiconstraints," in IEEE Transactions on Vehicular Technology, vol. 66, no. 2, pp. 952-964, Feb. 2017.

	\bibitem{onlineMPC}M. Werling and D. Liccardo, "Automatic collision avoidance using model-predictive online optimization," 2012 IEEE 51st IEEE Conference on Decision and Control (CDC), Maui, HI, 2012, pp. 6309-6314.

	\bibitem{swarms}Wei Xi and J. S. Baras, "MPC based motion control of car-like vehicle swarms," 2007 Mediterranean Conference on Control \& Automation, Athens, 2007, pp. 1-6.

	\bibitem{autoMPC}J. V. Frasch et al., "An auto-generated nonlinear MPC algorithm for real-time obstacle avoidance of ground vehicles," 2013 European Control Conference (ECC), Zurich, 2013, pp. 4136-4141.

	\bibitem{safety}T. Xu and H. Yuan, "Autonomous vehicle active safety system based on path planning and predictive control," 2016 35th Chinese Control Conference (CCC), Chengdu, 2016, pp. 8889-8895.

	\bibitem{matsumoto}N. Wada and T. Matsumoto, "Driver assistance for collision avoidance by constrained MPC," 2017 56th Annual Conference of the Society of Instrument and Control Engineers of Japan (SICE), Kanazawa, 2017, pp. 90-93.

	\bibitem{fuzzyMPC}Y. Nishio, K. Nonaka and K. Sekiguchi, "Moving obstacle avoidance control by fuzzy potential method and model predictive control," 2017 11th Asian Control Conference (ASCC), Gold Coast, QLD, 2017, pp. 1298-1303.

	\bibitem{NONMPC}Yu, S., Li, X., Chen, H. and Allgöwer, F. (2015), "Nonlinear model predictive control for path following problems". Int. J. Robust Nonlinear Control, 25: 1168–1182. 
\end{thebibliography}

\end{document}

### 2018-12-13 MATLAB/lane_following/LaneFollowingGetCurvature.m

@@ -14,7 +14,7 @@ Xref = Vx*time;
 % Desired Y position
 z1 = (2.4/50)*(Xref-27.19)-1.2;
 z2 = (2.4/43.9)*(Xref-56.46)-1.2;
-Yref = 5*sin(Xref/(20));%(2.4/50)*(Xref+3).^2 - (2.4/43.9)*(Xref-12).^2; %8.1/2*(1+tanh(z1)) - 11.4/2*(1+tanh(z2));  %z1.^2 - z2.^2;  
+Yref = 5*sin(Xref/(20))+5*cos((Xref)/(20)) ;%(2.4/50)*(Xref+3).^2 - (2.4/43.9)*(Xref-12).^2; %8.1/2*(1+tanh(z1)) - 11.4/2*(1+tanh(z2));  %z1.^2 - z2.^2;  
 
 figure()
 plot(Xref,Yref)

### 2018-12-13 MATLAB/random_N_obstacles/obstacleComputeCustomConstraint.m
update README

@@ -90,10 +90,10 @@ end
 if(obstacle(m).Y(end)<=0)
    E = [0 0;0 0;0 0];
    F = [0 1 0 0;0 -1 0 0;constraintSlope(m) -1 0 0];
-   G = [laneWidth*lanes/2;laneWidth*lanes/2;-1*constraintIntercept(m)];
+   G = [laneWidth*lanes/2+rand;laneWidth*lanes/2+rand;-1*constraintIntercept(m)]
 else
     E = [0 0;0 0;0 0];
     F = [0 1 0 0;0 -1 0 0;-1*constraintSlope(m) 1 0 0];
-    G = [laneWidth*lanes/2;laneWidth*lanes/2;constraintIntercept(m)];
+    G = [laneWidth*lanes/2+rand;laneWidth*lanes/2+rand;constraintIntercept(m)]
 end
 end

### 2018-12-18 Thesis_Latex/Paper/Paper.tex
update Paper References
update MATLAB files and PAPER

@@
 The goal for lane keeping control is to drive both lateral deviation and relative yaw angle close to zero.
+\subsection{Theoretical background - adaptive Model Predictive Control}
+Model Predictive Control is an advanced method that predicts future behavior using a linear-time-invariant (LTI) dynamic model. These predictions are never exact and a good strategy is
+to make MPC insensitive to prediction errors.
+If the plant is strongly nonlinear or its characteristics vary dramatically with time, MPC performance might become unacceptable because LTI prediction accuracy degrade.
+A method that can address this degradation by adapting the prediction model for changing operating conditions is called Adaptive MPC: this control strategy uses a fixed model structure, but allows the models parameters to evolve with time.
+Ideally, whenever the controller requires a prediction, it uses a model appropriate for the current conditions.
+At each control interval, the adaptive MPC controller updates the plant model and nominal conditions.
+Once updated, the model and conditions remain constant over the prediction horizon.
+The plant model used as the basis for the adaptive MPC must be an LTI discrete-time, state-space model with a structure as follows:
+\begin{equation*}
+\label{eqn:Adaptive_MPC_plant_discrete}
+\begin{aligned}
+x(k+1)&=Ax(k)+ B_u u(k)+B_v v(k)+B_d d(k)\\
+y(k)&=Cx(k) + D_v v(k)+ D_d d(k)
+\end{aligned}
+\end{equation*}
+where the matrices $A$, $B_u$, $B_v$, $B_d$, $C$, $D_v$ and $D_d$ can vary with time. The other parameters in the expression are:
+\begin{itemize}
+	\item $k$ is the time index / current control interval;
+	\item $x$ are the plant model states;
+	\item $u$ are the manipulated inputs that can be adjusted by the MPC controller;
+	\item $v$ are the measured disturbance inputs;
+	\item $d$ are the unmeasured disturbance inputs;
+	\item $y$ are the plant outputs, including both measured and unmeasured. Is it necessary at least one measured outuput.
+\end{itemize}
 
-TO DO THEORETICAL BACKGROUND ADAPTIVE MPC
+In the adaptive MPC control there are additional requirements for the plant model as the sample time that has to be constant and identical to the MPC control interval.
+This control strategy prohibits direct feed-through from any manipulated variable to any plant output.
+Thus, $D_u = 0$ in the above model.
+Finally the input and output signal configuration remains constant.
+A traditional MPC controller includes a nominal operating point at which the plant model applies, such as the condition at which you linearize a nonlinear model to obtain the LTI
+approximation.
+In adaptive MPC, as time evolves you should update the nominal operating point to be consistent with the updated plant model.
+It is possible to rewritten the plant model in terms of deviations from the nominal conditions:
+\begin{equation*}
+\label{eqn:Adaptive_MPC_nominal_condition}
+\begin{aligned}
+x(k+1)&=\overline{x}+A(x(k)-\overline{x})+ B(u_t(k)-\overline{u}_t)+\overline{\Delta x}\\
+y(k)&=\overline{y}+C(x(k)-\overline{x}) + D(u_t(k)-\overline{u}_t)
+\end{aligned}
+\end{equation*}
+where the matrices $A$, $B$, $C$ and $D$ that are uptaded. The other parameters in the expression are:
+\begin{itemize}
+	\item $u_t$ is the combined plant input variable, comprising $u$, $v$ and $d$ variables defined above;
+	\item $\overline{x}$ are the nominal states;
+	\item $\overline{\Delta x}$ are the nominal state increments;
+	\item $\overline{u}_t$ are the nominal inputs;
+	\item $\overline{y}$ are the nominal outputs.
+\end{itemize} 
+The adaptive MPC uses a Kalman filter to update its controller states and adjusts the two required gain matrices, $L$ and $M$, at each control interval to maintain consistency with the updated plat model.
+We are considering a linear-time-varying Kalman filter (LTVKF):
+\begin{equation*}
+\label{eqn:LTVKF}
+\begin{array}{lll}
+L_k=\big(A_kP_{k|k-1}C_{m,k}^{T}+N\big)\big(C_{m,k}P_{k|k-1}C_{m,k}^{T}+R\big)^{-1}\\
+M_k =P_{k|k-1}C_{m,k}^{T}\big(C_{m,k}P_{k|k-1}C_{m,k}^{T}+R\big)^{-1}\\
+P_{k+1|k}=A_kP_{k|k-1}A_k^{T}-\big(A_kP_{k|k-1}C_{m,k}^{T}+N\big)L_k^{T}+Q.
+\end{array}
+\end{equation*}
+where 
+\begin{itemize}
+ \item $Q$, $R$ and $N$ are constant covariance matrices defined as in MPC state estimation;
+ \item $A_k$ and $C_{m,k}$ are state-space parameter matrices for the entire controller state;
+ \item $P_{k|k-1}$ is the state estimate error covariance matrix at time $k$ based on the information available at time $k-1$;
+ \item $L_k$ and $M_k$ are the updated Kalmen filter gain matrices.
+\end{itemize}
+The gain and the state error covariance matrix depend upon the model parameters
+and the assumptions leading to the constant $Q$, $R$ and $N$ matrices.
 
@@
 	\item the second constraint is a lower bound on the $y$-coordinate (left boundary of the road);
-	\item the third constraint is for the obstacle avoidance; even though no obstacle is detected at the nominal condition, we must add this fake constraint here because we cannot change the dimensions of the constraint matrices at run time (it has the same form as the second one).ù
+	\item the third constraint is for the obstacle avoidance; even though no obstacle is detected at the nominal condition, we must add this fake constraint here because we cannot change the dimensions of the constraint matrices at run time (it has the same form as the second one).
 \end{itemize}
@@
 \subsection{Simulation Results}
-TO DO
+In this first simulation we assumed that the road is straight and has 3 lanes each of 4 meters wide.
+Moreover the ATLASCAR2 drives in the middle of the center lane when not passing and in this case the vehicle passes an obstacle only from the right lane (the same simulation can be launched so that the car goes over to the left fast lane).
+\begin{figure}[!h]
+	\centering
+	\includegraphics[width=1\columnwidth]{../../MATLAB/one_obstacle_right_overtaking/figure/overtaking_paper/overtaking_start.pdf}
+	\label{fig:obstacleAvoidance_start}
+\end{figure}
+\vspace{-3em}
+\begin{figure}[!h]
+	\centering
+	\includegraphics[width=1\columnwidth]{../../MATLAB/one_obstacle_right_overtaking/figure/overtaking_paper/overtaking_middle.pdf}
+	\label{fig:obstacleAvoidance_middle}
+\end{figure}
+\vspace{-3em}
+\begin{figure}[!h]
+	\centering
+	\includegraphics[width=1\columnwidth]{../../MATLAB/one_obstacle_right_overtaking/figure/overtaking_paper/overtaking_middle_end.pdf}
+	\label{fig:obstacleAvoidance_middle_end}
+\end{figure}
+\vspace{-3em}
+\begin{figure}[!h]
+	\centering
+	\includegraphics[width=1\columnwidth]{../../MATLAB/one_obstacle_right_overtaking/figure/overtaking_paper/overtaking_end.pdf}
+	\label{fig:obstacleAvoidance_end}
+	\vspace{-1.2em}
+	\caption{Simulation of right overtaking with one moving obstacle}
+\end{figure}
+
+Subsequently, additional obstacles were added to make the scenario more complex.
+The vehicle is capable of overcoming the obstacles to the right or left depending on their position with respect to the road.
+We also hypothesized that the obstacles move at a different speed but that they are initially at a common distance.
+In case two obstacles are too close during the simulation and their distance is less than the detection range, the ATLASCAR2 perceives the objects as a single entity and adapts to the situation.
+
+\begin{figure}[!h]
+	\centering
+	\includegraphics[width=1\columnwidth]{../../MATLAB/random_N_obstacles/figure/overtaking_random_2.pdf}
+	\label{fig:obstacleAvoidance_random_2}
+	\vspace{-1.3em}
+\end{figure}
+\begin{figure}[!h]
+	\centering
+	\includegraphics[width=1\columnwidth]{../../MATLAB/random_N_obstacles/figure/overtaking_random.pdf}
+	\label{fig:obstacleAvoidance_random}
+	\vspace{-1.3em}
+\end{figure}
+\begin{figure}[!h]
+	\centering
+	\includegraphics[width=1\columnwidth]{../../MATLAB/random_N_obstacles/figure/overtaking_random_1.pdf}
+	\label{fig:obstacleAvoidance_random_1}
+	\vspace{-1.2em}
+	\caption{Simulations of overtaking with $N = 2,3,4$ moving obstacles}
+\end{figure}
 
@@
 If these two goals cannot be met at the same moment, the system tries to balance them.
-
 The model that we are considering, contains a lot of parameters.
@@
 \subsection{Simulation Results}
+The proposed adaptive MPC algorithm is designed in the MATLAB/Simulink and validated through simulation. The objective of this
+test is to evaluate the behavior of the proposed control strategy in critical situations.
+Fig.\ref{fig:reference_laneFollowing} and Fig.\ref{fig:curvature_laneFollowing} show the desired path that the car must follow and its curvature.
+\begin{figure}[!h]
+	\centering
+	\includegraphics[width=1\columnwidth]{../../MATLAB/lane_following/figure/Reference.pdf}
+	\caption{Desired path of the ATLASCAR2.}
+	\label{fig:reference_laneFollowing}
+\end{figure}
+\begin{figure}[!h]
+	\centering
+	\includegraphics[width=1\columnwidth]{../../MATLAB/lane_following/figure/Curvature.pdf}
+	\caption{Desired curvature.}
+	\label{fig:curvature_laneFollowing}
+\end{figure}
 
-TO DO
+Moreover the following figures show the trend of the main parameters confirming that the control strategy used allows the vehicle to follow the path.
+In particular we simulated also a small error in the sensor dynamics in order to make the simulation more realistic:
 
-At the start of the simulation, this velocity is equal to the Initial condition for longitudinal velocity parameter. At run time, this velocity is equal to the Longitudinal velocity input signal.
+\begin{figure}[!h]
+	\centering
+	\hspace*{-0.5in}
+	\includegraphics[width=1.29\columnwidth]{../../MATLAB/lane_following/figure/AccelerationVsTime.pdf}
+	\caption{Acceleration $u_1$ with respect to time.}
+	\label{fig:acceleration_laneFollowing}
+\end{figure}
+\begin{figure}[!h]
+	\centering
+	\hspace*{-0.5in}
+	\includegraphics[width=1.29\columnwidth]{../../MATLAB/lane_following/figure/SteeringAngleVsTime.pdf}
+	\caption{Steering angle $u_2$ with respect to time.}
+	\label{fig:steering_laneFollowing}
+\end{figure}
+\begin{figure}[!h]
+	\centering
+	\hspace*{-0.5in}
+	\includegraphics[width=1.29\columnwidth]{../../MATLAB/lane_following/figure/RelativeYawAngleVsTime.pdf}
+	\caption{Relative yaw angle $e_2$ with respect to time.}
+	\label{fig:relative_yaw_angle_laneFollowing}
+\end{figure}
+\begin{figure}[!h]
+	\centering
+	\hspace*{-0.5in}
+	\includegraphics[width=1.29\columnwidth]{../../MATLAB/lane_following/figure/LateralDeviationVsTime.pdf}
+	\caption{Lateral deviation $e_1$ with respect to time.}
+	\label{fig:lateral_deviation_laneFollowing}
+\end{figure}
+Fig.{\ref{fig:longitudinal_velocity_laneFollowing}} shows the evolution of the vehicle longitudinal velocity as well as the vehicle sideslip angle throughout the simulation.
+Although the generated speed limit profiles change rapidly with respect to time, yet the vehicle speed increases or decreases gradually but still follows the reference speed closely.
+At the start of the simulation, this velocity is equal to the initial condition for longitudinal velocity parameter.
+At run time, this velocity is equal to the Longitudinal velocity input signal.
+\begin{figure}[!h]
+	\centering
+	\hspace*{-0.5in}
+	\includegraphics[width=1.29\columnwidth]{../../MATLAB/lane_following/figure/LongitudinalVelocityVsTime.pdf}
+	\caption{Longitudinal velocity $V_x$ with respect to time.}
+	\label{fig:longitudinal_velocity_laneFollowing}
+\end{figure}
+
+\begin{figure*}[!h]
+	\centering
+	\includegraphics[width=\textwidth]{./figure/lane_following_AMPC.pdf}
+	\caption{Overall procedure scheme lane following.}
+	\label{fig:scheme_lane_following}
+\end{figure*}
 
@@
 	\bibitem{NONMPC}Yu, S., Li, X., Chen, H. and Allgöwer, F. (2015), "Nonlinear model predictive control for path following problems". Int. J. Robust Nonlinear Control, 25: 1168–1182.
+
+	\bibitem{matPDF}A. Bemporad, M. Morafi, and N. Ricker, Model Predictive Control Toolbox User’s Guide, The MathWorks, Inc.,
+
+		\url{https://www.mathworks.com/help/pdf_doc/mpc/mpc_ug.pdf}
+
+	\bibitem{theory}J. Rawlings, D. Mayne (2010), "Model Predictive Control: Theory and Design", Nob Hill Publishing.	
 \end{thebibliography}

### 2018-12-18 MATLAB/lane_following/LaneFollowingGenerateAMPC.m

@@ -30,7 +30,7 @@ sysd = c2d(sys,Ts);
 mpc1 = mpc(sysd,Ts);
 
 % Specify the prediction horizon.
-mpc1.PredictionHorizon = 10;
+mpc1.PredictionHorizon = 25;
 % Specify MV limits.
 mpc1.MV(1).Min = -3;
 mpc1.MV(1).Max = 3;

### 2018-12-18 MATLAB/lane_following/LaneFollowingGetCurvature.m

@@ -14,9 +14,9 @@ Xref = Vx*time;
 % Desired Y position
 z1 = (2.4/50)*(Xref-27.19)-1.2;
 z2 = (2.4/43.9)*(Xref-56.46)-1.2;
-Yref = 5*sin(Xref/(20))+5*cos((Xref)/(20)) ;%(2.4/50)*(Xref+3).^2 - (2.4/43.9)*(Xref-12).^2; %8.1/2*(1+tanh(z1)) - 11.4/2*(1+tanh(z2));  %z1.^2 - z2.^2;  
+Yref = 5*sin(Xref/(20)) ;%(2.4/50)*(Xref+3).^2 - (2.4/43.9)*(Xref-12).^2; %8.1/2*(1+tanh(z1)) - 11.4/2*(1+tanh(z2));  %z1.^2 - z2.^2;  
 
-figure()
+h = figure ('Position',[100, 100, 340, 230], 'PaperPositionMode','auto');
 plot(Xref,Yref)
 hold on
 grid on
@@ -25,7 +25,10 @@ axis equal
 title('\textbf{Desired Path}','Interpreter','latex');
 xlabel('X-coordinate [m]','Interpreter','latex');
 ylabel('Y-coordinate [m]','Interpreter','latex');
-
+pos = get(h,'Position');
+set(h,'PaperPositionMode','Auto','PaperUnits','Points','PaperSize',[pos(3)*0.8, pos(4)-40])
+print(h,'figure\Reference','-dpdf','-r0')
+hold off
 
 % Desired curvature
 DX = gradient(Xref,0.1);
@@ -36,3 +39,17 @@ curvature = DX.*D2Y./(DX.^2+DY.^2).^(3/2);
 % Stored curvature (as input for LKA)
 rho.time = time;
 rho.signals.values = curvature';
+
+hcurv = figure ('Position',[100, 100, 340, 230], 'PaperPositionMode','auto');
+plot(rho.time,rho.signals.values)
+hold on
+grid on
+grid minor
+title('\textbf{Curvature}','Interpreter','latex');
+xlabel('Time [s]','Interpreter','latex');
+ylabel('Curvature [m]','Interpreter','latex');
+pos = get(hcurv,'Position');
+set(hcurv,'PaperPositionMode','Auto','PaperUnits','Points','PaperSize',[pos(3)*0.8, pos(4)-40])
+print(hcurv,'figure\Curvature','-dpdf','-r0')
+hold off
+hold off

### 2018-12-18 MATLAB/lane_following/LaneFollowingResults.m

@@ -5,10 +5,9 @@ function LaneFollowingResults(logsout)
 
 [e1_ampc,e2_ampc,delta_ampc,accel_ampc,vx_ampc,vy_ampc] = getData(logsout);
 
-%% Plot results. 
-figure; % lateral results
-% steering angle
-subplot(3,1,1);
+%% Steering Angle vs Time
+
+h1 = figure ('Position',[100, 100, 340, 230], 'PaperPositionMode','auto');
 hold on;
 grid on;
 grid minor;
@@ -16,9 +15,14 @@ plot(delta_ampc.Values.time,delta_ampc.Values.Data);
 title('\textbf{Steering Angle (u$_2$) vs Time}','Interpreter','latex');
 xlabel('Time [s]','Interpreter','latex');
 ylabel('Steering angle [rad]','Interpreter','latex');
-hold off;
-% lateral deviation
-subplot(3,1,2);
+pos = get(h1,'Position');
+set(h1,'PaperPositionMode','Auto','PaperUnits','Points','PaperSize',[pos(3), pos(4)-40])
+print(h1,'figure\SteeringAngleVsTime','-dpdf','-r0')
+hold off
+pause(2)
+%% Lateral deviation vs Time
+
+h2 = figure ('Position',[100, 100, 340, 230], 'PaperPositionMode','auto');
 hold on;
 grid on;
 grid minor;
@@ -26,9 +30,14 @@ plot(e1_ampc.Values.time,e1_ampc.Values.Data);
 title('\textbf{Lateral Deviation (e$_1$) vs Time}','Interpreter','latex');
 xlabel('Time [s]','Interpreter','latex');
 ylabel('Lateral Deviation [m]','Interpreter','latex');
-hold off;
-% relative yaw angle
-subplot(3,1,3);
+pos = get(h2,'Position');
+set(h2,'PaperPositionMode','Auto','PaperUnits','Points','PaperSize',[pos(3), pos(4)-41])
+print(h2,'figure\LateralDeviationVsTime','-dpdf','-r0')
+hold off
+pause(2)
+%% Relative Yaw Angle vs Time
+
+h3 = figure ('Position',[100, 100, 340, 230], 'PaperPositionMode','auto');
 hold on;
 grid on;
 grid minor;
@@ -36,11 +45,14 @@ plot(e2_ampc.Values.Time,e2_ampc.Values.Data);
 title('\textbf{Relative Yaw Angle (e$_2$) vs Time}','Interpreter','latex');
[…]

### 2018-12-18 MATLAB/lane_following/main_lane_following.m

@@ -21,7 +21,7 @@ v0 = 15;    % Initial velocity
 v_set = 20; % Driver set velocity
 
 % Set the controller sample time.
-Ts = 0.1;
+Ts = 0.02;
 
 % Obtain the lane curvature information seconds.
 Duration = 20;                              % Simulation duration
@@ -41,3 +41,5 @@ LaneFollowingGenerateAMPC;
 sim(mdl)
 logsout1 = logsout;
 LaneFollowingResults(logsout1)
+print -slane_following_AMPC -dpdf lane_following_AMPC.pdf
+movefile('lane_following_AMPC.pdf','figure')

### 2018-12-18 MATLAB/one_obstacle_right_overtaking/main_one_obstacle_right.m

@@ -187,19 +187,17 @@ mpcverbosity(status);
 %     Y = saveSlope(k)*X + saveIntercept(k);
 %     line(X,Y,'LineStyle','--','Color','g' )
 % end    
-%  plot(ympc(:,1),ympc(:,2),'-b');
+plot(ympc(:,1),ympc(:,2),'-b');
 % axis([0 ympc(end,1) -road.laneWidth*road.lanes/2 road.laneWidth*road.lanes/2]) % reset axis
 
 %% Animation
 % writerObj = VideoWriter('animation.avi');
 % writerObj.FrameRate = 1/Ts; 
 % open(writerObj);
-
-for k = 1:length(saveSlope) 
+for k = 1:length(saveSlope)  
     hold on 
     grid on
     grid minor
-    
     % ATLASCAR2 green rectangle
     p = patch([ympc(k,1)-car.length/2 ympc(k,1)-car.length/2 ympc(k,1)+car.length/2 ympc(k,1)+car.length/2], [ympc(k,2)-car.width/2, ympc(k,2)+car.width/2, ympc(k,2)+car.width/2, ympc(k,2)-car.width/2], [0 1 0]);
     rotate(p, [0 0 1], rad2deg(asin(ympc(k,3))), [ympc(k,1)-car.length/2 ympc(k,2)-car.width/2 0]);
@@ -211,9 +209,9 @@ for k = 1:length(saveSlope)
     safe.EdgeColor='[1 0 0]';
     safe.LineStyle='--';
 
-%     frame = getframe(gcf); 
-%     writeVideo(writerObj, frame);
-    
+     %frame = getframe(gcf); 
+     %writeVideo(writerObj, frame);
+     %%print('figure\overtaking_end','-dpdf','-r0'); 
     pause(80/car.V/length(T))
     delete(p)
     delete(o)
@@ -222,4 +220,5 @@ end
 % hold off
 % close(writerObj);
 close(f);
-
+% print -sMovingObstacleAvoidanceMPC -dpdf MovingObstacleAvoidance.pdf
+% movefile('MovingObstacleAvoidance.pdf','figure')

### 2018-12-18 MATLAB/random_N_obstacles/main_random_N_obstacles.m

@@ -32,7 +32,7 @@ dsys.OutputName = dsys.StateName;        % Output y
 road.lanes = 3;            % The road is straight and has 3 lanes.
 road.laneWidth = 4;        % Each lane is |4| meters wide.
 
-N =randi(6,1,1);          % Random number of obstacles (1,2,3,4,5,6)
+N = randi(6,1,1);          % Random number of obstacles (1,2,3,4,5,6)
 road.length = 150;         % length of the street
 car.minimum_dist=40;       % minimum distance between 2 cars
   
@@ -209,8 +209,8 @@ plot(ympc(:,1),ympc(:,2),'-b');
 
 for k = 1:length(saveSlope) 
     hold on 
-    grid on
-    grid minor
+%     grid on
+%     grid minor
     
     % ATLASCAR2 green rectangle
     p = patch([ympc(k,1)-car.length/2 ympc(k,1)-car.length/2 ympc(k,1)+car.length/2 ympc(k,1)+car.length/2], [ympc(k,2)-car.width/2, ympc(k,2)+car.width/2, ympc(k,2)+car.width/2, ympc(k,2)-car.width/2], [0 1 0]);
@@ -227,7 +227,7 @@ for k = 1:length(saveSlope)
     
 %     frame = getframe(gcf);
 %     writeVideo(writerObj, frame);
-    
+     %print('figure\overtaking_random_2','-dpdf','-r0')
     pause(80/car.V/length(T))
     delete(p)
     for i=1:N

### 2018-12-18 MATLAB/random_N_obstacles/obstacleComputeCustomConstraint.m

@@ -90,10 +90,10 @@ end
 if(obstacle(m).Y(end)<=0)
    E = [0 0;0 0;0 0];
    F = [0 1 0 0;0 -1 0 0;constraintSlope(m) -1 0 0];
-   G = [laneWidth*lanes/2+rand;laneWidth*lanes/2+rand;-1*constraintIntercept(m)]
+   G = [laneWidth*lanes/2+rand;laneWidth*lanes/2+rand;-1*constraintIntercept(m)];
 else
     E = [0 0;0 0;0 0];
     F = [0 1 0 0;0 -1 0 0;-1*constraintSlope(m) 1 0 0];
-    G = [laneWidth*lanes/2+rand;laneWidth*lanes/2+rand;constraintIntercept(m)]
+    G = [laneWidth*lanes/2+rand;laneWidth*lanes/2+rand;constraintIntercept(m)];
 end
 end

### 2018-12-19 Thesis_Latex/Paper/Paper.tex
update MATLAB files and PAPER

@@
 The obstacle can be static, such as a large pothole, or moving, such as a slow-moving vehicle.
-The most common maneuver from the driver is to temporarily move to another lane, drive past the obstacle, and move back to the original lane afterward
+The most common maneuver from the driver is to temporarily move to another lane, drive past the obstacle, and move back to the original lane afterward.
 In this case, we want to design an obstacle avoidance system that moves the ATLASCAR2 around a moving obstacle in the lane using throttle and steering angle.
@@
 	\item $d$ are the unmeasured disturbance inputs;
-	\item $y$ are the plant outputs, including both measured and unmeasured. Is it necessary at least one measured outuput.
+	\item $y$ are the plant outputs, including both measured and unmeasured. Is it necessary at least one measured output.
 \end{itemize}
 
-In the adaptive MPC control there are additional requirements for the plant model as the sample time that has to be constant and identical to the MPC control interval.
+In the adaptive MPC control there are additional requirements for the plant model as the sample time $T_s$ that has to be constant and identical to the MPC control interval.
 This control strategy prohibits direct feed-through from any manipulated variable to any plant output.
@@
 Finally the input and output signal configuration remains constant.
-A traditional MPC controller includes a nominal operating point at which the plant model applies, such as the condition at which you linearize a nonlinear model to obtain the LTI
-approximation.
+A traditional MPC controller includes a nominal operating point at which the plant model applies, such as the condition at which you linearize a nonlinear model to obtain the LTI approximation.
 In adaptive MPC, as time evolves you should update the nominal operating point to be consistent with the updated plant model.
-It is possible to rewritten the plant model in terms of deviations from the nominal conditions:
+It is possible to rewrite the plant model in terms of deviations from the nominal conditions:
 \begin{equation*}
@@
 \end{equation*}
-where the matrices $A$, $B$, $C$ and $D$ that are uptaded. The other parameters in the expression are:
+where the matrices $A$, $B$, $C$ and $D$ are updated with respect to time. The other parameters in the expression are:
 \begin{itemize}
@@
 	\item $\overline{\Delta x}$ are the nominal state increments;
-	\item $\overline{u}_t$ are the nominal inputs;
-	\item $\overline{y}$ are the nominal outputs.
+	\item $\overline{u}_t$ and $\overline{y}$ are the nominal inputs and outputs.
 \end{itemize} 
-The adaptive MPC uses a Kalman filter to update its controller states and adjusts the two required gain matrices, $L$ and $M$, at each control interval to maintain consistency with the updated plat model.
+The adaptive MPC uses a Kalman filter to update its controller states and adjusts the two required gain matrices, $L$ and $M$, at each control interval to maintain consistency with the updated plant model.
 We are considering a linear-time-varying Kalman filter (LTVKF):
@@
 \end{equation*}
-where $C_L$ is the car length. The state equations can be re-written in more compact form as follows:
+where $C_L$ is the car length. The state equations can be re-written in a more compact form as follows:
 \begin{equation}
@@
 \end{equation}
-where the input is the steering angle in radians, and the outputs are the lateral velocity in meters per second and yaw angle rate in radians per second.
+where the input is the steering angle in radians, and the outputs are the lateral velocity in meters per second and yaw angle rate in radians per second:
 \begin{equation*}
@@
 \]
-The parameters that we are considering are the following ones:
+The parameters in the previous matrices are:
 \begin{itemize}
@@
 However the system to be controlled is usually modeled by a discrete state-space model:
-\begin{equation}
+\begin{equation*}
 \label{eqn:full_dynamics_model_disc}
@@
 \end{array}
-\end{equation}
+\end{equation*}
 where $A$ and $B$ are the state and control matrices for the discrete state-space equation, respectively, which can be calculated, also in this case, with the Euler method as:
@@
 Moreover the following figures show the trend of the main parameters confirming that the control strategy used allows the vehicle to follow the path.
-In particular we simulated also a small error in the sensor dynamics in order to make the simulation more realistic:
+In particular we simulated also a small error in the sensor dynamics in order to make the simulation more realistic: we added a 3 percent error to the longitudinal velocity and this is evident from the small noise in the graphs of the steering angle and the lateral deviation.
 
@@
 \end{figure}
-Fig.{\ref{fig:longitudinal_velocity_laneFollowing}} shows the evolution of the vehicle longitudinal velocity as well as the vehicle sideslip angle throughout the simulation.
-Although the generated speed limit profiles change rapidly with respect to time, yet the vehicle speed increases or decreases gradually but still follows the reference speed closely.
+Fig.{\ref{fig:longitudinal_velocity_laneFollowing}} shows the evolution of the vehicle longitudinal velocity.
 At the start of the simulation, this velocity is equal to the initial condition for longitudinal velocity parameter.
 At run time, this velocity is equal to the Longitudinal velocity input signal.
+We can note that $V_x$ reaches the predefined value of $20$ meters for second and then it stabilizes near the cruising speed because it continues to vary the steering angle to adapt to the path to be followed.
 \begin{figure}[!h]
@@
 This system updates both the predictive model and the mixed input/output constraints at each control interval.
-Instead, in the second scenario  we have developted a lane following system that keeps the ATLASCAR2 travelling along the centerline of the lanes on the road by adjusting the front steering angle of the car.
+Instead, in the second scenario  we have developed a lane following system that keeps the ATLASCAR2 traveling along the centerline of the lanes on the road by adjusting the front steering angle of the car.
 The flexibility of the concepts used in these methods allows a multitude of refinements and extensions to this project.
-For example the next possible work cuold be to combine the two previous control strategies in a way that they can operate simultaneously.
+For example the next possible work could be to combine the two previous control strategies in a way that they can operate simultaneously.
 Moreover the final method could be tested in a real autonomous driving scenario.

### 2018-12-20 MATLAB/lane_following_constant_velocity/getCurvature.m
update MATLAB files and PAPER

@@ -1,0 +1,32 @@
+function md = getCurvature(Vx,time)
+% Get previewed curvature from desired X and Y positions for LKA
+%
+% Inputs:
+%   Vx: longitudinal velocity
+%   time: time vector
+%
+% Outputs:
+%   md: previewed curvature
+
+% Desired X position
+Xref = Vx*time;
+
+% Desired Y position
+z1 = (2.4/50)*(Xref-27.19)-1.2;
+z2 = (2.4/43.9)*(Xref-56.46)-1.2;
+Yref = 5*sin(Xref/20);%8.1/2*(1+tanh(z1)) - 11.4/2*(1+tanh(z2));
+figure()
+hold on
+grid on
+grid minor
+plot(Xref,Yref)
+
+% Desired curvature
+DX = gradient(Xref,0.1);
+DY = gradient(Yref,0.1);
+D2Y = gradient(DY,0.1);
+curvature = DX.*D2Y./(DX.^2+DY.^2).^(3/2);
+
+% Stored curvature (as input for LKA)
+md.time = time;
+md.signals.values = curvature';

### 2018-12-20 MATLAB/lane_following_constant_velocity/lane_following_constant_velocity_Results.m

@@ -1,0 +1,51 @@
+function lane_following_constant_velocity_Results(logsout)
+%% Get the data from simulation
+steering_angle = logsout.getElement('steering_angle');
+lateral_deviation = logsout.getElement('lateral_deviation');
+relative_yaw_angle = logsout.getElement('relative_yaw_angle');
+
+%% Lateral deviation vs Time
+
+h1 = figure ('Position',[100, 100, 340, 230], 'PaperPositionMode','auto');
+hold on;
+grid on;
+grid minor;
+plot(lateral_deviation.Values.time,lateral_deviation.Values.Data,'b')
+title('\textbf{Lateral Deviation (e$_1$) vs Time}','Interpreter','latex');
+xlabel('Time [s]','Interpreter','latex');
+ylabel('Lateral Deviation [m]','Interpreter','latex');
+pos = get(h1,'Position');
+set(h1,'PaperPositionMode','Auto','PaperUnits','Points','PaperSize',[pos(3), pos(4)-41])
+print(h1,'figure\LateralDeviationVsTime','-dpdf','-r0')
+hold off
+pause(2)
+
+%% Relative Yaw Angle vs Time
+
+h2 = figure ('Position',[100, 100, 340, 230], 'PaperPositionMode','auto');
+hold on;
+grid on;
+grid minor;
+plot(relative_yaw_angle.Values.time,relative_yaw_angle.Values.Data,'b')
+title('\textbf{Relative Yaw Angle (e$_2$) vs Time}','Interpreter','latex');
+xlabel('Time [s]','Interpreter','latex');
+ylabel('Relative Yaw Angle [rad]','Interpreter','latex');
+pos = get(h2,'Position');
+set(h2,'PaperPositionMode','Auto','PaperUnits','Points','PaperSize',[pos(3), pos(4)-40])
+print(h2,'figure\RelativeYawAngleVsTime','-dpdf','-r0')
+hold off
+pause(2)
+
+%% Steering angle vs Time
+h3 = figure ('Position',[100, 100, 340, 230], 'PaperPositionMode','auto');
+hold on;
+grid on;
+grid minor;
+plot(steering_angle.Values.time,steering_angle.Values.Data,'b')
+title('\textbf{Steering Angle (u$_2$) vs Time}','Interpreter','latex');
+xlabel('Time [s]','Interpreter','latex');
+ylabel('Steering angle [rad]','Interpreter','latex');
[…]

### 2018-12-20 MATLAB/lane_following_constant_velocity/main_lane_following_constant_velocity.m

@@ -1,0 +1,111 @@
+clear all
+close all
+clc
+
+%% Lane Following Using Adaptive Model Predictive Control - Constant Longitudinal Velocity
+mdl = 'lane_following_AMPC_constant_velocity';
+open_system(mdl)
+
+%%
+% Define the sample time, |Ts|, and simulation duration, |T|, in seconds.
+Ts = 0.02;
+Duration = 15;
+
+%%
+% To describe the lateral vehicle dynamics, this example uses a _bicycle
+% model_ with the following parameters:
+%
+% * |m| is the total vehicle mass (kg)
+% * |Iz| is the yaw moment of inertia of the vehicle (mNs^2).
+% * |lf| is the longitudinal distance from the center of gravity to the
+% front tires (m).
+% * |lr| is the longitudinal distance from center of gravity to the rear
+% tires (m).
+% * |Cf| is the cornering stiffness of the front tires (N/rad).
+% * |Cr| is the cornering stiffness of the rear tires (N/rad).
+%
+m = 1575;
+Iz = 2875;
+lf = 1.2;
+lr = 1.6;
+Cf = 19000;
+Cr = 33000;
+
+%%
+% You can represent the lateral vehicle dynamics using a linear
+% time-invariant (LTI) system with the following state, input, and output
+% variables. The initial conditions for the state variables are assumed to
+% be zero.
+%
+% * State variables: Lateral velocity $V_y$ and yaw angle rate $r$
+% * Input variable: Front steering angle $\delta$
+% * Output variables: Same as state variables
+
+%%
+% In this example, the longitudinal vehicle dynamics are separated from the
+% lateral vehicle dynamics. Therefore, the longitudinal velocity is assumed
+% to be constant. In practice, the longitudinal velocity can vary and the
+% Lane Keeping Assist System Block uses adaptive MPC to adjust the model of
+% the lateral dynamics accordingly.
+
+% Specify the longitudinal velocity in m/s.
+Vx = 20;
+
+%%
+% Specify a state-space model, |G(s)|, of the lateral vehicle dynamics.
+A = [-(2*Cf+2*Cr)/m/Vx, -Vx-(2*Cf*lf-2*Cr*lr)/m/Vx;...
+     -(2*Cf*lf-2*Cr*lr)/Iz/Vx, -(2*Cf*lf^2+2*Cr*lr^2)/Iz/Vx];
[…]

### 2018-12-20 MATLAB/lane_following/LaneFollowingGetCurvature.m
update MATLAB files and PAPER

@@ -52,4 +52,3 @@ pos = get(hcurv,'Position');
 set(hcurv,'PaperPositionMode','Auto','PaperUnits','Points','PaperSize',[pos(3)*0.8, pos(4)-40])
 print(hcurv,'figure\Curvature','-dpdf','-r0')
 hold off
-hold off

### 2018-12-20 MATLAB/lane_following_constant_velocity/getCurvature.m

@@ -15,11 +15,20 @@ Xref = Vx*time;
 z1 = (2.4/50)*(Xref-27.19)-1.2;
 z2 = (2.4/43.9)*(Xref-56.46)-1.2;
 Yref = 5*sin(Xref/20);%8.1/2*(1+tanh(z1)) - 11.4/2*(1+tanh(z2));
-figure()
+
+h = figure ('Position',[100, 100, 340, 230], 'PaperPositionMode','auto');
+plot(Xref,Yref)
 hold on
 grid on
 grid minor
-plot(Xref,Yref)
+axis equal
+title('\textbf{Desired Path}','Interpreter','latex');
+xlabel('X-coordinate [m]','Interpreter','latex');
+ylabel('Y-coordinate [m]','Interpreter','latex');
+pos = get(h,'Position');
+set(h,'PaperPositionMode','Auto','PaperUnits','Points','PaperSize',[pos(3)*0.8, pos(4)-40])
+print(h,'figure\Reference','-dpdf','-r0')
+hold off
 
 % Desired curvature
 DX = gradient(Xref,0.1);
@@ -30,3 +39,15 @@ curvature = DX.*D2Y./(DX.^2+DY.^2).^(3/2);
 % Stored curvature (as input for LKA)
 md.time = time;
 md.signals.values = curvature';
+hcurv = figure ('Position',[100, 100, 340, 230], 'PaperPositionMode','auto');
+plot(md.time,md.signals.values)
+hold on
+grid on
+grid minor
+title('\textbf{Curvature}','Interpreter','latex');
+xlabel('Time [s]','Interpreter','latex');
+ylabel('Curvature [m]','Interpreter','latex');
+pos = get(hcurv,'Position');
+set(hcurv,'PaperPositionMode','Auto','PaperUnits','Points','PaperSize',[pos(3)*0.8, pos(4)-40])
+print(hcurv,'figure\Curvature','-dpdf','-r0')
+hold off

### 2018-12-20 MATLAB/lane_following_constant_velocity/lane_following_constant_velocity_Results.m

@@ -10,7 +10,7 @@ h1 = figure ('Position',[100, 100, 340, 230], 'PaperPositionMode','auto');
 hold on;
 grid on;
 grid minor;
-plot(lateral_deviation.Values.time,lateral_deviation.Values.Data,'b')
+plot(lateral_deviation.Values.time,lateral_deviation.Values.Data)
 title('\textbf{Lateral Deviation (e$_1$) vs Time}','Interpreter','latex');
 xlabel('Time [s]','Interpreter','latex');
 ylabel('Lateral Deviation [m]','Interpreter','latex');
@@ -26,7 +26,7 @@ h2 = figure ('Position',[100, 100, 340, 230], 'PaperPositionMode','auto');
 hold on;
 grid on;
 grid minor;
-plot(relative_yaw_angle.Values.time,relative_yaw_angle.Values.Data,'b')
+plot(relative_yaw_angle.Values.time,relative_yaw_angle.Values.Data)
 title('\textbf{Relative Yaw Angle (e$_2$) vs Time}','Interpreter','latex');
 xlabel('Time [s]','Interpreter','latex');
 ylabel('Relative Yaw Angle [rad]','Interpreter','latex');
@@ -41,7 +41,7 @@ h3 = figure ('Position',[100, 100, 340, 230], 'PaperPositionMode','auto');
 hold on;
 grid on;
 grid minor;
-plot(steering_angle.Values.time,steering_angle.Values.Data,'b')
+plot(steering_angle.Values.time,steering_angle.Values.Data)
 title('\textbf{Steering Angle (u$_2$) vs Time}','Interpreter','latex');
 xlabel('Time [s]','Interpreter','latex');
 ylabel('Steering angle [rad]','Interpreter','latex');

### 2019-01-09 Thesis_Latex/Paper/Paper.tex
update MATLAB files and PAPER

@@
 
-\title{Advanced Methods for Autonomous Driving based on Adaptive Model Predictive Control}
+\title{Advanced Methods for short-term Path Planning in Autonomous Driving based on Adaptive MPC}
 \author{\IEEEauthorblockN{Alberto Franco}\\
@@
 \begin{abstract}
-	In this paper we present two different strategies for a self-driving car.
+	In this paper we present two different strategies for a self-driving car short-term path planning.
 The aim of this project is to study and implement a path tracking framework in order to prevent ATLASCAR2 collision with moving obstacle vehicles.
@@
 \section{Context of the Problem and \\  Proposed Solution}
-The ATLACAR2 has a sensor, such as lidar, that measures the distance to an obstacle in front of the vehicle and in the same lane.
-The obstacle can be static, such as a large pothole, or moving, such as a slow-moving vehicle.
+The ATLACAR2 has sensors, such as lidar, that measure the distance to obstacles in front and around the vehicle.
+The obstacles can be static, such as a large pothole, or moving, such as a slow-moving vehicle.
 The most common maneuver from the driver is to temporarily move to another lane, drive past the obstacle, and move back to the original lane afterward.
@@
 This system uses an adaptive Model Predictive Controller that updates both the predictive model and the mixed input/output constraints at each control interval.
-Moreover this vehicle is also
-equipped with a lane-keeping assist system: it has a sensor, such as camera, that measures the lateral deviation and relative yaw angle between the centerline of a lane and the ATLASCAR2.
+Moreover, this vehicle is also equipped with a lane-keeping assist system: it has a sensor, such as camera, that measures the lateral deviation and relative yaw angle between the centerline of a lane and the ATLASCAR2.
 The sensor also measures the current lane curvature and curvature derivative.
@@
 \subsection{Theoretical background - adaptive Model Predictive Control}
-Model Predictive Control is an advanced method that predicts future behavior using a linear-time-invariant (LTI) dynamic model. These predictions are never exact and a good strategy is
-to make MPC insensitive to prediction errors.
+Model Predictive Control is an advanced method that predicts future behavior using a linear-time-invariant (LTI) dynamic model.
+These predictions are never exact and a good strategy is to make MPC insensitive to prediction errors.
 If the plant is strongly nonlinear or its characteristics vary dramatically with time, MPC performance might become unacceptable because LTI prediction accuracy degrade.
-A method that can address this degradation by adapting the prediction model for changing operating conditions is called Adaptive MPC: this control strategy uses a fixed model structure, but allows the models parameters to evolve with time.
+A method that can address this degradation by adapting the prediction model for changing operating conditions is called Adaptive MPC: this control strategy uses a fixed model structure, but allows the model parameters to evolve with time.
 Ideally, whenever the controller requires a prediction, it uses a model appropriate for the current conditions.
@@
 	\centering
-	\includegraphics[width=1\columnwidth]{./figure/obstacleAvoidance.pdf}
+	\includegraphics[width=1\columnwidth]{./figure/obstacleAvoidance/obstacleAvoidance.pdf}
 	\caption{Problem description of collision avoidance on road.}
@@
 
-The simple non-linear model to describe the dynamics of the ATLASCAR2 is the following
+The simple non-linear model to describe the dynamics of the ATLASCAR2 is derived combining the equations in [2] and [3]:
 \begin{equation*}
@@
 For simplicity, we assume that all the states are measurable and the ATLASCAR2 drives east with a constant speed at the nominal operating point.
-In the scenario we are going to consider, the road is straight and our vehicle stays in the middle of the center lane when not passing.
+In the scenario that we are going to consider, the road is straight and our vehicle stays in the middle of the center lane when not passing.
 Without losing generality, the ATLASCAR2 passes an obstacle both to the right and to the left lane depending on where it is placed on the road.
-We create also a safe zone around the obstacles so that the vehicle does not get too close the osbtacle when passing it.
+We create also a safe zone around the obstacles so that the vehicle does not get too close to the osbtacle when passing it.
 
@@
 We designed a model predictive controller that can make the ATLASCAR2 mantain a desired velocity and stay in the middle of center lane.
-We used an Adaptive MPC controller because it handles the nonlinear vehicle dynamics more effectively than a traditional MPC controller in fact the latter uses a constant plant model, however, the former allows us to provide a new plant model at each control interval.
+We used an Adaptive MPC controller because it handles the nonlinear vehicle dynamics more effectively than a traditional MPC controller; in fact, the latter uses a constant plant model but the former allows us to provide a new plant model at each control interval.
 Because the new model describes the plant dynamics more accurately at the new operating condition, an adaptive MPC controller performs better than a traditional MPC controller.
@@
 	\centering
-	\includegraphics[width=1\columnwidth]{./figure/laneFollowing.pdf}
+	\includegraphics[width=0.75\columnwidth]{./figure/laneFollowing/laneFollowing.pdf}
 	\caption{Problem description of a lane following system.}
@@
 \subsubsection{Longitudinal dynamics}
+We can use the following state space to describe the longitudinal model:
 \begin{equation}
-	\label{eqn:longi_dynamics_simple_model}
-	G(s)=\frac{1}{\tau s^2+s} \quad \text{where $\tau$ is a time constant}
+\label{eqn:longi_dynamics_simple_model_ss}
+\begin{array}{ll}
+\dot{\textbf{x}}_{\text{lon}} =A_m \textbf{x}_{\text{lon}}+ B_m\textbf{u}_{\text{lon}}\\
+\textbf{y}_{\text{lon}} =C_m \textbf{x}_{\text{lon}} + D_m \textbf{u}_{\text{lon}}
+\end{array}
 \end{equation}
-
+where the input is the acceleration and the states are the longitudinal velocity and the actual acceleration which is also the only output of this system.
+\begin{equation*}
+\textbf{x}_{\text{lon}} = \begin{bmatrix}
+\dot{V}_x&V_x
+\end{bmatrix}^T,
+\qquad
+\textbf{u}_{\text{lon}} = a
+\end{equation*}
+and
+\[ 
+A_g=\begin{bmatrix}
+-\frac{1}{\tau}&0\\1&0
+\end{bmatrix},
+\quad
+B_g=\begin{bmatrix}
+\frac{1}{\tau}\\
+0
+\end{bmatrix},
+\]
+\[
+C_g=\begin{bmatrix}
+1&0
+\end{bmatrix}, 
+\quad
+D_g=0.
+\]
+where $\tau$ is a time constant; in practice we are considering a second order transfer function like in [5].
 \subsubsection{Lateral dynamics}
-Local function: we have a continuous vehicle lateral model from parameters
+Local function: we have a continuous vehicle lateral model from parameters obtained by simplifying the one in [7]: 
 \begin{equation}
@@
 \]
-Combining (\ref{eqn:longi_dynamics_simple_model}) with (\ref{eqn:lateral_dynamics_augmented_model}) yields the state-space model that characterizes the model predictive controller:
+Combining (\ref{eqn:longi_dynamics_simple_model_ss}) with (\ref{eqn:lateral_dynamics_augmented_model}) yields the state-space model that characterizes the model predictive controller:
 \begin{equation}
@@
 \textbf{x}_{\text{tot}} = \begin{bmatrix}
-V_x\\\dot{V}_x\\V_y\\\dot{\psi}\\e_1\\e_2
+\dot{V}_x\\V_x\\V_y\\\dot{\psi}\\e_1\\e_2
 \end{bmatrix},
@@
 A_f=\begin{bmatrix}
-\begin{matrix}-2&0\\1&0\end{matrix}&\textbf{0}_{2\times4}\\
+A_m&\textbf{0}_{2\times4}\\
 \textbf{0}_{4\times2}&A_a
@@
 \quad
-B_f=\begin{bmatrix}\begin{matrix}2\\0\end{matrix}&\textbf{0}_{2\times2}\\
+B_f=\begin{bmatrix}
+B_m&\textbf{0}_{2\times2}\\
 \textbf{0}_{4\times1}&B_a
@@
 C_f=\begin{bmatrix}
-\begin{matrix}0&1\end{matrix}&\textbf{0}_{1\times4}\\
+C_m&\textbf{0}_{1\times4}\\
 \textbf{0}_{2\times2}&C_a
@@
 
+	\bibitem{long_tf}Y. Wang, Y. Bin and K. Li, "Longitudinal acceleration tracking control of low speed heavy-duty vehicles," in Tsinghua Science and Technology, vol. 13, no. 5, pp. 636-643, Oct. 2008.
+
 	\bibitem{safety}T. Xu and H. Yuan, "Autonomous vehicle active safety system based on path planning and predictive control," 2016 35th Chinese Control Conference (CCC), Chengdu, 2016, pp. 8889-8895.
@@
 90-93.
+
+	\bibitem{rathai}Murali Madhavan Rathai, Karthik \& Amirthalingam, Jegan \& Jayaraman, Balaji. (2017). Robust tube-MPC based lane keeping system for autonomous driving vehicles. 1-6.
 

### 2019-01-09 MATLAB/lane_following/LaneFollowingGetCurvature.m

@@ -8,13 +8,20 @@ function rho = LaneFollowingGetCurvature(Vx,time)
 % Outputs:
 %   rho: previewed curvature
 
-% Desired X position
-Xref = Vx*time;
+%Xref=22*cos(Vx*time/60);
+%Yref=20*sin(Vx*time/60);
 
+% Desired X position
+
+Xref = Vx*time;
+%Xref=200*cos(Vx*time/60);
+%Yref=100*sin(Vx*time/60);
 % Desired Y position
 z1 = (2.4/50)*(Xref-27.19)-1.2;
 z2 = (2.4/43.9)*(Xref-56.46)-1.2;
-Yref = 5*sin(Xref/(20)) ;%(2.4/50)*(Xref+3).^2 - (2.4/43.9)*(Xref-12).^2; %8.1/2*(1+tanh(z1)) - 11.4/2*(1+tanh(z2));  %z1.^2 - z2.^2;  
+Yref = 5*sin(Xref/(20)); % Correct reference sinusoidal
+%Yref = (2.4/50)*(Xref+3).^2 - (2.4/43.9)*(Xref-12).^2; % Path Parabola
+%Yref = 8.1/2*(1+tanh(z1)) - 11.4/2*(1+tanh(z2)); % Avoid One obstacle
 
 h = figure ('Position',[100, 100, 340, 230], 'PaperPositionMode','auto');
 plot(Xref,Yref)

### 2019-01-09 MATLAB/lane_following/LaneFollowingGetModelForAMPC.m

@@ -26,6 +26,7 @@ function [A,B,C,D] = LaneFollowingGetModelForAMPC(Ts,Vx,Ag,Bg,Cg)
 %   specified, then the model Gf need to be discretized as well. 
 
 
+
 % Lateral model.
 [A2,B2] = getFullModel(Ag,Bg,Cg,Vx);
 n = size(Bg,1); % number of states for vehicle model                                              

### 2019-01-09 MATLAB/lane_following_circular_path/LaneFollowingGenerateAMPC.m

@@ -1,0 +1,93 @@
+
+% This is the script to design an adaptive MPCcontroller for lane following. 
+% MPC controller has the following structure:
+% 
+%   MV: acceleration and steering
+%   DV: curvature (with look-ahead)
+%   OV: longitudinal velocity, lateral deviation and relative yaw angle
+status = mpcverbosity('off');
+
+%% Longitudinal dynamics
+sys_longitudinal = ss(tf(1,[tau,1,0]));
+
+%% Lateral dynamics
+[Ag,Bg,Cg] = getVehModelFromParam(m,Iz,lf,lr,Cf,Cr,v0);
+% Constants
+n = size(Bg,1); % number of states for vehicle model                                              
+C = [zeros(2,n),eye(2)];
+D = zeros(2);
+% Augement the vehicle model into the MPC internal model
+[A,B] = getFullModel(Ag,Bg,Cg,v0);
+sys_lateral = ss(A,B,C,D);
+
+%% MPC internal model
+sys = [sys_longitudinal,zeros(1,2);zeros(2,1),sys_lateral];
+sys = minreal(sys);
+
+%% MPC design 
+sys = setmpcsignals(sys,'MV',[1,2],'MD',3); % acceleration, steering and desired yaw rate
+sysd = c2d(sys,Ts);
+mpc1 = mpc(sysd,Ts);
+
+% Specify the prediction horizon.
+mpc1.PredictionHorizon = 25;
+% Specify MV limits.
+mpc1.MV(1).Min = -3;
+mpc1.MV(1).Max = 3;
+mpc1.MV(2).Min = -1.13;
+mpc1.MV(2).Max = 1.13;
+% Specify nominal values.
+mpc1.Model.Nominal.Y(1) = v0; 
+mpc1.OV(1).ScaleFactor = 15;   % Typical value of longitudinal velocity
+mpc1.OV(2).ScaleFactor = 0.5;  % Range for lateral deviation
+mpc1.OV(3).ScaleFactor = 0.5;  % Range for relative yaw angle
+mpc1.MV(1).ScaleFactor = 6; % Range of steering angle
+mpc1.MV(2).ScaleFactor = 2.26;    % Range of acceleration
+mpc1.DV.ScaleFactor = 0.2;     % Range of Curvature
+% Specify weights.
[…]

### 2019-01-09 MATLAB/lane_following_circular_path/LaneFollowingGetCurvature.m

@@ -1,0 +1,54 @@
+function rho = LaneFollowingGetCurvature(Vx,time)
+% Get previewed curvature from desired X and Y positions for LKA
+%
+% Inputs:
+%   Vx: longitudinal velocity
+%   time: time vector
+%
+% Outputs:
+%   rho: previewed curvature
+
+Xref=200*cos(Vx*time/60);
+Yref=200*sin(Vx*time/60);
+% Xref = Vx*time;
+% 
+% % Desired Y position
+% z1 = (2.4/50)*(Xref-27.19)-1.2;
+% z2 = (2.4/43.9)*(Xref-56.46)-1.2;
+% Yref = 8.1/2*(1+tanh(z1)) - 11.4/2*(1+tanh(z2));
+h = figure ('Position',[100, 100, 340, 230], 'PaperPositionMode','auto');
+plot(Xref,Yref)
+hold on
+grid on
+grid minor
+axis equal
+title('\textbf{Desired Path}','Interpreter','latex');
+xlabel('X-coordinate [m]','Interpreter','latex');
+ylabel('Y-coordinate [m]','Interpreter','latex');
+pos = get(h,'Position');
+set(h,'PaperPositionMode','Auto','PaperUnits','Points','PaperSize',[pos(3)*0.8, pos(4)-40])
+print(h,'figure\Reference_circular','-dpdf','-r0')
+hold off
+
+% Desired curvature
+DX = gradient(Xref,0.1);
+DY = gradient(Yref,0.1);
+D2Y = gradient(DY,0.1);
+curvature = DX.*D2Y./(DX.^2+DY.^2).^(3/2);
+
+% Stored curvature (as input for LKA)
+rho.time = time;
+rho.signals.values = curvature';
+
+hcurv = figure ('Position',[100, 100, 340, 230], 'PaperPositionMode','auto');
+plot(rho.time,rho.signals.values)
+hold on
+grid on
+grid minor
+title('\textbf{Curvature}','Interpreter','latex');
+xlabel('Time [s]','Interpreter','latex');
+ylabel('Curvature [m]','Interpreter','latex');
+pos = get(hcurv,'Position');
+set(hcurv,'PaperPositionMode','Auto','PaperUnits','Points','PaperSize',[pos(3)*0.8, pos(4)-40])
+print(hcurv,'figure\Curvature_circular','-dpdf','-r0')
+hold off

### 2019-01-09 MATLAB/lane_following_circular_path/LaneFollowingGetModelForAMPC.m

@@ -1,0 +1,85 @@
+function [A,B,C,D] = LaneFollowingGetModelForAMPC(Ts,Vx,Ag,Bg,Cg)
+
+% Get discrete state-space model for Adaptive MPC. 
+
+% Inputs:
+%   Ts:                mask variable for sample time
+%   Vx:                mask inport for longitudinal velocity
+%   Ag,Bg,Cg:          continuous or discrete vehicle model with sample time Ts        
+% Outputs:
+%   A,B,C,D:           discrete time model for MPC
+
+% Get full model for MPC
+%   Vehicle model (continuous or discrete) with input delta (steering
+%   angle) and outputs [vy,phidot] (lateral velocity and yaw angle rate).
+%
+%   The first step is to get model Gp from input [delta,phidotdes] to
+%   [vy,phidot,phidotdes] with the desired yaw angle rate phidotdes.
+%
+%   The second step is to get continuous model Ge from
+%   [vy,phidot,phidotdes] to [e1,e2] (lateral error and yaw angle error).
+%   If a discrete-time vehicle model is specified, then Ge must be
+%   discretized as well.
+%
+%   The overall model Gf is the series connection of Gp and Ge, from input
+%   [delta,phidotdes] to output [e1,e2]. If continuous-time vehicle is
+%   specified, then the model Gf need to be discretized as well. 
+
+
+
+% Lateral model.
+[A2,B2] = getFullModel(Ag,Bg,Cg,Vx);
+n = size(Bg,1); % number of states for vehicle model                                              
+C2 = [zeros(2,n),eye(2)];
+
+% Longitudinal model.
+A1 = [-2,0;1,0]; 
+B1 = [2;0]; 
+C1 = [0,1];
+
+% Combined model.
+Af = [A1,zeros(2,n+2);zeros(n+2,2),A2];
+Bf = [B1,zeros(2);zeros(4,1),B2];
+C = [C1,zeros(1,4);zeros(2),C2];
+D = zeros(3);
+
+% Convert continuous to discrete time
+[A, B] = getDiscrete(Af, Bf, Ts); 
+
+
+%% Local function: Augement the vehicle model into the MPC internal model
+function [Af,Bf] = getFullModel(Ag,Bg,Cg,Vx)
[…]

### 2019-01-09 MATLAB/lane_following_circular_path/LaneFollowingResults.m

@@ -1,0 +1,89 @@
+function LaneFollowingResults(logsout)
+% Plot results for adaptive MPC. 
+
+%% Get the data from simulation
+
+[e1_ampc,e2_ampc,delta_ampc,accel_ampc,vx_ampc,vy_ampc] = getData(logsout);
+
+%% Steering Angle vs Time
+
+h1 = figure ('Position',[100, 100, 340, 230], 'PaperPositionMode','auto');
+hold on;
+grid on;
+grid minor;
+plot(delta_ampc.Values.time,delta_ampc.Values.Data);
+title('\textbf{Steering Angle (u$_2$) vs Time}','Interpreter','latex');
+xlabel('Time [s]','Interpreter','latex');
+ylabel('Steering angle [rad]','Interpreter','latex');
+pos = get(h1,'Position');
+set(h1,'PaperPositionMode','Auto','PaperUnits','Points','PaperSize',[pos(3), pos(4)-40])
+print(h1,'figure\SteeringAngleVsTime_circular','-dpdf','-r0')
+hold off
+pause(2)
+%% Lateral deviation vs Time
+
+h2 = figure ('Position',[100, 100, 340, 230], 'PaperPositionMode','auto');
+hold on;
+grid on;
+grid minor;
+plot(e1_ampc.Values.time,e1_ampc.Values.Data);
+title('\textbf{Lateral Deviation (e$_1$) vs Time}','Interpreter','latex');
+xlabel('Time [s]','Interpreter','latex');
+ylabel('Lateral Deviation [m]','Interpreter','latex');
+pos = get(h2,'Position');
+set(h2,'PaperPositionMode','Auto','PaperUnits','Points','PaperSize',[pos(3), pos(4)-41])
+print(h2,'figure\LateralDeviationVsTime_circular','-dpdf','-r0')
+hold off
+pause(2)
+%% Relative Yaw Angle vs Time
+
+h3 = figure ('Position',[100, 100, 340, 230], 'PaperPositionMode','auto');
+hold on;
+grid on;
+grid minor;
+plot(e2_ampc.Values.Time,e2_ampc.Values.Data);
+title('\textbf{Relative Yaw Angle (e$_2$) vs Time}','Interpreter','latex');
+xlabel('Time [s]','Interpreter','latex');
+ylabel('Relative Yaw Angle [rad]','Interpreter','latex');
+pos = get(h3,'Position');
+set(h3,'PaperPositionMode','Auto','PaperUnits','Points','PaperSize',[pos(3), pos(4)-40])
[…]

### 2019-01-09 MATLAB/lane_following_curve/LaneFollowingGetCurvature.m

@@ -1,0 +1,52 @@
+function rho = LaneFollowingGetCurvature(Vx,time)
+% Get previewed curvature from desired X and Y positions for LKA
+%
+% Inputs:
+%   Vx: longitudinal velocity
+%   time: time vector
+%
+% Outputs:
+%   rho: previewed curvature
+
+Xref = Vx*time;
+
+% % Desired Y position
+z1 = (2.4/50)*(Xref-27.19)-1.2;
+z2 = (2.4/43.9)*(Xref-56.46)-1.2;
+Yref = 8.1/2*(1+tanh(z1)) - 8.4/2*(1+tanh(z2))
+h = figure ('Position',[100, 100, 340, 230], 'PaperPositionMode','auto');
+plot(Xref,Yref)
+hold on
+grid on
+grid minor
+axis equal
+title('\textbf{Desired Path}','Interpreter','latex');
+xlabel('X-coordinate [m]','Interpreter','latex');
+ylabel('Y-coordinate [m]','Interpreter','latex');
+pos = get(h,'Position');
+set(h,'PaperPositionMode','Auto','PaperUnits','Points','PaperSize',[pos(3)*0.8, pos(4)-40])
+print(h,'figure\Reference_curve','-dpdf','-r0')
+hold off
+
+% Desired curvature
+DX = gradient(Xref,0.1);
+DY = gradient(Yref,0.1);
+D2Y = gradient(DY,0.1);
+curvature = DX.*D2Y./(DX.^2+DY.^2).^(3/2);
+
+% Stored curvature (as input for LKA)
+rho.time = time;
+rho.signals.values = curvature';
+
+hcurv = figure ('Position',[100, 100, 340, 230], 'PaperPositionMode','auto');
+plot(rho.time,rho.signals.values)
+hold on
+grid on
+grid minor
+title('\textbf{Curvature}','Interpreter','latex');
+xlabel('Time [s]','Interpreter','latex');
+ylabel('Curvature [m]','Interpreter','latex');
+pos = get(hcurv,'Position');
+set(hcurv,'PaperPositionMode','Auto','PaperUnits','Points','PaperSize',[pos(3)*0.8, pos(4)-40])
+print(hcurv,'figure\Curvature_curve','-dpdf','-r0')
+hold off

### 2019-01-09 MATLAB/lane_following_curve/LaneFollowingResults.m

@@ -1,0 +1,89 @@
+function LaneFollowingResults(logsout)
+% Plot results for adaptive MPC. 
+
+%% Get the data from simulation
+
+[e1_ampc,e2_ampc,delta_ampc,accel_ampc,vx_ampc,vy_ampc] = getData(logsout);
+
+%% Steering Angle vs Time
+
+h1 = figure ('Position',[100, 100, 340, 230], 'PaperPositionMode','auto');
+hold on;
+grid on;
+grid minor;
+plot(delta_ampc.Values.time,delta_ampc.Values.Data);
+title('\textbf{Steering Angle (u$_2$) vs Time}','Interpreter','latex');
+xlabel('Time [s]','Interpreter','latex');
+ylabel('Steering angle [rad]','Interpreter','latex');
+pos = get(h1,'Position');
+set(h1,'PaperPositionMode','Auto','PaperUnits','Points','PaperSize',[pos(3), pos(4)-40])
+print(h1,'figure\SteeringAngleVsTime_curve','-dpdf','-r0')
+hold off
+pause(2)
+%% Lateral deviation vs Time
+
+h2 = figure ('Position',[100, 100, 340, 230], 'PaperPositionMode','auto');
+hold on;
+grid on;
+grid minor;
+plot(e1_ampc.Values.time,e1_ampc.Values.Data);
+title('\textbf{Lateral Deviation (e$_1$) vs Time}','Interpreter','latex');
+xlabel('Time [s]','Interpreter','latex');
+ylabel('Lateral Deviation [m]','Interpreter','latex');
+pos = get(h2,'Position');
+set(h2,'PaperPositionMode','Auto','PaperUnits','Points','PaperSize',[pos(3), pos(4)-41])
+print(h2,'figure\LateralDeviationVsTime_curve','-dpdf','-r0')
+hold off
+pause(2)
+%% Relative Yaw Angle vs Time
+
+h3 = figure ('Position',[100, 100, 340, 230], 'PaperPositionMode','auto');
+hold on;
+grid on;
+grid minor;
+plot(e2_ampc.Values.Time,e2_ampc.Values.Data);
+title('\textbf{Relative Yaw Angle (e$_2$) vs Time}','Interpreter','latex');
+xlabel('Time [s]','Interpreter','latex');
+ylabel('Relative Yaw Angle [rad]','Interpreter','latex');
+pos = get(h3,'Position');
+set(h3,'PaperPositionMode','Auto','PaperUnits','Points','PaperSize',[pos(3), pos(4)-40])
[…]

### 2019-01-09 MATLAB/lane_following_curve/main_lane_following_curve.m

@@ -1,0 +1,45 @@
+clear all
+close all
+clc
+
+%% Lane Following Using Adaptive Model Predictive Control
+mdl = 'lane_following_AMPC';
+open_system(mdl)
+
+% Parameters of Vehicle Dynamics and Road Curvature. 
+% Specify the vehicle dynamics parameters
+m = 1575;   % Mass of ATLASCAR2
+Iz = 2875;  % Moment of inertia about Z axis
+lf = 1.2;   % Distance between Center of Gravity and Front axle 
+lr = 1.6;   % Distance between Center of Gravity and Rear axle
+Cf = 19000; % Cornering stiffness of the front tires (N/rad)
+Cr = 33000; % Cornering stiffness of the rear tires (N/rad).
+tau = 0.2;  % Time constant
+
+% Set the initial and driver-set velocities.
+v0 = 15;    % Initial velocity
+v_set = 20; % Driver set velocity
+
+% Set the controller sample time.
+Ts = 0.02;
+
+% Obtain the lane curvature information seconds.
+Duration = 20;                              % Simulation duration
+t = 0:Ts:Duration;                          % Time vector
+rho = LaneFollowingGetCurvature(v_set,t);   % Signal containing curvature information
+
+%% Design Adaptive Model Predictive Controller 
+% This controller uses a linear model for the vehicle dynamics and updates
+% the model online as the longitudinal velocity varies. The adaptive MPC
+% controller is designed in |LaneFollowingGenerateAMPC| and the model is
+% updated using |LaneFollowingGetModelForAMPC|.
+LaneFollowingGenerateAMPC;
+
+%% Simulation
+% Simulate the model using adaptive MPC and plot the results using the 
+% function |LaneFollowingResults|
+sim(mdl)
+logsout1 = logsout;
+LaneFollowingResults(logsout1)
+print -slane_following_AMPC -dpdf lane_following_AMPC.pdf
+movefile('lane_following_AMPC.pdf','figure')

### 2019-01-09 MATLAB/path_planning/goalfunction.m

@@ -1,0 +1,10 @@
+% Gaol function:
+% Author: K. Passino, Version: 1/25/01
+function Jg=goalfunction(x,xgoal,w2)
+
+% An example gaol function:
+
+	Jg=w2*(x-xgoal)'*(x-xgoal);
+%	Jg=0.01*(x-xgoal)'*(x-xgoal)/(1-0.01*(x-xgoal)'*(x-xgoal));
+	
+

### 2019-01-09 MATLAB/path_planning/main.m

@@ -1,0 +1,224 @@
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%   Vehicle guidance for obstacle avoidance example
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%   Kevin Passino
+%   Version: 1/25/01
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+clear                % Initialize memory
+
+xmin=[0; 0];         % Set edges of region want to search in
+xmax=[30;30];
+
+Nsteps=500;            % Maximum number of steps to produce
+
+% Next set the parameters of the vehicle:
+
+lambda=0.1;  % Step size to take in chosen direction at each move
+Ns=16;        % Number of points on circular pattern to sense
+r=1;          % Sensing radius
+xs=0*ones(2,Ns); % Initialize
+Jo(:,1)=0*ones(Ns,1);
+Jg(:,1)=0*ones(Ns,1);
+J(:,1)=0*ones(Ns,1);
+theta(:,1)=0*ones(Ns,1);
+for m=2:Ns  % Compute the angles to be used around the circle
+	theta(m,1)=theta(m-1,1)+(pi/180)*(360/Ns); 
+end
+
+% Goal position of vehicle
+xgoal=[25; 25];
+
+% Initial vehicle position
+x=[5; 5];
+
+% Weighting parameters for planning (sets priority for being aggresive
+% in the direction of the goal vs. avoiding obstacles
+w1=1;
+w2=1.0000e-04;
+
+% Allocate memory 
+
+x(:,2:Nsteps)=0*ones(2,Nsteps-1);
+
+% The obstacles:
+
+figure(1)
+clf
+% Plot initial and final positions
+plot(5,5,'s',25,25,'x')
+axis([0 30 0 30])
+hold on
+xlabel('x');
+ylabel('y');
+title('Obstacles (o), initial vehicle (square) and goal (x) positions');
+hold on
+% Plot obstacle positions (sets obstaclefunction)
[…]

### 2019-01-09 MATLAB/path_planning/obstaclefunction.m

@@ -1,0 +1,13 @@
+% Obstacle function:
+% Author: K. Passino, Version: 1/25/01
+function J=obstaclefunction(x,w1)
+
+% An example function to represent sensed obstacles:
+
+	J=...
+		w1*max([exp(-0.8*((x(1,1)-20)^2+(x(2,1)-15)^2)),...
+		exp(-0.8*((x(1,1)-8)^2+(x(2,1)-10)^2)),...
+		exp(-0.8*((x(1,1)-10)^2+(x(2,1)-10)^2)),...
+		exp(-0.8*((x(1,1)-12)^2+(x(2,1)-10)^2)),...
+		exp(-0.8*((x(1,1)-24)^2+(x(2,1)-20)^2)),...
+		exp(-0.8*((x(1,1)-18)^2+(x(2,1)-20)^2))]);

### 2019-01-24 Thesis_Latex/Thesis/Abstract/Abstract.tex
update Matlab files

\chapter*{Abstract}
\thispagestyle{empty}
abstact

### 2019-01-24 Thesis_Latex/Thesis/Acknowledgements/Acknowledgements.tex
update Matlab files

\chapter*{Acknowledgements}
\thispagestyle{empty}
Eventuali ringraziamenti personali.

### 2019-01-24 Thesis_Latex/Thesis/Bibliography/Bibliography.tex
update Matlab files

\bibliographystyle{IEEEtran}
%\bibliography{IEEEabrv,./7-Bibliografia/Biblio}

%Control tutorial for MATLAB e Simulink, sito web dedicato all'analisi e
%alla sintesi di alcuni sistemi di controllo, ctms.engin.umich.edu/

\begin{thebibliography}{9} 
\bibitem{uno} M. Bisiacco, M. E. Valcher, \textit{Controlli automatici}, Ed. Libreria Progetto, Padova, 2008
\bibitem{due} \textit{Control tutorial for MATLAB} \& \textit{Simulink}, University of Michigan, 2012,   \textbf{http://www.engin.umich.edu/class/ctms}
%\bibitem{tre} Alan V. Oppenheim, Alan S. Willsky with S. Hamid Nawab, \textit{Signals and Systems}, Prentice-Hall International, Inc., 1997
\end{thebibliography}

### 2019-01-24 Thesis_Latex/Thesis/Chapter4/Chapter4.tex
update Matlab files

\chapter{Moving Obstacle Avoidance}
\section{Problem Formulation}
\section{Design of Adaptive MPC}
\section{Simulation Results}

### 2019-01-24 Thesis_Latex/Thesis/Conclusions/Conclusions.tex
update Matlab files

\chapter*{Conclusions and Future Work}
\addcontentsline{toc}{chapter}{Conclusions and Future Work}

### 2019-01-24 Thesis_Latex/Thesis/Introduction/Introduction.tex
update Matlab files

\chapter{Introduction}
%\addcontentsline{toc}{chapter}{Introduction}
\section{ATLAS Project}
\section{Context of the Problem and Motivation}
\section{Proposed Approach}
\section{Thesis Outline and Contributions}

### 2019-01-24 MATLAB/NOTWORKINGcircular_path_random_N_obstacles/main_circular_path_random_N_obstacles.m

@@ -107,7 +107,7 @@ mpcobj.ManipulatedVariables(2).ScaleFactor = 0.2;
  
 % Choose the Y position and velocity by setting the weights of the other 
 % two outputs (X and theta) to zero
-mpcobj.Weights.OutputVariables = [1 1 0 1];
+mpcobj.Weights.OutputVariables = [0 1 0 1];
 
 % Update the controller with the nominal operating condition
 mpcobj.Model.Nominal = struct('U',U,'Y',Y,'X',X,'DX',DX);

### 2019-01-24 MATLAB/N_obstacles/N_obstaclesResults.m

@@ -1,0 +1,71 @@
+%% Plot results for adaptive MPC
+
+% Velocity vs Time
+h1 = figure ('Position',[100, 100, 340, 230], 'PaperPositionMode','auto');
+hold on;
+grid on;
+grid minor;
+plot(T,ympc(:,4));
+title('\textbf{Velocity ($v$) vs Time}','Interpreter','latex');
+xlabel('Time [s]','Interpreter','latex');
+ylabel('Velocity [m/s]','Interpreter','latex');
+pos = get(h1,'Position');
+set(h1,'PaperPositionMode','Auto','PaperUnits','Points','PaperSize',[pos(3), pos(4)-40])
+print(h1,'figure\VelocityVsTime','-dpdf','-r0')
+hold off
+
+% Y_mpc vs Time
+h2 = figure ('Position',[100, 100, 340, 230], 'PaperPositionMode','auto');
+hold on;
+grid on;
+grid minor;
+plot(T,ympc(:,2));
+title('\textbf{Lateral Position ($y$) vs Time}','Interpreter','latex');
+xlabel('Time [s]','Interpreter','latex');
+ylabel('Lateral Position [m]','Interpreter','latex');
+pos = get(h1,'Position');
+set(h2,'PaperPositionMode','Auto','PaperUnits','Points','PaperSize',[pos(3), pos(4)-40])
+print(h2,'figure\LateralPositionVsTime','-dpdf','-r0')
+hold off
+
+% Theta vs Time
+h3 = figure ('Position',[100, 100, 340, 230], 'PaperPositionMode','auto');
+hold on;
+grid on;
+grid minor;
+plot(T,ympc(:,3));
+title('\textbf{Heading Angle($\theta$) vs Time}','Interpreter','latex');
+xlabel('Time [s]','Interpreter','latex');
+ylabel('Heading Angle [rad]','Interpreter','latex');
+pos = get(h1,'Position');
+set(h3,'PaperPositionMode','Auto','PaperUnits','Points','PaperSize',[pos(3), pos(4)-40])
+print(h3,'figure\HeadingAngleVsTime','-dpdf','-r0')
+hold off
+
+% Throttle vs Time
+h4 = figure ('Position',[100, 100, 340, 230], 'PaperPositionMode','auto');
+hold on;
+grid on;
+grid minor;
+plot(T,umpc(:,1));
+title('\textbf{Throttle($T$) vs Time}','Interpreter','latex');
[…]

### 2019-01-24 MATLAB/N_obstacles/main_N_obstacles.m

@@ -148,7 +148,7 @@ for k = 1:length(T)
     
     % Create Obstacle Dynamics
     for i=1:N 
-        obstacle(i).X(k+1) = obstacle(i).X(k)+0.15*i;
+        obstacle(i).X(k+1) = obstacle(i).X(k)-0.15*i;
         % Safe zones for the plot
         flSafeX(k,i) = obstacle(i).X(k)+obstacle(i).safeDistanceX;
         frSafeX(k,i) = obstacle(i).X(k)+obstacle(i).safeDistanceX;
@@ -180,7 +180,8 @@ for k = 1:length(T)
     umpc(k,:) = u';
     
     % Update the plant state for the next iteration |k+1|.
-    x = Ad * x + Bd * u
+    x = Ad * x + Bd * u;
+    x_safe(k,:)=x;
 end
 
 mpcverbosity(status);
@@ -233,3 +234,7 @@ end
 % hold off
 % close(writerObj); % Saves the movie.
 close(f);
+
+%% Results
+N_obstaclesResults;
+

### 2019-01-24 MATLAB/three_obstacles_no_overtaking/main_three_obstacles_no_overtaking.m

@@ -38,12 +38,15 @@ for i=1:N
     obstacle(i).length = 5;    % The obstacles in this example are moving cars 
     obstacle(i).width = 2;     % with the same size and shape of the ATLASCAR2
 
-    obstacle(i).X = 39+3*i;      % Initial positions of the N obstacles   
-    obstacle(i).Y = -10+5*i; % (in this example the obstacles are DYNAMIC)    
-
+    obstacle(i).X = 33+3*i;      % Initial positions of the N obstacles   
+    obstacle(i).Y =-10+5*i; % (in this example the obstacles are DYNAMIC)    
+    
     obstacle(i).safeDistanceX = obstacle(i).length;    % Length equal to two car lengths
     obstacle(i).safeDistanceY = road.laneWidth;        % Width equal to two lane widths
-
+    
+    obstacle(i).space = 0.16;                
+    obstacle(i).velocity = obstacle(i).space/Ts;      % Velocity of the obstacle 8 m/s (0.16/Ts)         
+    
     % Assume that the LIDAR sensor can detect an obstacle 30
     % meters in front of the ATLASCAR2.
     obstacle(i).DetectionDistance = 30;
@@ -76,9 +79,9 @@ mpcobj.ControlHorizon = 5;
 
 % To prevent the ATLASCAR2 from accelerating or decelerating too quickly, 
 % add a hard constraint of 0.2 (m^2/sec) on the throttle rate of change.
-mpcobj.ManipulatedVariables(1).RateMin = -0.2; 
-mpcobj.ManipulatedVariables(1).RateMax = 0.2;
-
+mpcobj.ManipulatedVariables(1).RateMin = -2.5;  
+mpcobj.ManipulatedVariables(1).RateMax = 2.5;
+ 
 % add a hard constraint of 6 degrees per sec on the steering angle rate of change.
 mpcobj.ManipulatedVariables(2).RateMin = -pi/30;
 mpcobj.ManipulatedVariables(2).RateMax = pi/30;
@@ -119,34 +122,28 @@ E3 = [0 0];
 F3 = [0 -1 0 0]; 
 G3 = road.laneWidth*road.lanes/2;
 
-E4 = [1 0];
-F4 = [0 0 0 0];
-G4 = 0;
-
-E5 = [-1 0];
-F5 = [0 0 0 0];
-G5 = 0;
-
+% Constraint on x
 E6 = [0 0];
-F6 = [0 0 0 1];
-G6 = 20;
[…]

### 2019-01-24 MATLAB/three_obstacles_no_overtaking/obstacleComputeCustomConstraint.m

@@ -6,8 +6,23 @@ carY = x(2);
 
 % Compute constraints only if an obstacle is detected. Otherwise, set
 % constraint to lower road boundary (the inactive constraint).
-if(obstacle(m).Y(end)<=0)
-   for i=1:N 
+% If the street is full of obstacles the ATLASCAR2 must adapt its speed to 
+% that of the nearest obstacle; otherwise it can overcome the obstacles.
+
+% Compute the distance between the obstacles
+for i=1:N    
+    distObs(i)=sqrt((obstacle(m).X(end)-obstacle(i).X(end))^2 +(obstacle(m).Y(end)-obstacle(i).Y(end))^2);
+end
+maxObs = max(distObs);
+n = find(distObs==maxObs);
+distObs(m)=[]; % remove the distance of the obstacle m with itself.
+
+if (distObs>30)
+    x_max = obstacle(m).X(end)+1000;
+    x_min = carX;
+    % LEFT OVERTAKING
+    if(obstacle(m).Y(end)<=0)
+        for i=1:N 
    slope(i) = ( (obstacle(i).rlSafeY - carY)/(obstacle(i).rlSafeX - carX) );    
    pop(i) = ( (obstacle(i).rrSafeY - carY)/(obstacle(i).rrSafeX - carX) );
    if detection(:,m)
@@ -26,7 +41,7 @@ if(obstacle(m).Y(end)<=0)
         end
     % If the ATLASCAR2 is parallel to the obstacle, use the safety zone as
     % the constraint.
-    elseif  ((carX>obstacle(i).rlSafeX) && (carX<=obstacle(i).flX))
+    elseif  ((carX>obstacle(i).rlSafeX) && (carX<=obstacle(i).flSafeX))
         constraintSlope(i) = 0;
         constraintIntercept(i) = obstacle(i).rlSafeY; 
     % If the ATLASCAR2 has passed the obstacle, use the inactive constraint
@@ -45,9 +60,13 @@ if(obstacle(m).Y(end)<=0)
         constraintSlope(i) = 0;
         constraintIntercept(i) = obstacle(i).rlSafeY;
    end
-end
-else
-for i=1:N
+        end
+        E = [0 0; 0 0; 0 0; 0 0; 0 0];
+        F = [0 1 0 0;0 -1 0 0;constraintSlope(m) -1 0 0; 1 0 0 0; -1 0 0 0];
+        G = [laneWidth*lanes/2; laneWidth*lanes/2;-1*constraintIntercept(m); x_max; -x_min];
[…]

### 2019-01-24 MATLAB/three_obstacles_no_overtaking/three_obstaclesResults.m

@@ -1,0 +1,71 @@
+%% Plot results for adaptive MPC
+
+% Velocity vs Time
+h1 = figure ('Position',[100, 100, 340, 230], 'PaperPositionMode','auto');
+hold on;
+grid on;
+grid minor;
+plot(T,ympc(:,4));
+title('\textbf{Velocity ($v$) vs Time}','Interpreter','latex');
+xlabel('Time [s]','Interpreter','latex');
+ylabel('Velocity [m/s]','Interpreter','latex');
+pos = get(h1,'Position');
+set(h1,'PaperPositionMode','Auto','PaperUnits','Points','PaperSize',[pos(3), pos(4)-40])
+print(h1,'figure\VelocityVsTime','-dpdf','-r0')
+hold off
+
+% Y_mpc vs Time
+h2 = figure ('Position',[100, 100, 340, 230], 'PaperPositionMode','auto');
+hold on;
+grid on;
+grid minor;
+plot(T,ympc(:,2));
+title('\textbf{Lateral Position ($y$) vs Time}','Interpreter','latex');
+xlabel('Time [s]','Interpreter','latex');
+ylabel('Lateral Position [m]','Interpreter','latex');
+pos = get(h1,'Position');
+set(h2,'PaperPositionMode','Auto','PaperUnits','Points','PaperSize',[pos(3), pos(4)-40])
+print(h2,'figure\LateralPositionVsTime','-dpdf','-r0')
+hold off
+
+% Theta vs Time
+h3 = figure ('Position',[100, 100, 340, 230], 'PaperPositionMode','auto');
+hold on;
+grid on;
+grid minor;
+plot(T,ympc(:,3));
+title('\textbf{Heading Angle ($\theta$) vs Time}','Interpreter','latex');
+xlabel('Time [s]','Interpreter','latex');
+ylabel('Heading Angle [rad]','Interpreter','latex');
+pos = get(h1,'Position');
+set(h3,'PaperPositionMode','Auto','PaperUnits','Points','PaperSize',[pos(3), pos(4)-40])
+print(h3,'figure\HeadingAngleVsTime','-dpdf','-r0')
+hold off
+
+% Throttle vs Time
+h4 = figure ('Position',[100, 100, 340, 230], 'PaperPositionMode','auto');
+hold on;
+grid on;
+grid minor;
+plot(T,umpc(:,1));
+title('\textbf{Throttle ($T$) vs Time}','Interpreter','latex');
[…]

### 2019-01-30 Thesis_Latex/Paper/Paper.tex
update full version Paper

@@
 \end{abstract}
-
 \section{Introduction}
@@
 Though these two topics have been well researched, currently, there is no ideal solution to handling the navigation problem within cluttered dynamic environments.
-
 \section{Context of the Problem and \\  Proposed Solution}
@@
 This system uses an adaptive Model Predictive Controller that updates both the predictive model and the mixed input/output constraints at each control interval.
-Moreover, this vehicle is also equipped with a lane-keeping assist system: it has a sensor, such as camera, that measures the lateral deviation and relative yaw angle between the centerline of a lane and the ATLASCAR2.
-The sensor also measures the current lane curvature and curvature derivative.
-Depending on the curve length that the sensor can view, the curvature in front of the vehicle can be calculated from the current curvature and curvature derivative.
+Moreover, this vehicle is also equipped with a lane-keeping assist system: it has a sensor, such as camera or laser, that measures the lateral deviation and relative yaw angle between the centerline of a lane and the ATLASCAR2; it also measures the current lane curvature and its derivative.
+Depending on the curve length that the sensor can view, the curvature in front of the vehicle can be calculated from the current curvature and its derivative.
 This system keeps the autonomous car travelling along the centerline of the lanes on the road by adjusting the front steering angle.
 The goal for lane keeping control is to drive both lateral deviation and relative yaw angle close to zero.
-\subsection{Theoretical background - adaptive Model Predictive Control}
+\subsection{Theoretical background - Adaptive MPC}
 Model Predictive Control is an advanced method that predicts future behavior using a linear-time-invariant (LTI) dynamic model.
@@
 \end{itemize}
-
 In the adaptive MPC control there are additional requirements for the plant model as the sample time $T_s$ that has to be constant and identical to the MPC control interval.
@@
 and the assumptions leading to the constant $Q$, $R$ and $N$ matrices.
-
 \section{Obstacle Avoidance}
@@
 \end{figure}
-
 The model used in this paper should take into account the kinematic and dynamic aspects of the vehicle.
@@
   \end{bmatrix}^{T}
-\qquad 
+,\qquad 
 \textbf{u}=\begin{bmatrix}
@@
 where $(x,y)$ are the global coordinates of the center point of the car, $\theta$ is the heading angle of the car body with respect to the $x$-axis and $v$ is the speed of the car (positive).
-The manipulated variables are $T$ the throttle (positive when accelerating/negative when decelerating) and $\delta$ the steering angle ($0$ when aligned with car, counterclockwise positive).
-
-The simple non-linear model to describe the dynamics of the ATLASCAR2 is derived combining the equations in [2] and [3]:
+The manipulated variables are $T$ the throttle (positive when accelerating/negative when braking) and $\delta$ the steering angle ($0$ when aligned with car, counterclockwise positive).
+\begin{figure}[!h]
+	\centering
+	\includegraphics[width=0.70\columnwidth]{./figure/car_model.pdf}
+	\caption{Bicycle model of a car.}
+	\label{fig:car_model}
+\end{figure}
+The ATLASCAR2 can be modeled using the non-linear kinematic bicycle model described by the following equations of motion:
 \begin{equation*}
 \label{eqn:dynamics_model_obstacle_avoidance}
+\left \{ \begin{array}{llll}
+\dot{x} = v\cos(\theta)\\
+\dot{y} = v\sin(\theta)\\
+\dot{\theta} =\dfrac{v}{C_L}\tan(\delta)\\
+\dot{v} =0.5 \cdot T
+\end{array} 
+\right .
+\Longrightarrow 
+\begin{array}{llll}
+\dot{\textbf{x}} = f(\textbf{x},\textbf{u})\\
+\textbf{y} = g(\textbf{x},\textbf{u})
+\end{array}
+\end{equation*}
+where $C_L$ is the car length.
+In order to simplify the model, it is assumed that only the front wheel can be steered.
+Moreover, in this paper it is assumed that the ATLASCAR2 does not slip, any slippage is thus considered as an external disturbance.
+Under this assumption, the slip angle is zero, meaning that the velocity is directed along the heading of the vehicle.
+In order to use MPC, the state space model needs to be linearized and also re-written in a more compact form:
+\begin{equation}
+\label{eqn:dynamics_model_non_linear}
+\begin{array}{llll}
+\dot{\textbf{x}} = f(\textbf{x},\textbf{u})\\
+\textbf{y} = g(\textbf{x},\textbf{u})
+\end{array} \Longrightarrow
+\begin{array}{ll}
+\dot{\textbf{x}} =A_c \textbf{x}+ B_c \textbf{u}\\
+\textbf{y} =C_c \textbf{x} + D_c \textbf{u}
+\end{array}
+\end{equation}
+where the matrices $A_c$, $B_c$, $C_c$ and $D_c$ are obtained as follows:
+\[ 
+A_c=\frac{\partial f(\textbf{x},\textbf{u})}{\partial \textbf{x}}=\begin{bmatrix}
+0&0&-v\sin(\theta)&\cos(\theta)\\
+0&0&v\cos(\theta)&\sin(\theta)\\
+0&0&0&\tan(\delta)/C_L\\
+0&0&0&0
+\end{bmatrix},
+\]
+\[
+B_c=\frac{\partial f(\textbf{x},\textbf{u})}{\partial \textbf{u}}=\begin{bmatrix}
+0&0\\
+0&0\\
+0&\dfrac{v}{C_L}\big(\tan(\delta)^2+1\big)\\
+0.5&0
+\end{bmatrix},
+\]
+\[
+C_c=\frac{\partial g(\textbf{x},\textbf{u})}{\partial \textbf{u}} = \textbf{I}_4, 
+\qquad
+D_c=\frac{\partial g(\textbf{x},\textbf{u})}{\partial \textbf{u}}=\textbf{0}_{4\times2}. 
+\]
+The simple linearized approximation of the system to describe the dynamics of the ATLASCAR2 will be evaluated at the operating conditions; the extended form of the considered model is the following:
+\begin{equation*}
+	\label{eqn:dynamics_model_obstacle_avoidance_linearized}
 	\left \{ \begin{array}{llll}
@@
 \end{equation*}
-where $C_L$ is the car length. The state equations can be re-written in a more compact form as follows:
-\begin{equation}
-	\label{eqn:dynamics_ss_obstacle_avoidance_con}
+The system to be controlled is usually modeled by a discrete state-space model in the MPC literature. Therefore, (\ref{eqn:dynamics_model_non_linear})
+is transformed into a discrete state-space model to be used by the Model Predictive Controller:
+\begin{equation*}
+\label{eqn:dynamics_ss_obstacle_avoidance_dis}
 	\begin{array}{ll}
@@
 	\end{array}
-\end{equation}
-where
-\[ 
-A_c=\begin{bmatrix}
-0&0&-v\sin(\theta)&\cos(\theta)\\
-0&0&v\cos(\theta)&\sin(\theta)\\
-0&0&0&\tan(\delta)/C_L\\
-0&0&0&0
-\end{bmatrix},
-\]
-\[
-B_c=\begin{bmatrix}
-0&0\\
-0&0\\
-0&v\bigg(\tan(\delta)^2+1\bigg)/C_L\\
-0.5&0
-\end{bmatrix},
-\]
-\[
-C_c=\begin{bmatrix}
-1&0&0&0\\
-0&1&0&0\\
-0&0&1&0\\
-0&0&0&1
-\end{bmatrix} = \textbf{I}_4, 
-\qquad
-D_c=\begin{bmatrix}
-0&0\\
-0&0\\
-0&0\\
-0&0
-\end{bmatrix} = \textbf{0}_{4\times2}. 
-\]
-The system to be controlled is usually modeled by a discrete state-space model in the MPC literature. Therefore, (\ref{eqn:dynamics_ss_obstacle_avoidance_con})
-is transformed into a discrete state-space model to be used by the model predictive controller:
-\begin{equation}
-\label{eqn:dynamics_ss_obstacle_avoidance_dis}
+	\Rightarrow
 	\begin{array}{rr}
@@
 	\end{array}
-\end{equation}
+\end{equation*}
 where $A_d$ and $B d$ are the state and control matrices for the discrete state-space equation, respectively, which can be calculated with the Euler method as
@@
 We create also a safe zone around the obstacles so that the vehicle does not get too close to the osbtacle when passing it.
-
 \subsection{Design of Adaptive Model Predictive Control}
-
-We designed a model predictive controller that can make the ATLASCAR2 mantain a desired velocity and stay in the middle of center lane.
+We designed a Model Predictive Controller that can make the ATLASCAR2 mantain a desired velocity of and stay in the middle of center lane.
 We used an Adaptive MPC controller because it handles the nonlinear vehicle dynamics more effectively than a traditional MPC controller; in fact, the latter uses a constant plant model but the former allows us to provide a new plant model at each control interval.
@@
 Once updated, the model and the conditions remain constant over the prediction horizon.
-At the beginning, we specified the constraints for the manipulated variables: to prevent the ATLASCAR2 from accelerating or decelerating too quickly, we added an hard constraint on the throttle rate of change and another one on the steering angle rate of change.
+In path tracking using adaptive MPC, it is common to formulate the constrained control problem as a real-time optimization problem subject to hard constraints on plant variables and soft constraints on outputs; at the beginning, we specified the constraints for the manipulated variables: to prevent the ATLASCAR2 from accelerating or decelerating too quickly, we added an hard constraint on the throttle rate of change and another one on the steering angle rate of change.
 We used an approach that takes advantage of the ability of MPC to handle constraint explicitly.
@@
 \end{equation*}
-where $\textbf{u}$ and $\textbf{y}$ are respectively the manipulated variable vector and the output variable vector, while $E,F,G$ are the matrices that can be updated when the controller is running:
+where $\textbf{u}$ and $\textbf{y}$ are respectively the manipulated variable vector and the output variable vector, while $E,F,G$ are the constraint matrices that can be updated when the controller is running:
 \begin{itemize}
@@
 	\item the second constraint is a lower bound on the $y$-coordinate (left boundary of the road);
-	\item the third constraint is for the obstacle avoidance; even though no obstacle is detected at the nominal condition, we must add this fake constraint here because we cannot change the dimensions of the constraint matrices at run time (it has the same form as the second one).
+	\item the third constraint is for the obstacle avoidance; even though no obstacle is detected at the nominal condition, we must add this fake constraint here because we cannot change the dimensions of the constraint matrices at run time (it has the same form as the second one);
+	\item the fourth constraint is an upper bound on the $x$-coordinate (the position of the closest obstacle);
+	\item the fifth constraint is a lower bound on the $x$-coordinate (the position of the ATLASCAR2).
 \end{itemize}
@@
 0&0\\
+0&0\\
 0&0
 \end{bmatrix},
-\quad
+\;
 F=\begin{bmatrix}
@@
 0&-1&0&0\\
-cS&-1&0&0
-\end{bmatrix},\quad
+cS&-1&0&0\\
+1&0&0&0\\
+-1&0&0&0\\
+\end{bmatrix},\;
 G=
 \begin{bmatrix}
-W/2\\W/2\\-cI
+W/2\\W/2\\-cI\\x_{\max}\\x_{\min}
 \end{bmatrix}
 \]
-where $W$ is the width of the road and $cI$ and $cS$ are the required parameters such that the ATLASCAR2 must be above the line formed from the vehicle to safe zone corner for left/right passing.
-
+where $W$ is the width of the road, $cI$ and $cS$ are the required parameters such that the ATLASCAR2 must be above the line formed from the vehicle to safe zone corner for left/right passing and finally $x_{\max}$ represents the position of the closest obstacle while $x_{\min}$ depicts the location of our vehicle.
 \subsection{Simulation Results}
-In this first simulation we assumed that the road is straight and has 3 lanes each of 4 meters wide.
-Moreover the ATLASCAR2 drives in the middle of the center lane when not passing and in this case the vehicle passes an obstacle only from the right lane (the same simulation can be launched so that the car goes over to the left fast lane).
+The performances of the proposed adaptive MPC based vehicle control method are demonstrated in three
+simulation examples.
+We tried to choose parameters that were as close as possible to a real situation: the sampling time used in the discretization of the system is $T_s= 0.02$s while the values of the prediction and the control horizon are respectively $p_H=25$ and $c_H=5$.
+In all simulations, the distance between the front and rear axles is $C_L=5$m and the witdh of the vehicle is $C_W=2$m.
+The saturation ranges of the control inputs are: the steering angle lies in $\big[-\frac{\pi}{30}, +\frac{\pi}{30}\big]$rad/sec while in order to prevent the ATLASCAR2 from accelerating or decelerating too quickly, we impose an hard constraint of 2.5m$^2$/sec on the throttle rate of change.
+Moreover we are using a constant reference signal for the velocity of $v=20$m/s ($\simeq72$km/h).
+The vehicle is initially placed at $(0,0)$ and moves in a s­traight line.
+\subsubsection{One Moving Obstacle - Right Overtaking}
+In this first simulation we assumed that the road is straight and has 3 lanes each one 4 meters wide.
+Moreover the ATLASCAR2 drives in the middle of the center lane while the road is completely free and when there is an obstacle the vehicle passes it only using the right lane (the same simulation can be launched so that the car goes over to the left fast lane).
+When the vehicle detects the obstacle, the constraints are computed: if the ATLASCAR2 is already in the adjacent lane, it uses the safety zone as the constraint, otherwise the vehicle must be above the line formed from the ATLASCAR2 to safe zone corner for right passing.
+If the vehicle is parallel to the obstacle, it  uses the safety zone as the constraint and finally if it has passed the obstacle, it uses the inactive constraint to go back to the center lane.
+In this first example the obstacle moves in the same direction as the vehicle.
 \begin{figure}[!h]
 	\centering
+	\begin{minipage}[t]{\columnwidth}
 	\includegraphics[width=1\columnwidth]{../../MATLAB/one_obstacle_right_overtaking/figure/overtaking_paper/overtaking_start.pdf}
 	\label{fig:obstacleAvoidance_start}
+	\end{minipage}
+	\begin{minipage}[t]{\columnwidth}
+	\includegraphics[width=1\columnwidth]{../../MATLAB/one_obstacle_right_overtaking/figure/overtaking_paper/overtaking_middle.pdf}
+	\label{fig:obstacleAvoidance_middle}
+	\end{minipage}
+	\begin{minipage}[t]{\columnwidth}
+	\includegraphics[width=1\columnwidth]{../../MATLAB/one_obstacle_right_overtaking/figure/overtaking_paper/overtaking_middle_end.pdf}
+	\label{fig:obstacleAvoidance_middle_end}
+	\end{minipage}
+	\begin{minipage}[t]{\columnwidth}
+	\includegraphics[width=1\columnwidth]{../../MATLAB/one_obstacle_right_overtaking/figure/overtaking_paper/overtaking_end.pdf}
+	\label{fig:obstacleAvoidance_end}
+	\end{minipage}
+	\caption{Simulation of right overtaking with one moving obstacle}
 \end{figure}
-\vspace{-3em}
+\subsubsection{Multiple Moving Obstacles}
+Consequently, additional obstacles were added to make the scenario more complex.
+The vehicle is capable of overtaking the obstacles to the right or left depending on their positions with respect to the road.
+If the $y$-coordinate of the closest obstacle is greater than 0, then the vehicle overtakes to the right, while if the $y$-coordinate is less than 0 the overtaking takes place on the left lane.
+We also hypothesized that the obstacles move at a different speeds but that they are initially at a common distance.
+In case two obstacles are too close during the simulation and their distance is less than the detection range which is $30$m, the ATLASCAR2 perceives the objects as a single entity and adapts to the situation.
+In this case the obstacles drive in the wrong direction with respect to the ATLASCAR2 (but the same results can be verified in the same direction).
 \begin{figure}[!h]
 	\centering
-	\includegraphics[width=1\columnwidth]{../../MATLAB/one_obstacle_right_overtaking/figure/overtaking_paper/overtaking_middle.pdf}
-	\label{fig:obstacleAvoidance_middle}
+	\begin{minipage}[t]{\columnwidth}
+	\includegraphics[width=1\columnwidth]{../../MATLAB/random_N_obstacles/figure/overtaking_random_2.pdf}
+	\label{fig:obstacleAvoidance_random_2}
+	\end{minipage}
+	\begin{minipage}[t]{\columnwidth}
+	\includegraphics[width=1\columnwidth]{../../MATLAB/random_N_obstacles/figure/overtaking_random.pdf}
+	\label{fig:obstacleAvoidance_random}
+	\end{minipage}
+	\begin{minipage}[t]{\columnwidth}
+	\includegraphics[width=1\columnwidth]{../../MATLAB/random_N_obstacles/figure/overtaking_random_1.pdf}
+	\label{fig:obstacleAvoidance_random_1}
+	\end{minipage}
+	\caption{Simulations of overtaking with $N = 2,3,4$ moving obstacles}
 \end{figure}
-\vspace{-3em}
+\subsubsection{Vehicle Braking and Obstacles Overtaking}
+Finally we have improved the code related to the mixed Input/Output constraints so that in the case there are 3 obstacles that block the road and drive at a lower speed than the ATLASCAR2, the velocity of the vehicle decreases in order to prevent the collision.
+Here it is depicted a simulation in which there are the obstacles at the same $x$-coordinate.
+Two obstacles have a constant speed of $8$m/s while the one on the left lane has a velocity of $15$m/s.
+At the beginning the vehicle detects all the other cars on the road.
+In the first part of the simulation, the vehicle brakes because there is no enough space for overtaking the cars as shown in the Fig.\ref{fig:velocity_braking}.
+A collision will
+happen if the vehicle continues to follow the initially planned trajectory with the reference velocity.
+It is possible to notice that the speed decreases because the applied throttle is negative, so a consistent deceleration is set after $\simeq1.5$s as depicted in Fig.\ref{fig:throttle_braking}.
+After few seconds the fastest obstacle moves and makes available the left lane.
+Dramatic changes of steering angle in early stage are observed in Fig.\ref{fig:delta_braking} and consequently also on the heading angle in Fig.\ref{fig:theta_braking}.
+Then, the ATLASCAR2 returns to the reference velocity during the overtaking of the two obstacles.
+The path of the vehicle is is depicted in Fig.
+\ref{fig:lateral_braking}.
+It is seen that the ATLASCAR2 avoids the  obstacles and returns to the road  centerline with a low overshoot.
+%%% Simulation Braking
 \begin{figure}[!h]
 		\centering
-	\includegraphics[width=1\columnwidth]{../../MATLAB/one_obstacle_right_overtaking/figure/overtaking_paper/overtaking_middle_end.pdf}
-	\label{fig:obstacleAvoidance_middle_end}
-\end{figure}
-\vspace{-3em}
-\begin{figure}[!h]
-	\centering
-	\includegraphics[width=1\columnwidth]{../../MATLAB/one_obstacle_right_overtaking/figure/overtaking_paper/overtaking_end.pdf}
-	\label{fig:obstacleAvoidance_end}
-	\vspace{-1.2em}
-	\caption{Simulation of right overtaking with one moving obstacle}
-\end{figure}
-
-Subsequently, additional obstacles were added to make the scenario more complex.
-The vehicle is capable of overcoming the obstacles to the right or left depending on their position with respect to the road.
-We also hypothesized that the obstacles move at a different speed but that they are initially at a common distance.
-In case two obstacles are too close during the simulation and their distance is less than the detection range, the ATLASCAR2 perceives the objects as a single entity and adapts to the situation.
-
-\begin{figure}[!h]
-	\centering
-	\includegraphics[width=1\columnwidth]{../../MATLAB/random_N_obstacles/figure/overtaking_random_2.pdf}
-	\label{fig:obstacleAvoidance_random_2}
-	\vspace{-1.3em}
+	\begin{minipage}[t]{\columnwidth}
+		\includegraphics[width=1\columnwidth]{../../MATLAB/three_obstacles_no_overtaking/figure/braking_0.pdf}
+		\label{fig:braking_0}
+	\end{minipage}
+	\begin{minipage}[t]{\columnwidth}
+		\includegraphics[width=1\columnwidth]{../../MATLAB/three_obstacles_no_overtaking/figure/braking_1.pdf}
+		\label{fig:braking_1}
+	\end{minipage}
+	\begin{minipage}[t]{\columnwidth}
+		\includegraphics[width=1\columnwidth]{../../MATLAB/three_obstacles_no_overtaking/figure/braking_2.pdf}
+		\label{fig:braking_2}
+	\end{minipage}
+	\begin{minipage}[t]{\columnwidth}
+		\includegraphics[width=1\columnwidth]{../../MATLAB/three_obstacles_no_overtaking/figure/braking_3.pdf}
+		\label{fig:braking_3}
+	\end{minipage}
+	\begin{minipage}[t]{\columnwidth}
+		\includegraphics[width=1\columnwidth]{../../MATLAB/three_obstacles_no_overtaking/figure/braking_4.pdf}
+		\label{fig:braking_4}
+	\end{minipage}
+	\begin{minipage}[t]{\columnwidth}
+		\includegraphics[width=1\columnwidth]{../../MATLAB/three_obstacles_no_overtaking/figure/braking_5.pdf}
+		\label{fig:braking_5}
+	\end{minipage}
+	\begin{minipage}[t]{\columnwidth}
+		\includegraphics[width=1\columnwidth]{../../MATLAB/three_obstacles_no_overtaking/figure/braking_6.pdf}
+		\label{fig:braking_6}
+	\end{minipage}	
+	\caption{Simulation of braking and overtaking obstacles.}
 \end{figure}
@@
 	\centering
-	\includegraphics[width=1\columnwidth]{../../MATLAB/random_N_obstacles/figure/overtaking_random.pdf}
-	\label{fig:obstacleAvoidance_random}
-	\vspace{-1.3em}
+	\includegraphics[width=1\columnwidth]{../../MATLAB/three_obstacles_no_overtaking/figure/VelocityVsTime.pdf}
+	\caption{Velocity $v$ with respect to time.}
+	\label{fig:velocity_braking}
 \end{figure}
@@
 	\centering
-	\includegraphics[width=1\columnwidth]{../../MATLAB/random_N_obstacles/figure/overtaking_random_1.pdf}
-	\label{fig:obstacleAvoidance_random_1}
-	\vspace{-1.2em}
-	\caption{Simulations of overtaking with $N = 2,3,4$ moving obstacles}
+	\includegraphics[width=1\columnwidth]{../../MATLAB/three_obstacles_no_overtaking/figure/ThrottleVsTime.pdf}
+	\caption{Throttle $T$ with respect to time.}
+	\label{fig:throttle_braking}
 \end{figure}
-
+\begin{figure}[!h]
+	\centering
+	\includegraphics[width=1\columnwidth]{../../MATLAB/three_obstacles_no_overtaking/figure/SteeringAngleVsTime.pdf}
+	\caption{Steering angle $\delta$ with respect to time.}
+	\label{fig:delta_braking}
+\end{figure}
+\begin{figure}[!h]
+	\centering
+	\includegraphics[width=1\columnwidth]{../../MATLAB/three_obstacles_no_overtaking/figure/HeadingAngleVsTime.pdf}
+	\caption{Heading angle $\theta$ with respect to time.}
+	\label{fig:theta_braking}
+\end{figure}
+\begin{figure}[!h]
+	\centering
+	\includegraphics[width=1\columnwidth]{../../MATLAB/three_obstacles_no_overtaking/figure/LateralPositionVsTime.pdf}
+	\caption{Lateral position $y$ with respect to time.}
+	\label{fig:lateral_braking}
+\end{figure}
 \section{Lane Following}
@@
 \]
-where $\tau$ is a time constant; in practice we are considering a second order transfer function like in [5].
+where $\tau$ is a time constant; in practice we are considering a second order transfer function like in \cite{long_tf}.
 \subsubsection{Lateral dynamics}
-Local function: we have a continuous vehicle lateral model from parameters obtained by simplifying the one in [7]: 
+Local function: we have a continuous vehicle lateral model from parameters obtained by simplifying the one in \cite{rathai}: 
 \begin{equation}
@@
 \]
-Combining (\ref{eqn:longi_dynamics_simple_model_ss}) with (\ref{eqn:lateral_dynamics_augmented_model}) yields the state-space model that characterizes the model predictive controller:
+Combining (\ref{eqn:longi_dynamics_simple_model_ss}) with (\ref{eqn:lateral_dynamics_augmented_model}) yields the state-space model that characterizes the Model Predictive Controller:
 \begin{equation}
@@
 and
-
 \[ 
@@
 \]
-
-However the system to be controlled is usually modeled by a discrete state-space model:
+However the system to be controlled is usually modeled by a linear discrete state-space model:
 \begin{equation*}
@@
 \subsection{Simulation Results}
-The proposed adaptive MPC algorithm is designed in the MATLAB/Simulink and validated through simulation. The objective of this
-test is to evaluate the behavior of the proposed control strategy in critical situations.
-Fig.\ref{fig:reference_laneFollowing} and Fig.\ref{fig:curvature_laneFollowing} show the desired path that the car must follow and its curvature.
+The proposed adaptive MPC algorithm is designed in the MATLAB/Simulink and validated through simulation.
+The objective of this test is to evaluate the behavior of the proposed control strategy in critical situations.
+Table 3 shows the parameters used in the lane following simulation.
+\begin{table}[!h]
+	\centering
+	\begin{tabular}{|c|c|}
+		\hline
+		Parameters          & Values      \\
+		\hline
+		$m$          & 1575 kg              \\
+		$I_z$         & 2875 kg$\cdot$m$^2$              \\
+		$l_F$           & 1.2 m               \\
+		$l_R$         & 1.6 m               \\
+		$C_F$          & 19000 N/rad      \\
+		$C_R$           & 33000 N/rad            \\
+		$\tau$             & 0.2                \\
+		$V_0$           & 15 m/s       \\
+		$V_{\text{set}}$          & 20 m/s \\
+		$T_s$         & 0.02 s        \\
+		\hline
+	\end{tabular}
+\end{table}
+
+Fig.\ref{fig:reference_laneFollowing} and Fig.\ref{fig:curvature_laneFollowing} show the desired path that the car must follow and its curvature, where the former is described in terms of the lateral position $Y_{\text{ref}}$ as function of the longitudinal position $X_{\text{ref}}$.
+The ATLASCAR2 is controlled to
+follow a sinusoidal trajectory which is given as follows:
+\begin{equation*}
+	X_\text{ref}=V_x\cdot t, \quad Y_\text{ref}=5\sin(X_\text{ref}/20)\quad \text{with}\quad t\in[0,20]\text{s}
+\end{equation*}
 \begin{figure}[!h]
@@
 In particular we simulated also a small error in the sensor dynamics in order to make the simulation more realistic: we added a 3 percent error to the longitudinal velocity and this is evident from the small noise in the graphs of the steering angle and the lateral deviation.
-
 \begin{figure}[!h]
 	\centering
-	\hspace*{-0.5in}
-	\includegraphics[width=1.29\columnwidth]{../../MATLAB/lane_following/figure/AccelerationVsTime.pdf}
+	\includegraphics[width=1\columnwidth]{../../MATLAB/lane_following/figure/AccelerationVsTime.pdf}
 	\caption{Acceleration $u_1$ with respect to time.}
@@
 	\centering
-	\hspace*{-0.5in}
-	\includegraphics[width=1.29\columnwidth]{../../MATLAB/lane_following/figure/SteeringAngleVsTime.pdf}
+	\includegraphics[width=1\columnwidth]{../../MATLAB/lane_following/figure/SteeringAngleVsTime.pdf}
 	\caption{Steering angle $u_2$ with respect to time.}
@@
 	\centering
-	\hspace*{-0.5in}
-	\includegraphics[width=1.29\columnwidth]{../../MATLAB/lane_following/figure/RelativeYawAngleVsTime.pdf}
+	\includegraphics[width=1\columnwidth]{../../MATLAB/lane_following/figure/RelativeYawAngleVsTime.pdf}
 	\caption{Relative yaw angle $e_2$ with respect to time.}
@@
 	\centering
-	\hspace*{-0.5in}
-	\includegraphics[width=1.29\columnwidth]{../../MATLAB/lane_following/figure/LateralDeviationVsTime.pdf}
+	\includegraphics[width=1\columnwidth]{../../MATLAB/lane_following/figure/LateralDeviationVsTime.pdf}
 	\caption{Lateral deviation $e_1$ with respect to time.}
@@
 \end{figure}
+
 Fig.{\ref{fig:longitudinal_velocity_laneFollowing}} shows the evolution of the vehicle longitudinal velocity.
@@
 	\centering
-	\hspace*{-0.5in}
-	\includegraphics[width=1.29\columnwidth]{../../MATLAB/lane_following/figure/LongitudinalVelocityVsTime.pdf}
+	\includegraphics[width=\columnwidth]{../../MATLAB/lane_following/figure/LongitudinalVelocityVsTime.pdf}
 	\caption{Longitudinal velocity $V_x$ with respect to time.}
@@
 \end{figure}
-
 \begin{figure*}[!h]
@@
 This system updates both the predictive model and the mixed input/output constraints at each control interval.
+The vehicle is also able to brake in order to prevent collisions against closest obstacles.
 Instead, in the second scenario  we have developed a lane following system that keeps the ATLASCAR2 traveling along the centerline of the lanes on the road by adjusting the front steering angle of the car.
@@
 Moreover the final method could be tested in a real autonomous driving scenario.
-
 \begin{thebibliography}{00}
@@
 	\bibitem{theory}J. Rawlings, D. Mayne (2010), "Model Predictive Control: Theory and Design", Nob Hill Publishing.
+
+	\bibitem{backward}C.
+Son and C.
+Ahn, "Vehicle backward driving control with obstacle avoidance," 2015 15th International Conference on Control, Automation and Systems (ICCAS), Busan, 2015, pp.
+1771-1774.
+
+	\bibitem{archi}M.
+Nolte, M.
+Rose, T.
+Stolte and M.
+Maurer, "Model predictive control based trajectory generation for autonomous vehicles — An architectural approach," 2017 IEEE Intelligent Vehicles Symposium (IV), Los Angeles, CA, 2017, pp.
+798-805.
+
+	\bibitem{zhou}H.
+Zhou, L.
+Güvenç and Z.
+Liu, "Design and evaluation of path following controller based on MPC for autonomous vehicle," 2017 36th Chinese Control Conference (CCC), Dalian, 2017, pp.
+9934-9939.
+
+	\bibitem{yu} Z. T. Yu, Obstacle Avoidance for Autonomous Vehicle Driving on Highways Based on MPC, JinLin University, 2012.
+
+	\bibitem{ricky}M. Riccardo and S. Stefano, Integrated Control of Active Steering and Electronic Differentials in Four Wheel Drive Vehicles,
+	SAE International Journal of Passenger Cars: Electronic and Electrical Systems, Vol.2, No.1, 141-149, 2009.
+
+	\bibitem{mikumo}R.
+Mikumo and H.
+Ichihara, "Dynamic collision avoidance among multiple mobile robots: A model predictive control approach," 2017 56th Annual Conference of the Society of Instrument and Control Engineers of Japan (SICE), Kanazawa, 2017, pp.
+1136-1137.
+
+	\bibitem{qian}X.
+Qian, A.
+de La Fortelle and F.
+Moutarde, "A hierarchical Model Predictive Control framework for on-road formation control of autonomous vehicles," 2016 IEEE Intelligent Vehicles Symposium (IV), Gothenburg, 2016, pp.
+376-381.
+
+	\bibitem{berger}Berger, Niels. (2018). Lane Change Path Planning With state-dependent safety constraints using Nonlinear Model Predictive Control.
+
+	\bibitem{kth_thilen}E. Thilén, ‘Robust Model Predictive Control for Autonomous Driving’, Dissertation, 2017.
+
+	\bibitem{kth_nordell}B. Nordell, ‘Trajectory Planning for Autonomous Vehicles and Cooperative Driving’, Dissertation, 2016.
+
+	\bibitem{shen}C. Shen, H. Guo, F. Liu and H. Chen, "MPC-based path tracking controller design for autonomous ground vehicles," 2017 36th Chinese Control Conference (CCC), Dalian, 2017, pp. 9584-9589.
+
+	\bibitem{borelli}V.
+Turri, A.
+Carvalho, H.
+E.
+Tseng, K.
+H.
+Johansson and F.
+Borrelli, "Linear model predictive control for lane keeping and obstacle avoidance on low curvature roads," 16th International IEEE Conference on Intelligent Transportation Systems (ITSC 2013), The Hague, 2013, pp.
+378-383.
 \end{thebibliography}

### 2019-01-30 MATLAB/lane_following/LaneFollowingGetCurvature.m

@@ -28,12 +28,11 @@ plot(Xref,Yref)
 hold on
 grid on
 grid minor
-axis equal
 title('\textbf{Desired Path}','Interpreter','latex');
 xlabel('X-coordinate [m]','Interpreter','latex');
 ylabel('Y-coordinate [m]','Interpreter','latex');
 pos = get(h,'Position');
-set(h,'PaperPositionMode','Auto','PaperUnits','Points','PaperSize',[pos(3)*0.8, pos(4)-40])
+set(h,'PaperPositionMode','Auto','PaperUnits','Points','PaperSize',[pos(3), pos(4)-40])
 print(h,'figure\Reference','-dpdf','-r0')
 hold off
 
@@ -56,6 +55,6 @@ title('\textbf{Curvature}','Interpreter','latex');
 xlabel('Time [s]','Interpreter','latex');
 ylabel('Curvature [m]','Interpreter','latex');
 pos = get(hcurv,'Position');
-set(hcurv,'PaperPositionMode','Auto','PaperUnits','Points','PaperSize',[pos(3)*0.8, pos(4)-40])
+set(hcurv,'PaperPositionMode','Auto','PaperUnits','Points','PaperSize',[pos(3), pos(4)-40])
 print(hcurv,'figure\Curvature','-dpdf','-r0')
 hold off

### 2019-01-30 MATLAB/lane_following/LaneFollowingResults.m

@@ -15,8 +15,8 @@ plot(delta_ampc.Values.time,delta_ampc.Values.Data);
 title('\textbf{Steering Angle (u$_2$) vs Time}','Interpreter','latex');
 xlabel('Time [s]','Interpreter','latex');
 ylabel('Steering angle [rad]','Interpreter','latex');
-pos = get(h1,'Position');
-set(h1,'PaperPositionMode','Auto','PaperUnits','Points','PaperSize',[pos(3), pos(4)-40])
+pos1 = get(h1,'Position');
+set(h1,'PaperPositionMode','Auto','PaperUnits','Points','PaperSize',[pos1(3), pos1(4)-40])
 print(h1,'figure\SteeringAngleVsTime','-dpdf','-r0')
 hold off
 pause(2)
@@ -30,8 +30,8 @@ plot(e1_ampc.Values.time,e1_ampc.Values.Data);
 title('\textbf{Lateral Deviation (e$_1$) vs Time}','Interpreter','latex');
 xlabel('Time [s]','Interpreter','latex');
 ylabel('Lateral Deviation [m]','Interpreter','latex');
-pos = get(h2,'Position');
-set(h2,'PaperPositionMode','Auto','PaperUnits','Points','PaperSize',[pos(3), pos(4)-41])
+pos2 = get(h2,'Position');
+set(h2,'PaperPositionMode','Auto','PaperUnits','Points','PaperSize',[pos2(3), pos2(4)-40])
 print(h2,'figure\LateralDeviationVsTime','-dpdf','-r0')
 hold off
 pause(2)
@@ -45,8 +45,8 @@ plot(e2_ampc.Values.Time,e2_ampc.Values.Data);
 title('\textbf{Relative Yaw Angle (e$_2$) vs Time}','Interpreter','latex');
 xlabel('Time [s]','Interpreter','latex');
 ylabel('Relative Yaw Angle [rad]','Interpreter','latex');
-pos = get(h3,'Position');
-set(h3,'PaperPositionMode','Auto','PaperUnits','Points','PaperSize',[pos(3), pos(4)-40])
+pos3 = get(h3,'Position');
+set(h3,'PaperPositionMode','Auto','PaperUnits','Points','PaperSize',[pos3(3), pos3(4)-40])
 print(h3,'figure\RelativeYawAngleVsTime','-dpdf','-r0')
 hold off
 pause(2)
[…]

### 2019-01-30 MATLAB/three_obstacles_no_overtaking/main_three_obstacles_no_overtaking.m

@@ -38,7 +38,7 @@ for i=1:N
     obstacle(i).length = 5;    % The obstacles in this example are moving cars 
     obstacle(i).width = 2;     % with the same size and shape of the ATLASCAR2
 
-    obstacle(i).X = 33+3*i;      % Initial positions of the N obstacles   
+    obstacle(i).X = 33+3;      % Initial positions of the N obstacles   
     obstacle(i).Y =-10+5*i; % (in this example the obstacles are DYNAMIC)    
     
     obstacle(i).safeDistanceX = obstacle(i).length;    % Length equal to two car lengths
@@ -161,7 +161,7 @@ for k = 1:length(T)
     % Create Obstacle Dynamics
     for i=1:N 
         obstacle(i).X(k+1) = obstacle(i).X(k)+obstacle(i).space;
-        obstacle(1).X(k+1) = obstacle(1).X(k)+0.28;
+        obstacle(3).X(k+1) = obstacle(3).X(k)+0.3;
         % Safe zones for the plot
         flSafeX(k,i) = obstacle(i).X(k)+obstacle(i).safeDistanceX;
         frSafeX(k,i) = obstacle(i).X(k)+obstacle(i).safeDistanceX;
@@ -219,7 +219,7 @@ plot(ympc(:,1),ympc(:,2),'-b');
 for k = 1:length(saveSlope) 
     hold on 
     grid on
-    grid minor
+    %grid minor
     
     % ATLASCAR2 green rectangle
     p = patch([ympc(k,1)-car.length/2 ympc(k,1)-car.length/2 ympc(k,1)+car.length/2 ympc(k,1)+car.length/2], [ympc(k,2)-car.width/2, ympc(k,2)+car.width/2, ympc(k,2)+car.width/2, ympc(k,2)-car.width/2], [0 1 0]);
@@ -236,7 +236,7 @@ for k = 1:length(saveSlope)
     
    %  frame = getframe(gcf);
    %  writeVideo(writerObj, frame);
-    
+      % print('figure\braking_4','-dpdf','-r0')
     pause(80/car.V/length(T))
     delete(p)
     for i=1:N

### 2019-01-30 MATLAB/three_obstacles_no_overtaking/obstaclePlotInitialCondition.m

@@ -10,7 +10,7 @@ Y0 = car.x0(2);
 plot(X0,Y0,'gx');
 hold on 
 grid on
-grid minor
+%grid minor
 axis equal
 
 % ATLASCAR2 initialization

### 2019-02-01 Thesis_Latex/Paper/Paper.tex
update full version Paper

@@
 \section{Introduction}
-In robotic research, the problem of navigation is among the most important. Basically all autonomous mobile robots need some kind of navigation to fulfill the mobile term.
-We understand navigation as a process of planning a path of a mobile robot from its current position to a desired goal location, following the planned path, and avoiding any discovered obstacles along the way.
+In robotic research, the problem of navigation is among the most important. Basically all autonomous mobile robots need some kind of navigation to fulfill the mobile term \cite{skoda}.
+We understand navigation as a process of planning a path of a mobile robot from its current position to a desired goal location, following the planned path, and avoiding any discovered obstacles along the way \cite{fuzzyMPC}, \cite{NONMPC}.
 The desired paths have to
-fulfill several conditions to ensure safety and feasibility of the navigation.
+fulfill several conditions to ensure safety and feasibility of the navigation \cite{safety}.
 Moreover, the paths can be also compared in terms of desirability for example short or smooth paths are usually more desirable than long and curved ones.
-Such paths should therefore be preferred in the navigation process.
+Such paths should therefore be preferred in the navigation process \cite{archi}.
 Beyond the path planning, the navigation problem also involves reacting to changes of the environment model.
-Robots are required to move towards target in a short time and avoid either static or dynamic obstacles observed by their sensors, which involves efficient path planning and valid obstacle avoidance.
+Robots are required to move towards target in a short time and avoid either static or dynamic obstacles observed by their sensors, which involves efficient path planning and valid obstacle avoidance \cite{MMPC}, \cite{autoMPC}, \cite{borelli}.
 Though these two topics have been well researched, currently, there is no ideal solution to handling the navigation problem within cluttered dynamic environments.
+The proposed algorithms were studied for the ATLASCAR project in which the group for Robotics and Automation at the University of Aveiro, has setup and adapted a common commercial vehicle to provide a versatile  framework  to  develop  studies  and  research
+\cite{atlas}, \cite{atlascar1}, \cite{atlascar2}.
 \section{Context of the Problem and \\  Proposed Solution}
@@
 \begin{thebibliography}{00}
+
+	\bibitem{skoda}J. Škoda, ‘3D Navigation for Mobile Robots’, Dissertation, 2017.
+
+	\bibitem{fuzzyMPC}Y.
+Nishio, K.
+Nonaka and K.
+Sekiguchi, "Moving obstacle avoidance control by fuzzy potential method and model predictive control," 2017 11th Asian Control Conference (ASCC), Gold Coast, QLD, 2017, pp.
+1298-1303.
+
+	\bibitem{NONMPC}Yu, S., Li, X., Chen, H. and Allgöwer, F. (2015), "Nonlinear model predictive control for path following problems". Int. J. Robust Nonlinear Control, 25: 1168–1182.
+
+	\bibitem{safety}T. Xu and H. Yuan, "Autonomous vehicle active safety system based on path planning and predictive control," 2016 35th Chinese Control Conference (CCC), Chengdu, 2016, pp. 8889-8895.
+
+	\bibitem{archi}M.
+Nolte, M.
+Rose, T.
+Stolte and M.
+Maurer, "Model predictive control based trajectory generation for autonomous vehicles — An architectural approach," 2017 IEEE Intelligent Vehicles Symposium (IV), Los Angeles, CA, 2017, pp.
+798-805.
+
 	\bibitem{MMPC}J.
@@
 
+	\bibitem{autoMPC}J.
+V.
+Frasch et al., "An auto-generated nonlinear MPC algorithm for real-time obstacle avoidance of ground vehicles," 2013 European Control Conference (ECC), Zurich, 2013, pp.
+4136-4141.
+
+	\bibitem{borelli}V.
+Turri, A.
+Carvalho, H.
+E.
+Tseng, K.
+H.
+Johansson and F.
+Borrelli, "Linear model predictive control for lane keeping and obstacle avoidance on low curvature roads," 16th International IEEE Conference on Intelligent Transportation Systems (ITSC 2013), The Hague, 2013, pp.
+378-383.
+
+	\bibitem{atlas}ATLAS  Project,  Aveiro  University, Portugal, \url{http://atlas.web.ua.pt/}, last visited July 2010.
+
+	\bibitem{atlascar1}V.
+Santos et al., "ATLASCAR - technologies for a computer assisted driving system on board a common automobile", 13th International IEEE Conference on Intelligent Transportation Systems, Funchal, 2010, pp.
+1421-1427.
+
+	\bibitem{atlascar2}V. Santos, "ATLASCAR: A Sample of the Quests and Concerns for Autonomous Cars", 14th International Conference, ICINCO 2017 Madrid, 2017.
+
 	\bibitem{onlineMPC}M.
@@
 
-	\bibitem{autoMPC}J.
-V.
-Frasch et al., "An auto-generated nonlinear MPC algorithm for real-time obstacle avoidance of ground vehicles," 2013 European Control Conference (ECC), Zurich, 2013, pp.
-4136-4141.
-
 	\bibitem{long_tf}Y. Wang, Y. Bin and K. Li, "Longitudinal acceleration tracking control of low speed heavy-duty vehicles," in Tsinghua Science and Technology, vol. 13, no. 5, pp. 636-643, Oct. 2008.
-
-	\bibitem{safety}T. Xu and H. Yuan, "Autonomous vehicle active safety system based on path planning and predictive control," 2016 35th Chinese Control Conference (CCC), Chengdu, 2016, pp. 8889-8895.
-
-	\bibitem{matsumoto}N.
-Wada and T.
-Matsumoto, "Driver assistance for collision avoidance by constrained MPC," 2017 56th Annual Conference of the Society of Instrument and Control Engineers of Japan (SICE), Kanazawa, 2017, pp.
-90-93.
-
-	\bibitem{rathai}Murali Madhavan Rathai, Karthik \& Amirthalingam, Jegan \& Jayaraman, Balaji. (2017). Robust tube-MPC based lane keeping system for autonomous driving vehicles. 1-6.
-
-	\bibitem{fuzzyMPC}Y.
-Nishio, K.
-Nonaka and K.
-Sekiguchi, "Moving obstacle avoidance control by fuzzy potential method and model predictive control," 2017 11th Asian Control Conference (ASCC), Gold Coast, QLD, 2017, pp.
-1298-1303.
-
-	\bibitem{NONMPC}Yu, S., Li, X., Chen, H. and Allgöwer, F. (2015), "Nonlinear model predictive control for path following problems". Int. J. Robust Nonlinear Control, 25: 1168–1182.
 
@@
 1771-1774.
-
-	\bibitem{archi}M.
-Nolte, M.
-Rose, T.
-Stolte and M.
-Maurer, "Model predictive control based trajectory generation for autonomous vehicles — An architectural approach," 2017 IEEE Intelligent Vehicles Symposium (IV), Los Angeles, CA, 2017, pp.
-798-805.
 
@@
 
+	\bibitem{rathai}Murali Madhavan Rathai, Karthik \& Amirthalingam, Jegan \& Jayaraman, Balaji. (2017). Robust tube-MPC based lane keeping system for autonomous driving vehicles. 1-6.
+
 	\bibitem{kth_nordell}B. Nordell, ‘Trajectory Planning for Autonomous Vehicles and Cooperative Driving’, Dissertation, 2016.
@@
 
-	\bibitem{borelli}V.
-Turri, A.
-Carvalho, H.
-E.
-Tseng, K.
-H.
-Johansson and F.
-Borrelli, "Linear model predictive control for lane keeping and obstacle avoidance on low curvature roads," 16th International IEEE Conference on Intelligent Transportation Systems (ITSC 2013), The Hague, 2013, pp.
-378-383.
+		\bibitem{matsumoto}N.
+Wada and T.
+Matsumoto, "Driver assistance for collision avoidance by constrained MPC," 2017 56th Annual Conference of the Society of Instrument and Control Engineers of Japan (SICE), Kanazawa, 2017, pp.
+90-93.
+
 \end{thebibliography}

### 2019-02-01 MATLAB/lane_following_curve/LaneFollowingGetCurvature.m

@@ -1,4 +1,4 @@
-function rho = LaneFollowingGetCurvature(Vx,time)
+function [rho, Yref] = LaneFollowingGetCurvature(Vx,time)
 % Get previewed curvature from desired X and Y positions for LKA
 %
 % Inputs:
@@ -13,13 +13,12 @@ Xref = Vx*time;
 % % Desired Y position
 z1 = (2.4/50)*(Xref-27.19)-1.2;
 z2 = (2.4/43.9)*(Xref-56.46)-1.2;
-Yref = 8.1/2*(1+tanh(z1)) - 8.4/2*(1+tanh(z2))
+Yref = 8.1/2*(1+tanh(z1)) - 8.4/2*(1+tanh(z2));
 h = figure ('Position',[100, 100, 340, 230], 'PaperPositionMode','auto');
 plot(Xref,Yref)
 hold on
 grid on
 grid minor
-axis equal
 title('\textbf{Desired Path}','Interpreter','latex');
 xlabel('X-coordinate [m]','Interpreter','latex');
 ylabel('Y-coordinate [m]','Interpreter','latex');

### 2019-02-01 MATLAB/lane_following_curve/LaneFollowingResults.m

@@ -1,4 +1,4 @@
-function LaneFollowingResults(logsout)
+function LaneFollowingResults(logsout,Yref)
 % Plot results for adaptive MPC. 
 
 %% Get the data from simulation
@@ -79,8 +79,9 @@ pos = get(h5,'Position');
 set(h5,'PaperPositionMode','Auto','PaperUnits','Points','PaperSize',[pos(3), pos(4)-40])
 print(h5,'figure\LongitudinalVelocityVsTime_curve','-dpdf','-r0')
 hold off
+
 %% Local function: Get data from simulation
-function [e1,e2,delta,accel,vx,vy,xp,yp] = getData(logsout)
+function [e1,e2,delta,accel,vx,vy] = getData(logsout)
 e1 = logsout.getElement('Lateral Deviation');    % lateral deviation
 e2 = logsout.getElement('Relative Yaw Angle');   % relative yaw angle
 delta = logsout.getElement('Steering');          % steering angle

### 2019-02-01 MATLAB/lane_following_curve/main_lane_following_curve.m

@@ -24,9 +24,9 @@ v_set = 20; % Driver set velocity
 Ts = 0.02;
 
 % Obtain the lane curvature information seconds.
-Duration = 20;                              % Simulation duration
+Duration = 10;                              % Simulation duration
 t = 0:Ts:Duration;                          % Time vector
-rho = LaneFollowingGetCurvature(v_set,t);   % Signal containing curvature information
+[rho,Yref] = LaneFollowingGetCurvature(v_set,t);   % Signal containing curvature information
 
 %% Design Adaptive Model Predictive Controller 
 % This controller uses a linear model for the vehicle dynamics and updates
@@ -40,6 +40,6 @@ LaneFollowingGenerateAMPC;
 % function |LaneFollowingResults|
 sim(mdl)
 logsout1 = logsout;
-LaneFollowingResults(logsout1)
+LaneFollowingResults(logsout1,Yref)
 print -slane_following_AMPC -dpdf lane_following_AMPC.pdf
 movefile('lane_following_AMPC.pdf','figure')

### 2019-02-01 MATLAB/path planning/main_path_planning.m

@@ -1,0 +1,199 @@
+clear all
+close all
+clc
+
+%% ATLASCAR2 - Moving Obstacle Avoidance based on MPC
+
+car = struct;
+road = struct;
+obstacle = struct;
+
+%% Vehicle model
+
+% Parameters definition
+car.length = 5;                 % Length of the ATLASCAR2
+car.width = 2;                  % Witdh of the ATLASCAR2
+car.V = 20;                     % Constant speed of the ATLASCAR2
+car.x0 = [150; -20; pi/2; car.V];      % Initial conditions
+car.u0 = [0; 0];
+Ts = 0.02;                      % Sampling time
+
+% Obtain a linear plant model at the nominal operating point and convert it
+% into a discrete-time model to be used by the model predictive controller.
+[Ad,Bd,Cd,Dd,U,Y,X,DX] = ATLASCAR2ModelDT(Ts,car.x0,car.u0);
+
+dsys = ss(Ad,Bd,Cd,Dd,'Ts',Ts);          % State space
+dsys.InputName = {'Throttle','Delta'};   % Input u
+dsys.StateName = {'X','Y','Theta','V'};  % State x
+dsys.OutputName = dsys.StateName;        % Output y   
+
+%% Plot initial condition
+
+% ATLASCAR2 - Green with black boundary
+% Horizontal lanes - Dashed black lines
+% Obstacle/Car - Red with with black boundary
+% Safe zone - Dashed red boundary.
+
+f = obstaclePlotInitialCondition(car, obstacle, road);
+
+%% MPC design
+
+% MPC object: sampling time Ts, Prediction Horizon 10, Control Horizon 2
+status = mpcverbosity('off');
+mpcobj = mpc(dsys);
+
+% Set the values of the prediction horizon and the control horizon
+mpcobj.PredictionHorizon = 25;   % number of steps = 0.5 seconds
+mpcobj.ControlHorizon = 5;
+
+%% Constraints and Weights
+% To prevent the ATLASCAR2 from accelerating or decelerating too quickly, 
+% add a hard constraint of 0.2 (m^2/sec) on the throttle rate of change.
+%mpcobj.ManipulatedVariables(1).RateMin = -0.2; 
+%mpcobj.ManipulatedVariables(1).RateMax = 0.2;
+  
+% add a hard constraint of 6 degrees per sec on the steering angle rate of change.
[…]

### 2019-02-01 MATLAB/path planning/obstacleComputeCustomConstraint.m

@@ -1,0 +1,43 @@
+function [E,F,G,constraintSlope,constraintIntercept] = obstacleComputeCustomConstraint(x,detection,obstacle,laneWidth,lanes)
+%% Compute custom constraints for the obstacle.
+
+carX = x(1);
+carY = x(2);
+
+% Compute constraints only if an obstacle is detected. Otherwsie, set
+% constraint to lower road boundary (the inactive constraint).
+if detection
+    slope = ( (obstacle.rlSafeY - carY)/(obstacle.rlSafeX - carX) );
+    % If ATLASCAR2 is to the left of the obstacle
+    if (carX<=obstacle.rlSafeX)
+        % if the ATLASCAR2 is already in the adjacent lane, use the safety
+        % zone as the constraint.
+        if (carY>obstacle.rlSafeY)
+            constraintSlope = 0;
+            constraintIntercept = obstacle.rlSafeY;
+        else
+            % The ATLASCAR2 must be above the line formed from the ATLASCAR2 to
+            % safe zone corner for left passing.
+            constraintSlope = tan(atan2(slope,1));
+            constraintIntercept = obstacle.rlSafeY - constraintSlope*obstacle.rlSafeX;
+        end
+    % If the ATLASCAR2 is parallel to the obstacle, use the safety zone as
+    % the constraint.
+    elseif ( (carX>obstacle.rlSafeX) && (carX<=obstacle.flX) )
+        constraintSlope = 0;
+        constraintIntercept = obstacle.rlSafeY; 
+    % If the ATLASCAR2 has passed the obstacle, use the inactive constraint
+    % to go back to the center lane.
+    else 
+        constraintSlope = 0;
+        constraintIntercept = -laneWidth*lanes/2;
+    end
+else
+    constraintSlope = 0;
+    constraintIntercept = -laneWidth*lanes/2;
+end
+
+%% Define constraint matrices.
+E = [0 0;0 0;0 0];
+F = [0 1 0 0;0 -1 0 0;constraintSlope -1 0 0]; 
+G = [laneWidth*lanes/2;laneWidth*lanes/2;-1*constraintIntercept];

### 2019-02-01 MATLAB/path planning/obstaclePlotInitialCondition.m

@@ -1,0 +1,28 @@
+function f = obstaclePlotInitialCondition(car,obstacle,road)
+
+% Create figure
+
+f = figure;
+
+% Plot the ATLASCAR2
+
+X0 = car.x0(1);
+Y0 = car.x0(2);
+plot(X0,Y0,'gx'); 
+hold on 
+grid on
+grid minor
+p = patch([X0-car.length/2 X0-car.length/2 X0+car.length/2 X0+car.length/2], [Y0-car.width/2, Y0+car.width/2, Y0+car.width/2, Y0-car.width/2], [0 1 0]); 
+%rectangle('Position',[X0-car.length/2,Y0 - car.width/2,car.length,car.width],'FaceColor',[0 1 0],'Curvature',0.2,'LineStyle','-','LineWidth', 1.2, 'EdgeColor','k');
+axis equal
+
+%,'EdgeColor','[1 0 0]','LineStyle','--'
+delete(p)
+
+% Reset the axis.
+axis([-155 155 -330 330]);
+xlabel('X');
+ylabel('Y');
+title('ATLASCAR2 Moving Obstacle Avoidance');
+
+

### 2019-02-04 Thesis_Latex/Paper/PaperFinalVersion.tex
update full version Paper

--- 2019-02-01 Thesis_Latex/Paper/Paper.tex
@@
 \usepackage[utf8x]{inputenc}
-
+\usepackage{float}
 \usepackage{bbm}
@@
 \newtheorem{cor}[thm]{Cor.}
-
+\renewcommand\IEEEkeywordsname{Keywords}
 \def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
@@
 
-\title{Advanced Methods for short-term Path Planning in Autonomous Driving based on Adaptive MPC}
-\author{\IEEEauthorblockN{Alberto Franco}\\
-\IEEEauthorblockA{Department of Information Engineering\\
-Università degli Studi di Padova\\ \href{mailto:alberto.franco.3@studenti.unipd.it}{alberto.franco.3@studenti.unipd.it}}}
+\title{Short-term Path Planning with Collision Avoidance in Autonomous Driving based on Adaptive MPC}
+\author{
+	\IEEEauthorblockN{Alberto Franco}
+	\IEEEauthorblockA{Department of Information Engineering,\\ Università degli Studi di Padova, Italy\\		 \href{mailto:alberto.franco.3@studenti.unipd.it}{alberto.franco.3@studenti.unipd.it}\\
+	\href{mailto:alberto.franco@ua.pt}{alberto.franco@ua.pt}}
+	\and
+	\IEEEauthorblockN{Vitor Santos}
+	\IEEEauthorblockA{Department of Mechanical Engineering,\\ IEETA, Universidade de Aveiro, Portugal\\ \href{mailto:vitor@ua.pt}{vitor@ua.pt}}}
 
@@
 \begin{abstract}
-	In this paper we present two different strategies for a self-driving car short-term path planning.
+	In this paper we present a different strategy for a self-driving car short-term path planning in space-based approach.
 The aim of this project is to study and implement a path tracking framework in order to prevent ATLASCAR2 collision with moving obstacle vehicles.
-The proposed algorithms, based on the Model Predictive Control paradigm, solve optimal problems formulated in terms of cost minimization under constraints.
+The proposed algorithm, based on the Model Predictive Control paradigm, solves an optimal problem formulated in terms of cost minimization under constraints.
+Results demonstrate and verifies the feasibility and the usefulness of the method considering different scenarios.
 \end{abstract}
+
+\begin{IEEEkeywords}
+	autonomous driving, Model Predictive Control, obstacle avoidance.
+\end{IEEEkeywords}
+
 \section{Introduction}
-In robotic research, the problem of navigation is among the most important. Basically all autonomous mobile robots need some kind of navigation to fulfill the mobile term \cite{skoda}.
-We understand navigation as a process of planning a path of a mobile robot from its current position to a desired goal location, following the planned path, and avoiding any discovered obstacles along the way \cite{fuzzyMPC}, \cite{NONMPC}.
-The desired paths have to
-fulfill several conditions to ensure safety and feasibility of the navigation \cite{safety}.
-Moreover, the paths can be also compared in terms of desirability for example short or smooth paths are usually more desirable than long and curved ones.
+In robotic research, the problem of navigation is among the most important. Basically, all autonomous mobile robots need some kind of navigation to fulfill the mobile term \cite{skoda}.
+We understand navigation as a process of planning a path of a mobile robot from its current position to a desired goal location, following the planned path, and avoiding any discovered obstacles along the way \cite{fuzzyMPC} \cite{NONMPC}.
+The desired paths have to fulfill several conditions to ensure safety and feasibility of the navigation \cite{safety}.
+Moreover, the paths can be also compared in terms of specifications for example short or smooth paths are usually more desirable than long and curved ones.
 Such paths should therefore be preferred in the navigation process \cite{archi}.
 Beyond the path planning, the navigation problem also involves reacting to changes of the environment model.
-Robots are required to move towards target in a short time and avoid either static or dynamic obstacles observed by their sensors, which involves efficient path planning and valid obstacle avoidance \cite{MMPC}, \cite{autoMPC}, \cite{borelli}.
+Robots are required to move towards the target in a short time and avoid either static or dynamic obstacles observed by their sensors, which involves efficient path planning and valid obstacle avoidance \cite{MMPC} \cite{autoMPC} \cite{borelli}.
 Though these two topics have been well researched, currently, there is no ideal solution to handling the navigation problem within cluttered dynamic environments.
-The proposed algorithms were studied for the ATLASCAR project in which the group for Robotics and Automation at the University of Aveiro, has setup and adapted a common commercial vehicle to provide a versatile  framework  to  develop  studies  and  research
-\cite{atlas}, \cite{atlascar1}, \cite{atlascar2}.
 \section{Context of the Problem and \\  Proposed Solution}
+The proposed algorithm was studied for the ATLASCAR project in which the group for Robotics and Automation at the University of Aveiro, has setup and adapted a common commercial vehicle to provide a versatile  framework  to  develop  studies  and  research \cite{atlas} \cite{atlascar1} \cite{atlascar2}.
+In Fig.\ref{fig:atlascar2} is reported the chosen platform which is an electric car, a Mitsubishii-MiEV of 2015 with a range of a $100$km.
+The fact that the vehicle is electric allows to use the energy stored in the batteries, making it easier to power the sensors installed.
+\begin{figure}[H]
+	\centering
+	\includegraphics[width=0.70\columnwidth]{./figure/atlascar2.jpg}
+	\vspace{-12pt}
+	\caption{ATLASCAR2, based on an electric car, a Mitsubishii-MiEV}
+	\label{fig:atlascar2}
+\end{figure}
+
 The ATLACAR2 has sensors, such as lidar, that measure the distance to obstacles in front and around the vehicle.
@@
 This system uses an adaptive Model Predictive Controller that updates both the predictive model and the mixed input/output constraints at each control interval.
-Moreover, this vehicle is also equipped with a lane-keeping assist system: it has a sensor, such as camera or laser, that measures the lateral deviation and relative yaw angle between the centerline of a lane and the ATLASCAR2; it also measures the current lane curvature and its derivative.
-Depending on the curve length that the sensor can view, the curvature in front of the vehicle can be calculated from the current curvature and its derivative.
-This system keeps the autonomous car travelling along the centerline of the lanes on the road by adjusting the front steering angle.
-The goal for lane keeping control is to drive both lateral deviation and relative yaw angle close to zero.
-\subsection{Theoretical background - Adaptive MPC}
+\section{Theoretical background\\ Adaptive Model Predictive Control}
 Model Predictive Control is an advanced method that predicts future behavior using a linear-time-invariant (LTI) dynamic model.
 These predictions are never exact and a good strategy is to make MPC insensitive to prediction errors.
-If the plant is strongly nonlinear or its characteristics vary dramatically with time, MPC performance might become unacceptable because LTI prediction accuracy degrade.
+If the plant is strongly nonlinear or its characteristics vary dramatically with time, MPC performance might become unacceptable because LTI prediction accuracy degrade \cite{mpctoolbox}.
 A method that can address this degradation by adapting the prediction model for changing operating conditions is called Adaptive MPC: this control strategy uses a fixed model structure, but allows the model parameters to evolve with time.
@@
 The plant model used as the basis for the adaptive MPC must be an LTI discrete-time, state-space model with a structure as follows:
-\begin{equation*}
+\begin{equation}
 \label{eqn:Adaptive_MPC_plant_discrete}
@@
 \end{aligned}
-\end{equation*}
-where the matrices $A$, $B_u$, $B_v$, $B_d$, $C$, $D_v$ and $D_d$ can vary with time. The other parameters in the expression are:
+\end{equation}
+where the matrices $A$, $B_u$, $B_v$, $B_d$, $C$, $D_v$ and $D_d$ can vary with time. The other parameters in (\ref{eqn:Adaptive_MPC_plant_discrete}) are:
 \begin{itemize}
@@
 	\item $d$ are the unmeasured disturbance inputs;
-	\item $y$ are the plant outputs, including both measured and unmeasured. Is it necessary at least one measured output.
+	\item $y$ are the plant outputs, including both measured (necessary at least one) and unmeasured.
 \end{itemize}
-In the adaptive MPC control there are additional requirements for the plant model as the sample time $T_s$ that has to be constant and identical to the MPC control interval.
+In the adaptive MPC control, there are additional requirements for the plant model, like the sample time $T_s$ that has to be constant and identical to the MPC control interval.
 This control strategy prohibits direct feed-through from any manipulated variable to any plant output.
 Thus, $D_u = 0$ in the above model.
-Finally the input and output signal configuration remains constant.
-A traditional MPC controller includes a nominal operating point at which the plant model applies, such as the condition at which you linearize a nonlinear model to obtain the LTI approximation.
+A traditional MPC controller includes a nominal operating point at which the plant model applies, such as the condition at which you linearize a nonlinear model to obtain the LTI approximation (equilibrium, reference trajectory and the
+most updated value) \cite{mpctoolbox}.
 In adaptive MPC, as time evolves you should update the nominal operating point to be consistent with the updated plant model.
 It is possible to rewrite the plant model in terms of deviations from the nominal conditions:
-\begin{equation*}
+\begin{equation}
 \label{eqn:Adaptive_MPC_nominal_condition}
@@
 \end{aligned}
-\end{equation*}
-where the matrices $A$, $B$, $C$ and $D$ are updated with respect to time. The other parameters in the expression are:
+\end{equation}
+where the matrices $A$, $B$, $C$ and $D$ are updated with respect to time. The other parameters in (\ref{eqn:Adaptive_MPC_nominal_condition}) are:
 \begin{itemize}
@@
 \end{itemize} 
-The adaptive MPC uses a Kalman filter to update its controller states and adjusts the two required gain matrices, $L$ and $M$, at each control interval to maintain consistency with the updated plant model.
-We are considering a linear-time-varying Kalman filter (LTVKF):
-\begin{equation*}
-\label{eqn:LTVKF}
-\begin{array}{lll}
-L_k=\big(A_kP_{k|k-1}C_{m,k}^{T}+N\big)\big(C_{m,k}P_{k|k-1}C_{m,k}^{T}+R\big)^{-1}\\
-M_k =P_{k|k-1}C_{m,k}^{T}\big(C_{m,k}P_{k|k-1}C_{m,k}^{T}+R\big)^{-1}\\
-P_{k+1|k}=A_kP_{k|k-1}A_k^{T}-\big(A_kP_{k|k-1}C_{m,k}^{T}+N\big)L_k^{T}+Q.
-\end{array}
-\end{equation*}
-where 
-\begin{itemize}
- \item $Q$, $R$ and $N$ are constant covariance matrices defined as in MPC state estimation;
- \item $A_k$ and $C_{m,k}$ are state-space parameter matrices for the entire controller state;
- \item $P_{k|k-1}$ is the state estimate error covariance matrix at time $k$ based on the information available at time $k-1$;
- \item $L_k$ and $M_k$ are the updated Kalmen filter gain matrices.
-\end{itemize}
-The gain and the state error covariance matrix depend upon the model parameters
-and the assumptions leading to the constant $Q$, $R$ and $N$ matrices.
-\section{Obstacle Avoidance}
+The adaptive MPC uses a Kalman filter to update its controller states which include the plant, the disturbance and measurement noise model states.
+\section{Moving Obstacle Avoidance}
 \subsection{Problem Formulation}
 The collision avoidance problem is very dependent on the vehicle modeling since it is a requirement for  adaptive MPC law design.
-\begin{figure}[!h]
+In Fig.\ref{fig:obstacleAvoidance} is depicted a typical scenario of overtaking of a moving obstacle.
+\begin{figure}[H]
 	\centering
 	\includegraphics[width=1\columnwidth]{./figure/obstacleAvoidance/obstacleAvoidance.pdf}
+	\vspace{-25pt}
 	\caption{Problem description of collision avoidance on road.}
@@
 \end{figure}
+
 The model used in this paper should take into account the kinematic and dynamic aspects of the vehicle.
@@
 \]
-where $(x,y)$ are the global coordinates of the center point of the car, $\theta$ is the heading angle of the car body with respect to the $x$-axis and $v$ is the speed of the car (positive).
+where $(x,y)$ are the global coordinates of the center point of the car, $\theta$ is the heading angle of the car body with respect to the $x$-axis and $v$ is the linear speed of the car (positive).
 The manipulated variables are $T$ the throttle (positive when accelerating/negative when braking) and $\delta$ the steering angle ($0$ when aligned with car, counterclockwise positive).
+Fig.\ref{fig:car_model} shows a schematic sketch of the applied nonlinear bicycle model and the related parameters.
 \begin{figure}[!h]
@@
 	\includegraphics[width=0.70\columnwidth]{./figure/car_model.pdf}
+	\vspace{-12pt}
 	\caption{Bicycle model of a car.}
@@
 \end{figure}
-The ATLASCAR2 can be modeled using the non-linear kinematic bicycle model described by the following equations of motion:
+
+The ATLASCAR2 can be modeled using the non-linear kinematic bicycle model described by the following equations of motion \cite{safety} \cite{swarms}:
 \begin{equation*}
@@
 In order to simplify the model, it is assumed that only the front wheel can be steered.
-Moreover, in this paper it is assumed that the ATLASCAR2 does not slip, any slippage is thus considered as an external disturbance.
+Moreover, in this paper it is assumed that the ATLASCAR2 does not slip, so any slippage is thus considered as an external disturbance.
 Under this assumption, the slip angle is zero, meaning that the velocity is directed along the heading of the vehicle.
-In order to use MPC, the state space model needs to be linearized and also re-written in a more compact form:
+In order to use MPC, the state space model needs to be linearized with a first order approximation and also re-written in a more compact form:
 \begin{equation}
@@
 \]
-The simple linearized approximation of the system to describe the dynamics of the ATLASCAR2 will be evaluated at the operating conditions; the extended form of the considered model is the following:
-\begin{equation*}
-	\label{eqn:dynamics_model_obstacle_avoidance_linearized}
-	\left \{ \begin{array}{llll}
-	\dot{x} = -v\sin(\theta)\cdot\theta+\cos(\theta)\cdot v\\
-	\dot{y} = v\cos(\theta)\cdot\theta+\sin(\theta)\cdot v\\
-	\dot{\theta} =(\tan(\delta)/C_L)\cdot v+ \bigg(v\bigg(\tan(\delta)^2+1\bigg)/C_L\bigg)\cdot \delta\\
-	\dot{v} =0.5\cdot T
-	\end{array} 
-	\right .
-\end{equation*}
-The system to be controlled is usually modeled by a discrete state-space model in the MPC literature. Therefore, (\ref{eqn:dynamics_model_non_linear})
+The simple linearized approximation of the system to describe the dynamics of the ATLASCAR2 will be evaluated at the operating conditions.
+The system to be controlled is usually modeled by a discrete state-space model in the MPC literature.
+Therefore, (\ref{eqn:dynamics_model_non_linear})
 is transformed into a discrete state-space model to be used by the Model Predictive Controller:
@@
 \end{equation*}
-where $A_d$ and $B d$ are the state and control matrices for the discrete state-space equation, respectively, which can be calculated with the Euler method as
+where $A_d$ and $B_d$ are the state and control matrices for the discrete state-space equation, respectively, which can be calculated with the Euler method as
 \[
@@
 \subsection{Design of Adaptive Model Predictive Control}
-We designed a Model Predictive Controller that can make the ATLASCAR2 mantain a desired velocity of and stay in the middle of center lane.
+We designed a Model Predictive Controller that can make the ATLASCAR2 mantain a desired velocity and stay in the middle of center lane.
 We used an Adaptive MPC controller because it handles the nonlinear vehicle dynamics more effectively than a traditional MPC controller; in fact, the latter uses a constant plant model but the former allows us to provide a new plant model at each control interval.
 Because the new model describes the plant dynamics more accurately at the new operating condition, an adaptive MPC controller performs better than a traditional MPC controller.
-In practice at each control interval, the adaptive MPC controller updates the plant model and the nominal conditions.
+In practice, at each control interval, the adaptive MPC controller updates the plant model and the nominal conditions.
 Once updated, the model and the conditions remain constant over the prediction horizon.
-In path tracking using adaptive MPC, it is common to formulate the constrained control problem as a real-time optimization problem subject to hard constraints on plant variables and soft constraints on outputs; at the beginning, we specified the constraints for the manipulated variables: to prevent the ATLASCAR2 from accelerating or decelerating too quickly, we added an hard constraint on the throttle rate of change and another one on the steering angle rate of change.
+In motion planning using adaptive MPC, it is common to formulate the constrained control problem as a real-time optimization problem subject to hard constraints on plant variables and soft constraints on outputs; at the beginning, we specified the constraints for the manipulated variables: to prevent the ATLASCAR2 from accelerating or decelerating too quickly, we added an hard constraint on the throttle rate of change and another one on the steering angle rate of change.
 We used an approach that takes advantage of the ability of MPC to handle constraint explicitly.
+In Fig.\ref{fig:flowchart} is depicted a conditional state machine designed for higher-level behavior planning:
+\begin{figure}[H]
+	\centering
+	\includegraphics[width=1\columnwidth]{./figure/flowchart/flowchart.pdf}
+	\vspace{-20pt}
+	\caption{Behaviour planning conditional flowchart.}
+	\label{fig:flowchart}
+\end{figure}
+
 When an obstacle is detected, it defines an area on the road (in terms of constraints) that the ATLASCAR2 must not enter during the prediction horizon.
@@
 \begin{itemize}
-	\item the first constraint is an upper bound on the $y$-coordinate (right boundary of the road);
-	\item the second constraint is a lower bound on the $y$-coordinate (left boundary of the road);
-	\item the third constraint is for the obstacle avoidance; even though no obstacle is detected at the nominal condition, we must add this fake constraint here because we cannot change the dimensions of the constraint matrices at run time (it has the same form as the second one);
+	\item the first constraint is an upper bound on the $y$-coordinate (left boundary of the road);
+	\item the second constraint is a lower bound on the $y$-coordinate (right boundary of the road);
+	\item the third constraint is for the obstacle avoidance; even though no obstacle is detected at the nominal condition, we must add this fake constraint here because we cannot change the dimensions of the constraint matrices at run time;
 	\item the fourth constraint is an upper bound on the $x$-coordinate (the position of the closest obstacle);
@@
 where $W$ is the width of the road, $cI$ and $cS$ are the required parameters such that the ATLASCAR2 must be above the line formed from the vehicle to safe zone corner for left/right passing and finally $x_{\max}$ represents the position of the closest obstacle while $x_{\min}$ depicts the location of our vehicle.
+Fig.\ref{fig:constraint} shows a schematic sketch of the constraints that are computed at each sampling time $T_s$ in the case of a left overtaking.
+\begin{figure}[H]
+	\centering
+	\includegraphics[width=1\columnwidth]{./figure/constraint/constraint.pdf}
+	\vspace{-20pt}
+	\caption{Constraints in the case of left overtaking.}
+	\label{fig:constraint}
+\end{figure}
 \subsection{Simulation Results}
@@
 In all simulations, the distance between the front and rear axles is $C_L=5$m and the witdh of the vehicle is $C_W=2$m.
-The saturation ranges of the control inputs are: the steering angle lies in $\big[-\frac{\pi}{30}, +\frac{\pi}{30}\big]$rad/sec while in order to prevent the ATLASCAR2 from accelerating or decelerating too quickly, we impose an hard constraint of 2.5m$^2$/sec on the throttle rate of change.
+The saturation ranges of the control inputs are: the steering angle lies in $\big[-\frac{\pi}{30}, +\frac{\pi}{30}\big]$rad/sec while in order to prevent the ATLASCAR2 from accelerating or decelerating too quickly, we impose an hard constraint of 2.5m/sec$^2$ on the throttle rate of change.
 Moreover we are using a constant reference signal for the velocity of $v=20$m/s ($\simeq72$km/h).
@@
 \subsubsection{One Moving Obstacle - Right Overtaking}
-In this first simulation we assumed that the road is straight and has 3 lanes each one 4 meters wide.
-Moreover the ATLASCAR2 drives in the middle of the center lane while the road is completely free and when there is an obstacle the vehicle passes it only using the right lane (the same simulation can be launched so that the car goes over to the left fast lane).
+In this first simulation
+(Fig.\ref{fig:obstacleAvoidance_one_obstacle}) we assumed that the road is straight and has 3 lanes of 4 meters wide each.
+Moreover the ATLASCAR2 drives in the middle of the center lane while the road is completely free and when there is an obstacle, the vehicle passes it only using the right lane (the same simulation can be launched so that the car goes over to the left fast lane).
 When the vehicle detects the obstacle, the constraints are computed: if the ATLASCAR2 is already in the adjacent lane, it uses the safety zone as the constraint, otherwise the vehicle must be above the line formed from the ATLASCAR2 to safe zone corner for right passing.
 If the vehicle is parallel to the obstacle, it  uses the safety zone as the constraint and finally if it has passed the obstacle, it uses the inactive constraint to go back to the center lane.
-In this first example the obstacle moves in the same direction as the vehicle.
-\begin{figure}[!h]
+In this example the obstacle moves in the same direction as the vehicle.
+\begin{figure}[H]
 	\centering
@@
 	\includegraphics[width=1\columnwidth]{../../MATLAB/one_obstacle_right_overtaking/figure/overtaking_paper/overtaking_start.pdf}
-	\label{fig:obstacleAvoidance_start}
 	\end{minipage}
@@
 	\includegraphics[width=1\columnwidth]{../../MATLAB/one_obstacle_right_overtaking/figure/overtaking_paper/overtaking_middle.pdf}
-	\label{fig:obstacleAvoidance_middle}
 	\end{minipage}
@@
 	\includegraphics[width=1\columnwidth]{../../MATLAB/one_obstacle_right_overtaking/figure/overtaking_paper/overtaking_middle_end.pdf}
-	\label{fig:obstacleAvoidance_middle_end}
 	\end{minipage}
@@
 	\includegraphics[width=1\columnwidth]{../../MATLAB/one_obstacle_right_overtaking/figure/overtaking_paper/overtaking_end.pdf}
-	\label{fig:obstacleAvoidance_end}
 	\end{minipage}
+	\vspace{-20pt}
 	\caption{Simulation of right overtaking with one moving obstacle}
+	\label{fig:obstacleAvoidance_one_obstacle}
 \end{figure}
 \subsubsection{Multiple Moving Obstacles}
-Consequently, additional obstacles were added to make the scenario more complex.
+Consequently, additional obstacles were added to make the scenario more complex (Fig.\ref{fig:obstacleAvoidance_random}).
 The vehicle is capable of overtaking the obstacles to the right or left depending on their positions with respect to the road.
-If the $y$-coordinate of the closest obstacle is greater than 0, then the vehicle overtakes to the right, while if the $y$-coordinate is less than 0 the overtaking takes place on the left lane.
+If the $y$-coordinate of the closest obstacle is greater than 0, then the vehicle overtakes to the right, while if the $y$-coordinate is less than 0, the overtaking takes place on the left lane.
 We also hypothesized that the obstacles move at a different speeds but that they are initially at a common distance.
 In case two obstacles are too close during the simulation and their distance is less than the detection range which is $30$m, the ATLASCAR2 perceives the objects as a single entity and adapts to the situation.
-In this case the obstacles drive in the wrong direction with respect to the ATLASCAR2 (but the same results can be verified in the same direction).
-\begin{figure}[!h]
+In this case the obstacles drive in the opposite direction with respect to the ATLASCAR2 (but the same results can be verified in the same direction).
+\begin{figure}[H]
 	\centering
@@
 	\includegraphics[width=1\columnwidth]{../../MATLAB/random_N_obstacles/figure/overtaking_random_2.pdf}
-	\label{fig:obstacleAvoidance_random_2}
 	\end{minipage}
@@
 	\includegraphics[width=1\columnwidth]{../../MATLAB/random_N_obstacles/figure/overtaking_random.pdf}
-	\label{fig:obstacleAvoidance_random}
 	\end{minipage}
@@
 	\includegraphics[width=1\columnwidth]{../../MATLAB/random_N_obstacles/figure/overtaking_random_1.pdf}
-	\label{fig:obstacleAvoidance_random_1}
 	\end{minipage}
+	\vspace{-20pt}
 	\caption{Simulations of overtaking with $N = 2,3,4$ moving obstacles}
+	\label{fig:obstacleAvoidance_random}
 \end{figure}
+
 \subsubsection{Vehicle Braking and Obstacles Overtaking}
 Finally we have improved the code related to the mixed Input/Output constraints so that in the case there are 3 obstacles that block the road and drive at a lower speed than the ATLASCAR2, the velocity of the vehicle decreases in order to prevent the collision.
-Here it is depicted a simulation in which there are the obstacles at the same $x$-coordinate.
+In Fig.\ref{fig:braking} is depicted a simulation in which there are the obstacles at the same $x$-coordinate.
 Two obstacles have a constant speed of $8$m/s while the one on the left lane has a velocity of $15$m/s.
+\begin{figure}[H]
+	\centering
+	\begin{minipage}[t]{\columnwidth}
+		\includegraphics[width=1\columnwidth]{../../MATLAB/three_obstacles_no_overtaking/figure/braking_0.pdf}
+	\end{minipage}
+	\begin{minipage}[t]{\columnwidth}
+		\includegraphics[width=1\columnwidth]{../../MATLAB/three_obstacles_no_overtaking/figure/braking_1.pdf}
+	\end{minipage}
+	\begin{minipage}[t]{\columnwidth}
+		\includegraphics[width=1\columnwidth]{../../MATLAB/three_obstacles_no_overtaking/figure/braking_2.pdf}
+	\end{minipage}
+	\begin{minipage}[t]{\columnwidth}
+		\includegraphics[width=1\columnwidth]{../../MATLAB/three_obstacles_no_overtaking/figure/braking_3.pdf}
+	\end{minipage}
+	\begin{minipage}[t]{\columnwidth}
+		\includegraphics[width=1\columnwidth]{../../MATLAB/three_obstacles_no_overtaking/figure/braking_4.pdf}
+	\end{minipage}
+	\begin{minipage}[t]{\columnwidth}
+		\includegraphics[width=1\columnwidth]{../../MATLAB/three_obstacles_no_overtaking/figure/braking_5.pdf}
+	\end{minipage}
+	\begin{minipage}[t]{\columnwidth}
+		\includegraphics[width=1\columnwidth]{../../MATLAB/three_obstacles_no_overtaking/figure/braking_6.pdf}
+	\end{minipage}	
+	\vspace{-20pt}
+	\caption{Simulation of braking and overtaking obstacles.}
+	\label{fig:braking}
+\end{figure}
+
 At the beginning the vehicle detects all the other cars on the road.
-In the first part of the simulation, the vehicle brakes because there is no enough space for overtaking the cars as shown in the Fig.\ref{fig:velocity_braking}.
-A collision will
-happen if the vehicle continues to follow the initially planned trajectory with the reference velocity.
-It is possible to notice that the speed decreases because the applied throttle is negative, so a consistent deceleration is set after $\simeq1.5$s as depicted in Fig.\ref{fig:throttle_braking}.
+In the first part of the simulation, the ATLASCAR2 brakes because there is no enough space for overtaking the cars as shown in the Fig.\ref{fig:velocity_braking} (pag.6).
+A collision will happen if the vehicle continues to follow the initially planned trajectory with the reference velocity.
+It is possible to notice that the speed decreases because the applied throttle is negative, so a consistent deceleration is set after $\simeq1.5$s as depicted in Fig.\ref{fig:throttle_braking} (pag.6).
 After few seconds the fastest obstacle moves and makes available the left lane.
@@
 Then, the ATLASCAR2 returns to the reference velocity during the overtaking of the two obstacles.
-The path of the vehicle is is depicted in Fig.
-\ref{fig:lateral_braking}.
 It is seen that the ATLASCAR2 avoids the  obstacles and returns to the road  centerline with a low overshoot.
-%%% Simulation Braking
-\begin{figure}[!h]
+\begin{figure*}[!b]
+	\vspace{-1.5em}
 	\centering
 	\begin{minipage}[t]{\columnwidth}
-		\includegraphics[width=1\columnwidth]{../../MATLAB/three_obstacles_no_overtaking/figure/braking_0.pdf}
-		\label{fig:braking_0}
+		\includegraphics[width=1.1\textwidth,height=0.5\columnwidth]{../../MATLAB/three_obstacles_no_overtaking/figure/VelocityVsTime.pdf}
+		\vspace{-22pt}
+		\caption{Velocity $v$ with respect to time.}
+		\label{fig:velocity_braking}
 	\end{minipage}
 	\begin{minipage}[t]{\columnwidth}
-		\includegraphics[width=1\columnwidth]{../../MATLAB/three_obstacles_no_overtaking/figure/braking_1.pdf}
-		\label{fig:braking_1}
+		\includegraphics[width=1.1\columnwidth,height=0.5\columnwidth]{../../MATLAB/three_obstacles_no_overtaking/figure/ThrottleVsTime.pdf}
+		\vspace{-22pt}
+		\caption{Throttle $T$ with respect to time.}
+		\label{fig:throttle_braking}
+	\end{minipage}
+\end{figure*}
+	\begin{figure*}[!b]
+		\vspace{-1.2em}
+		\centering
+	\begin{minipage}[t]{\columnwidth}
+	\includegraphics[width=1.1\columnwidth,height=0.5\columnwidth]{../../MATLAB/three_obstacles_no_overtaking/figure/SteeringAngleVsTime.pdf}
+	\vspace{-22pt}
+	\caption{Steering angle $\delta$ with respect to time.}
+	\label{fig:delta_braking}
 	\end{minipage}
 	\begin{minipage}[t]{\columnwidth}
-		\includegraphics[width=1\columnwidth]{../../MATLAB/three_obstacles_no_overtaking/figure/braking_2.pdf}
-		\label{fig:braking_2}
-	\end{minipage}
-	\begin{minipage}[t]{\columnwidth}
-		\includegraphics[width=1\columnwidth]{../../MATLAB/three_obstacles_no_overtaking/figure/braking_3.pdf}
-		\label{fig:braking_3}
-	\end{minipage}
-	\begin{minipage}[t]{\columnwidth}
-		\includegraphics[width=1\columnwidth]{../../MATLAB/three_obstacles_no_overtaking/figure/braking_4.pdf}
-		\label{fig:braking_4}
-	\end{minipage}
-	\begin{minipage}[t]{\columnwidth}
-		\includegraphics[width=1\columnwidth]{../../MATLAB/three_obstacles_no_overtaking/figure/braking_5.pdf}
-		\label{fig:braking_5}
-	\end{minipage}
-	\begin{minipage}[t]{\columnwidth}
-		\includegraphics[width=1\columnwidth]{../../MATLAB/three_obstacles_no_overtaking/figure/braking_6.pdf}
-		\label{fig:braking_6}
-	\end{minipage}	
-	\caption{Simulation of braking and overtaking obstacles.}
-\end{figure}
-\begin{figure}[!h]
-	\centering
-	\includegraphics[width=1\columnwidth]{../../MATLAB/three_obstacles_no_overtaking/figure/VelocityVsTime.pdf}
-	\caption{Velocity $v$ with respect to time.}
-	\label{fig:velocity_braking}
-\end{figure}
-\begin{figure}[!h]
-	\centering
-	\includegraphics[width=1\columnwidth]{../../MATLAB/three_obstacles_no_overtaking/figure/ThrottleVsTime.pdf}
-	\caption{Throttle $T$ with respect to time.}
-	\label{fig:throttle_braking}
-\end{figure}
-\begin{figure}[!h]
-	\centering
-	\includegraphics[width=1\columnwidth]{../../MATLAB/three_obstacles_no_overtaking/figure/SteeringAngleVsTime.pdf}
-	\caption{Steering angle $\delta$ with respect to time.}
-	\label{fig:delta_braking}
-\end{figure}
-\begin{figure}[!h]
-	\centering
-	\includegraphics[width=1\columnwidth]{../../MATLAB/three_obstacles_no_overtaking/figure/HeadingAngleVsTime.pdf}
+	\includegraphics[width=1.1\columnwidth,height=0.5\columnwidth]{../../MATLAB/three_obstacles_no_overtaking/figure/HeadingAngleVsTime.pdf}
+	\vspace{-22pt}
 	\caption{Heading angle $\theta$ with respect to time.}
 	\label{fig:theta_braking}
-\end{figure}
-\begin{figure}[!h]
-	\centering
-	\includegraphics[width=1\columnwidth]{../../MATLAB/three_obstacles_no_overtaking/figure/LateralPositionVsTime.pdf}
-	\caption{Lateral position $y$ with respect to time.}
-	\label{fig:lateral_braking}
-\end{figure}
-\section{Lane Following}
-\subsection{Problem Formulation}
-A lane-following system is a control system that keeps the vehicle traveling along the centerline of a highway lane, while maintaining a user-set velocity.
-The lane-following scenario is depicted in the following figure:
-\begin{figure}[!h]
-	\centering
-	\includegraphics[width=0.75\columnwidth]{./figure/laneFollowing/laneFollowing.pdf}
-	\caption{Problem description of a lane following system.}
-	\label{fig:laneFollowing}
-\end{figure}
-
-In a classic lane keeping assist, it is assumed that the longitudinal velocity is constant.
-This restriction is relaxed in this model because the longitudinal acceleration varies in this MIMO control system.
-This lane-following system manipulates both the longitudinal acceleration and the front steering angle of the vehicle to keep the lateral deviation and the relative yaw angle small and the longitudinal velocity close to a driver set velocity.
-If these two goals cannot be met at the same moment, the system tries to balance them.
-The model that we are considering, contains a lot of parameters.
-The first fundamental block describes the vehicle dynamics: we have applied the bicycle model of lateral vehicle dynamics and approximate the longitudinal dynamics using a time constant:
-\subsubsection{Longitudinal dynamics}
-We can use the following state space to describe the longitudinal model:
-\begin{equation}
-\label{eqn:longi_dynamics_simple_model_ss}
-\begin{array}{ll}
-\dot{\textbf{x}}_{\text{lon}} =A_m \textbf{x}_{\text{lon}}+ B_m\textbf{u}_{\text{lon}}\\
-\textbf{y}_{\text{lon}} =C_m \textbf{x}_{\text{lon}} + D_m \textbf{u}_{\text{lon}}
-\end{array}
-\end{equation}
-where the input is the acceleration and the states are the longitudinal velocity and the actual acceleration which is also the only output of this system.
-\begin{equation*}
-\textbf{x}_{\text{lon}} = \begin{bmatrix}
-\dot{V}_x&V_x
-\end{bmatrix}^T,
-\qquad
-\textbf{u}_{\text{lon}} = a
-\end{equation*}
-and
-\[ 
-A_g=\begin{bmatrix}
--\frac{1}{\tau}&0\\1&0
-\end{bmatrix},
-\quad
-B_g=\begin{bmatrix}
-\frac{1}{\tau}\\
-0
-\end{bmatrix},
-\]
-\[
-C_g=\begin{bmatrix}
-1&0
-\end{bmatrix}, 
-\quad
-D_g=0.
-\]
-where $\tau$ is a time constant; in practice we are considering a second order transfer function like in \cite{long_tf}.
-\subsubsection{Lateral dynamics}
-Local function: we have a continuous vehicle lateral model from parameters obtained by simplifying the one in \cite{rathai}: 
-\begin{equation}
-\label{eqn:lateral_dynamics_simple_model}
-\begin{array}{ll}
-\dot{\textbf{x}}_{\text{lat}} =A_g \textbf{x}_{\text{lat}}+ B_g \textbf{u}_{\text{lat}}\\
-\textbf{y}_{\text{lat}} =C_g \textbf{x}_{\text{lat}} + D_g \textbf{u}_{\text{lat}}
-\end{array}
-\end{equation}
-where the input is the steering angle in radians, and the outputs are the lateral velocity in meters per second and yaw angle rate in radians per second:
-\begin{equation*}
-\textbf{x}_{\text{lat}} = \begin{bmatrix}
-V_y&\dot{\psi}
-\end{bmatrix}^T
-\qquad
-\textbf{u}_{\text{lat}} = \delta
-\end{equation*}
-and
-\[ 
-A_g=\begin{bmatrix}
--\frac{2C_F+2C_R}{mV_x}&-\frac{2C_Fl_F-2C_Rl_R}{mV_x} - V_x\\
--\frac{2C_Fl_F-2C_Rl_R}{I_ZV_x}&-\frac{2C_Fl_F^2+2C_Rl_R^2}{I_ZV_x}
-\end{bmatrix},
-\]
-\[
-B_g=\begin{bmatrix}
-2C_F/m\\
-2C_Fl_F/I_Z
-\end{bmatrix},
-\quad
-C_g=\textbf{I}_2, 
-\quad
-D_g=\textbf{0}_{2\times1}.
-\]
-The parameters in the previous matrices are:
-\begin{itemize}
-	\item $V_x$ is the longitudinal velocity of the car;	
-	\item $m$ is the total mass parameter; 
-	\item $I_Z$ is the yaw moment of inertia parameter;
-	\item $l_F$ and $l_R$ are the longitudinal distances from center of gravity to front and rear tires parameters;
-	\item $C_F$ and $C_R$ are the cornering stiffnesses of front and rear tires parameters.
-\end{itemize}
-The goal for the driver steering model is to keep the vehicle in its lane and follow the curved road by controlling the front steering angle .
-This goal is achieved by driving the yaw angle error $e_2 = \psi -\psi_{\text{des}}$ and lateral displacement error $e_1$ to zero ($\dot{e}_1 = V_xe_2+V_y$).
-We can incorporate these two paramenters in the augmented model:
-\begin{equation}
-\label{eqn:lateral_dynamics_augmented_model}
-\begin{array}{ll}
-\dot{\textbf{x}}_{\text{aug}} =A_a \textbf{x}_{\text{aug}}+ B_a \textbf{u}_{\text{aug}}\\
-\textbf{y}_{\text{aug}} =C_a \textbf{x}_{\text{aug}} + D_a \textbf{u}_{\text{aug}}
-\end{array}
-\end{equation}
-where
-\begin{equation*}
-\textbf{x}_{\text{aug}} = \begin{bmatrix}
-V_y&\dot{\psi}&e_1&e_2
-\end{bmatrix}^T,
-\qquad
-\textbf{u}_{\text{aug}} = 
-\begin{bmatrix}
-\delta&\dot{\psi}_{\text{des}}
-\end{bmatrix}^T
-\end{equation*}
-and
-\[ 
-A_a=\begin{bmatrix}
-A_g&\textbf{0}_{2\times2}\\
-\textbf{I}_2&\begin{matrix}
-0&V_x\\
-0&0
-\end{matrix}
-\end{bmatrix},
-\quad
-B_a=\begin{bmatrix}
-B_g&\textbf{0}_{2\times1}\\
-0&0\\
-0&-1
-\end{bmatrix},
-\]
-\[
-C_a=\begin{bmatrix}
-\textbf{0}_{2\times2}&\textbf{I}_2
-\end{bmatrix}, 
-\quad
-D_a=
-\textbf{0}_{2\times2}. 
-\]
-Combining (\ref{eqn:longi_dynamics_simple_model_ss}) with (\ref{eqn:lateral_dynamics_augmented_model}) yields the state-space model that characterizes the Model Predictive Controller:
-\begin{equation}
-\label{eqn:full_dynamics_model}
-\begin{array}{ll}
-\dot{\textbf{x}}_{\text{tot}} =A_f \textbf{x}_{\text{tot}}+ B_f \textbf{u}_{\text{tot}}\\
-\textbf{y}_{\text{tot}} =C_f \textbf{x}_{\text{tot}} + D_f \textbf{u}_{\text{tot}}
-\end{array}
-\end{equation}
-where
-\begin{equation*}
-\textbf{x}_{\text{tot}} = \begin{bmatrix}
-\dot{V}_x\\V_x\\V_y\\\dot{\psi}\\e_1\\e_2
-\end{bmatrix},
-\qquad
-\textbf{u}_{\text{tot}} = 
-\begin{bmatrix}
-a\\\delta\\\dot{\psi}_{\text{des}}
-\end{bmatrix}
-\end{equation*}
-and
-\[ 
-A_f=\begin{bmatrix}
-A_m&\textbf{0}_{2\times4}\\
-\textbf{0}_{4\times2}&A_a
-\end{bmatrix},
-\quad
-B_f=\begin{bmatrix}
-B_m&\textbf{0}_{2\times2}\\
-\textbf{0}_{4\times1}&B_a
-\end{bmatrix},
-\]
-\[
-C_f=\begin{bmatrix}
-C_m&\textbf{0}_{1\times4}\\
-\textbf{0}_{2\times2}&C_a
-\end{bmatrix}, 
-\quad
-D_f=\textbf{0}_{3\times3}. 
-\]
-However the system to be controlled is usually modeled by a linear discrete state-space model:
-\begin{equation*}
-\label{eqn:full_dynamics_model_disc}
-\begin{array}{rr}
-{\textbf{x}}_{\text{tot}}(k+1) =A \textbf{x}_{\text{tot}}(k)+ B \textbf{u}_{\text{tot}}(k)\\
-\textbf{y}_{\text{tot}}(k) =C\textbf{x}_{\text{tot}}(k) + D \textbf{u}_{\text{tot}}(k)
-\end{array}
-\end{equation*}
-where $A$ and $B$ are the state and control matrices for the discrete state-space equation, respectively, which can be calculated, also in this case, with the Euler method as:
-\[
-A = e^{A_fT_s},\qquad B = \int_{kT_s}^{(k+1)T_s} e^{A_f[(k+1)T_s-\eta]}B_f d\eta
-\]
-where $T_s$ is the sampling interval for the discrete state-space model. The matrices $C$ and $D$ are equivalent to those in the continuous case.
-
-\subsection{Design of Adaptive Model Predictive Control}
-We created an Adaptive MPC controller with a prediction model that has six states, three outputs (longitudinal velocity, lateral deviation, relative yaw angle), and two inputs.
-The model has two manipulated signals: acceleration and steering.
-The product of the road curvature and the longitudinal velocity is modeled as a measured disturbance.
-We have set the constraints for manipulated variables and the scale factors.
-Moreover we have specified the weights in the standard MPC cost function.
-The third output, yaw angle, is allowed to float because there are only two manipulated variables to make it a square system.
-In this controller, there is no steady-state error in the yaw angle as long as the second output, lateral deviation, reaches 0 at steady state.
-Finally we have also penalized acceleration change more for smooth driving experience.
-This controller uses a linear model for the vehicle dynamics and updates the model online as the longitudinal velocity varies.
-
-\subsection{Simulation Results}
-The proposed adaptive MPC algorithm is designed in the MATLAB/Simulink and validated through simulation.
-The objective of this test is to evaluate the behavior of the proposed control strategy in critical situations.
-Table 3 shows the parameters used in the lane following simulation.
-\begin{table}[!h]
-	\centering
-	\begin{tabular}{|c|c|}
-		\hline
-		Parameters          & Values      \\
-		\hline
-		$m$          & 1575 kg              \\
-		$I_z$         & 2875 kg$\cdot$m$^2$              \\
-		$l_F$           & 1.2 m               \\
-		$l_R$         & 1.6 m               \\
-		$C_F$          & 19000 N/rad      \\
-		$C_R$           & 33000 N/rad            \\
-		$\tau$             & 0.2                \\
-		$V_0$           & 15 m/s       \\
-		$V_{\text{set}}$          & 20 m/s \\
-		$T_s$         & 0.02 s        \\
-		\hline
-	\end{tabular}
-\end{table}
-
-Fig.\ref{fig:reference_laneFollowing} and Fig.\ref{fig:curvature_laneFollowing} show the desired path that the car must follow and its curvature, where the former is described in terms of the lateral position $Y_{\text{ref}}$ as function of the longitudinal position $X_{\text{ref}}$.
-The ATLASCAR2 is controlled to
-follow a sinusoidal trajectory which is given as follows:
-\begin{equation*}
-	X_\text{ref}=V_x\cdot t, \quad Y_\text{ref}=5\sin(X_\text{ref}/20)\quad \text{with}\quad t\in[0,20]\text{s}
-\end{equation*}
-\begin{figure}[!h]
-	\centering
-	\includegraphics[width=1\columnwidth]{../../MATLAB/lane_following/figure/Reference.pdf}
-	\caption{Desired path of the ATLASCAR2.}
-	\label{fig:reference_laneFollowing}
-\end{figure}
-\begin{figure}[!h]
-	\centering
-	\includegraphics[width=1\columnwidth]{../../MATLAB/lane_following/figure/Curvature.pdf}
-	\caption{Desired curvature.}
-	\label{fig:curvature_laneFollowing}
-\end{figure}
-
-Moreover the following figures show the trend of the main parameters confirming that the control strategy used allows the vehicle to follow the path.
-In particular we simulated also a small error in the sensor dynamics in order to make the simulation more realistic: we added a 3 percent error to the longitudinal velocity and this is evident from the small noise in the graphs of the steering angle and the lateral deviation.
-\begin{figure}[!h]
-	\centering
-	\includegraphics[width=1\columnwidth]{../../MATLAB/lane_following/figure/AccelerationVsTime.pdf}
-	\caption{Acceleration $u_1$ with respect to time.}
-	\label{fig:acceleration_laneFollowing}
-\end{figure}
-\begin{figure}[!h]
-	\centering
-	\includegraphics[width=1\columnwidth]{../../MATLAB/lane_following/figure/SteeringAngleVsTime.pdf}
-	\caption{Steering angle $u_2$ with respect to time.}
-	\label{fig:steering_laneFollowing}
-\end{figure}
-\begin{figure}[!h]
-	\centering
-	\includegraphics[width=1\columnwidth]{../../MATLAB/lane_following/figure/RelativeYawAngleVsTime.pdf}
-	\caption{Relative yaw angle $e_2$ with respect to time.}
-	\label{fig:relative_yaw_angle_laneFollowing}
-\end{figure}
-\begin{figure}[!h]
-	\centering
-	\includegraphics[width=1\columnwidth]{../../MATLAB/lane_following/figure/LateralDeviationVsTime.pdf}
-	\caption{Lateral deviation $e_1$ with respect to time.}
-	\label{fig:lateral_deviation_laneFollowing}
-\end{figure}
-
-Fig.{\ref{fig:longitudinal_velocity_laneFollowing}} shows the evolution of the vehicle longitudinal velocity.
-At the start of the simulation, this velocity is equal to the initial condition for longitudinal velocity parameter.
-At run time, this velocity is equal to the Longitudinal velocity input signal.
-We can note that $V_x$ reaches the predefined value of $20$ meters for second and then it stabilizes near the cruising speed because it continues to vary the steering angle to adapt to the path to be followed.
-\begin{figure}[!h]
-	\centering
-	\includegraphics[width=\columnwidth]{../../MATLAB/lane_following/figure/LongitudinalVelocityVsTime.pdf}
-	\caption{Longitudinal velocity $V_x$ with respect to time.}
-	\label{fig:longitudinal_velocity_laneFollowing}
-\end{figure}
-\begin{figure*}[!h]
-	\centering
-	\includegraphics[width=\textwidth]{./figure/lane_following_AMPC.pdf}
-	\caption{Overall procedure scheme lane following.}
-	\label{fig:scheme_lane_following}
+	\end{minipage}
 \end{figure*}
@@
 \section{Conclusions and Future Work}
-In this work we proposed two advanced methods for the ATLASCAR2 based on adaptive Model Predictive Control.
-In the first case we analyzed an obstacle avoidance system that moves the vehicle around different moving obstacles in the lane using throttle and steering angle.
+In this work we proposed an advanced method for the ATLASCAR2 based on adaptive Model Predictive Control.
+In this paper we analyzed an obstacle avoidance system that moves the vehicle around different moving obstacles in the lane using throttle and steering angle.
 This system updates both the predictive model and the mixed input/output constraints at each control interval.
 The vehicle is also able to brake in order to prevent collisions against closest obstacles.
-Instead, in the second scenario  we have developed a lane following system that keeps the ATLASCAR2 traveling along the centerline of the lanes on the road by adjusting the front steering angle of the car.
-The flexibility of the concepts used in these methods allows a multitude of refinements and extensions to this project.
-For example the next possible work could be to combine the two previous control strategies in a way that they can operate simultaneously.
+The flexibility of the concepts used in the algorithm allows a multitude of refinements and extensions to this work.
+We can add to this algorithm a lane following system that keeps the ATLASCAR2 traveling along the centerline of the lanes on the road by adjusting the front steering angle of the car.
+For example the next possible work could be to combine these two control strategies in a way that they can operate simultaneously.
 Moreover the final method could be tested in a real autonomous driving scenario.
@@
 
-	\bibitem{matPDF}A. Bemporad, M. Morafi, and N. Ricker, Model Predictive Control Toolbox User’s Guide, The MathWorks, Inc.,
+	\bibitem{mpctoolbox}A. Bemporad, M. Morafi, and N. Ricker, Model Predictive Control Toolbox User’s Guide, The MathWorks, Inc.,
 

### 2019-02-04 Thesis_Latex/Paper/figure/flowchart/flowchart.tex
update full version Paper

\documentclass[preview,float]{standalone}

\usepackage[latin1]{inputenc}
\usepackage{tikz}
\usetikzlibrary{shapes,arrows}
\begin{document}
\pagestyle{empty}

% Define block styles
\tikzstyle{decision} = [diamond, draw, fill=blue!20, 
    text width=4.5em, text badly centered, node distance=3cm, inner sep=0pt]
\tikzstyle{block} = [rectangle, draw, fill=green!20, 
    text width=5em, text centered, rounded corners, minimum height=4em]
\tikzstyle{line} = [draw, -latex']
\tikzstyle{cloud} = [draw, ellipse,fill=red!20, node distance=3cm,
    minimum height=2em]

\begin{tikzpicture}[node distance = 3.3cm, auto]
    % Place nodes
    \node [decision] (detection) {Obstacle 
    detected?}; 
    \node [cloud,right of=detection] (start) {Start};
    \node [decision,below of=detection] (multiObstacles) {Multiple Obstacles detected?};
	\node [block,left of=detection] (reference) {Follow Path: stick to the lane};
    \node [block,below of=multiObstacles] (distance) {Distance to closest obstacle};
    \node [block,right of=multiObstacles] (distances) {Distance between the obstacles};
    \node [decision,below of=distances](space) {Free Space for Overtaking?};
    \node [block,right of=space](braking){Braking/ Ostacle Velocity};
    \node [block,below of=space](free){Overtaking on free lane};
    \node [decision,below of=distance] (decisionOvertaking) {Left w.r.t vehicle?};
    \node [block, below of=decisionOvertaking] (rightOver) {Right Overtaking};     
    \node [block, left of=decisionOvertaking] (leftOver) {Left Overtaking};

  %  \node [block] (init) {initialize model};
   % \node [cloud, left of=init] (expert) {expert};
   % \node [cloud, right of=init] (system) {system};
   % \node [block, below of=init] (identify) {identify candidate models};
%    \node [block, below of=identify] (evaluate) {evaluate candidate models};
 %   \node [block, left of=evaluate, node distance=3cm] (update) {update model};
  %  \node [decision, below of=evaluate] (decide) {is best candidate better?};
   % \node [block, below of=decide, node distance=3cm] (stop) {stop};
    % Draw edges
    \path [line] (start) -- (detection);
    \path [line] (detection) -- node {yes} (multiObstacles);
    \path [line] (detection) -- node {no} (reference);
    \path [line] (multiObstacles) -- node {no} (distance);
    \path [line] (multiObstacles) -- node {yes} (distances);
    \path [line] (distances)--(space);
    \path [line] (space) -- node{no}(braking);
    \path [line] (space) -- node{yes} (free);
    \path [line] (braking) |- (distances);
    \path [line] (distance) -- (decisionOvertaking);
    \path[line] (decisionOvertaking) -- node {no}(leftOver);
    \path[line] (decisionOvertaking) -- node{yes} (rightOver);
\end{tikzpicture}

\end{document}

### 2019-02-04 MATLAB/three_obstacles_no_overtaking/three_obstaclesResults.m

@@ -2,70 +2,71 @@
 
 % Velocity vs Time
 h1 = figure ('Position',[100, 100, 340, 230], 'PaperPositionMode','auto');
+plot(T,ympc(:,4));
 hold on;
 grid on;
 grid minor;
-plot(T,ympc(:,4));
-title('\textbf{Velocity ($v$) vs Time}','Interpreter','latex');
+%title('\textbf{Velocity ($v$) vs Time}','Interpreter','latex');
 xlabel('Time [s]','Interpreter','latex');
 ylabel('Velocity [m/s]','Interpreter','latex');
+axis([0 10 6.5 20.5])
 pos1 = get(h1,'Position');
-set(h1,'PaperPositionMode','Auto','PaperUnits','Points','PaperSize',[pos1(3), pos1(4)-40])
+set(h1,'PaperPositionMode','Auto','PaperUnits','Points','PaperSize',[pos1(3)*0.8, pos1(4)-40])
 print(h1,'figure\VelocityVsTime','-dpdf','-r0')
-hold off
+
 
 % Y_mpc vs Time
 h2 = figure ('Position',[100, 100, 340, 230], 'PaperPositionMode','auto');
+plot(T,ympc(:,2));
 hold on;
 grid on;
 grid minor;
-plot(T,ympc(:,2));
-title('\textbf{Lateral Position ($y$) vs Time}','Interpreter','latex');
+%title('\textbf{Lateral Position ($y$) vs Time}','Interpreter','latex');
 xlabel('Time [s]','Interpreter','latex');
 ylabel('Lateral Position [m]','Interpreter','latex');
 pos2 = get(h2,'Position');
-set(h2,'PaperPositionMode','Auto','PaperUnits','Points','PaperSize',[pos2(3), pos2(4)-40])
+set(h2,'PaperPositionMode','Auto','PaperUnits','Points','PaperSize',[pos2(3)*0.8, pos2(4)-40])
 print(h2,'figure\LateralPositionVsTime','-dpdf','-r0')
-hold off
+
 
 % Theta vs Time
 h3 = figure ('Position',[100, 100, 340, 230], 'PaperPositionMode','auto');
+plot(T,ympc(:,3));
 hold on;
 grid on;
 grid minor;
-plot(T,ympc(:,3));
-title('\textbf{Heading Angle ($\theta$) vs Time}','Interpreter','latex');
[…]

### 2019-02-13 Thesis_Latex/FinalReport/FinalReport.tex
update path planning, Paper, Final Report

\documentclass[conference,11pt]{IEEEtran}
\IEEEoverridecommandlockouts

\usepackage{algorithm}
\usepackage{algpseudocode}
\usepackage{multirow}
\usepackage{multicol}
\usepackage{siunitx}
\usepackage{booktabs}
\usepackage{listings}
\usepackage{stfloats}
\usepackage{midfloat}
\usepackage{color}
\usepackage[table]{xcolor}
\usepackage{lipsum}
\usepackage[utf8x]{inputenc}
\usepackage{float}
\usepackage{bbm}
\usepackage{graphicx}
\usepackage{caption,subcaption}
%\usepackage{amsmath}
\usepackage{amsmath,amsfonts,amssymb}
\usepackage[font={small,it}]{caption}
\usepackage[colorlinks=true,linkcolor=black,anchorcolor=black,citecolor=black,filecolor=black,menucolor=black,runcolor=black,urlcolor=black]{hyperref}
\usepackage{tikz}
\usetikzlibrary{shapes,arrows}
\usepackage{standalone}
\usepackage{balance}
%\usepackage{isomath}
%\renewcommand{\vec}{\mathbfit}
\renewcommand{\vec}[1]{\ensuremath{\boldsymbol{\mathit{#1}}}}

\newtheorem{thm}{Theorem}[section]
\newtheorem{defn}[thm]{Def.}
\newtheorem{propen}[thm]{Prop.}
\newtheorem{cor}[thm]{Cor.}
\renewcommand\IEEEkeywordsname{Keywords}
\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
		T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}

\title{Local Path Planning with Moving Obstacle Avoidance based on adaptive MPC in ATLASCAR2}
\author{
	\IEEEauthorblockN{Alberto Franco}
	\IEEEauthorblockA{Department of Information Engineering,\\ Università degli Studi di Padova, Italy\\		 \href{mailto:alberto.franco.3@studenti.unipd.it}{alberto.franco.3@studenti.unipd.it}\\
	\href{mailto:alberto.franco@ua.pt}{alberto.franco@ua.pt}}
	}

\begin{document}
\maketitle
\thispagestyle{plain}
\pagestyle{plain}
\begin{abstract}
	This report presents two different strategies for a self-driving car short-term path planning among multiple moving obstacles. The main task is to study and implement a motion planning and execution framework in order to make ATLASCAR2 coexist with other moving obstacle vehicles by avoiding collision and overtake them when necessary and possible. The proposed techniques, based on the Model Predictive Control paradigm, solve optimization problems formulated in terms of cost minimization under constraints. Simulation results demonstrate and verify the feasibility and the usefulness of methods considering different scenarios, opening space for real scenario implementation.
\end{abstract}

\section{Introduction}
In robotic research, the problem of navigation is among the most important. Basically, all autonomous mobile robots need some kind of navigation abilities to perform, localization, motion planning and guidance \cite{skoda}.
In the present context, we focus on navigation as a process of planning a path of a mobile robot from its current position to a desired goal location, following the planned path, and avoiding any discovered obstacles along the way \cite{fuzzyMPC} \cite{NONMPC}. The desired paths have to fulfill several conditions to ensure safety and feasibility of the navigation \cite{safety}. Moreover, the paths can be also defined in terms of specifications; for example, short or smooth paths are usually more desirable than long and curved ones in very dynamic environments \cite{archi}. Beyond the path planning, the navigation problem also involves reacting to changes of the environment model. Robots are required to move towards the target in a short time and avoid either static or dynamic obstacles observed by their sensors, which involves efficient path planning and valid obstacle avoidance \cite{MMPC} \cite{autoMPC}. Though these two topics have been well researched, currently, there is no definitive solution to manage the navigation problem within cluttered dynamic environments. In the literature many collision avoidance methods have been developed for wheeled mobile robots; they can be grouped in four categories: graph-search based methods \cite{RRT}, artificial potential field based methods \cite{potential}, meta-heuristic based methods \cite{meta-heuristic} and mathematical optimization based methods \cite{borelli2}.
The latter are very interesting because they offer a systematic and precise way to take vehicle dynamics and safety constraints into account and can produce optimal control inputs. This approach can be used in an closed-loop with a feedback controller for a stronger solution regarding to the Model Predictive Control (MPC). A prior research about obstacle avoidance using MPC in UGVs is described in \cite{borelli} while the applications of nonlinear MPC to ground vehicles is described and evaluated in \cite{nonlinearmpc}.
\section{Context and Proposed Solution}

The proposed algorithms were studied for the ATLASCAR project in which the group for Robotics and Automation at the University of Aveiro has setup and adapted a common commercial vehicle to provide a versatile  framework  to  develop  studies  and  research %\cite{atlas}
\cite{atlascar1} \cite{atlascar2}.
Figure \ref{fig:atlascar2} shows the chosen platform for the second generation of ATLASCAR, which is an electric car, a Mitsubishi iMiEV with a range of a \SI{100}{km}.
\begin{figure}[!h]
	\centering
	\includegraphics[width=0.6\columnwidth]{./figure/atlascar2.jpg}
	\caption{ATLASCAR2, based on an electric car, a Mitsubishi iMiEV, (adapted from \protect\cite{ricardo}) }
	\label{fig:atlascar2}
\end{figure}

The fact that the vehicle is electric allows to use the energy stored in the batteries, making it easier to power the sensors installed. In fact, the ATLACAR2 is equipped with sensors, such as lidar, that measure the distance to obstacles in front and around the vehicle. The obstacles can be static, such as a large pothole, or moving, such as a moving vehicle on the same or a nearby lane. The most common maneuver from the driver is to temporarily move to another lane, drive past the obstacle, and move back to the original lane afterward. In this case, we want to design an obstacle avoidance system that moves the ATLASCAR2 around a moving obstacle in the lane using throttle and steering angle. This system uses an adaptive Model Predictive Controller that updates both the predictive model and the mixed input/output constraints at each control interval. Moreover we want to develop a lane-keeping assist system for the vehicle: it has a sensor, such as camera or laser, that measures the lateral deviation and relative yaw angle between the centerline of a lane and the ATLASCAR2; it also measures the current lane curvature and its derivative. Depending on the curve length that the sensor can view, the curvature in front of the vehicle can be calculated from the current curvature and its derivative. This system keeps the autonomous car travelling along the centerline of the lanes on the road by adjusting the front steering angle. The goal for lane keeping control is to drive both lateral deviation and relative yaw angle close to zero.

\section{Theoretical background\\ Adaptive Model Predictive Control}
Model Predictive Control is an advanced method that predicts future behavior using a linear-time-invariant (LTI) dynamic model. These predictions are not exact and a good strategy is to make MPC insensitive to prediction errors. If the plant is strongly nonlinear or its characteristics vary dramatically with time, MPC performance might become unacceptable because LTI prediction accuracy degrade \cite{mpctoolbox}. A method that can address this degradation by adapting the prediction model for changing operating conditions is called Adaptive MPC: this control strategy uses a fixed model structure, but allows the model parameters to evolve with time. Ideally, whenever the controller requires a prediction, it uses a model appropriate for the current conditions. At each control interval, the adaptive MPC controller updates the plant model and nominal conditions. Once updated, the model and conditions remain constant over the prediction horizon. The plant model used as the basis for the adaptive MPC must be an LTI discrete-time, state-space model with a structure as follows:
\begin{equation*}
\label{eqn:Adaptive_MPC_plant_discrete}
\begin{aligned}
\vec{x}(k+1)&=\vec{A}\vec{x}(k)+ \vec{B}_u \vec{u}(k)+\vec{B}_v \vec{v}(k)+\vec{B}_d \vec{d}(k)\\
\vec{y}(k)&=\vec{C}\vec{x}(k) + \vec{D}_v \vec{v}(k)+ \vec{D}_d \vec{d}(k)
\end{aligned}
\end{equation*}
where the matrices \vec{A}, $\vec{B}_u$, $\vec{B}_v$, $\vec{B}_d$, \vec{C}, $\vec{D}_v$ and $\vec{D}_d$ can vary with time. The other parameters in the previous expression are:
\begin{itemize}
	\item $k$ is the time index/current control interval;
	\item \vec{x} are the plant model states;
	\item \vec{u} are the manipulated inputs that can be adjusted by the MPC controller;
	\item \vec{v} are the measured disturbance inputs;
	\item \vec{d} are the unmeasured disturbance inputs;
	\item \vec{y} are the plant outputs, including both measured (necessary at least one) and unmeasured.
\end{itemize}
In the adaptive MPC control, there are additional requirements for the plant model, like the sample time $T_s$ that has to be constant and identical to the MPC control interval. This control strategy prohibits direct feed-through from any manipulated variable to any plant output. Thus, $\vec{D_v} = \vec{0}$ in the above model.
A traditional MPC controller includes a nominal operating point at which the plant model applies, such as the condition at which you linearize a nonlinear model to obtain the LTI approximation (equilibrium, reference trajectory and the	
most updated value) \cite{mpctoolbox}. In adaptive MPC, as time evolves it should update the nominal operating point to be consistent with the updated plant model. It is possible to rewrite the plant model in terms of deviations from the nominal conditions as follows:
\begin{equation*}
\label{eqn:Adaptive_MPC_nominal_condition}
\begin{aligned}
\vec{x}(k+1)&=\overline{\vec{x}}+\vec{A}(\vec{x}(k)-\overline{\vec{x}})+ \vec{B}(\vec{u}_t(k)-\overline{\vec{u}}_t)+\overline{\Delta \vec{x}} \\
\vec{y}(k)&=\overline{\vec{y}}+\vec{C}(\vec{x}(k)-\overline{\vec{x}}) + \vec{D}(\vec{u}_t(k)-\overline{\vec{u}}_t)
\end{aligned}
\end{equation*}
where the matrices \vec{A}, \vec{B}, \vec{C} and \vec{D} are updated with respect to time. The other parameters in the previous structure are:
\begin{itemize}
	\item $\vec{u}_t$ is the combined plant input variable, comprising $\vec{u}$, $\vec{v}$ and $\vec{d}$ variables defined earlier;
	\item $\overline{\vec{x}}$ are the nominal states;
	\item $\overline{\Delta \vec{x}}$ are the nominal state increments;
	\item $\overline{\vec{u}_t}$ and $\overline{\vec{y}}$ are the nominal inputs and outputs.
\end{itemize} 
The adaptive MPC uses a Kalman filter to update its controller states which include the plant, the disturbance and measurement noise model states. In particular this filter is linear-time-varying (LTV) because adjusts the gains at each control
interval to maintain consistency with the updated plant model.
\section{Moving Obstacle Avoidance}
\subsection{Problem Formulation}
The collision avoidance problem is very dependent on the vehicle modeling since it is a requirement for  adaptive MPC law design. Figure \ref{fig:obstacleAvoidance} illustrates a typical scenario of overtaking of a moving obstacle.
\begin{figure}[!h]
	\centering
	\includegraphics[width=\columnwidth]{./figure/obstacleAvoidance/obstacleAvoidance.pdf}
	\caption{Problem description of collision avoidance on a road with only two lanes.}
	\label{fig:obstacleAvoidance}
\end{figure}

The model used in this report should take into account the kinematic and dynamic aspects of the vehicle. Here, we present a non linear mathematical model of a vehicle used for the development of a collision avoidance system.
The model has four states and two inputs:
\begin{equation*} 
\vec{x}=\begin{bmatrix}
   x&y&\theta&v 
  \end{bmatrix}^\intercal
,\qquad 
\vec{u}=\begin{bmatrix}
T&\delta 
\end{bmatrix}^\intercal
\end{equation*}
where $(x,y)$ are the global coordinates of the contact point between the rear wheel and the ground, $\theta$ is the heading angle of the car body with respect to the $x$-axis and $v$ is the linear speed of the car (positive). The manipulated variables are $T$ the throttle (positive when accelerating/negative when braking) and $\delta$ the steering angle of the front wheel with respect to the vehicle ($0$ when aligned with car, counterclockwise positive). Figure \ref{fig:car_model} illustrates the applied nonlinear bicycle model and the related parameters.
\begin{figure}[H]
	\centering
	\includegraphics[width=
	0.80\columnwidth]{./figure/car_model.pdf}
	\caption{Bicycle model of a car, (adapted from \cite{siciliano}).}
	\label{fig:car_model}
\end{figure}

The ATLASCAR2 can be modeled using the non-linear kinematic bicycle model described by the following equations of motion \cite{safety} \cite{swarms}:
\begin{equation*}
\label{eqn:dynamics_model_obstacle_avoidance}
\left \{ \begin{array}{llll}
\dot{x} = v\cos(\theta)\\
\dot{y} = v\sin(\theta)\\
\dot{\theta} =\dfrac{v}{C_L}\tan(\delta)\\
\dot{v} =0.5 \cdot T
\end{array} 
\right .
\Longrightarrow 
\begin{array}{llll}
\dot{\vec{x}} = \vec{f}(\vec{x},\vec{u})\\
\vec{y} = \vec{g}(\vec{x},\vec{u})
\end{array}
\end{equation*}
where $C_L$ is the car length. In order to simplify the model, it is assumed that only the front wheel can be steered. Moreover, in this paper it is assumed that the ATLASCAR2 does not slip, so any slippage is thus considered as an external disturbance. Under this assumption, the slip angle is zero, meaning that the velocity is directed along the heading of the vehicle. In order to use MPC, the state space model needs to be linearized with a first order approximation and also re-written in a more compact form:
\begin{equation}
\label{eqn:dynamics_model_non_linear}
\begin{array}{llll}
\dot{\vec{x}} = \vec{f}(\vec{x},\vec{u})\\
\vec{y} = \vec{g}(\vec{x},\vec{u})
\end{array} \Longrightarrow
\begin{array}{ll}
\dot{\vec{x}} =\vec{A}_c \vec{x}+ \vec{B}_c \vec{u}\\
\vec{y} =\vec{C}_c \vec{x} + \vec{D}_c \vec{u}
\end{array}
\end{equation}
where the matrices $\vec{A}_c$, $\vec{B}_c$, $\vec{C}_c$ and $\vec{D}_c$ are obtained as follows:
\[ 
\vec{A}_c=\frac{\partial \vec{f}(\vec{x},\vec{u})}{\partial \vec{x}}=\begin{bmatrix}
0&0&-v\sin(\theta)&\cos(\theta)\\
0&0&v\cos(\theta)&\sin(\theta)\\
0&0&0&\tan(\delta)/C_L\\
0&0&0&0
\end{bmatrix},
\]
\[
\vec{B}_c=\frac{\partial \vec{f}(\vec{x},\vec{u})}{\partial \vec{u}}=\begin{bmatrix}
0&0\\
0&0\\
0&\dfrac{v}{C_L}\big(\tan(\delta)^2+1\big)\\
0.5&0
\end{bmatrix},
\]
\[
\vec{C}_c=\frac{\partial \vec{g}(\vec{x},\vec{u})}{\partial \vec{u}} = \mathbf{I}_4, 
\qquad
\vec{D}_c=\frac{\partial \vec{g}(\vec{x},\vec{u})}{\partial \vec{u}}=\mathbf{0}_{4\times2}. 
\]
The simple linearized approximation of the system to describe the dynamics of the ATLASCAR2 will be evaluated at the operating conditions. Note also that the system we are considering is a linear state-space model whose dynamics vary as a function of certain time-varying parameters. The system to be controlled is usually modeled by a discrete state-space model in the MPC literature. Therefore, (\ref{eqn:dynamics_model_non_linear})
is transformed into a discrete state-space model to be used by the Model Predictive Controller:
\begin{equation*}
\label{eqn:dynamics_ss_obstacle_avoidance_dis}
	\begin{array}{ll}
	\dot{\vec{x}} =\vec{A}_c \vec{x}+ \vec{B}_c \vec{u}\\
	\vec{y} =\vec{C}_c \vec{x} + \vec{D}_c \vec{u}
	\end{array}
	\Rightarrow
	\begin{array}{rr}
	{\vec{x}}(k+1) =\vec{A}_d \vec{x}(k)+ \vec{B}_d \vec{u}(k)\\
	\vec{y}(k) =\vec{C}_d \vec{x}(k) + \vec{D}_d \vec{u}(k)
	\end{array}
\end{equation*}

where $\vec{A}_d$ and $\vec{B}_d$ are the state and control matrices for the discrete state-space equation, respectively, which can be calculated with the Euler method as
\begin{equation*}
\vec{A}_d = e^{\vec{A}_cT_s},\qquad \vec{B}_d = \int_{kT_s}^{(k+1)T_s} e^{\vec{A}_c[(k+1)T_s-\eta]}\vec{B}_c d\eta
\end{equation*}

where $T_s$ is the sampling interval for the discrete state-space model. The matrices $\vec{C}_d$ and $\vec{D}_d$ are equivalent to those in the continuous case. For simplicity, we assume that all the states are measurable and the ATLASCAR2 drives east with a constant speed at the nominal operating point. In the scenario that we are going to consider, the road is straight and our vehicle stays in the middle of the center lane when not passing. Without losing generality, the ATLASCAR2 passes an obstacle both to the right and to the left lane depending on where it is placed on the road. We create also a safe zone around the obstacles so that the vehicle does not get too close to the obstacle when passing it.

\subsection{Design of Adaptive Model Predictive Control}
We designed a Model Predictive Controller that can make the ATLASCAR2 maintain a desired velocity and stay in the middle of center lane. We used an Adaptive MPC controller because it handles the nonlinear vehicle dynamics more effectively than a traditional MPC controller; in fact, the latter uses a constant plant model but the former allows us to provide a new plant model at each control interval. Because the new model describes the plant dynamics more accurately at the new operating condition, an adaptive MPC controller performs better than a traditional MPC controller. In practice, at each control interval, the adaptive MPC controller updates the plant model and the nominal conditions. Once updated, the model and the conditions remain constant over the prediction horizon. In motion planning that uses adaptive MPC, it is common to formulate the constrained control problem as a real-time optimization problem subject to hard constraints on plant variables and soft constraints on outputs; at the beginning, we specified the constraints for the manipulated variables: to prevent the ATLASCAR2 from accelerating or decelerating too quickly, we added an hard constraint on the throttle rate of change and another one on the steering angle rate of change. We used an approach that takes advantage of the ability of MPC to handle constraint explicitly. Figure \ref{fig:flowchart} shows a conditional state machine designed for higher-level behavior planning.
\begin{figure}[H]
	\centering
	\input{./figure/flowchart/flowchart}
	\caption{Behaviour planning conditional flowchart.}
	\label{fig:flowchart}
\end{figure}

When an obstacle is detected, it defines an area on the road (in terms of constraints) that the ATLASCAR2 must not enter during the prediction horizon. At the next control interval the area is redefined based on the new positions of the vehicle and the obstacle until passing is completed.
To define the area to avoid, we used the following mixed Input/Output constraints:
\begin{equation*}
	\label{eqn:mixed_IO_constraints}
	\vec{E}\vec{u}+\vec{F}\vec{y}\leq \vec{G}
\end{equation*}
where $\vec{u}$ and $\vec{y}$ are respectively the manipulated variable vector and the output variable vector, while $\vec{E},\vec{F},\vec{G}$ are the constraint matrices that can be updated when the controller is running. Five constraints were defined:
\begin{enumerate}
	\item upper bound on the $y$-coordinate (left boundary of the road);
	\item lower bound on the $y$-coordinate (right boundary of the road);
	\item constraint for obstacle avoidance; although no obstacle is considered in the nominal condition, we must add this virtual constraint here because we cannot change the dimensions of the constraint matrices at run time;
	\item upper bound on the $x$-coordinate (position of the closest obstacle);
	\item lower bound on the $x$-coordinate (position of the ATLASCAR2).
\end{enumerate}
The matrices for the above inequality are the following:
\[
\vec{E}= 
\begin{bmatrix}
0&0\\
0&0\\
0&0\\
0&0\\
0&0
\end{bmatrix},
\;
\vec{F}=\begin{bmatrix}
0&1&0&0\\
0&-1&0&0\\
cS&-1&0&0\\
1&0&0&0\\
-1&0&0&0\\
\end{bmatrix},\;
\vec{G}=
\begin{bmatrix}
W/2\\W/2\\-cI\\x_{\max}\\x_{\min}
\end{bmatrix}
\]
where $W$ is the width of the road, $cI$ and $cS$ are the required parameters such that the ATLASCAR2 must be above the line formed from the vehicle to safe zone corner for left/right passing and finally $x_{\max}$ represents the position of the closest obstacle in the case there is not free space for the overtaking (otherwise $x_{\max}=+\infty$) while $x_{\min}$ depicts the location of our vehicle. Figure \ref{fig:constraint} illustrates the constraints that are computed at each $T_s$ in the case of a left overtaking.
\begin{figure}[!h]
	\centering
	\includegraphics[width=\columnwidth]{./figure/constraint/constraint.pdf}
	\caption{Constraints in the case of left overtaking.}
	\label{fig:constraint}
\end{figure}

\subsection{Simulation Results}
The performances of the proposed adaptive MPC based vehicle control method are demonstrated in three simulation examples. We tried to choose parameters that were as close as possible to a real situation: the sampling time used in the discretization of the system is $T_s=\SI{0.02}{s}$ while the values of the prediction and the control horizon are respectively $p_H=25$ and $c_H=5$. In all simulations, the distance between the front and rear axles is $C_L=\SI{5}{m}$ and the width of the vehicle is $C_W=\SI{2}{m}$. The saturation ranges of the control inputs are: the steering angle lies in $\big[-\frac{\pi}{30}, +\frac{\pi}{30}\big]$ rad/s while in order to prevent the ATLASCAR2 from accelerating or decelerating too quickly, we impose an hard constraint of \SI{2.5}{m/s^2} on the throttle rate of change. Moreover we are using a constant reference signal for the velocity of $v=\SI{20}{m/s}$ ($\approx\SI{72}{km/h}$).
Blue paths in Figures \ref{fig:obstacleAvoidance_one_obstacle}, \ref{fig:obstacleAvoidance_random}, \ref{fig:braking} are known only at the end of the simulations.
\begin{figure}[h!]
	\centering
	\begin{minipage}[t]{\columnwidth}
	\includegraphics[width=\columnwidth]{./figure/one_obstacle_right_overtaking/overtaking_start.pdf}
	\end{minipage}
	\begin{minipage}[t]{\columnwidth}
	\includegraphics[width=\columnwidth]{./figure/one_obstacle_right_overtaking/overtaking_middle.pdf}
	\end{minipage}
	\begin{minipage}[t]{\columnwidth}
	\includegraphics[width=\columnwidth]{./figure/one_obstacle_right_overtaking/overtaking_middle_end.pdf}
	\end{minipage}
	\begin{minipage}[t]{\columnwidth}
	\includegraphics[width=\columnwidth]{./figure/one_obstacle_right_overtaking/overtaking_end.pdf}
	\end{minipage}
	\caption{Simulation of right overtaking with one moving obstacle that moves in the same direction as the vehicle.}
	\label{fig:obstacleAvoidance_one_obstacle}
\end{figure}

\begin{algorithm}%[b]
\caption{Right Overtaking if an obstacle is detected}
\small
\begin{algorithmic}[1]
\Function{RightOvertaking}{car, obstacle, road}
  \State $x_\text{min} \gets \text{car}X $,  $x_\text{max} \gets +\infty$;
  \State obsYrr = obstacle.RearRightSafeY;
  \State obsXrr = obstacle.RearRightSafeX;
  \If{ATLASCAR2 is behind the obstacle} 
        \If{ATLASCAR2 is in the adjacent lane}
        \State $cS \gets 0$; $cI \gets \text{obsYrr}$;
        \Else
        \State $cS \gets \text{tan}(\text{atan2}(\frac{\text{obsYrr}-\text{ carY}}{\text{obsXrr}-\text{carX}},1))$;
        \State $cI \gets \text{obsYrr}-cS*\text{obsXrr}$;
        \EndIf
    \Else
    \If{ATLASCAR2 is parallel to the obstacle}
    \State $cS \gets 0$; $cI \gets \text{obsYrr}$;
    \Else
        \State $cS \gets 0$; $cI \gets W/2$;
    \EndIf
    \EndIf
  \State \Return $x_\text{min}$, $x_\text{max}$, $cI$, $cS$
\EndFunction
\end{algorithmic}
\label{alg:rightOvertaking}
\end{algorithm}
%
%\begin{algorithm}
%\caption{Right Overtaking if an obstacle is detected}
%\small
%\begin{algorithmic}[1]
%\Function{RightOvertaking}{car, obstacle, road}
%  \State $x_\text{min} \gets \text{car}X $,  $x_\text{max} \gets +\infty$;
%  \State obsYrr = obstacle.RearRightSafeY;
%  \State obsXrr = obstacle.RearRightSafeX;
%  \State obsXfr = obstacle.FrontRightSafeX;
%  \If{(carX$\leq$obsXrr)} 
%        \If{(carY$\leq$obsYrr)}
%        \State $cS \gets 0$; $cI \gets \text{obsYrr}$;
%        \Else
%        \State $cS \gets \text{tan}(\text{atan2}(\frac{\text{obsYrr}-\text{ carY}}{\text{obsXrr}-\text{carX}},1))$;
%        \State $cI \gets \text{obsYrr}-cS*\text{obsXrr}$;
%       \EndIf
%    \Else
%    \If{(carX$>$obsXrr)$\And$(carX$\leq$obsXfr)}
%    \State $cS \gets 0$; $cI \gets \text{obsYrr}$;
%    \Else
%        \State $cS \gets 0$; $cI \gets W/2$;
%    \EndIf
%    \EndIf
%  \State \Return $x_\text{min}$, $x_\text{max}$, $cI$, $cS$
%\EndFunction
%\end{algorithmic}
%\label{alg:rightOvertaking}
%\end{algorithm}
%

\subsubsection{One Moving Obstacle - Right Overtaking}
In this first simulation
(Fig. \ref{fig:obstacleAvoidance_one_obstacle}) the ATLASCAR2 drives in the middle of the center lane while the road is completely free and when there is an obstacle, the vehicle passes it only using the right lane (the same simulation can be launched so that the car goes over to the left fast lane). In other words if the ATLASCAR2 is already in the adjacent lane, it uses the safety zone as the constraint, otherwise the vehicle must be above the line formed from the ATLASCAR2 to safe zone corner for right passing. If the vehicle is parallel to the obstacle, it  uses the safety zone as the constraint and finally if it has passed the obstacle, it uses the inactive constraint to go back to the center lane.
Algorithm \ref{alg:rightOvertaking} summarizes the main steps to compute custom constraints for the obstacle; when the vehicle detects the obstacle, the constraints are computed. In this simulation only the first three constraints are necessary because there is space for the overtaking without braking (the fourth and fifth constraints don't change).  
%
\subsubsection{Multiple Moving Obstacles}
For a second test, additional obstacles were added to make the scenario more complex (Fig. \ref{fig:obstacleAvoidance_random}).
\begin{figure}[!h]
	\centering
	\begin{minipage}[t]{\columnwidth}
	\includegraphics[width=1\columnwidth]{./figure/random_N_obstacles/overtaking_random_2.pdf}
	\end{minipage}
	\begin{minipage}[t]{\columnwidth}
	\includegraphics[width=1\columnwidth]{./figure/random_N_obstacles/overtaking_random.pdf}
	\end{minipage}
	\begin{minipage}[t]{\columnwidth}
	\includegraphics[width=1\columnwidth]{./figure/random_N_obstacles/overtaking_random_1.pdf}
	\end{minipage}
	\caption{Simulations of overtaking with $N = 2,3,4$ moving obstacles that drive in the opposite direction with respect to the ATLASCAR2.}
	\label{fig:obstacleAvoidance_random}
\end{figure}

The vehicle is capable of overtaking the obstacles on the right or left depending on their positions with respect to the road. If the $y$-coordinate of the closest obstacle is greater than 0, then the vehicle overtakes to the right, otherwise the overtaking takes place on the left lane. We also hypothesized that the obstacles move at different speeds but that they are initially at a common distance; they can have a uniform motion or a uniformely accelerated motion. In case two obstacles are too close during the simulation and their distance is less than the detection range, which is \SI{30}{m}, the ATLASCAR2 perceives the objects as a single entity and adapts to the situation. The same test can be done with the obstacles that drive in the same direction as the vehicle but to better assess and demonstrate results we decided to show a very unusual scenario.

\subsubsection{Vehicle Braking and Obstacles Overtaking}
Finally we have improved the code related to the mixed Input/Output constraints so that in the case there are 3 obstacles that block the road and drive at a lower speed than the ATLASCAR2, the velocity of the vehicle decreases in order to prevent the collision. Figure \ref{fig:braking} depicts a simulation in which there are 3 obstacles at the same $x$-coordinate. Two obstacles have a constant speed of \SI{8}{m/s} while the one on the left lane of \SI{15}{m/s}.
In this particular case it is essential to consider the fourth and the fifth restriction in order to allow the ATLASCAR2 to slow down without colliding with the cars in front. The fifth constraint is simply the position of the ATLASCAR2 that updates at each interval, while the fourth constraint, until there is a free lane, is the position of the closest obstacle (both the positions are with respect to the global reference frame). In the calculation of the fourth constraint is necessary  to consider the speed at which the vehicle and the obstacle are moving in order to keep a safe distance. In particular three parameters have been identified as the key
factors computing the safe distance between cars:
\begin{itemize}
	\item detection range of the ATLASCAR2;
	\item velocities of the vehicle and the obstacle;
	\item distance between the cars.
\end{itemize}
\begin{figure}[!h]
	\centering
	\begin{minipage}[t]{\columnwidth}
		\includegraphics[width=\columnwidth]{./figure/three_obstacles_no_overtaking/braking_0.pdf}
	\end{minipage}
	\begin{minipage}[t]{\columnwidth}
		\includegraphics[width=\columnwidth]{./figure/three_obstacles_no_overtaking/braking_1.pdf}
	\end{minipage}
	\begin{minipage}[t]{\columnwidth}
		\includegraphics[width=\columnwidth]{./figure/three_obstacles_no_overtaking/braking_2.pdf}
	\end{minipage}
	\begin{minipage}[t]{\columnwidth}
		\includegraphics[width=\columnwidth]{./figure/three_obstacles_no_overtaking/braking_3.pdf}
	\end{minipage}
	\begin{minipage}[t]{\columnwidth}
		\includegraphics[width=\columnwidth]{./figure/three_obstacles_no_overtaking/braking_4.pdf}
	\end{minipage}
	\begin{minipage}[t]{\columnwidth}
		\includegraphics[width=\columnwidth]{./figure/three_obstacles_no_overtaking/braking_5.pdf}
	\end{minipage}
	\begin{minipage}[t]{\columnwidth}
		\includegraphics[width=\columnwidth]{./figure/three_obstacles_no_overtaking/braking_6.pdf}
	\end{minipage}
	\caption{Simulation of braking and overtaking obstacles.}
	\label{fig:braking}
\end{figure}

At the beginning, the vehicle moves with the reference velocity of $v=\SI{20}{m/s}$. When the ATLASCAR2 detects all the other cars on the road, checks if there is a free lane. In the first part of the simulation, the ATLASCAR2 brakes because there is not enough space for overtaking the cars as shown in Fig. \ref{fig:velocity_braking}. A collision would happen if the vehicle continues to follow the initially planned path with the reference velocity. It is possible to notice that the speed decreases because the applied throttle is negative, so a consistent deceleration is set after $\approx\SI{1.5}{s}$ as depicted in Fig. \ref{fig:throttle_braking}. The velocity of the ATLASCAR2 for $\approx\SI{2}{s}$ adapts to that of the closest obstacle. After a few seconds the fastest car moves and makes available the left lane for overtaking. Dramatic changes of steering angle in early stage are observed in Fig. \ref{fig:delta_braking} and consequently also on the heading angle in Fig. \ref{fig:theta_braking}. Then, the ATLASCAR2 returns to the reference velocity during the overtaking of the two obstacles (the applied throttle after $\approx\SI{5}{s}$ is positive). It is seen that the ATLASCAR2 avoids the obstacles and returns to the road center line with a low overshoot.
\begin{figure*}[!t] %vs changes to t instead of b
	\begin{minipage}[t]{\columnwidth}
		\includegraphics[width=\columnwidth]{./figure/three_obstacles_no_overtaking/VelocityVsTime.pdf}
		\vspace{-17pt}
		\subcaption{}\label{fig:velocity_braking}
	\end{minipage}
	\begin{minipage}[t]{\columnwidth}
		\includegraphics[width=\columnwidth]{./figure/three_obstacles_no_overtaking/ThrottleVsTime.pdf}
		\vspace{-17pt}
		\subcaption{}\label{fig:throttle_braking}
	\end{minipage}
	\begin{minipage}[t]{\columnwidth}
	    \includegraphics[width=\columnwidth]{./figure/three_obstacles_no_overtaking/SteeringAngleVsTime.pdf}
	    \vspace{-17pt}
	    \subcaption{}\label{fig:delta_braking}
	\end{minipage}
	\begin{minipage}[t]{\columnwidth}
	    \includegraphics[width=\columnwidth]{./figure/three_obstacles_no_overtaking/HeadingAngleVsTime.pdf}
	    \vspace{-17pt}
	    \subcaption{}\label{fig:theta_braking}
	\end{minipage}
	\caption{Time signals of the ATLASCAR2 in the simulation of braking and overtaking in the situation illustrated in Fig. \ref{fig:braking}.}
	\label{fig:components}
\end{figure*}

\section{Lane Following System}
\subsection{Problem Formulation}
A lane-following system is a control system that keeps the vehicle traveling along the centerline of a highway lane, while maintaining a user-set velocity. Figure \ref{fig:laneFollowing} illustrates a typical lane following scenario.
\begin{figure}[!h]
	\centering
	\includegraphics[width=0.75\columnwidth]{./figure/laneFollowing/laneFollowing.pdf}
	\caption{Problem description of a lane following system.}
	\label{fig:laneFollowing}
\end{figure}
In a classic lane keeping assist, it is assumed that the longitudinal velocity is constant \cite{borelli3}. This restriction is relaxed in this model because the longitudinal acceleration varies in this MIMO control system. This lane-following system manipulates both the longitudinal acceleration and the front steering angle of the vehicle to keep the lateral deviation and the relative yaw angle small and the longitudinal velocity close to a driver set velocity. If these two goals cannot be met at the same moment, the system tries to balance them. The model that we are considering contains many parameters. The first fundamental block describes the vehicle dynamics: we have applied the bicycle model of lateral vehicle dynamics and approximate the longitudinal dynamics using a time constant obtaining  a linear model.
\subsubsection{Longitudinal dynamics}
We can use the following state space to describe the longitudinal model:
\begin{equation}
\label{eqn:longi_dynamics_simple_model_ss}
\begin{array}{ll}
\dot{\vec{x}}_{\text{lon}} =\vec{A}_m \vec{x}_{\text{lon}}+ \vec{B_m}\vec{u}_{\text{lon}}\\
\vec{y}_{\text{lon}} =\vec{C_m} \vec{x}_{\text{lon}} + \vec{D_m} \vec{u}_{\text{lon}}
\end{array}
\end{equation}
where the input is the acceleration and the states are the longitudinal velocity and the actual acceleration which is also the only output of this system.
\begin{equation*}
\vec{x}_{\text{lon}} = \begin{bmatrix}
\dot{V}_x&V_x
\end{bmatrix}^T,
\qquad
\vec{u}_{\text{lon}} = a
\end{equation*}
and
\[ 
\vec{A_m}=\begin{bmatrix}
-\frac{1}{\tau}&0\\1&0
\end{bmatrix},
\quad
\vec{B_m}=\begin{bmatrix}
\frac{1}{\tau}\\
0
\end{bmatrix},
\]
\[
\vec{C_m}=\begin{bmatrix}
1&0
\end{bmatrix}, 
\quad
\vec{D_m}=0.
\]
where $\tau$ is a time constant \cite{long_tf}; in practice we are considering a second order transfer function like in \cite{longitudinal}.
\subsubsection{Lateral dynamics}
Local function: we have a continuous vehicle lateral model from parameters obtained by simplifying the one in \cite{rathai}: 
\begin{equation}
\label{eqn:lateral_dynamics_simple_model}
\begin{array}{ll}
\dot{\vec{x}}_{\text{lat}} =\vec{A}_g \vec{x}_{\text{lat}}+ \vec{B}_g \vec{u}_{\text{lat}}\\
\vec{y}_{\text{lat}} =\vec{C}_g \vec{x}_{\text{lat}} + \vec{D}_g \vec{u}_{\text{lat}}
\end{array}
\end{equation}
where the input is the steering angle in radians, and the outputs are the lateral velocity in meters per second and yaw angle rate in radians per second:
\begin{equation*}
\vec{x}_{\text{lat}} = \begin{bmatrix}
V_y&\dot{\psi}
\end{bmatrix}^T
\qquad
\vec{u}_{\text{lat}} = \delta
\end{equation*}
and
\[ 
\vec{A}_g=\begin{bmatrix}
-\frac{2C_F+2C_R}{mV_x}&-\frac{2C_Fl_F-2C_Rl_R}{mV_x} - V_x\\
-\frac{2C_Fl_F-2C_Rl_R}{I_ZV_x}&-\frac{2C_Fl_F^2+2C_Rl_R^2}{I_ZV_x}
\end{bmatrix},
\]
\[
\vec{B}_g=\begin{bmatrix}
2C_F/m\\
2C_Fl_F/I_Z
\end{bmatrix},
\quad
\vec{C}_g=\vec{I}_2, 
\quad
\vec{D}_g=\vec{0}_{2\times1}.
\]
The parameters in the previous matrices are:
\begin{itemize}
	\item $V_x$ is the longitudinal velocity of the car;	
	\item $m$ is the total mass parameter; 
	\item $I_Z$ is the yaw moment of inertia parameter;
	\item $l_F$ and $l_R$ are the longitudinal distances from center of gravity to front and rear tires parameters;
	\item $C_F$ and $C_R$ are the cornering stiffnesses of front and rear tires parameters.
\end{itemize}
The goal for the driver steering model is to keep the vehicle in its lane and follow the curved road by controlling the front steering angle . This goal is achieved by driving the yaw angle error $e_2 = \psi -\psi_{\text{des}}$ and lateral displacement error $e_1$ to zero ($\dot{e}_1 = V_xe_2+V_y$). We can incorporate these two paramenters in the augmented model:
\begin{equation}
\label{eqn:lateral_dynamics_augmented_model}
\begin{array}{ll}
\dot{\vec{x}}_{\text{aug}} =\vec{A}_a \vec{x}_{\text{aug}}+ \vec{B}_a \vec{u}_{\text{aug}}\\
\vec{y}_{\text{aug}} = \vec{C}_a \vec{x}_{\text{aug}} + \vec{D}_a \vec{u}_{\text{aug}}
\end{array}
\end{equation}
where
\begin{equation*}
\vec{x}_{\text{aug}} = \begin{bmatrix}
V_y&\dot{\psi}&e_1&e_2
\end{bmatrix}^T,
\qquad
\vec{u}_{\text{aug}} = 
\begin{bmatrix}
\delta&\dot{\psi}_{\text{des}}
\end{bmatrix}^T
\end{equation*}
and
\[ 
\vec{A}_a=\begin{bmatrix}
\vec{A}_g&\vec{0}_{2\times2}\\
\vec{I}_2&\begin{matrix}
0&V_x\\
0&0
\end{matrix}
\end{bmatrix},
\quad
\vec{B}_a=\begin{bmatrix}
\vec{B}_g&\vec{0}_{2\times1}\\
0&0\\
0&-1
\end{bmatrix},
\]
\[
C_a=\begin{bmatrix}
\vec{0}_{2\times2}&\vec{I}_2
\end{bmatrix}, 
\quad
D_a=
\vec{0}_{2\times2}. 
\]
Combining (\ref{eqn:longi_dynamics_simple_model_ss}) with (\ref{eqn:lateral_dynamics_augmented_model}) yields the state-space model that characterizes the Model Predictive Controller:
\begin{equation}
\label{eqn:full_dynamics_model}
\begin{array}{ll}
\dot{\vec{x}}_{\text{tot}} = \vec{A}_f \vec{x}_{\text{tot}}+ \vec{B}_f \vec{u}_{\text{tot}}\\
\vec{y}_{\text{tot}} = \vec{C}_f \vec{x}_{\text{tot}} + \vec{D}_f \vec{u}_{\text{tot}}
\end{array}
\end{equation}
where
\begin{equation*}
\vec{x}_{\text{tot}} = \begin{bmatrix}
\dot{V}_x\\V_x\\V_y\\\dot{\psi}\\e_1\\e_2
\end{bmatrix},
\qquad
\vec{u}_{\text{tot}} = 
\begin{bmatrix}
a\\\delta\\\dot{\psi}_{\text{des}}
\end{bmatrix}
\end{equation*}
and
\[ 
\vec{A}_f=\begin{bmatrix}
\vec{A}_m&\vec{0}_{2\times4}\\
\vec{0}_{4\times2}&\vec{A}_a
\end{bmatrix},
\quad
\vec{B}_f=\begin{bmatrix}
\vec{B}_m&\vec{0}_{2\times2}\\
\vec{0}_{4\times1}&\vec{B}_a
\end{bmatrix},
\]
\[
\vec{C}_f=\begin{bmatrix}
\vec{C}_m&\vec{0}_{1\times4}\\
\vec{0}_{2\times2}&\vec{C}_a
\end{bmatrix}, 
\quad
\vec{D}_f=\vec{0}_{3\times3}. 
\]
However the system to be controlled is usually modeled by a linear discrete state-space model:
\begin{equation*}
\label{eqn:full_dynamics_model_disc}
\begin{array}{rr}
{\vec{x}}_{\text{tot}}(k+1) =\vec{A} \vec{x}_{\text{tot}}(k)+ \vec{B} \vec{u}_{\text{tot}}(k)\\
\vec{y}_{\text{tot}}(k) = \vec{C}\vec{x}_{\text{tot}}(k) + \vec{D} \vec{u}_{\text{tot}}(k)
\end{array}
\end{equation*}
where $\vec{A}$ and $\vec{B}$ are the state and control matrices for the discrete state-space equation, respectively, which can be calculated, also in this case, with the Euler method as:
\[
\vec{A} = e^{\vec{A}_fT_s},\qquad \vec{B} = \int_{kT_s}^{(k+1)T_s} e^{\vec{A}_f[(k+1)T_s-\eta]}\vec{B}_f d\eta
\]
where $T_s$ is the sampling interval for the discrete state-space model. The matrices $\vec{C}$ and $\vec{D}$ are equivalent to those in the continuous case.

\subsection{Design of Adaptive Model Predictive Control}
We created an Adaptive MPC controller with a prediction model that has six states, three outputs (longitudinal velocity, lateral deviation, relative yaw angle), and two manipulated signals (acceleration and steering). 
The objective of the trajectory planning along specified path can be described as follows: given a path which the vehicle is expected to follow design a trajectory of a car-vehicle configuration.
In order to do this, according with \cite{curvature} it is possible to derive the road curvature and its derivative.
The product of the road curvature and the longitudinal velocity is modeled as a measured disturbance. We have set the constraints for manipulated variables and the scale factors. Moreover we have specified the weights in the standard MPC cost function. The third output, yaw angle, is allowed to float because there are only two manipulated variables to make it a square system. In this controller, there is no steady-state error in the yaw angle as long as the second output, lateral deviation, reaches 0 at steady state. Finally we have also penalized acceleration change more for smooth driving experience. This controller uses a linear model for the vehicle dynamics and updates the model online as the longitudinal velocity varies.

\subsection{Simulation Results}
The proposed adaptive MPC algorithm is designed in the MATLAB/Simulink and validated through simulation. The objective of this test is to evaluate the behavior of the proposed control strategy in critical situations.
Table 3 shows the parameters used in the lane following simulation.
\begin{table}[!h]
	\centering
	\begin{tabular}{|c|c|}
		\hline
		Parameters          & Values      \\
		\hline
		$m$          & \SI{1575}{kg}              \\
		$I_z$         & \SI{2875}{kgm^2}               \\
		$l_F$           & \SI{1.2}{m}               \\
		$l_R$         & \SI{1.6}{m}               \\
		$C_F$          & \SI{19000}{\newton/rad}      \\
		$C_R$           & \SI{33000}{\newton/rad}  \\
		$\tau$             & 0.2                \\
		$V_0$           & \SI{15}{m/s}       \\
		$V_{\text{set}}$          & \SI{20}{m/s}   \\
		$T_s$         & \SI{0.02}{s}          \\
		\hline
	\end{tabular}
\end{table}

Figures \ref{fig:reference_laneFollowing} and \ref{fig:curvature_laneFollowing} show the desired path that the car must follow and its curvature, where the former is described in terms of the lateral position $Y_{\text{ref}}$ as function of the longitudinal position $X_{\text{ref}}$ and the latter is derived according with \cite{curvature}. The ATLASCAR2 is controlled to follow a sinusoidal trajectory which is given as follows:
\begin{equation*}
X_\text{ref}=V_x\cdot t, \quad Y_\text{ref}=5\sin(X_\text{ref}/20)\quad \text{with}\quad t\in[0,20]\SI{}{s}
\end{equation*}
\begin{figure}[!t]
	\centering
	\begin{minipage}[t]{\columnwidth}
		\includegraphics[width=\columnwidth]{../../MATLAB/lane_following/figure/Reference.pdf}
		\vspace{-17pt}
		\subcaption{}
		\label{fig:reference_laneFollowing}
	\end{minipage}
	\begin{minipage}[t]{\columnwidth}
		\includegraphics[width=\columnwidth]{../../MATLAB/lane_following/figure/Curvature.pdf}
		\vspace{-17pt}
		\subcaption{}
		\label{fig:curvature_laneFollowing}
	\end{minipage}
	\caption{Desired path and curvature of the ATLASCAR2 in a simulation of \SI{20}{s}}
	\label{fig:laneFollowing_desired}
	\vspace{-30pt}
\end{figure}

Moreover the following figures show the trend of the main parameters confirming that the control strategy used allows the vehicle to follow the path. In particular we simulated also a small error in the sensor dynamics in order to make the simulation more realistic: we added a 3 percent error to the longitudinal velocity and this is evident from the small noise in the graphs of the steering angle (Fig.\ref{fig:steering_laneFollowing}) and the lateral deviation (Fig.\ref{fig:lateral_deviation_laneFollowing}).
Figure {\ref{fig:longitudinal_velocity_laneFollowing}} shows the evolution of the vehicle longitudinal velocity. At the start of the simulation, this velocity is equal to the initial condition for longitudinal velocity parameter $V_0$. At run time, we can note that $V_x$ reaches the predefined value of \SI{20}{m/s} meters for second and then it stabilizes near the cruising speed because it continues to vary the steering angle to adapt to the path to be followed. Finally we presents the overall scheme for the lane following developted in Simulink depicted in Figure \ref{fig:scheme_lane_following}.
\begin{figure*}[!t]
\centering
\begin{minipage}[t]{\columnwidth}
	\includegraphics[width=\columnwidth]{../../MATLAB/lane_following/figure/LongitudinalVelocityVsTime.pdf}
	\subcaption{Longitudinal velocity $V_x$ with respect to time.}
	\label{fig:longitudinal_velocity_laneFollowing}
\end{minipage}
\begin{minipage}[t]{\columnwidth}
	\includegraphics[width=\columnwidth]{../../MATLAB/lane_following/figure/AccelerationVsTime.pdf}
	\subcaption{Acceleration $u_1$ with respect to time.}
	\label{fig:acceleration_laneFollowing}
\end{minipage}
\begin{minipage}[t]{\columnwidth}
	\includegraphics[width=\columnwidth]{../../MATLAB/lane_following/figure/SteeringAngleVsTime.pdf}
	\subcaption{Steering angle $u_2$ with respect to time.}
	\label{fig:steering_laneFollowing}
\end{minipage}
%\begin{minipage}[t]{\columnwidth}
%	\includegraphics[width=\columnwidth]{../../MATLAB/lane_following/figure/RelativeYawAngleVsTime.pdf}
%	\subcaption{Relative yaw angle $e_2$ with respect to time.}
%	\label{fig:relative_yaw_angle_laneFollowing}
%\end{minipage}
\begin{minipage}[t]{\columnwidth}
	\includegraphics[width=\columnwidth]{../../MATLAB/lane_following/figure/LateralDeviationVsTime.pdf}
	\subcaption{Lateral deviation $e_1$ with respect to time.}
	\label{fig:lateral_deviation_laneFollowing}
\end{minipage}
\caption{Time signals of the ATLASCAR2 in the simulation with a sinusoidal path}
\label{fig:laneFollowing_signals}
\end{figure*}

\begin{figure*}[!b]
	\centering
	\includegraphics[width=1\textwidth]{./figure/lane_following_AMPC.pdf}
	\caption{Overall procedure scheme lane following.}
	\label{fig:scheme_lane_following}
\end{figure*}
\section{Conclusions and Future Work}
This report proposes two advanced methods for short term motion planning of an autonomous car based on adaptive Model Predictive Control. The first component is an obstacle avoidance system that moves the vehicle around different moving obstacles in the lane using throttle and steering angle. This system updates both the predictive model and the mixed input/output constraints at each control interval. The vehicle is also able to brake in order to prevent collisions against closest obstacles. Instead, in the second scheme  we have developed a lane following system that keeps the ATLASCAR2 traveling along the centerline of the lanes on the road by adjusting the front steering angle of the car.  The flexibility of the concepts used in the algorithms allows a multitude of refinements and extensions to this work. The future work includes the combination of these two control strategies in a way that they can operate simultaneously. Next expected steps include the migration to ROS-Gazebo simulation environment and, later on, the usage of real data collected on board the ATLASCAR2 and, ultimately, test it in a real autonomous driving scenario.

\balance

\begin{thebibliography}{00}

	\bibitem{RRT}Kuwata, Y., Fiore, G. A., Teo, J., Frazzoli, E., and How, J. P., “Motion Planning for Urban Driving using RRT,” Proceedings of the IEEE International Conference on Intelligent Robots and Systems, Nice, France: 2008, pp. 1681–1686.

	\bibitem{potential}Lei Tang, Songyi Dian, Gangxu Gu, Kunli Zhou, Suihe Wang and Xinghuan Feng, "A novel potential field method for obstacle avoidance and path planning of mobile robot," 2010 3rd International Conference on Computer Science and Information Technology, Chengdu, 2010, pp. 633-637.

	\bibitem{meta-heuristic}Hussein, H. Mostafa, M. Badrel-Din, O. Sultan, and A. Khamis, "Metaheuristic optimization approach to mobile robot path planning," in 1st International Conference on Engineering and Technology (ICET), New Cairo, Egypt, 2012.

	\bibitem{borelli2}Y. Gao, T. Lin, F. Borrelli, E. Tseng, and D. Hrovat, "Predictive control of autonomous ground vehicles with obstacle avoidance on slippery roads," in Proceedings of Dynamic Systems and Control Conference (DSCC), 2010.

	\bibitem{nonlinearmpc}L. Grune and J. Pannek, in Nonlinear Model Predictive Control: Theory and Algorithms. Springer London, 2011, pp. 43-66

	\bibitem{skoda}J. Škoda, ‘3D Navigation for Mobile Robots’, Dissertation, 2017.

	\bibitem{fuzzyMPC}Y. Nishio, K. Nonaka and K. Sekiguchi, "Moving obstacle avoidance control by fuzzy potential method and model predictive control," 2017 11th Asian Control Conference (ASCC), Gold Coast, QLD, 2017, pp. 1298-1303.

	\bibitem{NONMPC}Yu, S., Li, X., Chen, H. and Allgöwer, F. (2015), "Nonlinear model predictive control for path following problems". Int. J. Robust Nonlinear Control, 25: 1168–1182.

	\bibitem{safety}T. Xu and H. Yuan, "Autonomous vehicle active safety system based on path planning and predictive control," 2016 35th Chinese Control Conference (CCC), Chengdu, 2016, pp. 8889-8895.

	\bibitem{archi}M. Nolte, M. Rose, T. Stolte and M. Maurer, "Model predictive control based trajectory generation for autonomous vehicles — An architectural approach," 2017 IEEE Intelligent Vehicles Symposium (IV), Los Angeles, CA, 2017, pp. 798-805.

	\bibitem{MMPC}J. Ji, A. Khajepour, W. W. Melek and Y. Huang, "Path Planning and Tracking for Vehicle Collision Avoidance Based on Model Predictive Control With Multiconstraints," in IEEE Transactions on Vehicular Technology, vol. 66, no. 2, pp. 952-964, Feb. 2017.

	\bibitem{autoMPC}J. V. Frasch et al., "An auto-generated nonlinear MPC algorithm for real-time obstacle avoidance of ground vehicles," 2013 European Control Conference (ECC), Zurich, 2013, pp. 4136-4141.

	\bibitem{borelli}V. Turri, A. Carvalho, H. E. Tseng, K. H. Johansson and F. Borrelli, "Linear model predictive control for lane keeping and obstacle avoidance on low curvature roads," 16th International IEEE Conference on Intelligent Transportation Systems (ITSC 2013), The Hague, 2013, pp. 378-383.

	\bibitem{borelli3}Monimoy Bujarbaruah, Xiaojing Zhang, H. Eric Tseng, Francesco Borrelli; Adaptive MPC for Autonomous Lane Keeping, 14th International Symposium on Advanced Vehicle Control (AVEC), Beijing, China, July 2018
%	\bibitem{atlas}ATLAS  Project,  Aveiro  University, Portugal, \url{http://atlas.web.ua.pt/}, last visited July 2010.

	\bibitem{atlascar1}V. Santos et al., "ATLASCAR - technologies for a computer assisted driving system on board a common automobile", 13th International IEEE Conference on Intelligent Transportation Systems, Funchal, 2010, pp. 1421-1427.

	\bibitem{atlascar2}V. Santos, "ATLASCAR: A Sample of the Quests and Concerns for Autonomous Cars", Informatics in Control, Automation and Robotics: 14th International Conference, ICINCO 2017 Madrid, Spain, Revised Selected Papers (in press March 2019).

    \bibitem{ricardo}R. Silva, "Navegação Local do ATLASCAR2 para Condução Autónoma e Assistência ao Condutor", Dissertação de mestrado. Departamento de Engenharia Mecanica, Universidade de Aveiro, 2018.

	\bibitem{siciliano}B. Siciliano, L. Sciavicco, L. Villani, and G. Oriolo. "Robotics: Modelling, Planning and Control", Springer Publishing Company, Incorporated, 2008.

	\bibitem{onlineMPC}M. Werling and D. Liccardo, "Automatic collision avoidance using model-predictive online optimization," 2012 IEEE 51st IEEE Conference on Decision and Control (CDC), Maui, HI, 2012, pp. 6309-6314.

	\bibitem{swarms}Wei Xi and J. S. Baras, "MPC based motion control of car-like vehicle swarms," 2007 Mediterranean Conference on Control \& Automation, Athens, 2007, pp. 1-6.

	\bibitem{long_tf}Y. Wang, Y. Bin and K. Li, "Longitudinal acceleration tracking control of low speed heavy-duty vehicles," in Tsinghua Science and Technology, vol. 13, no. 5, pp. 636-643, Oct. 2008.

	\bibitem{mpctoolbox}A. Bemporad, M. Morafi, and N. Ricker, Model Predictive Control Toolbox User’s Guide, The MathWorks, Inc.,

		\url{https://www.mathworks.com/help/pdf_doc/mpc/mpc_ug.pdf}

	%\bibitem{theory}J. Rawlings, D. Mayne (2010), "Model Predictive Control: Theory and Design", Nob Hill Publishing.

	%\bibitem{backward}C. Son and C. Ahn, "Vehicle backward driving control with obstacle avoidance," 2015 15th International Conference on Control, Automation and Systems (ICCAS), Busan, 2015, pp. 1771-1774.

	%\bibitem{zhou}H. Zhou, L. Güvenç and Z. Liu, "Design and evaluation of path following controller based on MPC for autonomous vehicle," 2017 36th Chinese Control Conference (CCC), Dalian, 2017, pp. 9934-9939.

	%\bibitem{yu} Z. T. Yu, Obstacle Avoidance for Autonomous Vehicle Driving on Highways Based on MPC, JinLin University, 2012.

	%\bibitem{berger}Berger, Niels. (2018). Lane Change Path Planning With state-dependent safety constraints using Nonlinear Model Predictive Control.

	%\bibitem{kth_thilen}E. Thilén, ‘Robust Model Predictive Control for Autonomous Driving’, Dissertation, 2017.

	\bibitem{rathai}Murali Madhavan Rathai, Karthik \& Amirthalingam, Jegan \& Jayaraman, Balaji. (2017). Robust tube-MPC based lane keeping system for autonomous driving vehicles. 1-6.

	%\bibitem{kth_nordell}B. Nordell, ‘Trajectory Planning for Autonomous Vehicles and Cooperative Driving’, Dissertation, 2016.

	%\bibitem{shen}C. Shen, H. Guo, F. Liu and H. Chen, "MPC-based path tracking controller design for autonomous ground vehicles," 2017 36th Chinese Control Conference (CCC), Dalian, 2017, pp. 9584-9589.

	%\bibitem{matsumoto}N. Wada and T. Matsumoto, "Driver assistance for collision avoidance by constrained MPC," 2017 56th Annual Conference of the Society of Instrument and Control Engineers of Japan (SICE), Kanazawa, 2017, pp. 90-93.

	\bibitem{longitudinal}Filip, Jan. (2018). Trajectory Tracking for Autonomous Vehicles.

	\bibitem{curvature}Danwei Wang, Feng Qi, "Trajectory planning for a four-wheel-steering vehicle," 2001 International Conference on Robotics and Automation, Seoul, Korea, 2001
\end{thebibliography}

\end{document}

### 2019-02-13 Thesis_Latex/FinalReport/figure/flowchart/flowchart.tex
update path planning, Paper, Final Report

--- 2019-02-04 Thesis_Latex/Paper/figure/flowchart/flowchart.tex
@@
 	% Define block styles
-\tikzstyle{decision} = [diamond, draw, fill=blue!20, 
-    text width=4.5em, text badly centered, node distance=3cm, inner sep=0pt]
-\tikzstyle{block} = [rectangle, draw, fill=green!20, 
+	\tikzstyle{decision} = [diamond, draw, fill=blue!10, 
+	text width=4.5em, text centered, node distance=3cm, inner sep=0pt]
+	\tikzstyle{block} = [rectangle, draw, fill=green!10, 
 	text width=5em, text centered, rounded corners, minimum height=4em]
 	\tikzstyle{line} = [draw, -latex']
-\tikzstyle{cloud} = [draw, ellipse,fill=red!20, node distance=3cm,
+	\tikzstyle{cloud} = [draw, ellipse,fill=red!10, node distance=3cm,
 	minimum height=2em]
 
-\begin{tikzpicture}[node distance = 3.3cm, auto]
+	\begin{tikzpicture}[font={\small\sffamily}, node distance = 3cm, auto, scale=0.75,every node/.style={transform shape}]
 	% Place nodes
@@
 		detected?}; 
-    \node [cloud,right of=detection] (start) {Start};
+	\node [cloud,left of=detection] (start) {Start};
 	\node [decision,below of=detection] (multiObstacles) {Multiple Obstacles detected?};
-	\node [block,left of=detection] (reference) {Follow Path: stick to the lane};
-    \node [block,below of=multiObstacles] (distance) {Distance to closest obstacle};
-    \node [block,right of=multiObstacles] (distances) {Distance between the obstacles};
+	\node [block,right of=detection] (reference) {Follow Path: stick to the lane};
+	\node [block,left of=multiObstacles] (distance) {Obtain distance to closest obstacle};
+	\node [block,right of=multiObstacles] (distances) {Obtain distance between the obstacles};
 	\node [decision,below of=distances](space) {Free Space for Overtaking?};
-    \node [block,right of=space](braking){Braking/ Ostacle Velocity};
+	\node [block,right of=space,node distance=3.3cm](braking){Braking/ Ostacle Velocity};
 	\node [block,below of=space](free){Overtaking on free lane};
-    \node [decision,below of=distance] (decisionOvertaking) {Left w.r.t vehicle?};
-    \node [block, below of=decisionOvertaking] (rightOver) {Right Overtaking};     
-    \node [block, left of=decisionOvertaking] (leftOver) {Left Overtaking};
+	\node [decision,below of=distance,node distance=2.5cm] (decisionOvertaking) {Left w.r.t vehicle?};
+	\node [block, below of=decisionOvertaking,node distance=2.5cm] (rightOver) {Right Overtaking};     
+	\node [block, right of=decisionOvertaking] (leftOver) {Left Overtaking};
 

### 2019-02-13 Thesis_Latex/Paper/Paper_released/PaperFinalVersion.tex
update path planning, Paper, Final Report

--- 2019-02-13 Thesis_Latex/FinalReport/FinalReport.tex
@@
 
-\title{Local Path Planning with Moving Obstacle Avoidance based on adaptive MPC in ATLASCAR2}
+\title{Short-term Path Planning with Multiple Moving Obstacle Avoidance based on Adaptive MPC}
 \author{
@@
 	\href{mailto:alberto.franco@ua.pt}{alberto.franco@ua.pt}}
-	}
+	\and
+    \IEEEauthorblockN{Vitor Santos}
+	\IEEEauthorblockA{Department of Mechanical Engineering,\\ IEETA, Universidade de Aveiro, Portugal\\ \href{mailto:vitor@ua.pt}{vitor@ua.pt}}}
 
@@
 \begin{abstract}
-	This report presents two different strategies for a self-driving car short-term path planning among multiple moving obstacles.
+	This paper presents a different strategy for a self-driving car short-term path planning among multiple moving obstacles.
 The main task is to study and implement a motion planning and execution framework in order to make ATLASCAR2 coexist with other moving obstacle vehicles by avoiding collision and overtake them when necessary and possible.
-The proposed techniques, based on the Model Predictive Control paradigm, solve optimization problems formulated in terms of cost minimization under constraints.
-Simulation results demonstrate and verify the feasibility and the usefulness of methods considering different scenarios, opening space for real scenario implementation.
+The proposed technique, based on the Model Predictive Control paradigm, solves an optimization problem formulated in terms of cost minimization under constraints.
+Simulation results demonstrate and verify the feasibility and the usefulness of the method considering different scenarios, opening space for real scenario implementation.
 \end{abstract}
@@
 This approach can be used in an closed-loop with a feedback controller for a stronger solution regarding to the Model Predictive Control (MPC).
-A prior research about obstacle avoidance using MPC in UGVs is described in \cite{borelli} while the applications of nonlinear MPC to ground vehicles is described and evaluated in \cite{nonlinearmpc}.
-\section{Context and Proposed Solution}
-
-The proposed algorithms were studied for the ATLASCAR project in which the group for Robotics and Automation at the University of Aveiro has setup and adapted a common commercial vehicle to provide a versatile  framework  to  develop  studies  and  research %\cite{atlas}
-\cite{atlascar1} \cite{atlascar2}.
-Figure \ref{fig:atlascar2} shows the chosen platform for the second generation of ATLASCAR, which is an electric car, a Mitsubishi iMiEV with a range of a \SI{100}{km}.
-\begin{figure}[!h]
+A prior research about obstacle avoidance using MPC in UGVs is dscribed in \cite{borelli} while the applications of nonlinear MPC to ground vehicles is described and evaluated in \cite{nonlinearmpc}.
+\begin{figure}[b]
 	\centering
@@
 \end{figure}
+\section{Context and Proposed Solution}
+The proposed algorithm was studied for the ATLASCAR project in which the group for Robotics and Automation at the University of Aveiro has setup and adapted a common commercial vehicle to provide a versatile  framework  to  develop  studies  and  research %\cite{atlas}
+\cite{atlascar1} \cite{atlascar2}.
+Figure \ref{fig:atlascar2} shows the chosen platform for the second generation of ATLASCAR, which is an electric car, a Mitsubishi iMiEV with a range of a \SI{100}{km}.
+The fact that the vehicle is electric allows to use the energy stored in the batteries, making it easier to power the sensors installed.
 
-The fact that the vehicle is electric allows to use the energy stored in the batteries, making it easier to power the sensors installed.
-In fact, the ATLACAR2 is equipped with sensors, such as lidar, that measure the distance to obstacles in front and around the vehicle.
+The ATLACAR2 has sensors, such as lidar, that measure the distance to obstacles in front and around the vehicle.
 The obstacles can be static, such as a large pothole, or moving, such as a moving vehicle on the same or a nearby lane.
@@
 This system uses an adaptive Model Predictive Controller that updates both the predictive model and the mixed input/output constraints at each control interval.
-Moreover we want to develop a lane-keeping assist system for the vehicle: it has a sensor, such as camera or laser, that measures the lateral deviation and relative yaw angle between the centerline of a lane and the ATLASCAR2; it also measures the current lane curvature and its derivative.
-Depending on the curve length that the sensor can view, the curvature in front of the vehicle can be calculated from the current curvature and its derivative.
-This system keeps the autonomous car travelling along the centerline of the lanes on the road by adjusting the front steering angle.
-The goal for lane keeping control is to drive both lateral deviation and relative yaw angle close to zero.
-
-\section{Theoretical background\\ Adaptive Model Predictive Control}
+%\section{Theoretical background\\ Adaptive Model Predictive Control}
+\section{Adaptive Model Predictive Control}
 Model Predictive Control is an advanced method that predicts future behavior using a linear-time-invariant (LTI) dynamic model.
@@
 \end{aligned}
-\end{equation*}
-where the matrices \vec{A}, $\vec{B}_u$, $\vec{B}_v$, $\vec{B}_d$, \vec{C}, $\vec{D}_v$ and $\vec{D}_d$ can vary with time. The other parameters in the previous expression are:
+\end{equation}
+where the matrices \vec{A}, $\vec{B}_u$, $\vec{B}_v$, $\vec{B}_d$, \vec{C}, $\vec{D}_v$ and $\vec{D}_d$ can vary with time. The other parameters in (\ref{eqn:Adaptive_MPC_plant_discrete}) are:
 \begin{itemize}
@@
 It is possible to rewrite the plant model in terms of deviations from the nominal conditions as follows:
-\begin{equation*}
+\begin{equation}
 \label{eqn:Adaptive_MPC_nominal_condition}
@@
 \end{aligned}
-\end{equation*}
-where the matrices \vec{A}, \vec{B}, \vec{C} and \vec{D} are updated with respect to time. The other parameters in the previous structure are:
+\end{equation}
+where the matrices \vec{A}, \vec{B}, \vec{C} and \vec{D} are updated with respect to time. The other parameters in (\ref{eqn:Adaptive_MPC_nominal_condition}) are:
 \begin{itemize}
@@
 The adaptive MPC uses a Kalman filter to update its controller states which include the plant, the disturbance and measurement noise model states.
-In particular this filter is linear-time-varying (LTV) because adjusts the gains at each control
-interval to maintain consistency with the updated plant model.
 \section{Moving Obstacle Avoidance}
@@
 Figure \ref{fig:obstacleAvoidance} illustrates a typical scenario of overtaking of a moving obstacle.
-\begin{figure}[!h]
+%\vspace{-1em}
+\begin{figure}[H]
 	\centering
-	\includegraphics[width=\columnwidth]{./figure/obstacleAvoidance/obstacleAvoidance.pdf}
+	\includegraphics[width=1\columnwidth]{./figure/obstacleAvoidance/obstacleAvoidance.pdf}
+%	\vspace{-10pt}
 	\caption{Problem description of collision avoidance on a road with only two lanes.}
@@
 \end{figure}
-
-The model used in this report should take into account the kinematic and dynamic aspects of the vehicle.
+%\vspace{-0.5em}
+The model used in this paper should take into account the kinematic and dynamic aspects of the vehicle.
 Here, we present a non linear mathematical model of a vehicle used for the development of a collision avoidance system.
 The model has four states and two inputs:
-\begin{equation*} 
+\[ 
 \vec{x}=\begin{bmatrix}
@@
 \end{bmatrix}^\intercal
-\end{equation*}
+\]
 where $(x,y)$ are the global coordinates of the contact point between the rear wheel and the ground, $\theta$ is the heading angle of the car body with respect to the $x$-axis and $v$ is the linear speed of the car (positive).
-The manipulated variables are $T$ the throttle (positive when accelerating/negative when braking) and $\delta$ the steering angle of the front wheel with respect to the vehicle ($0$ when aligned with car, counterclockwise positive).
+The manipulated variables are $T$ the throttle (positive when accelerating/negative when braking) and $\delta$ the steering angle ($0$ when aligned with car, counterclockwise positive).
 Figure \ref{fig:car_model} illustrates the applied nonlinear bicycle model and the related parameters.
@@
 	\centering
-	\includegraphics[width=
-	0.80\columnwidth]{./figure/car_model.pdf}
+	\includegraphics[width=0.70\columnwidth]{./figure/car_model.pdf}
+%	\vspace{-5pt}
 	\caption{Bicycle model of a car, (adapted from \cite{siciliano}).}
@@
 \end{figure}
-
+%\vspace{-0.5em}
 The ATLASCAR2 can be modeled using the non-linear kinematic bicycle model described by the following equations of motion \cite{safety} \cite{swarms}:
@@
 The simple linearized approximation of the system to describe the dynamics of the ATLASCAR2 will be evaluated at the operating conditions.
-Note also that the system we are considering is a linear state-space model whose dynamics vary as a function of certain time-varying parameters.
 The system to be controlled is usually modeled by a discrete state-space model in the MPC literature.
@@
 \end{equation*}
-
 where $\vec{A}_d$ and $\vec{B}_d$ are the state and control matrices for the discrete state-space equation, respectively, which can be calculated with the Euler method as
-\begin{equation*}
+\[
 \vec{A}_d = e^{\vec{A}_cT_s},\qquad \vec{B}_d = \int_{kT_s}^{(k+1)T_s} e^{\vec{A}_c[(k+1)T_s-\eta]}\vec{B}_c d\eta
-\end{equation*}
-
+\]
 where $T_s$ is the sampling interval for the discrete state-space model.
@@
 We create also a safe zone around the obstacles so that the vehicle does not get too close to the obstacle when passing it.
-
 \subsection{Design of Adaptive Model Predictive Control}
@@
 \begin{figure}[H]
+%\vspace{-1em}
 	\centering
+%	\includegraphics[width=1\columnwidth]{./figure/flowchart/flowchart.pdf}
 	\input{./figure/flowchart/flowchart}
+%	\vspace{-15pt}
 	\caption{Behaviour planning conditional flowchart.}
@@
 \end{figure}
-
+%\vspace{-15pt}
 When an obstacle is detected, it defines an area on the road (in terms of constraints) that the ATLASCAR2 must not enter during the prediction horizon.
@@
 Figure \ref{fig:constraint} illustrates the constraints that are computed at each $T_s$ in the case of a left overtaking.
-\begin{figure}[!h]
+\begin{figure}[H]
+%\vspace{-12pt}
 	\centering
-	\includegraphics[width=\columnwidth]{./figure/constraint/constraint.pdf}
+	\includegraphics[width=0.9\columnwidth]{./figure/constraint/constraint.pdf}
+%	\input{./figure/constraint/constraintvs}
 	\caption{Constraints in the case of left overtaking.}
@@
 \end{figure}
-
+%\vspace{-12pt}
 \subsection{Simulation Results}
-The performances of the proposed adaptive MPC based vehicle control method are demonstrated in three simulation examples.
+The performances of the proposed adaptive MPC based vehicle control method are demonstrated in three
+simulation examples.
 We tried to choose parameters that were as close as possible to a real situation: the sampling time used in the discretization of the system is $T_s=\SI{0.02}{s}$ while the values of the prediction and the control horizon are respectively $p_H=25$ and $c_H=5$.
@@
 Blue paths in Figures \ref{fig:obstacleAvoidance_one_obstacle}, \ref{fig:obstacleAvoidance_random}, \ref{fig:braking} are known only at the end of the simulations.
-\begin{figure}[h!]
+%
+\begin{figure}[t]
 	\centering
 	\begin{minipage}[t]{\columnwidth}
-	\includegraphics[width=\columnwidth]{./figure/one_obstacle_right_overtaking/overtaking_start.pdf}
+	\includegraphics[width=1\columnwidth]{./figure/one_obstacle_right_overtaking/overtaking_start.pdf}
 	\end{minipage}
 	\begin{minipage}[t]{\columnwidth}
-	\includegraphics[width=\columnwidth]{./figure/one_obstacle_right_overtaking/overtaking_middle.pdf}
+	\includegraphics[width=1\columnwidth]{./figure/one_obstacle_right_overtaking/overtaking_middle.pdf}
 	\end{minipage}
 	\begin{minipage}[t]{\columnwidth}
-	\includegraphics[width=\columnwidth]{./figure/one_obstacle_right_overtaking/overtaking_middle_end.pdf}
+	\includegraphics[width=1\columnwidth]{./figure/one_obstacle_right_overtaking/overtaking_middle_end.pdf}
 	\end{minipage}
 	\begin{minipage}[t]{\columnwidth}
-	\includegraphics[width=\columnwidth]{./figure/one_obstacle_right_overtaking/overtaking_end.pdf}
+	\includegraphics[width=1\columnwidth]{./figure/one_obstacle_right_overtaking/overtaking_end.pdf}
 	\end{minipage}
+	\vspace{-16pt}
 	\caption{Simulation of right overtaking with one moving obstacle that moves in the same direction as the vehicle.}
@@
 \end{figure}
-
+%
+%
 \begin{algorithm}%[b]
@@
 \ref{fig:obstacleAvoidance_one_obstacle}) the ATLASCAR2 drives in the middle of the center lane while the road is completely free and when there is an obstacle, the vehicle passes it only using the right lane (the same simulation can be launched so that the car goes over to the left fast lane).
-In other words if the ATLASCAR2 is already in the adjacent lane, it uses the safety zone as the constraint, otherwise the vehicle must be above the line formed from the ATLASCAR2 to safe zone corner for right passing.
+%\vspace{-10pt}
+%\vspace{-13pt}
+%\vspace{-7pt}
+
+%If the ATLASCAR2 is already in the adjacent lane, it uses the safety zone as the constraint, otherwise the vehicle must be above the line formed from the ATLASCAR2 to safe zone corner for right passing.
 If the vehicle is parallel to the obstacle, it  uses the safety zone as the constraint and finally if it has passed the obstacle, it uses the inactive constraint to go back to the center lane.
+%\vspace{-5pt}
 Algorithm \ref{alg:rightOvertaking} summarizes the main steps to compute custom constraints for the obstacle; when the vehicle detects the obstacle, the constraints are computed.
-In this simulation only the first three constraints are necessary because there is space for the overtaking without braking (the fourth and fifth constraints don't change).
 %
@@
 For a second test, additional obstacles were added to make the scenario more complex (Fig. \ref{fig:obstacleAvoidance_random}).
-\begin{figure}[!h]
+%\vspace{-17pt}
+\begin{figure}%[t]
 	\centering
@@
 	\end{minipage}
+	\vspace{-21pt}
 	\caption{Simulations of overtaking with $N = 2,3,4$ moving obstacles that drive in the opposite direction with respect to the ATLASCAR2.}
@@
 \end{figure}
-
+%\vspace{-10pt}
 The vehicle is capable of overtaking the obstacles on the right or left depending on their positions with respect to the road.
 If the $y$-coordinate of the closest obstacle is greater than 0, then the vehicle overtakes to the right, otherwise the overtaking takes place on the left lane.
-We also hypothesized that the obstacles move at different speeds but that they are initially at a common distance; they can have a uniform motion or a uniformely accelerated motion.
+We also hypothesized that the obstacles move at different speeds but that they are initially at a common distance.
 In case two obstacles are too close during the simulation and their distance is less than the detection range, which is \SI{30}{m}, the ATLASCAR2 perceives the objects as a single entity and adapts to the situation.
-The same test can be done with the obstacles that drive in the same direction as the vehicle but to better assess and demonstrate results we decided to show a very unusual scenario.
 
+%\vspace{-9pt}
+\begin{figure}%[h]
+	\centering
+	\begin{minipage}[t]{\columnwidth}
+		\includegraphics[width=1\columnwidth]{./figure/three_obstacles_no_overtaking/braking_0.pdf}
+	\end{minipage}
+	\begin{minipage}[t]{\columnwidth}
+		\includegraphics[width=1\columnwidth]{./figure/three_obstacles_no_overtaking/braking_1.pdf}
+	\end{minipage}
+	\begin{minipage}[t]{\columnwidth}
+		\includegraphics[width=1\columnwidth]{./figure/three_obstacles_no_overtaking/braking_2.pdf}
+	\end{minipage}
+%	\begin{minipage}[t]{\columnwidth}
+%		\includegraphics[width=1\columnwidth]{./figure/three_obstacles_no_overtaking/braking_3.pdf}
+%	\end{minipage}
+	\begin{minipage}[t]{\columnwidth}
+		\includegraphics[width=1\columnwidth]{./figure/three_obstacles_no_overtaking/braking_4.pdf}
+	\end{minipage}
+%	\begin{minipage}[t]{\columnwidth}
+%		\includegraphics[width=1\columnwidth]{./figure/three_obstacles_no_overtaking/braking_5.pdf}
+%	\end{minipage}
+	\begin{minipage}[t]{\columnwidth}
+		\includegraphics[width=1\columnwidth]{./figure/three_obstacles_no_overtaking/braking_6.pdf}
+	\end{minipage}	
+	\vspace{-23pt}
+	\caption{Simulation of braking and overtaking obstacles.}
+	\label{fig:braking}
+\end{figure}
+%\vspace{-12pt}
+%
 \subsubsection{Vehicle Braking and Obstacles Overtaking}
@@
 Two obstacles have a constant speed of \SI{8}{m/s} while the one on the left lane of \SI{15}{m/s}.
-In this particular case it is essential to consider the fourth and the fifth restriction in order to allow the ATLASCAR2 to slow down without colliding with the cars in front.
-The fifth constraint is simply the position of the ATLASCAR2 that updates at each interval, while the fourth constraint, until there is a free lane, is the position of the closest obstacle (both the positions are with respect to the global reference frame).
-In the calculation of the fourth constraint is necessary  to consider the speed at which the vehicle and the obstacle are moving in order to keep a safe distance.
-In particular three parameters have been identified as the key
-factors computing the safe distance between cars:
-\begin{itemize}
-	\item detection range of the ATLASCAR2;
-	\item velocities of the vehicle and the obstacle;
-	\item distance between the cars.
-\end{itemize}
-\begin{figure}[!h]
-	\centering
-	\begin{minipage}[t]{\columnwidth}
-		\includegraphics[width=\columnwidth]{./figure/three_obstacles_no_overtaking/braking_0.pdf}
-	\end{minipage}
-	\begin{minipage}[t]{\columnwidth}
-		\includegraphics[width=\columnwidth]{./figure/three_obstacles_no_overtaking/braking_1.pdf}
-	\end{minipage}
-	\begin{minipage}[t]{\columnwidth}
-		\includegraphics[width=\columnwidth]{./figure/three_obstacles_no_overtaking/braking_2.pdf}
-	\end{minipage}
-	\begin{minipage}[t]{\columnwidth}
-		\includegraphics[width=\columnwidth]{./figure/three_obstacles_no_overtaking/braking_3.pdf}
-	\end{minipage}
-	\begin{minipage}[t]{\columnwidth}
-		\includegraphics[width=\columnwidth]{./figure/three_obstacles_no_overtaking/braking_4.pdf}
-	\end{minipage}
-	\begin{minipage}[t]{\columnwidth}
-		\includegraphics[width=\columnwidth]{./figure/three_obstacles_no_overtaking/braking_5.pdf}
-	\end{minipage}
-	\begin{minipage}[t]{\columnwidth}
-		\includegraphics[width=\columnwidth]{./figure/three_obstacles_no_overtaking/braking_6.pdf}
-	\end{minipage}
-	\caption{Simulation of braking and overtaking obstacles.}
-	\label{fig:braking}
-\end{figure}
 
-At the beginning, the vehicle moves with the reference velocity of $v=\SI{20}{m/s}$.
-When the ATLASCAR2 detects all the other cars on the road, checks if there is a free lane.
+At the beginning, the vehicle detects all the other cars on the road.
 In the first part of the simulation, the ATLASCAR2 brakes because there is not enough space for overtaking the cars as shown in Fig.
@@
 \ref{fig:throttle_braking}.
-The velocity of the ATLASCAR2 for $\approx\SI{2}{s}$ adapts to that of the closest obstacle.
-After a few seconds the fastest car moves and makes available the left lane for overtaking.
+After a few seconds the fastest obstacle moves and makes available the left lane.
 Dramatic changes of steering angle in early stage are observed in Fig.
@@
 \ref{fig:theta_braking}.
-Then, the ATLASCAR2 returns to the reference velocity during the overtaking of the two obstacles (the applied throttle after $\approx\SI{5}{s}$ is positive).
+Then, the ATLASCAR2 returns to the reference velocity during the overtaking of the two obstacles.
 It is seen that the ATLASCAR2 avoids the obstacles and returns to the road center line with a low overshoot.
 \begin{figure*}[!t] %vs changes to t instead of b
+	\vspace{-1.7em}
 	\begin{minipage}[t]{\columnwidth}
-		\includegraphics[width=\columnwidth]{./figure/three_obstacles_no_overtaking/VelocityVsTime.pdf}
+		\includegraphics[width=\columnwidth,height=0.5\columnwidth]{./figure/three_obstacles_no_overtaking/VelocityVsTime.pdf}
 		\vspace{-17pt}
@@
 	\end{minipage}
+	\hfill
 	\begin{minipage}[t]{\columnwidth}
-		\includegraphics[width=\columnwidth]{./figure/three_obstacles_no_overtaking/ThrottleVsTime.pdf}
+		\includegraphics[width=\columnwidth,height=0.5\columnwidth]{./figure/three_obstacles_no_overtaking/ThrottleVsTime.pdf}
 		\vspace{-17pt}
@@
 	\end{minipage}
+		\vspace{-0.5em}
 	\begin{minipage}[t]{\columnwidth}
-	    \includegraphics[width=\columnwidth]{./figure/three_obstacles_no_overtaking/SteeringAngleVsTime.pdf}
+	    \includegraphics[width=\columnwidth,height=0.5\columnwidth]{./figure/three_obstacles_no_overtaking/SteeringAngleVsTime.pdf}
 	    \vspace{-17pt}
@@
 	\end{minipage}
+	\hfill
 	\begin{minipage}[t]{\columnwidth}
-	    \includegraphics[width=\columnwidth]{./figure/three_obstacles_no_overtaking/HeadingAngleVsTime.pdf}
+	    \includegraphics[width=\columnwidth,height=0.5\columnwidth]{./figure/three_obstacles_no_overtaking/HeadingAngleVsTime.pdf}
 	    \vspace{-17pt}
@@
 
-\section{Lane Following System}
-\subsection{Problem Formulation}
-A lane-following system is a control system that keeps the vehicle traveling along the centerline of a highway lane, while maintaining a user-set velocity.
-Figure \ref{fig:laneFollowing} illustrates a typical lane following scenario.
-\begin{figure}[!h]
-	\centering
-	\includegraphics[width=0.75\columnwidth]{./figure/laneFollowing/laneFollowing.pdf}
-	\caption{Problem description of a lane following system.}
-	\label{fig:laneFollowing}
-\end{figure}
-In a classic lane keeping assist, it is assumed that the longitudinal velocity is constant \cite{borelli3}.
-This restriction is relaxed in this model because the longitudinal acceleration varies in this MIMO control system.
-This lane-following system manipulates both the longitudinal acceleration and the front steering angle of the vehicle to keep the lateral deviation and the relative yaw angle small and the longitudinal velocity close to a driver set velocity.
-If these two goals cannot be met at the same moment, the system tries to balance them.
-The model that we are considering contains many parameters.
-The first fundamental block describes the vehicle dynamics: we have applied the bicycle model of lateral vehicle dynamics and approximate the longitudinal dynamics using a time constant obtaining  a linear model.
-\subsubsection{Longitudinal dynamics}
-We can use the following state space to describe the longitudinal model:
-\begin{equation}
-\label{eqn:longi_dynamics_simple_model_ss}
-\begin{array}{ll}
-\dot{\vec{x}}_{\text{lon}} =\vec{A}_m \vec{x}_{\text{lon}}+ \vec{B_m}\vec{u}_{\text{lon}}\\
-\vec{y}_{\text{lon}} =\vec{C_m} \vec{x}_{\text{lon}} + \vec{D_m} \vec{u}_{\text{lon}}
-\end{array}
-\end{equation}
-where the input is the acceleration and the states are the longitudinal velocity and the actual acceleration which is also the only output of this system.
-\begin{equation*}
-\vec{x}_{\text{lon}} = \begin{bmatrix}
-\dot{V}_x&V_x
-\end{bmatrix}^T,
-\qquad
-\vec{u}_{\text{lon}} = a
-\end{equation*}
-and
-\[ 
-\vec{A_m}=\begin{bmatrix}
--\frac{1}{\tau}&0\\1&0
-\end{bmatrix},
-\quad
-\vec{B_m}=\begin{bmatrix}
-\frac{1}{\tau}\\
-0
-\end{bmatrix},
-\]
-\[
-\vec{C_m}=\begin{bmatrix}
-1&0
-\end{bmatrix}, 
-\quad
-\vec{D_m}=0.
-\]
-where $\tau$ is a time constant \cite{long_tf}; in practice we are considering a second order transfer function like in \cite{longitudinal}.
-\subsubsection{Lateral dynamics}
-Local function: we have a continuous vehicle lateral model from parameters obtained by simplifying the one in \cite{rathai}: 
-\begin{equation}
-\label{eqn:lateral_dynamics_simple_model}
-\begin{array}{ll}
-\dot{\vec{x}}_{\text{lat}} =\vec{A}_g \vec{x}_{\text{lat}}+ \vec{B}_g \vec{u}_{\text{lat}}\\
-\vec{y}_{\text{lat}} =\vec{C}_g \vec{x}_{\text{lat}} + \vec{D}_g \vec{u}_{\text{lat}}
-\end{array}
-\end{equation}
-where the input is the steering angle in radians, and the outputs are the lateral velocity in meters per second and yaw angle rate in radians per second:
-\begin{equation*}
-\vec{x}_{\text{lat}} = \begin{bmatrix}
-V_y&\dot{\psi}
-\end{bmatrix}^T
-\qquad
-\vec{u}_{\text{lat}} = \delta
-\end{equation*}
-and
-\[ 
-\vec{A}_g=\begin{bmatrix}
--\frac{2C_F+2C_R}{mV_x}&-\frac{2C_Fl_F-2C_Rl_R}{mV_x} - V_x\\
--\frac{2C_Fl_F-2C_Rl_R}{I_ZV_x}&-\frac{2C_Fl_F^2+2C_Rl_R^2}{I_ZV_x}
-\end{bmatrix},
-\]
-\[
-\vec{B}_g=\begin{bmatrix}
-2C_F/m\\
-2C_Fl_F/I_Z
-\end{bmatrix},
-\quad
-\vec{C}_g=\vec{I}_2, 
-\quad
-\vec{D}_g=\vec{0}_{2\times1}.
-\]
-The parameters in the previous matrices are:
-\begin{itemize}
-	\item $V_x$ is the longitudinal velocity of the car;	
-	\item $m$ is the total mass parameter; 
-	\item $I_Z$ is the yaw moment of inertia parameter;
-	\item $l_F$ and $l_R$ are the longitudinal distances from center of gravity to front and rear tires parameters;
-	\item $C_F$ and $C_R$ are the cornering stiffnesses of front and rear tires parameters.
-\end{itemize}
-The goal for the driver steering model is to keep the vehicle in its lane and follow the curved road by controlling the front steering angle .
-This goal is achieved by driving the yaw angle error $e_2 = \psi -\psi_{\text{des}}$ and lateral displacement error $e_1$ to zero ($\dot{e}_1 = V_xe_2+V_y$).
-We can incorporate these two paramenters in the augmented model:
-\begin{equation}
-\label{eqn:lateral_dynamics_augmented_model}
-\begin{array}{ll}
-\dot{\vec{x}}_{\text{aug}} =\vec{A}_a \vec{x}_{\text{aug}}+ \vec{B}_a \vec{u}_{\text{aug}}\\
-\vec{y}_{\text{aug}} = \vec{C}_a \vec{x}_{\text{aug}} + \vec{D}_a \vec{u}_{\text{aug}}
-\end{array}
-\end{equation}
-where
-\begin{equation*}
-\vec{x}_{\text{aug}} = \begin{bmatrix}
-V_y&\dot{\psi}&e_1&e_2
-\end{bmatrix}^T,
-\qquad
-\vec{u}_{\text{aug}} = 
-\begin{bmatrix}
-\delta&\dot{\psi}_{\text{des}}
-\end{bmatrix}^T
-\end{equation*}
-and
-\[ 
-\vec{A}_a=\begin{bmatrix}
-\vec{A}_g&\vec{0}_{2\times2}\\
-\vec{I}_2&\begin{matrix}
-0&V_x\\
-0&0
-\end{matrix}
-\end{bmatrix},
-\quad
-\vec{B}_a=\begin{bmatrix}
-\vec{B}_g&\vec{0}_{2\times1}\\
-0&0\\
-0&-1
-\end{bmatrix},
-\]
-\[
-C_a=\begin{bmatrix}
-\vec{0}_{2\times2}&\vec{I}_2
-\end{bmatrix}, 
-\quad
-D_a=
-\vec{0}_{2\times2}. 
-\]
-Combining (\ref{eqn:longi_dynamics_simple_model_ss}) with (\ref{eqn:lateral_dynamics_augmented_model}) yields the state-space model that characterizes the Model Predictive Controller:
-\begin{equation}
-\label{eqn:full_dynamics_model}
-\begin{array}{ll}
-\dot{\vec{x}}_{\text{tot}} = \vec{A}_f \vec{x}_{\text{tot}}+ \vec{B}_f \vec{u}_{\text{tot}}\\
-\vec{y}_{\text{tot}} = \vec{C}_f \vec{x}_{\text{tot}} + \vec{D}_f \vec{u}_{\text{tot}}
-\end{array}
-\end{equation}
-where
-\begin{equation*}
-\vec{x}_{\text{tot}} = \begin{bmatrix}
-\dot{V}_x\\V_x\\V_y\\\dot{\psi}\\e_1\\e_2
-\end{bmatrix},
-\qquad
-\vec{u}_{\text{tot}} = 
-\begin{bmatrix}
-a\\\delta\\\dot{\psi}_{\text{des}}
-\end{bmatrix}
-\end{equation*}
-and
-\[ 
-\vec{A}_f=\begin{bmatrix}
-\vec{A}_m&\vec{0}_{2\times4}\\
-\vec{0}_{4\times2}&\vec{A}_a
-\end{bmatrix},
-\quad
-\vec{B}_f=\begin{bmatrix}
-\vec{B}_m&\vec{0}_{2\times2}\\
-\vec{0}_{4\times1}&\vec{B}_a
-\end{bmatrix},
-\]
-\[
-\vec{C}_f=\begin{bmatrix}
-\vec{C}_m&\vec{0}_{1\times4}\\
-\vec{0}_{2\times2}&\vec{C}_a
-\end{bmatrix}, 
-\quad
-\vec{D}_f=\vec{0}_{3\times3}. 
-\]
-However the system to be controlled is usually modeled by a linear discrete state-space model:
-\begin{equation*}
-\label{eqn:full_dynamics_model_disc}
-\begin{array}{rr}
-{\vec{x}}_{\text{tot}}(k+1) =\vec{A} \vec{x}_{\text{tot}}(k)+ \vec{B} \vec{u}_{\text{tot}}(k)\\
-\vec{y}_{\text{tot}}(k) = \vec{C}\vec{x}_{\text{tot}}(k) + \vec{D} \vec{u}_{\text{tot}}(k)
-\end{array}
-\end{equation*}
-where $\vec{A}$ and $\vec{B}$ are the state and control matrices for the discrete state-space equation, respectively, which can be calculated, also in this case, with the Euler method as:
-\[
-\vec{A} = e^{\vec{A}_fT_s},\qquad \vec{B} = \int_{kT_s}^{(k+1)T_s} e^{\vec{A}_f[(k+1)T_s-\eta]}\vec{B}_f d\eta
-\]
-where $T_s$ is the sampling interval for the discrete state-space model. The matrices $\vec{C}$ and $\vec{D}$ are equivalent to those in the continuous case.
-
-\subsection{Design of Adaptive Model Predictive Control}
-We created an Adaptive MPC controller with a prediction model that has six states, three outputs (longitudinal velocity, lateral deviation, relative yaw angle), and two manipulated signals (acceleration and steering).
-The objective of the trajectory planning along specified path can be described as follows: given a path which the vehicle is expected to follow design a trajectory of a car-vehicle configuration.
-In order to do this, according with \cite{curvature} it is possible to derive the road curvature and its derivative.
-The product of the road curvature and the longitudinal velocity is modeled as a measured disturbance.
-We have set the constraints for manipulated variables and the scale factors.
-Moreover we have specified the weights in the standard MPC cost function.
-The third output, yaw angle, is allowed to float because there are only two manipulated variables to make it a square system.
-In this controller, there is no steady-state error in the yaw angle as long as the second output, lateral deviation, reaches 0 at steady state.
-Finally we have also penalized acceleration change more for smooth driving experience.
-This controller uses a linear model for the vehicle dynamics and updates the model online as the longitudinal velocity varies.
-
-\subsection{Simulation Results}
-The proposed adaptive MPC algorithm is designed in the MATLAB/Simulink and validated through simulation.
-The objective of this test is to evaluate the behavior of the proposed control strategy in critical situations.
-Table 3 shows the parameters used in the lane following simulation.
-\begin{table}[!h]
-	\centering
-	\begin{tabular}{|c|c|}
-		\hline
-		Parameters          & Values      \\
-		\hline
-		$m$          & \SI{1575}{kg}              \\
-		$I_z$         & \SI{2875}{kgm^2}               \\
-		$l_F$           & \SI{1.2}{m}               \\
-		$l_R$         & \SI{1.6}{m}               \\
-		$C_F$          & \SI{19000}{\newton/rad}      \\
-		$C_R$           & \SI{33000}{\newton/rad}  \\
-		$\tau$             & 0.2                \\
-		$V_0$           & \SI{15}{m/s}       \\
-		$V_{\text{set}}$          & \SI{20}{m/s}   \\
-		$T_s$         & \SI{0.02}{s}          \\
-		\hline
-	\end{tabular}
-\end{table}
-
-Figures \ref{fig:reference_laneFollowing} and \ref{fig:curvature_laneFollowing} show the desired path that the car must follow and its curvature, where the former is described in terms of the lateral position $Y_{\text{ref}}$ as function of the longitudinal position $X_{\text{ref}}$ and the latter is derived according with \cite{curvature}.
-The ATLASCAR2 is controlled to follow a sinusoidal trajectory which is given as follows:
-\begin{equation*}
-X_\text{ref}=V_x\cdot t, \quad Y_\text{ref}=5\sin(X_\text{ref}/20)\quad \text{with}\quad t\in[0,20]\SI{}{s}
-\end{equation*}
-\begin{figure}[!t]
-	\centering
-	\begin{minipage}[t]{\columnwidth}
-		\includegraphics[width=\columnwidth]{../../MATLAB/lane_following/figure/Reference.pdf}
-		\vspace{-17pt}
-		\subcaption{}
-		\label{fig:reference_laneFollowing}
-	\end{minipage}
-	\begin{minipage}[t]{\columnwidth}
-		\includegraphics[width=\columnwidth]{../../MATLAB/lane_following/figure/Curvature.pdf}
-		\vspace{-17pt}
-		\subcaption{}
-		\label{fig:curvature_laneFollowing}
-	\end{minipage}
-	\caption{Desired path and curvature of the ATLASCAR2 in a simulation of \SI{20}{s}}
-	\label{fig:laneFollowing_desired}
-	\vspace{-30pt}
-\end{figure}
-
-Moreover the following figures show the trend of the main parameters confirming that the control strategy used allows the vehicle to follow the path.
-In particular we simulated also a small error in the sensor dynamics in order to make the simulation more realistic: we added a 3 percent error to the longitudinal velocity and this is evident from the small noise in the graphs of the steering angle (Fig.\ref{fig:steering_laneFollowing}) and the lateral deviation (Fig.\ref{fig:lateral_deviation_laneFollowing}).
-Figure {\ref{fig:longitudinal_velocity_laneFollowing}} shows the evolution of the vehicle longitudinal velocity.
-At the start of the simulation, this velocity is equal to the initial condition for longitudinal velocity parameter $V_0$.
-At run time, we can note that $V_x$ reaches the predefined value of \SI{20}{m/s} meters for second and then it stabilizes near the cruising speed because it continues to vary the steering angle to adapt to the path to be followed.
-Finally we presents the overall scheme for the lane following developted in Simulink depicted in Figure \ref{fig:scheme_lane_following}.
-\begin{figure*}[!t]
-\centering
-\begin{minipage}[t]{\columnwidth}
-	\includegraphics[width=\columnwidth]{../../MATLAB/lane_following/figure/LongitudinalVelocityVsTime.pdf}
-	\subcaption{Longitudinal velocity $V_x$ with respect to time.}
-	\label{fig:longitudinal_velocity_laneFollowing}
-\end{minipage}
-\begin{minipage}[t]{\columnwidth}
-	\includegraphics[width=\columnwidth]{../../MATLAB/lane_following/figure/AccelerationVsTime.pdf}
-	\subcaption{Acceleration $u_1$ with respect to time.}
-	\label{fig:acceleration_laneFollowing}
-\end{minipage}
-\begin{minipage}[t]{\columnwidth}
-	\includegraphics[width=\columnwidth]{../../MATLAB/lane_following/figure/SteeringAngleVsTime.pdf}
-	\subcaption{Steering angle $u_2$ with respect to time.}
-	\label{fig:steering_laneFollowing}
-\end{minipage}
-%\begin{minipage}[t]{\columnwidth}
-%	\includegraphics[width=\columnwidth]{../../MATLAB/lane_following/figure/RelativeYawAngleVsTime.pdf}
-%	\subcaption{Relative yaw angle $e_2$ with respect to time.}
-%	\label{fig:relative_yaw_angle_laneFollowing}
-%\end{minipage}
-\begin{minipage}[t]{\columnwidth}
-	\includegraphics[width=\columnwidth]{../../MATLAB/lane_following/figure/LateralDeviationVsTime.pdf}
-	\subcaption{Lateral deviation $e_1$ with respect to time.}
-	\label{fig:lateral_deviation_laneFollowing}
-\end{minipage}
-\caption{Time signals of the ATLASCAR2 in the simulation with a sinusoidal path}
-\label{fig:laneFollowing_signals}
-\end{figure*}
-
-\begin{figure*}[!b]
-	\centering
-	\includegraphics[width=1\textwidth]{./figure/lane_following_AMPC.pdf}
-	\caption{Overall procedure scheme lane following.}
-	\label{fig:scheme_lane_following}
-\end{figure*}
 \section{Conclusions and Future Work}
-This report proposes two advanced methods for short term motion planning of an autonomous car based on adaptive Model Predictive Control.
-The first component is an obstacle avoidance system that moves the vehicle around different moving obstacles in the lane using throttle and steering angle.
+This paper proposes an advanced method for short term motion planning of an autonomous car based on adaptive Model Predictive Control.
+The central component is an obstacle avoidance system that moves the vehicle around different moving obstacles in the lane using throttle and steering angle.
 This system updates both the predictive model and the mixed input/output constraints at each control interval.
 The vehicle is also able to brake in order to prevent collisions against closest obstacles.
-Instead, in the second scheme  we have developed a lane following system that keeps the ATLASCAR2 traveling along the centerline of the lanes on the road by adjusting the front steering angle of the car.
-The flexibility of the concepts used in the algorithms allows a multitude of refinements and extensions to this work.
+The flexibility of the concepts used in the algorithm allows a multitude of refinements and extensions to this work.
+We can add to this algorithm a lane following system that keeps the ATLASCAR2 traveling along the center line of the lanes on the road by adjusting the front steering angle of the car.
 The future work includes the combination of these two control strategies in a way that they can operate simultaneously.
@@
 
-	\bibitem{borelli3}Monimoy Bujarbaruah, Xiaojing Zhang, H.
-Eric Tseng, Francesco Borrelli; Adaptive MPC for Autonomous Lane Keeping, 14th International Symposium on Advanced Vehicle Control (AVEC), Beijing, China, July 2018
 %	\bibitem{atlas}ATLAS  Project,  Aveiro  University, Portugal, \url{http://atlas.web.ua.pt/}, last visited July 2010.
@@
 	\bibitem{siciliano}B. Siciliano, L. Sciavicco, L. Villani, and G. Oriolo. "Robotics: Modelling, Planning and Control", Springer Publishing Company, Incorporated, 2008. 
-
-	\bibitem{onlineMPC}M.
+%	\bibitem{onlineMPC}M.
 Werling and D.
@@
 
-	%\bibitem{theory}J. Rawlings, D. Mayne (2010), "Model Predictive Control: Theory and Design", Nob Hill Publishing.
+%	\bibitem{theory}J. Rawlings, D. Mayne (2010), "Model Predictive Control: Theory and Design", Nob Hill Publishing.
 
-	%\bibitem{backward}C.
+%	\bibitem{backward}C.
 Son and C.
@@
 
-	%\bibitem{zhou}H.
+%	\bibitem{zhou}H.
 Zhou, L.
@@
 
-	%\bibitem{yu} Z. T. Yu, Obstacle Avoidance for Autonomous Vehicle Driving on Highways Based on MPC, JinLin University, 2012.
+%	\bibitem{yu} Z. T. Yu, Obstacle Avoidance for Autonomous Vehicle Driving on Highways Based on MPC, JinLin University, 2012.
 
-	%\bibitem{berger}Berger, Niels. (2018). Lane Change Path Planning With state-dependent safety constraints using Nonlinear Model Predictive Control.
+%	\bibitem{berger}Berger, Niels. (2018). Lane Change Path Planning With state-dependent safety constraints using Nonlinear Model Predictive Control.
 
-	%\bibitem{kth_thilen}E. Thilén, ‘Robust Model Predictive Control for Autonomous Driving’, Dissertation, 2017.
+%	\bibitem{kth_thilen}E. Thilén, ‘Robust Model Predictive Control for Autonomous Driving’, Dissertation, 2017.
 
-	\bibitem{rathai}Murali Madhavan Rathai, Karthik \& Amirthalingam, Jegan \& Jayaraman, Balaji. (2017). Robust tube-MPC based lane keeping system for autonomous driving vehicles. 1-6.
+%	\bibitem{rathai}Murali Madhavan Rathai, Karthik \& Amirthalingam, Jegan \& Jayaraman, Balaji. (2017). Robust tube-MPC based lane keeping system for autonomous driving vehicles. 1-6.
 
-	%\bibitem{kth_nordell}B. Nordell, ‘Trajectory Planning for Autonomous Vehicles and Cooperative Driving’, Dissertation, 2016.
+%	\bibitem{kth_nordell}B. Nordell, ‘Trajectory Planning for Autonomous Vehicles and Cooperative Driving’, Dissertation, 2016.
 
-	%\bibitem{shen}C.
+%	\bibitem{shen}C.
 Shen, H.
@@
 
-	%\bibitem{matsumoto}N.
+%	\bibitem{matsumoto}N.
 Wada and T.
@@
 
-	\bibitem{longitudinal}Filip, Jan. (2018). Trajectory Tracking for Autonomous Vehicles.
-
-	\bibitem{curvature}Danwei Wang, Feng Qi, "Trajectory planning for a four-wheel-steering vehicle," 2001 International Conference on Robotics and Automation, Seoul, Korea, 2001
 \end{thebibliography}

### 2019-02-13 MATLAB/lane_following/LaneFollowingGetCurvature.m

@@ -23,17 +23,17 @@ Yref = 5*sin(Xref/(20)); % Correct reference sinusoidal
 %Yref = (2.4/50)*(Xref+3).^2 - (2.4/43.9)*(Xref-12).^2; % Path Parabola
 %Yref = 8.1/2*(1+tanh(z1)) - 11.4/2*(1+tanh(z2)); % Avoid One obstacle
 
-h = figure ('Position',[100, 100, 340, 230], 'PaperPositionMode','auto');
+h1 = figure ('Position',[100, 100, 340, 230], 'PaperPositionMode','auto');
 plot(Xref,Yref)
 hold on
 grid on
 grid minor
-title('\textbf{Desired Path}','Interpreter','latex');
+%title('\textbf{Desired Path}','Interpreter','latex');
 xlabel('X-coordinate [m]','Interpreter','latex');
 ylabel('Y-coordinate [m]','Interpreter','latex');
-pos = get(h,'Position');
-set(h,'PaperPositionMode','Auto','PaperUnits','Points','PaperSize',[pos(3), pos(4)-40])
-print(h,'figure\Reference','-dpdf','-r0')
+pos1 = get(h1,'Position');
+set(h1,'PaperPositionMode','Auto','PaperUnits','Points','PaperSize',[pos1(3)*0.8, pos1(4)-40])
+print(h1,'figure\Reference','-dpdf','-r0')
 hold off
 
 % Desired curvature
@@ -51,10 +51,10 @@ plot(rho.time,rho.signals.values)
 hold on
 grid on
 grid minor
-title('\textbf{Curvature}','Interpreter','latex');
+%title('\textbf{Curvature}','Interpreter','latex');
 xlabel('Time [s]','Interpreter','latex');
 ylabel('Curvature [m]','Interpreter','latex');
-pos = get(hcurv,'Position');
-set(hcurv,'PaperPositionMode','Auto','PaperUnits','Points','PaperSize',[pos(3), pos(4)-40])
+pos2 = get(hcurv,'Position');
+set(hcurv,'PaperPositionMode','Auto','PaperUnits','Points','PaperSize',[pos2(3)*0.8, pos2(4)-40])
 print(hcurv,'figure\Curvature','-dpdf','-r0')
 hold off

### 2019-02-13 MATLAB/lane_following/LaneFollowingResults.m

@@ -7,76 +7,76 @@ function LaneFollowingResults(logsout)
 
 %% Steering Angle vs Time
 
-h1 = figure ('Position',[100, 100, 340, 230], 'PaperPositionMode','auto');
+h7 = figure ('Position',[100, 100, 340, 230], 'PaperPositionMode','auto');
+plot(delta_ampc.Values.time,delta_ampc.Values.Data);
 hold on;
 grid on;
 grid minor;
-plot(delta_ampc.Values.time,delta_ampc.Values.Data);
-title('\textbf{Steering Angle (u$_2$) vs Time}','Interpreter','latex');
+%title('\textbf{Steering Angle (u$_2$) vs Time}','Interpreter','latex');
 xlabel('Time [s]','Interpreter','latex');
 ylabel('Steering angle [rad]','Interpreter','latex');
-pos1 = get(h1,'Position');
-set(h1,'PaperPositionMode','Auto','PaperUnits','Points','PaperSize',[pos1(3), pos1(4)-40])
-print(h1,'figure\SteeringAngleVsTime','-dpdf','-r0')
+pos7 = get(h7,'Position');
+set(h7,'PaperPositionMode','Auto','PaperUnits','Points','PaperSize',[pos7(3)*0.8, pos7(4)-40])
+print(h7,'figure\SteeringAngleVsTime','-dpdf','-r0')
 hold off
 pause(2)
 %% Lateral deviation vs Time
 
-h2 = figure ('Position',[100, 100, 340, 230], 'PaperPositionMode','auto');
+h8 = figure ('Position',[100, 100, 340, 230], 'PaperPositionMode','auto');
+plot(e1_ampc.Values.time,e1_ampc.Values.Data);
 hold on;
 grid on;
 grid minor;
-plot(e1_ampc.Values.time,e1_ampc.Values.Data);
-title('\textbf{Lateral Deviation (e$_1$) vs Time}','Interpreter','latex');
+%title('\textbf{Lateral Deviation (e$_1$) vs Time}','Interpreter','latex');
 xlabel('Time [s]','Interpreter','latex');
 ylabel('Lateral Deviation [m]','Interpreter','latex');
-pos2 = get(h2,'Position');
-set(h2,'PaperPositionMode','Auto','PaperUnits','Points','PaperSize',[pos2(3), pos2(4)-40])
-print(h2,'figure\LateralDeviationVsTime','-dpdf','-r0')
[…]

### 2019-02-13 MATLAB/lane_following_constant_velocity/example1.m

@@ -1,0 +1,127 @@
+
+Fz=5;
+%Longitudinal Force(pure longitudinal slip)  
+%input:slip ratio s 
+s=linspace(-20,20,40);                       %-20~20插值40个，生成滑移率横坐标
+%*************longitudinal coefficients*******************************%
+b0=2.37272;
+b1=-9.46;
+b2=1490;
+b3=130;
+b4=276;
+b5=0.0886;
+b6=0.00402;
+b7=-0.0615;
+b8=1.2;
+b9=0.0299;
+b10=-0.176;
+%**********parameters *********************%
+Cx=b0;
+Dx=b1*Fz^2+b2*Fz;
+BCDx=(b3*Fz^2+b4*Fz)*exp(-b5*Fz);%纵向力零点处的纵向刚度
+Bx=BCDx/(Cx*Dx);%刚度因子
+Shx=b9*Fz+b10;%曲线的水平方向漂移
+kx=s+Shx;%输入变量X1
+Svx=0;%%曲线的垂直方向漂移
+Ex=b6*Fz^2+b7*Fz+b8;%曲线的曲率因子
+Fx=Dx*sin(Cx*atan(Bx*kx-Ex*(Bx*kx-atan(Bx*kx))))+Svx; %纵向力的计算公式
+
+figure (1);
+plot(s,Fx);%绘制纵向力曲线
+grid  on  %绘制栅格
+set(gca,'xlim',[-20 20]);                              %设置x轴范围 
+set(gca,'xtick',[-20:5:20]);                          %设置x轴间隔 
+set(gca,'ylim',[-8000 8000])                        %设置x轴范围 
+set(gca,'ytick',[-8000:1000:8000]);                   %设置x轴间隔 
+xlabel('纵向滑移率'); 
+ylabel('纵向力/（N）'); 
+title('纵向力(纯纵滑)');
+
+%%
+%Lateral Force(pure side slip)  
+%input:横向侧偏 是侧偏角 alpha
+alpha=linspace(-8,8,16);   %-8~8插值16个，生成侧偏角横坐标
+r=0;  %外倾角，设为零
+%*************lateral coefficients*******************************%
+a0 = 1.65;
+a1 = -34;
+a2 = 1250;
+a3 = 3036;
+a4 = 12.8;
+a5 = 0.00501;
+a6 = -0.02103;
+a7 = 0.77394;
[…]

### 2019-02-13 MATLAB/path planning/Path Planning v1/main_path_planning.m

@@ -1,0 +1,175 @@
+clear all
+close all
+clc
+
+%% ATLASCAR2 - Moving Obstacle Avoidance based on MPC
+
+car = struct;
+road = struct;
+obstacle = struct;
+
+%% Vehicle model
+
+% Parameters definition
+car.length = 5;                 % Length of the ATLASCAR2
+car.width = 2;                  % Witdh of the ATLASCAR2
+car.V = 20;                     % Constant speed of the ATLASCAR2
+car.x0 = [0; 0; pi/33; car.V];      % Initial conditions
+car.u0 = [0; 0];
+Ts = 0.02;                      % Sampling time
+
+% Obtain a linear plant model at the nominal operating point and convert it
+% into a discrete-time model to be used by the model predictive controller.
+[Ad,Bd,Cd,Dd,U,Y,X,DX] = ATLASCAR2ModelDT(Ts,car.x0,car.u0);
+                       
+dsys = ss(Ad,Bd,Cd,Dd,'Ts',Ts);          % State space
+dsys.InputName = {'Throttle','Delta'};   % Input u
+dsys.StateName = {'X','Y','Theta','V'};  % State x
+dsys.OutputName = dsys.StateName;        % Output y   
+
+%% Plot initial condition
+
+% ATLASCAR2 - Green with black boundary
+% Horizontal lanes - Dashed black lines
+% Obstacle/Car - Red with with black boundary
+% Safe zone - Dashed red boundary.
+
+f = obstaclePlotInitialCondition(car, obstacle, road);
+
+%% MPC design
+
+% MPC object: sampling time Ts, Prediction Horizon 10, Control Horizon 2
+status = mpcverbosity('off');
+mpcobj = mpc(dsys);
+
+% Set the values of the prediction horizon and the control horizon
+mpcobj.PredictionHorizon = 25;   % number of steps = 0.5 seconds
+mpcobj.ControlHorizon = 5;
+
+%% Constraints and Weights
+% To prevent the ATLASCAR2 from accelerating or decelerating too quickly, 
+% add a hard constraint of 0.2 (m^2/sec) on the throttle rate of change.
+% mpcobj.ManipulatedVariables(1).RateMin = -0.2; 
+% mpcobj.ManipulatedVariables(1).RateMax = 0.2;
+
[…]

### 2019-02-13 MATLAB/path planning/Path Planning v1/obstaclePlotInitialCondition.m

@@ -1,0 +1,28 @@
+function f = obstaclePlotInitialCondition(car,obstacle,road)
+
+% Create figure
+
+f = figure;
+
+% Plot the ATLASCAR2
+
+X0 = car.x0(1);
+Y0 = car.x0(2);
+plot(X0,Y0,'gx'); 
+hold on 
+grid on
+grid minor
+p = patch([X0-car.length/2 X0-car.length/2 X0+car.length/2 X0+car.length/2], [Y0-car.width/2, Y0+car.width/2, Y0+car.width/2, Y0-car.width/2], [0 1 0]); 
+%rectangle('Position',[X0-car.length/2,Y0 - car.width/2,car.length,car.width],'FaceColor',[0 1 0],'Curvature',0.2,'LineStyle','-','LineWidth', 1.2, 'EdgeColor','k');
+axis equal
+
+%,'EdgeColor','[1 0 0]','LineStyle','--'
+delete(p)
+
+% Reset the axis.
+%axis([-155 155 -330 330]);
+xlabel('X');
+ylabel('Y');
+title('ATLASCAR2 Moving Obstacle Avoidance');
+
+

### 2019-02-13 MATLAB/path planning/Path Planning v2/ATLASCAR2ErrorModelDT.m

@@ -1,0 +1,55 @@
+function [Ad,Bd,Cd,Dd,U,Y,X,DX] = ATLASCAR2ErrorModelDT(Ts,x,u)
+
+% The ATLASCAR2 has rectangular shaper with a length of 5 meters and width of
+% 2 meters. The model has four states:
+%
+% * |xPos| - Global horizontal position of the car center
+% * |yPos| - Global vertical position of the car center
+% * |theta| - Heading angle of the car (0 when facing east, counterclockwise positive)
+% * |V| - Speed of the car (positve)
+%
+% There are two manipulated variables:
+%
+% * |throttle| - Throttle (positive when accelerating, negative when braking)
+% * |delta| - Steering angle change (counterclockwise positive)
+
+% Inizialization
+carLength = 5;  % Length of the ATLASCAR2
+theta = x(3);   % Heading angle of the ATLASCAR2 (0 when facing east, counterclockwise positive) 
+V = u(1);       % Speed of the ATLASCAR2 (positve)
+delta = u(2);   % Steering angle change (counterclockwise positive)
+
+% Generate continuous-time model (Ac,Bc,Cc,Dc)
+Ac = [0, 0, -V*sin(theta);
+      0, 0,  V*cos(theta);
+      0, 0, 0];          
+Bc = [cos(theta) , 0;
+      sin(theta) , 0;
+      tan(delta)/carLength  , (V*(tan(delta)^2 + 1))/carLength];
+Cc = eye(3);
+Dc = zeros(3,2);
+
+% Generate discrete-time model (Ad, Bd, Cd, Dd)
+% Use Simpson's rule to compute integral(0,Ts){expm(a*s)*ds*b}
+n = 4;          % Number of points for Simpson's Rule, an even integer >= 2.
+Ad = expm(Ac*Ts);
+h = Ts/n;
+Ai = eye(3) + Ad;
+Coef = 2;
+for i = 1:n-1
+    if Coef == 2
+        Coef = 4;
+    else
+        Coef = 2;
+    end
+    Ai = Ai + Coef*expm(Ac*i*h);
+end
+Bd = (h/3)*Ai*Bc;
+Cd = Cc;
+Dd = Dc;
+
+% Nominal conditions for discrete-time plant
+X = x;
+U = u;
+Y = x;
+DX = Ad*x+Bd*u-x;

### 2019-02-13 MATLAB/path planning/Path Planning v2/main_path_planning_error.m

@@ -1,0 +1,194 @@
+clear all
+close all
+clc
+
+%% ATLASCAR2 - Moving Obstacle Avoidance based on MPC
+
+car = struct;
+road = struct;
+obstacle = struct;
+
+%% Vehicle model
+
+% Parameters definition
+car.length = 5;                 % Length of the ATLASCAR2
+car.width = 2;                  % Witdh of the ATLASCAR2
+car.V = 20;                     % Constant speed of the ATLASCAR2
+car.x0 = [0; -3; 0];             % Initial conditions
+car.u0 = [0.01; 0];
+Ts = 0.02;                      % Sampling time
+
+% Obtain a linear plant model at the nominal operating point and convert it
+% into a discrete-time model to be used by the model predictive controller.
+[Ae,Be,Ce,De,U,Y,X,DX] = ATLASCAR2ErrorModelDT(Ts,car.x0,car.u0);
+                       
+dsys = ss(Ae,Be,Ce,De,'Ts',Ts);          % State space
+dsys.InputName = {'err_V','err_delta'};   % Input u
+dsys.StateName = {'err_x','err_y','err_theta'};  % State x
+dsys.OutputName = dsys.StateName;        % Output y   
+
+%% Plot initial condition
+
+% ATLASCAR2 - Green with black boundary
+% Horizontal lanes - Dashed black lines
+% Obstacle/Car - Red with with black boundary
+% Safe zone - Dashed red boundary.
+
+f = obstaclePlotInitialCondition(car, obstacle, road);
+
+%% MPC design
+
+% MPC object: sampling time Ts, Prediction Horizon 10, Control Horizon 2
+status = mpcverbosity('off');
+mpcobj = mpc(dsys);
+
+% Set the values of the prediction horizon and the control horizon
+mpcobj.PredictionHorizon = 25;   % number of steps = 0.5 seconds
+mpcobj.ControlHorizon = 5;
+
+%% Constraints and Weights
+% To prevent the ATLASCAR2 from accelerating or decelerating too quickly, 
+% add a hard constraint of 0.2 (m^2/sec) on the throttle rate of change.
+% mpcobj.ManipulatedVariables(1).RateMin = -0.2; 
+% mpcobj.ManipulatedVariables(1).RateMax = 0.2;
+
[…]

### 2019-02-13 MATLAB/path planning/main_path_planning.m

@@ -1,199 +1,0 @@
-clear all
-close all
-clc
-
-%% ATLASCAR2 - Moving Obstacle Avoidance based on MPC
-
-car = struct;
-road = struct;
-obstacle = struct;
-
-%% Vehicle model
-
-% Parameters definition
-car.length = 5;                 % Length of the ATLASCAR2
-car.width = 2;                  % Witdh of the ATLASCAR2
-car.V = 20;                     % Constant speed of the ATLASCAR2
-car.x0 = [150; -20; pi/2; car.V];      % Initial conditions
-car.u0 = [0; 0];
-Ts = 0.02;                      % Sampling time
-
-% Obtain a linear plant model at the nominal operating point and convert it
-% into a discrete-time model to be used by the model predictive controller.
-[Ad,Bd,Cd,Dd,U,Y,X,DX] = ATLASCAR2ModelDT(Ts,car.x0,car.u0);
-
-dsys = ss(Ad,Bd,Cd,Dd,'Ts',Ts);          % State space
-dsys.InputName = {'Throttle','Delta'};   % Input u
-dsys.StateName = {'X','Y','Theta','V'};  % State x
-dsys.OutputName = dsys.StateName;        % Output y   
-
-%% Plot initial condition
-
-% ATLASCAR2 - Green with black boundary
-% Horizontal lanes - Dashed black lines
-% Obstacle/Car - Red with with black boundary
-% Safe zone - Dashed red boundary.
-
-f = obstaclePlotInitialCondition(car, obstacle, road);
-
-%% MPC design
-
-% MPC object: sampling time Ts, Prediction Horizon 10, Control Horizon 2
-status = mpcverbosity('off');
-mpcobj = mpc(dsys);
-
-% Set the values of the prediction horizon and the control horizon
-mpcobj.PredictionHorizon = 25;   % number of steps = 0.5 seconds
-mpcobj.ControlHorizon = 5;
-
-%% Constraints and Weights
-% To prevent the ATLASCAR2 from accelerating or decelerating too quickly, 
-% add a hard constraint of 0.2 (m^2/sec) on the throttle rate of change.
-%mpcobj.ManipulatedVariables(1).RateMin = -0.2; 
-%mpcobj.ManipulatedVariables(1).RateMax = 0.2;
-  
-% add a hard constraint of 6 degrees per sec on the steering angle rate of change.
[…]

### 2019-02-13 MATLAB/path planning/obstaclePlotInitialCondition.m

@@ -1,28 +1,0 @@
-function f = obstaclePlotInitialCondition(car,obstacle,road)
-
-% Create figure
-
-f = figure;
-
-% Plot the ATLASCAR2
-
-X0 = car.x0(1);
-Y0 = car.x0(2);
-plot(X0,Y0,'gx'); 
-hold on 
-grid on
-grid minor
-p = patch([X0-car.length/2 X0-car.length/2 X0+car.length/2 X0+car.length/2], [Y0-car.width/2, Y0+car.width/2, Y0+car.width/2, Y0-car.width/2], [0 1 0]); 
-%rectangle('Position',[X0-car.length/2,Y0 - car.width/2,car.length,car.width],'FaceColor',[0 1 0],'Curvature',0.2,'LineStyle','-','LineWidth', 1.2, 'EdgeColor','k');
-axis equal
-
-%,'EdgeColor','[1 0 0]','LineStyle','--'
-delete(p)
-
-% Reset the axis.
-axis([-155 155 -330 330]);
-xlabel('X');
-ylabel('Y');
-title('ATLASCAR2 Moving Obstacle Avoidance');
-
-

### 2019-02-14 Thesis_Latex/FinalReport/FinalReport.tex
update final report

@@
 \IEEEoverridecommandlockouts
-
 \usepackage{algorithm}
@@
 	}
-
+\usepackage{pdfpages}
 \begin{document}
+\includepdf[page=-]{./coverpage/coverpage.pdf}
 \maketitle
@@
 The future work includes the combination of these two control strategies in a way that they can operate simultaneously.
+In order to achieve this objective we have started to simulate a trajectory tracking framework using a slight modification of the linearized tracking error model in \cite{error_model}.
 Next expected steps include the migration to ROS-Gazebo simulation environment and, later on, the usage of real data collected on board the ATLASCAR2 and, ultimately, test it in a real autonomous driving scenario.
@@
 	\bibitem{curvature}Danwei Wang, Feng Qi, "Trajectory planning for a four-wheel-steering vehicle," 2001 International Conference on Robotics and Automation, Seoul, Korea, 2001
+
+	\bibitem{error_model}H.
+Yang, M.
+Guo, Y.
+Xia and L.
+Cheng, "Trajectory tracking for wheeled mobile robots via model predictive control with softening constraints," in IET Control Theory \& Applications, vol.
+12, no.
+2, pp.
+206-214, 30 1 2018.
 \end{thebibliography}

### 2019-02-14 Thesis_Latex/FinalReport/coverpage/coverpage.tex
update final report

%pdflatex -synctex=1 -interaction=nonstopmode %.tex
% uaThesis example (for a thesis written in Portuguese)
%
% the complete list of options and commands can be found in uaThesis.sty 
%

\documentclass[11pt,twoside,a4paper]{report}
\usepackage[DEM,newLogo]{uaThesis}
%encoding
%--------------------------------------
\usepackage[latin1]{inputenc} 
%%%%\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
%--------------------------------------

%Portuguese-specific commands
%--------------------------------------
\usepackage[portuguese]{babel}
%--------------------------------------

%Hyphenation rules
%--------------------------------------
\usepackage{hyphenat}
\hyphenation{mate-mática recu-perar}
%--------------

%Sections Numbering rule
%--------------------------------------
%\setcounter{secnumdepth}{4}
%--------------------------------------

%Svg Stuff
%--------------------------------------
\usepackage{svg}                   %to include directly svg graphics.
\setsvg{inkscape=inkscape -z -D}   %Options to invoke inkscape (assuming inkspace is in the PATH)
\setsvg{svgpath=Imagens/}           %Or any other path where SVG images are
%--------------------------------------

%\usepackage[backend=bibtex]{biblatex}
  \usepackage[
    backend=bibtex,
    style=ieee,
  ]{biblatex}

\addbibresource{bibliografie.bib}
%--------------------------------------

\def\ThesisYear{2019}

% custom macros
\def\I{\mathtt{i}}
\def\Exp#1{e^{2\pi\I #1}} % argument inside braces, i.e., "{}"
\def\EXP#1.{e^{2\pi\I #1}} % argument finishes when a full stop is encountered, i.e., "."

% optional: visual delimiters for floats (figures and tables)
\def\topfigrule{\kern 7.8pt \hrule width\textwidth\kern -8.2pt\relax}
\def\dblfigrule{\kern 7.8pt \hrule width\textwidth\kern -8.2pt\relax}
\def\botfigrule{\kern -7.8pt \hrule width\textwidth\kern 8.2pt\relax}

\begin{document}

%
% Cover page (use only one of the first two \TitlePage)
%

% First alternative, with a figure
\TitlePage
  %\GRID  % for debugging ONLY
  \HEADER{\BAR\FIG{\includegraphics[height=60mm]{uaLogoNew}}} % the \FIG{} is optional
         {\ThesisYear}
  \TITLE{Alberto Franco \newline 92137}
        {Local Path Planning with Moving Obstacle Avoidance based on adaptive MPC in ATLASCAR2}

\EndTitlePage
\titlepage\ \endtitlepage % empty page

%
% First thesis pages
%

\TitlePage
  \HEADER{}{\ThesisYear}
  \TITLE{14$^{\text{th}}$ February 2019}
        {Projeto de Dissertação - 49992 }
  \vspace*{15mm}
  \TEXT{}
       {Project Report presented at the University of Aveiro for fulfilling the necessary requirements to write a dissertation and obtain the Master Degree in Automation Engineering, carried out with the scientific supervision of Vítor Manuel Ferreira dos Santos, Associate Professor in the Department of Mechanical Engineering at the University of Aveiro.
       \newline\\
       The research work for this project  was developed at the Laboratory for Automation and Robotics (LAR) during a period of 5 months as an exchange student. Inserted in the ATLASCAR2 project this work aims to develop a short-term path planning algorithm
       for driver assistance in dynamic environments. In order to achieve this objective, it was made a preliminary study of the existing local path planning methods and the projects that have already been developed in this field. It was possible to identify a different solution based on a mathematical optimization approach (Model Predictive Control) that was simulated in a MATLAB/Simulink enviroment. At the beginning of this work all the ROS tutorials were carried out in order to understand if the proposed solution was feasible for this project. The first method developted, is an obstacle avoidance system that moves the vehicle around different moving obstacles while the second algorithm is a lane following system that keeps the ATLASCAR2 traveling along the centerline of the lanes on the road.  Simulation results demonstrate and verify the feasibility and the usefulness of methods considering different scenarios, opening space for real scenario implementation with Gazebo and ROS.
       All my work has been documented through a blog and the related code is stored on the Github platform.
       Moreover this research has allowed the submission of a paper for the 19th IEEE International Conference on Autonomous Robot Systems and Competitions (ICARSC' 2019).}
\EndTitlePage
\titlepage\ \endtitlepage % empty page
\end{document}

### 2019-02-14 Thesis_Latex/Thesis/Chapter2/Chapter2.tex
update final report

\chapter{Literature Review}
\cite{4651075}
\cite{vsantos2010}
\cite{borelli}
\cite{Skoda:Thesis:2016}

### 2019-02-14 MATLAB/path planning/Path Planning v2/main_path_planning_error.m

@@ -81,8 +81,8 @@ mpcobj.Model.Nominal = struct('U',U,'Y',Y,'X',X,'DX',DX);
 %% Simulation
 Duration = 50;
 T = 0:Ts:Duration; 
-x_ref = 30*sin(T/4);
-y_ref = 15*sin(T/8);
+x_ref = 300*sin(T/4);
+y_ref = 150*sin(T/8);
 x_dot = gradient(x_ref,Ts);
 y_dot = gradient(y_ref,Ts);
 theta_ref = atan2(x_dot,y_dot);

### 2019-02-28 Thesis_Latex/Thesis/Introduction/Introduction.tex
update thesis

@@
 %\addcontentsline{toc}{chapter}{Introduction}
-\section{ATLAS Project}
+......
+\section{ATLAS Project}\label{sec:ATLAS}
+The ATLAS project was created in 2003 by the Group for Automation and Robotics from the Department of Mechanical Engineering at the University of Aveiro \cite{vsantos2010}.
+The objective of this project is to study and develop advanced sensors and active systems to promote the autonomous control of cars and other platforms.
+The first projects in the autonomous driving area focused on small scale models in controlled environments for participation in the National Robotics Festival (FNR) and in many other competitions winning some awards for the best performance (subsection \ref{sec:ATLASplatform}).
+The success and experience gained with these models allowed the evolution of the project for full-scale vehicles, where ATLASCAR (subsection \ref{sec:ATLASCAR}) in 2010 and ATLASCAR2 (subsection \ref{sec:ATLASCAR2}) in 2016 have been developed.
+
+\subsection{ATLAS platforms}\label{sec:ATLASplatform}	
+The first developed robot (Figure \ref{fig:modelosatlas1}) was based on an aluminum and wood structure.
+In this prototype only one camera was installed that pointed to a mirror to allow the complete visualization of the road in which the robot circulated.
+The traction movement was assured by a mechanical differential coupled to the rear wheels and the steering movement was given by a single front wheel.
+In order to create a model more similar to an ordinary car, the ATLAS group developed the ATLAS 2000 (Figure \ref{fig:modelosatlas2}) in scale (1:4), with which it managed to win the first autonomous driving competition of the FNR in 2006.
+After several improvements made in ATLAS 2000, in 2008 a new platform, ATLAS MV (Figure \ref{fig:modelosatlas3}) was created.
+This robot was designed on a smaller scale (1:5), with the intention of being lighter and faster.
+On board were installed a new steering system, hydraulic braking and an active perception unit.
+This robot allowed the conquest of new victories in the autonomus driving competitions.
+\begin{figure}[!h]
+	\centering
+		\begin{minipage}[t]{0.32\textwidth}
+			\includegraphics[width=\textwidth]{../figure/modelosatlas1.pdf}
+			\subcaption{First ATLAS prototype.}
+			\label{fig:modelosatlas1}
+		\end{minipage}
+		\begin{minipage}[t]{0.32\textwidth}
+			\includegraphics[width=\textwidth]{../figure/modelosatlas2.pdf}
+			\subcaption{ATLAS 2000.}
+			\label{fig:modelosatlas2}
+		\end{minipage}
+		\begin{minipage}[t]{0.32\textwidth}
+			\includegraphics[width=\textwidth]{../figure/modelosatlas3.pdf}
+			\subcaption{ATLAS MV.}
+			\label{fig:modelosatlas3}
+		\end{minipage}
+		\caption{Some of the ATLAS project small scale platforms (adapted from \cite{Pereira2012}).}
+		\label{fig:modelosatlas}
+\end{figure}
+
+\subsection{ATLASCAR}\label{sec:ATLASCAR}
+\begin{figure}[!h]
+	\centering
+	\includegraphics[width=\textwidth]{../figure/atlascar1.jpg}
+	\caption{The car used in ATLASCAR, based on Ford Escort Station Wagon of 1998 (adapted from \cite{Pereira2012}).}
+	\label{fig:atlascar1}
+\end{figure}
+
+\subsection{ATLASCAR2}\label{sec:ATLASCAR2}
+\begin{figure}[!h]
+	\centering
+	\includegraphics[width=\textwidth]{../figure/atlascar2.jpg}
+	\caption{The vehicle used in ATLASCAR2, based on an electric car, a Mitsubishi iMiEV of 2015 (adapted from \cite{Ricardo:Thesis:2018}).}
+	\label{fig:atlascar2}
+\end{figure}
 \section{Context of the Problem and Motivation}

### 2019-03-06 Thesis_Latex/Thesis/Acknowledgements/Acknowledgements.tex
update thesis

@@
-\chapter*{Acknowledgements}
+\chapter*{Ringraziamenti/Acknowledgements}
 \thispagestyle{empty}
-Eventuali ringraziamenti personali.
+dedica a parenti e amici
+
+The research work for this thesis was carried out at the Laboratory for Automation and Robotics (LAR) in the Department of Mechanical Engineering of Aveiro (Portugal), during a period of 5 months as an exchange student.
+\begin{figure}[!h]
+	\centering
+	\includegraphics[width=0.50\textwidth]{../figure/logo_ua.png}
+	\label{fig:logo_ua}
+\end{figure}
+
+I would like to express my gratitude to Professor Vitor Santos, for welcoming me at the Laboratory for Automation and Robotics and making possible my experience of study at the University of Aveiro.
+His help has been invaluable both personally and academically.
+Moreover I would like to thank Professor Angelo Cenedese for his advices and his help during this work.

### 2019-03-06 Thesis_Latex/Thesis/Chapter4/Chapter4.tex
update thesis

@@
 \chapter{Moving Obstacle Avoidance}
+
 \section{Problem Formulation}
+% COLLISION AVOIDANCE FIGURE
+\begin{figure}[!h]
+	\centering
+	\includegraphics[width=\textwidth]{../figure/obstacleAvoidance/obstacleAvoidance.pdf}
+	\caption{Problem description of collision avoidance on a road with only two lanes.}
+	\label{fig:obstacleAvoidance}
+\end{figure}
+% BICYCLE MODEL
+\begin{figure}[!h]
+	\centering
+	\includegraphics[width=0.80\textwidth]{../figure/car_model.pdf}
+	\caption{Bicycle model of a car, (adapted from \cite{siciliano}).}
+	\label{fig:car_model}
+\end{figure}
 \section{Design of Adaptive MPC}
+% FLOWCHART
+\begin{figure}[!h]
+	\centering
+	\includegraphics[width=\textwidth]{../figure/flowchart/flowchart.pdf}
+	\caption{Behaviour planning conditional flowchart.}
+	\label{fig:flowchart}
+\end{figure}
+% FIGURE CONSTRAINT
+\begin{figure}[!h]
+	\centering
+	\includegraphics[width=\textwidth]{../figure/constraint/constraint.pdf}
+	\caption{Constraints in the case of left overtaking.}
+	\label{fig:constraint}
+\end{figure}
+
 \section{Simulation Results}
+% ONE MOVING OBSTACLE
+\begin{figure}[h!]
+	\centering
+	\begin{minipage}[t]{\textwidth}
+		\includegraphics[width=\textwidth]{../figure/one_obstacle_right_overtaking/overtaking_start.pdf}
+	\end{minipage}
+	\begin{minipage}[t]{\textwidth}
+		\includegraphics[width=\textwidth]{../figure/one_obstacle_right_overtaking/overtaking_middle.pdf}
+	\end{minipage}
+	\begin{minipage}[t]{\textwidth}
+		\includegraphics[width=\textwidth]{../figure/one_obstacle_right_overtaking/overtaking_middle_end.pdf}
+	\end{minipage}
+	\begin{minipage}[t]{\textwidth}
+		\includegraphics[width=\textwidth]{../figure/one_obstacle_right_overtaking/overtaking_end.pdf}
+	\end{minipage}
+	\caption{Simulation of right overtaking with one moving obstacle that moves in the same direction as the vehicle.}
+	\label{fig:obstacleAvoidance_one_obstacle}
+\end{figure}
+% ALGORITHM FOR RIGHT OVERTAKING OF ONE MOVING OBSTACLE
+\begin{algorithm}%[b]
+	\caption{Right Overtaking if an obstacle is detected}
+	\small
+	\begin{algorithmic}[1]
+		\Function{RightOvertaking}{car, obstacle, road}
+		\State $x_\text{min} \gets \text{car}X $,  $x_\text{max} \gets +\infty$;
+		\State obsYrr = obstacle.RearRightSafeY;
+		\State obsXrr = obstacle.RearRightSafeX;
+		\If{ATLASCAR2 is behind the obstacle} 
+		\If{ATLASCAR2 is in the adjacent lane}
+		\State $cS \gets 0$; $cI \gets \text{obsYrr}$;
+		\Else
+		\State $cS \gets \text{tan}(\text{atan2}(\frac{\text{obsYrr}-\text{ carY}}{\text{obsXrr}-\text{carX}},1))$;
+		\State $cI \gets \text{obsYrr}-cS*\text{obsXrr}$;
+		\EndIf
+		\Else
+		\If{ATLASCAR2 is parallel to the obstacle}
+		\State $cS \gets 0$; $cI \gets \text{obsYrr}$;
+		\Else
+		\State $cS \gets 0$; $cI \gets W/2$;
+		\EndIf
+		\EndIf
+		\State \Return $x_\text{min}$, $x_\text{max}$, $cI$, $cS$
+		\EndFunction
+	\end{algorithmic}
+	\label{alg:rightOvertaking}
+\end{algorithm}
+% OVERALL SCHEME ONE MOVING OBSTACLE
+\begin{figure}[!h]
+	\centering
+	\includegraphics[width=\textwidth]{../figure/MovingObstacleAvoidance.pdf}
+	\caption{Overall procedure scheme moving obstacle avoidance.}
+	\label{fig:MovingObstacleAvoidance}
+\end{figure}
+% MULTIPLE MOVING OBSTACLE
+\begin{figure}[!h]
+	\centering
+	\begin{minipage}[t]{\textwidth}
+		\includegraphics[width=\textwidth]{./figure/random_N_obstacles/overtaking_random_2.pdf}
+	\end{minipage}
+	\begin{minipage}[t]{\textwidth}
+		\includegraphics[width=\textwidth]{./figure/random_N_obstacles/overtaking_random.pdf}
+	\end{minipage}
+	\begin{minipage}[t]{\textwidth}
+		\includegraphics[width=\textwidth]{./figure/random_N_obstacles/overtaking_random_1.pdf}
+	\end{minipage}
+	\caption{Simulations of overtaking with $N = 2,3,4$ moving obstacles that drive in the opposite direction with respect to the ATLASCAR2.}
+	\label{fig:obstacleAvoidance_random}
+\end{figure}
+
+% BRAKING THREE OBSTACLE
+\begin{figure}[!h]
+	\centering
+	\begin{minipage}[t]{\textwidth}
+		\includegraphics[width=\textwidth]{./figure/three_obstacles_no_overtaking/braking_0.pdf}
+	\end{minipage}
+	\begin{minipage}[t]{\textwidth}
+		\includegraphics[width=\textwidth]{./figure/three_obstacles_no_overtaking/braking_1.pdf}
+	\end{minipage}
+	\begin{minipage}[t]{\textwidth}
+		\includegraphics[width=\textwidth]{./figure/three_obstacles_no_overtaking/braking_2.pdf}
+	\end{minipage}
+	\begin{minipage}[t]{\textwidth}
+		\includegraphics[width=\textwidth]{./figure/three_obstacles_no_overtaking/braking_3.pdf}
+	\end{minipage}
+	\begin{minipage}[t]{\textwidth}
+		\includegraphics[width=\textwidth]{./figure/three_obstacles_no_overtaking/braking_4.pdf}
+	\end{minipage}
+	\begin{minipage}[t]{\textwidth}
+		\includegraphics[width=\textwidth]{./figure/three_obstacles_no_overtaking/braking_5.pdf}
+	\end{minipage}
+	\begin{minipage}[t]{\textwidth}
+		\includegraphics[width=\textwidth]{./figure/three_obstacles_no_overtaking/braking_6.pdf}
+	\end{minipage}
+	\caption{Simulation of braking and overtaking obstacles.}
+	\label{fig:braking}
+\end{figure}
+% RESULTS BRAKING THREE OBSTACLES
+\begin{figure}[!t] %vs changes to t instead of b
+	\begin{minipage}[t]{0.5\textwidth}
+		\includegraphics[width=\textwidth]{./figure/three_obstacles_no_overtaking/VelocityVsTime.pdf}
+		\vspace{-17pt}
+		\subcaption{}\label{fig:velocity_braking}
+	\end{minipage}
+	\begin{minipage}[t]{0.5\textwidth}
+		\includegraphics[width=\textwidth]{./figure/three_obstacles_no_overtaking/ThrottleVsTime.pdf}
+		\vspace{-17pt}
+		\subcaption{}\label{fig:throttle_braking}
+	\end{minipage}
+	\begin{minipage}[t]{0.5\textwidth}
+		\includegraphics[width=\textwidth]{./figure/three_obstacles_no_overtaking/SteeringAngleVsTime.pdf}
+		\vspace{-17pt}
+		\subcaption{}\label{fig:delta_braking}
+	\end{minipage}
+	\begin{minipage}[t]{0.5\textwidth}
+		\includegraphics[width=\textwidth]{./figure/three_obstacles_no_overtaking/HeadingAngleVsTime.pdf}
+		\vspace{-17pt}
+		\subcaption{}\label{fig:theta_braking}
+	\end{minipage}
+	\caption{Time signals of the ATLASCAR2 in the simulation of braking and overtaking in the situation illustrated in Fig. \ref{fig:braking}.}
+	\label{fig:components}
+\end{figure}

### 2019-03-06 Thesis_Latex/Thesis/Chapter5/Chapter5.tex
update Matlab files
update thesis

--- 2019-01-24 Thesis_Latex/Thesis/Chapter4/Chapter4.tex
@@
-\chapter{Moving Obstacle Avoidance}
+\chapter{Lane Following}
 \section{Problem Formulation}
+\begin{figure}[!h]
+	\centering
+	\includegraphics[width=0.75\textwidth]{../figure/laneFollowing/laneFollowing.pdf}
+	\caption{Problem description of a lane following system.}
+	\label{fig:laneFollowing}
+\end{figure}
 \section{Design of Adaptive MPC}
 \section{Simulation Results}
+\begin{table}[!h]
+	\centering
+	\begin{tabular}{|c|c|}
+		\hline
+		Parameters          & Values      \\
+		\hline
+		$m$          & \SI{1575}{kg}              \\
+		$I_z$         & \SI{2875}{kgm^2}               \\
+		$l_F$           & \SI{1.2}{m}               \\
+		$l_R$         & \SI{1.6}{m}               \\
+		$C_F$          & \SI{19000}{\newton/rad}      \\
+		$C_R$           & \SI{33000}{\newton/rad}  \\
+		$\tau$             & 0.2                \\
+		$V_0$           & \SI{15}{m/s}       \\
+		$V_{\text{set}}$          & \SI{20}{m/s}   \\
+		$T_s$         & \SI{0.02}{s}          \\
+		\hline
+	\end{tabular}
+\end{table}
+
+\begin{figure}[!t]
+	\centering
+	\begin{minipage}[t]{0.49\textwidth}
+		\includegraphics[width=\textwidth]{../../MATLAB/lane_following/figure/Reference.pdf}
+		\vspace{-17pt}
+		\subcaption{}
+		\label{fig:reference_laneFollowing}
+	\end{minipage}
+	\begin{minipage}[t]{0.5\textwidth}
+		\includegraphics[width=\textwidth]{../../MATLAB/lane_following/figure/Curvature.pdf}
+		\vspace{-17pt}
+		\subcaption{}
+		\label{fig:curvature_laneFollowing}
+	\end{minipage}
+	\caption{Desired path and curvature of the ATLASCAR2 in a simulation of \SI{20}{s}}
+	\label{fig:laneFollowing_desired}
+	\vspace{-30pt}
+\end{figure}
+
+\begin{figure}[!t]
+	\centering
+	\begin{minipage}[t]{0.49\textwidth}
+		\includegraphics[width=\textwidth]{../../MATLAB/lane_following/figure/LongitudinalVelocityVsTime.pdf}
+		\subcaption{Longitudinal velocity $V_x$ with respect to time.}
+		\label{fig:longitudinal_velocity_laneFollowing}
+	\end{minipage}
+	\begin{minipage}[t]{0.49\textwidth}
+		\includegraphics[width=\textwidth]{../../MATLAB/lane_following/figure/AccelerationVsTime.pdf}
+		\subcaption{Acceleration $u_1$ with respect to time.}
+		\label{fig:acceleration_laneFollowing}
+	\end{minipage}
+	\begin{minipage}[t]{0.49\textwidth}
+		\includegraphics[width=\textwidth]{../../MATLAB/lane_following/figure/SteeringAngleVsTime.pdf}
+		\subcaption{Steering angle $u_2$ with respect to time.}
+		\label{fig:steering_laneFollowing}
+	\end{minipage}
+	%\begin{minipage}[t]{\columnwidth}
+	%	\includegraphics[width=\columnwidth]{../../MATLAB/lane_following/figure/RelativeYawAngleVsTime.pdf}
+	%	\subcaption{Relative yaw angle $e_2$ with respect to time.}
+	%	\label{fig:relative_yaw_angle_laneFollowing}
+	%\end{minipage}
+	\begin{minipage}[t]{0.49\textwidth}
+		\includegraphics[width=\textwidth]{../../MATLAB/lane_following/figure/LateralDeviationVsTime.pdf}
+		\subcaption{Lateral deviation $e_1$ with respect to time.}
+		\label{fig:lateral_deviation_laneFollowing}
+	\end{minipage}
+	\caption{Time signals of the ATLASCAR2 in the simulation with a sinusoidal path.}
+	\label{fig:laneFollowing_signals}
+\end{figure}
+
+\begin{figure}[!h]
+	\centering
+	\includegraphics[width=1\textwidth]{../figure/lane_following_AMPC.pdf}
+	\caption{Overall procedure scheme lane following.}
+	\label{fig:scheme_lane_following}
+\end{figure}

### 2019-03-06 Thesis_Latex/Thesis/Introduction/Introduction.tex
update thesis

@@
 \subsection{ATLASCAR}\label{sec:ATLASCAR}
+Driven by the positive results achieved with scale models and years of navigation experience in controlled environments, in 2010 the Group of Automation and Robotics decided to invest in a large-scale project, ATLASCAR (Figure \ref{fig:atlascar1}).
+The vehicle used for this project was a Ford Escort Station Wagon of 1998 powered by a gasoline internal combustion engine, in which several sensors, processing units and actuators were installed.
+On-board sensors processed data collected from the vehicle and its surroundings, with different LIDARs for obstacle detection and environmental reconstruction, pedestrian detection cameras and a Global Navigation Satellite System (GNSS) for location and route planning.
+After passing through the processing units, these data were sent to the actuators that allowed the movement and execution of the maneuvers in a completely autonomous way on the part of the vehicle.
+To power all the equipment, a Uninterruptible Power Supply (UPS) was used, loaded from an auxiliary alternator.
+During this project, many works were developed in the Laboratory for Automation and Robotics, many of which produced master thesis.
+For example, in 2014 Cabral de Azevedo \cite{Azevedo2014} developed a module to detect pedestrians using sensory fusion of LIDAR and vision data while in 2016 Vieira da Silva \cite{Silva2016} created a multisensory calibration module that was exported to subsequent projects.
 \begin{figure}[!h]
@@
 \subsection{ATLASCAR2}\label{sec:ATLASCAR2}
+Given the different limits, to continue the project, in 2016, a new vehicle was acquired: ATLASCAR2 (Figure \ref{fig:atlascar2}). This time it was chosen as a platform
+an electric car, a Mitsubishi iMiEV, with an autonomy range of \SI{100}{km}.
+The fact that the vehicle is electric allows to use the energy stored in the batteries, making it easier to power the sensors installed.
+In fact, despite the short time of existence, 3 LIDARs, a camera, inclinometry sensors and a GNSS unit are already installed on the ATLASCAR2.
+Many of these sensors were transferred from ATLASCAR to this project during the work of Madureira Correia \cite{Madureira2017} in 2017, where a module for detecting free space around the car was also developed while in 2018 Ricardo Silva \cite{Ricardo:Thesis:2018} created a local navigation module for driver assistance in the immediate decision making, identifing a solution based on a multiple hypothesis approach.
 \begin{figure}[!h]
@@
 \end{figure}
+
+\section{Autonomous Cars}
+The modern automobile companies keep coming up with newer autonomous features in their recent models.
+Technological advancements seen every day in areas like information technology, communication, data analysis and storage etc.
+is not exclusive to these areas alone.
+The realm of autonomous cars is also progressing at a rapid rate these days \cite{Bimbraw2015}.
+Google's development of self-driving technology began in January 2009.
+The initial objective of the project was to develop a car able to navigate on highways with minimal human intervention.
+In December 2016, the unit was renamed Waymo; this name derived from its mission, "a new way forward in mobility".
+Waymo moved to further test its cars on public roads after becoming its own subsidiary.
+\begin{figure}[!h]
+	\centering
+	\begin{minipage}[t]{0.65\textwidth}
+		\includegraphics[width=\textwidth]{../figure/veiculos0.png}
+		\subcaption{Google's Firefly self-driving prototype in 2015 (adapted from \cite{waymoh}).}
+		\label{fig:veiculos0}
+	\end{minipage}
+	\begin{minipage}[t]{0.65\textwidth}
+		\includegraphics[width=\textwidth]{../figure/veiculos1.png}
+		\subcaption{Waymo Chrysler Pacifica Hybrid self-driving prototype in 2017 (adapted from \cite{waymoh}).}
+		\label{fig:veiculos1}
+	\end{minipage}
+	\caption{Some of the Waymo/Google prototypes tested across multiple locations in the Unided States in recent years.}
+	\label{fig:waymo}
+\end{figure}
+
+Waymo uses LIDAR which sends out millions of laser beams per second to build up a detailed picture of the world all 360 degrees around it.
+It also uses radar to detect how far away objects are and their speed and high-resolution cameras detect visual information like whether a traffic signal is red or green.
+It then combines all that data to understand the world around it and predict what those things might do next.
+It can do that for things up to three football fields away.
+Based on all this information, Waymo's software determines the exact trajectory, speed, lane and steering maneuvers needed to progress along this route safely \cite{waymoh} \cite{waymot}.
+With the advances in autonomous technology, VIAC or VisLab Intercontinental Autonomous Challenge was one of the major competitions which led to improvements in the testing and analysis of autonomous vehicles and robotics.
+It was a 13,000 kilometers trip, nearly three months from Parma, Italy to Shanghai, China from July 20, 2010 to October 28, 2010.
+It involved four autonomous vehicles with negligible human intervention and high level of autonomy \cite{Broggi2010}.
+\begin{figure}[!h]
+	\centering
+	\includegraphics[width=0.65\textwidth]{../figure/veiculos4.png}
+	\caption{BRAiVE prototype developted by VisLab, based on a Hyundai Sonata (adapted from \cite{Broggi2013}).}
+	\label{fig:veiculos4}
+\end{figure}
 \section{Context of the Problem and Motivation}

### 2019-03-06 Thesis_Latex/Thesis/figure/laneFollowing/laneFollowing.tex
update thesis

\documentclass[preview,float]{standalone}
\usepackage{tikz}
\usetikzlibrary{hobby,decorations.markings}
\usepackage{graphicx}

\begin{document}
\begin{tikzpicture}
\coordinate (origo) at (0,0);

\draw [green,rotate around={50:(1.7,2.4)},->] (1.7,2.4) -- (3.3,2.4) node(mary)[above,right] {$V_x$};

\draw[green,
  postaction={
    decorate,
    decoration={
      markings,
      mark=between positions 0 and 1 step 0.33 with
      {
        \node[transform shape] {\includegraphics[width=1.5cm,angle=50]{car}};
      }
    }
  }
]
(1.7,2.4);

\draw[dashed]
(-1,0.7) parabola (5,5.0);
\draw
(-1,-0.7) parabola (5+1.4,5.0);
\draw
(-1,2.1) parabola (5-1.4,5.0);

\draw [red,rotate around={50+90:(1.7,2.4)},->] (2,2.4) -- (2.6,2.4) node[above] {$V_y$};

\draw [] (1.7,2.4) -- (2,1.8) node[below] {$e_1$};

\fill(2,1.8) circle (0.06);

\draw[dashed,thick,rotate around={30:(2,1.8)}] (2,1.8)--(4,1.6);

\draw[dashed,thick,rotate around={30:(1.7,2.4)}] (1.7,2.4)--(4-0.25,2.4) node(bob)[right]{};

\draw (2.63,2.93) arc (30:82-30:1) node[right]{$e_2$};

\draw[gray,->](2.2,1.5)--(4.5,0.4) node[below] {lateral deviation};
\draw[gray,->](2.4,3.3)--(1.1,4) node[above] {relative yaw angle};
\end{tikzpicture}
\end{document}

### 2019-03-06 Thesis_Presentation/template_beamer_padova/example.tex
update thesis

\documentclass{beamer}

\usetheme{Padova}

\title{Local Path Planning with Moving Obstacle Avoidance based on Adaptive MPC in ATLASCAR2}
\author{Alberto Franco 1156523}
\date{15 Aprile 2019}

\begin{document}

	\maketitle

	\begin{frame}{Outline}
		\tableofcontents
	\end{frame}

	\section{Introduction}

	\begin{frame}{Introduction}

		Etiam eu interdum ligula

		Nunc mi eros, vulputate in ornare a, viverra eget quam \vspace{.5em}

		\begin{itemize}
			\item Morbi \textbf{vitae lacus} porta neque tincidunt sodales \vspace{.5em}
			\item Proin tincidunt, \textbf{neque} at tincidunt mollis \vspace{.5em}
			\item Ut \alert{lacinia sem a nibh} consequat porttitor
		\end{itemize}
	\end{frame}

	\section{First section}

	\begin{frame}{First section}
		\begin{block}{Normal block}
			Fusce luctus venenatis felis quis semper
		\end{block}

		\begin{alertblock}{Alert block}
			$$ E = (x_1 \vee \neg x_2 \vee \neg x_3) \wedge (x_1 \vee x_2 \vee x_4) $$
		\end{alertblock}

		\begin{exampleblock}{Example block}
			Proin tincidunt, neque at tincidunt mollis
		\end{exampleblock}
	\end{frame}

\end{document}

### 2019-03-08 Thesis_Latex/Thesis/Abstract/Abstract.tex
update thesis

@@
 \thispagestyle{empty}
-abstact
+Inserted in the ATLASCAR2 project this work aims to develop a short-term path planning algorithm
+for driver assistance in dynamic environments.
+In order to achieve this objective, it was made a preliminary study of the existing local path planning methods and the projects that have already been developed in this field, their advantages and disadvantages were weighed
+and the most successful approaches applied to local navigation in real autonomous driving projects were taken into account.
+This thesis presents two different strategies for a self-driving car short-term path planning among multiple moving obstacles.
+The main task is to study and implement a motion planning and execution framework in order to make ATLASCAR2 coexist with other moving obstacle vehicles by avoiding collision and overtake them when necessary and possible.
+The first method developted, is an obstacle avoidance system that moves the vehicle around different moving obstacles while the second algorithm is a lane following system that keeps the ATLASCAR2 traveling along the centerline of the lanes on the road.
+The proposed techniques, based on the adaptive Model Predictive Control paradigm, solve optimization problems formulated in terms of cost minimization under constraints.
+Simulation results, developted in a MATLAB/Simulink enviroment, demonstrate and verify the feasibility and the usefulness of methods considering different scenarios, opening space for real scenario implementation.

### 2019-03-08 Thesis_Latex/Thesis/Chapter3/Chapter3.tex
update thesis

\chapter{Model Predictive Control}

In this chapter, the theory of Model Predictive Control is discussed in detail to highlight working principle. In particular for this work we used an advanced control strategy based on this paradigm called Adaptive MPC that uses a fixed model structure, but allows the model parameters to evolve with the time.

\section{Generic Model Predictive Control problem}
Model Predictive Control (MPC), also known as Moving Horizon Control (MHC) or Receding Horizon Control (RHC), is a popular method for the control of slow dynamical systems, to generate the required
control inputs that are calculated at each sampling instance $k$, using the current state as initial
conditions to solve a finite optimal control problem. Some of the advantages of using MPC are:
\begin{itemize}
\item the ability to handle unstable, time variable, non-minimum phase systems;
\item robustness feature with the uncertainties in the nonlinear systems;
\item built in feed-forward control to handle disturbances in the processes;
\item enhanced tuning features to achieve the best response including transient responses;
\item the possibility to introduce constraints in a natural form;
\item if the references are known in advance, they can be used in order to optimize the reference tracking.
\end{itemize}

The methodology of all the controllers belonging to the MPC family is characterized by the following strategy, represented in Figure \ref{fig:mpc_theory}. The future outputs for a  determined horizon, called  the  prediction horizon, are predicted at each instant $k$ using the process model. These predicted outputs depend on the known values up to instant $k$ (past inputs and outputs) and on the future control signals which are those to be sent to the system and calculated. The set of future control signals is calculated by optimizing a determined criterion to keep the process as close as possible to the reference trajectory. This criterion usually takes the form of a quadratic function of the errors between the predicted output signal and the predicted reference trajectory. The control effort is included in the objective function in most
cases. An explicit solution can be obtained if the criterion is quadratic, the model is linear, and there are no constraints; otherwise an iterative
optimization method has to be used. Some assumptions about the structure of the future control law are also made in some cases, such as that it will be constant from a given instant. Only the current control signal is send to the process. At the next sampling instant the measured output is evaluated and the sequence is repeated and all the steps brought up to date. Thus the predicted control input is then calculated using the receding horizon concept.
\begin{figure}[!h]
	\centering
	\includegraphics[width=\textwidth]{../figure/mpc_theory.png}
	\caption{A discrete Model Predictive Control scheme adapted from \cite{mpctoolbox}.}
	\label{fig:mpc_theory}
\end{figure}

MPC is typically formulated in the state space. For a given discrete linear time-invariant (LTI) system:
\begin{equation}
\label{eqn:MPC_plant_discrete}
\vec{x}(k+1)=\vec{A}\vec{x}(k)+ \vec{B} \vec{u}(k)
\end{equation}
where $\vec{x}(k)\in\mathbb{R}^n$, $\vec{u}(k)\in\mathbb{R}^m$ are the state and the input, respectively. The central idea in the Model Predictive Control is to minimize some cost function, while still ensuring that some constraints are fulfilled. The generic MPC problem can be written as follows:
\begin{equation}
\label{eqn:MPC_optimization}
\begin{aligned}
& \underset{\textbf{u}}{\text{minimize}}
& & J(\vec{x}(k), \textbf{u}) \\
& \text{subject to}
& & \vec{x}_{k+i+1} = \vec{A}\vec{x}_{k+i}+ \vec{B} \vec{u}_{k+i}\quad\forall i=0,\dots N-1;\\
& & & \vec{x}_{k+i}\in \mathbb{X}\quad\forall i=0,\dots N-1;\\
& & & \vec{u}_{k+i}\in \mathbb{U}\quad\forall i=0,\dots N-1;\\  
& & & \vec{x}_{k+N}\in \mathbb{X}_f;\quad\vec{x}_k = \vec{x}(k).
\end{aligned}
\end{equation}
where $\textbf{u}=(\vec{u}_k,\dots,\vec{u}_{k+N-1})$ is a sequence of control inputs, $\vec{x}_{k+i}$ is the state at time $k+i$ as predicted at time $k$, and $N$ is the prediction horizon. The sets $\mathbb{X}\in\mathbb{R}^n$ and $\mathbb{U}\in\mathbb{R}^m$ define the constraints on the state and the input, respectively. Finally, the set $\mathbb{X}_f\subseteq\mathbb{X}$ defines the terminal constraint on the state. If we consider a regulation problem, the system \ref{eqn:MPC_plant_discrete} should be steered to the origin and the cost function $J(\vec{x}(k), \textbf{u})$ could be in a quadratic form as follows:
\begin{equation}
\label{eqn:MPC_cost_function_regulation}
	J(\vec{x}(k), \textbf{u}) = \vec{x}^\intercal_{k+N}\vec{P}_f\vec{x}_{k+N}+\sum_{i=1}^{N}\vec{x}^\intercal_{k+i}\vec{Q}\vec{x}_{k+i}+\vec{u}_{k+i}^\intercal\vec{R}\vec{u}_{k+i}
\end{equation}
where $\vec{P}_f,\vec{Q}\geq0$ (positive semi-definite) and $\vec{R}>0$ (positive definite) are weighting matrices.

Instead if we consider a servo problem, like tracking of a reference signal, the cost function is changed as follows:
\begin{equation}
\label{eqn:MPC_cost_function_servo}
\begin{aligned}
J(\vec{x}(k), \textbf{u})=& (\vec{x}_{k+N}-\vec{x}^\text{ref}_{k+N})^\intercal\vec{P}_f(\vec{x}_{k+N}-\vec{x}^\text{ref}_{k+N})\\
&+\sum_{i=1}^{N}(\vec{x}_{k+i}-\vec{x}^\text{ref}_{k+i})^\intercal\vec{Q}(\vec{x}_{k+i}-\vec{x}^\text{ref}_{k+i})+\vec{u}_{k+i}^\intercal\vec{R}\vec{u}_{k+i}
\end{aligned}
\end{equation}
where $\vec{x}^\text{ref}_{k+i}$, $\vec{x}^\text{ref}_{k+N}$ describe the reference trajectory. The standard MPC algorithm can be summarized by the following steps:
\begin{algorithm}%[b]
	\caption{Basic Model Predictive Control loop}
	\small
	\begin{algorithmic}[1]
		\State Measure the current state $\vec{x}(k)$;
		\State Solve the optimization problem \ref{eqn:MPC_optimization} with $\vec{x}(k)$ as initial state, where $\vec{u}(k)$ is calculated;
		\State Apply the first control of the optimal control sequence;
		\State Wait one sampling time and repeat steps 1-3;
	\end{algorithmic}
	\label{alg:rightOvertaking}
\end{algorithm}

An MPC has many strengths. Given that the model is discrete and linear it handles multivariable problems very well. Also mathematical convexity is an important part of the resulting problem formulation of an MPC. In fact there exists efficient solvers for convex optimization problems but it is therefore desirable that the MPC problem \ref{eqn:MPC_optimization} is convex which is ensured if:
\begin{enumerate}
\item the cost function is convex;
\item the prediction model is linear;
\item the constraint sets $\mathbb{X}, \mathbb{U}$ are convex.	
\end{enumerate}	
The optimization handles actuator constraints and state constraints naturally in the optimization which allows for
the process to be operated much closer to the hard constraints, which improves control performance and efficiency. Because of its predictive nature it is able to solve a variety of problems and handle disturbances smoothly.

\subsection{Tuning Parameters}
The two most important parameters to tune in order to satisfy the control objectives are the diagonal matrices $\vec{Q}$ and $\vec{R}$ that can be used to weight the system state matrix and the control inputs respectively. The response of the system that is too slow can be influenced by adding high weighting values in the $\vec{Q}$ matrix, whereas the control gains are damped with high weighing values in the $\vec{R}$ matrix. Find an optimal trade-off is a fundamental aspect for the constroller behaviour.

\subsection{Stability of MPC controller}
A limited horizon on the MPC problem affects the stability of the controllers; in order to avoid this problem it is possible to set an infinite horizon, impose end point constraints, terminal cost function or use other techniques. To obtain a stable controller, the parameters to tune are: the terminal cost, prediction horizon and constraints. Also the weights on the cost function can be tuned to ensure a stabilizing solution.

\subsection{Robustness}
If the stability can be guaranteed and the performance specifications are met with respect to a certain set of uncertainties, the system is said to be robust; in particular a controller with this property has to ensure that the constraints are never violated for any admissible disturbance realization. The uncertainties in a system are due to external disturbances, measurement noise, inaccurate values of the model parameters, non-linearities etc...
The most common type of uncertainties considered in the literature is additive disturbance because usually the current state of the system can be measured hence there is no noise in the measurements.

\section{Adaptive Model Predictive Control}
We understood that Model Predictive Control is an advanced method that predicts future behavior using a linear-time-invariant (LTI) dynamic model. These predictions are not exact and a good strategy is to make MPC insensitive to prediction errors. If the plant is strongly nonlinear or its characteristics vary dramatically with time, MPC performance might become unacceptable because LTI prediction accuracy degrade \cite{mpctoolbox}. A method that can address this degradation by adapting the prediction model for changing operating conditions is called Adaptive MPC: this control strategy uses a fixed model structure, but allows the model parameters to evolve with time. Ideally, whenever the controller requires a prediction, it uses a model appropriate for the current conditions. At each control interval, the adaptive MPC controller updates the plant model and nominal conditions. Once updated, the model and conditions remain constant over the prediction horizon. The plant model used as the basis for the adaptive MPC must be an LTI discrete-time, state-space model with a structure as follows:
\begin{equation}
\label{eqn:Adaptive_MPC_plant_discrete}
\begin{aligned}
\vec{x}(k+1)&=\vec{A}\vec{x}(k)+ \vec{B}_u \vec{u}(k)+\vec{B}_v \vec{v}(k)+\vec{B}_d \vec{d}(k)\\
\vec{y}(k)&=\vec{C}\vec{x}(k) + \vec{D}_v \vec{v}(k)+ \vec{D}_d \vec{d}(k)
\end{aligned}
\end{equation}
where the matrices \vec{A}, $\vec{B}_u$, $\vec{B}_v$, $\vec{B}_d$, \vec{C}, $\vec{D}_v$ and $\vec{D}_d$ can vary with time. The other parameters in the previous expression (\ref{eqn:Adaptive_MPC_plant_discrete}) are:
\begin{itemize}
	\item $k$ is the time index/current control interval;
	\item \vec{x} are the plant model states;
	\item \vec{u} are the manipulated inputs that can be adjusted by the MPC controller;
	\item \vec{v} are the measured disturbance inputs;
	\item \vec{d} are the unmeasured disturbance inputs;
	\item \vec{y} are the plant outputs, including both measured (necessary at least one) and unmeasured.
\end{itemize}
In the adaptive MPC control, there are additional requirements for the plant model, like the sample time $T_s$ that has to be constant and identical to the MPC control interval. This control strategy prohibits direct feed-through from any manipulated variable to any plant output. Thus, $\vec{D_v} = \vec{0}$ in the above model.
A traditional MPC controller includes a nominal operating point at which the plant model applies, such as the condition at which you linearize a nonlinear model to obtain the LTI approximation (equilibrium, reference trajectory and the	
most updated value) \cite{mpctoolbox}. In adaptive MPC, as time evolves it should update the nominal operating point to be consistent with the updated plant model. It is possible to rewrite the plant model in terms of deviations from the nominal conditions as follows:
\begin{equation}
\label{eqn:Adaptive_MPC_nominal_condition}
\begin{aligned}
\vec{x}(k+1)&=\overline{\vec{x}}+\vec{A}(\vec{x}(k)-\overline{\vec{x}})+ \vec{B}(\vec{u}_t(k)-\overline{\vec{u}}_t)+\overline{\Delta \vec{x}} \\
\vec{y}(k)&=\overline{\vec{y}}+\vec{C}(\vec{x}(k)-\overline{\vec{x}}) + \vec{D}(\vec{u}_t(k)-\overline{\vec{u}}_t)
\end{aligned}
\end{equation}
where the matrices \vec{A}, \vec{B}, \vec{C} and \vec{D} are updated with respect to time. The other parameters in the previous structure (\ref{eqn:Adaptive_MPC_nominal_condition}) are:
\begin{itemize}
	\item $\vec{u}_t$ is the combined plant input variable, comprising $\vec{u}$, $\vec{v}$ and $\vec{d}$ variables defined earlier;
	\item $\overline{\vec{x}}$ are the nominal states;
	\item $\overline{\Delta \vec{x}}$ are the nominal state increments;
	\item $\overline{\vec{u}_t}$ and $\overline{\vec{y}}$ are the nominal inputs and outputs.
\end{itemize} 
The adaptive MPC uses a Kalman filter to update its controller states which include the plant, the disturbance and measurement noise model states. In particular this filter is linear-time-varying (LTV) because adjusts the gains at each control
interval to maintain consistency with the updated plant model.

### 2019-03-08 Thesis_Latex/Thesis/Introduction/Introduction.tex
update thesis

@@
 %\addcontentsline{toc}{chapter}{Introduction}
-......
+In robotic research, the problem of navigation is among the most important.
+Basically, all autonomous mobile robots need some kind of navigation abilities to perform, localization, motion planning and guidance \cite{Skoda:Thesis:2016}.
+In the present context, we focus on navigation as a process of planning a path of a mobile robot from its current position to a desired goal location, following the planned path, and avoiding any discovered obstacles along the way.
+The desired paths have to fulfill several conditions to ensure safety and feasibility of the navigation.
+Moreover, the paths can be also defined in terms of specifications; for example, short or smooth paths are usually more desirable than long and curved ones in every dynamic environments.
+
+Beyond the path planning, the navigation problem also involves reacting to changes of the environment model.
+Robots are required to move towards the target in a short time and avoid either static or dynamic obstacles observed by their sensors, which involves efficient path planning and valid obstacle avoidance.
+
+Research and development of Unmanned Ground Vehicles has been dominated by DARPA (Defense Advanced Research Projects Agency) and NASA (National Aeronautics and Space Administration).
+The DARPA initiative started with the development of the first mobile robot, Shakey, and also includes the Autonomous Land Vehicle and the DARPA Demo I1 Program.
+NASA sponsors the development of unmanned vehicles for planetary surface exploration, from the Jet Propulsion Laboratory Mars Rover to the most recent Mars Pathfinder.
+Recent UGV design and development has been enhanced to build UGVs capable of operating in Intelligent Vehicle Highway Systems \cite{Bai2015}.
+
+Over the last decades, the development of Advanced Driver Assistance Systems has become a critical endeavor to attain different objectives: safety enhancement, mobility improvement, energy optimization and comfort \cite{Gruyer2017}.
+Much of the argument used in this discussion is based on the road mortality we see today.
+According to data from the World Health Organization, in 2013 there were about 1.25 million road deaths worldwide, and this number is expected to increase in the next decade \cite{world2015global}.
+Algorithms for autonomous navigation are increasingly robust and reliable and are starting to handle complex situations and decision problems.
+
+According to Katrakazas \cite{Katrakazas2015}, local navigation is responsible for guiding the vehicle, that is, for the planning of the direction and speed to be taken, in a space close to the current position based on information exclusively obtained by the sensors on board.
+The guiding must be planned in such a way as to guarantee the displacement, from the current state to the objective, without collisions.
+
+The algorithms we have developed at the LAR, follow a new and different approach for an advanced control strategy for autonomous navigation.
+The idea is that these methods do not replace the algorithms developed previously but are a valid alternative, so that depending on the situation, the vehicle can choose the best strategy to overcome obstacles or solve problems that can occur on the road that need a decision in real time.
+Simulation results demonstrate and verify the feasibility and the usefulness of methods considering different scenarios.
+
+In this introductory chapter, the ATLAS project is presented in more detail in section \ref{sec:ATLAS}, while examples of autonomous navigation projects are discussed later (section \ref{sec:autonomous_examples}).
+The context of the problem and the proposed solution of this thesis are carried out in section \ref{sec:context} while the organization of the document is discussed in section \ref{sec:outline}.
 \section{ATLAS Project}\label{sec:ATLAS}
@@
 
-\section{Autonomous Cars}
+\section{Autonomous Cars}\label{sec:autonomous_examples}
+The legal definition of autonomous vehicle in the District of Columbia code is:
+\begin{quotation}
+	\itshape ''Autonomous vehicle'' means a vehicle capable of navigating District roadways and interpreting traffic-control devices without a driver actively operating any of the vehicle's control systems.
+The term ''autonomous vehicle'' excludes a motor vehicle enabled with active safety systems or driver-assistance systems, including systems to provide electronic blind-spot assistance, crash avoidance, emergency braking, parking assistance, adaptive cruise control (ACC), lane-keep assistance (LKA), lane-departure warning, or traffic-jam and queuing assistance, unless the system alone or in combination with other systems enables the vehicle on which the technology is installed to drive without active control or monitoring by a human operator.
+\end{quotation}
+
 The modern automobile companies keep coming up with newer autonomous features in their recent models.
@@
 Based on all this information, Waymo's software determines the exact trajectory, speed, lane and steering maneuvers needed to progress along this route safely \cite{waymoh} \cite{waymot}.
+
 With the advances in autonomous technology, VIAC or VisLab Intercontinental Autonomous Challenge was one of the major competitions which led to improvements in the testing and analysis of autonomous vehicles and robotics.
@@
 It involved four autonomous vehicles with negligible human intervention and high level of autonomy \cite{Broggi2010}.
+One of VisLab's advanced autonomous car, BRAiVE (Figure \ref{fig:veiculos4}), drove in downtown Parma on July 12th, 2013.
+It successfully navigated narrow rural roads, crosswalks, traffic lights, pedestrian areas, roundabouts and artificial hazards.
+It was a pioneer in the field of vehicular robotics, since it was totally autonomous \cite{Broggi2013}.
 \begin{figure}[!h]
@@
 \end{figure}
-\section{Context of the Problem and Motivation}
-\section{Proposed Approach}
-\section{Thesis Outline and Contributions}
+
+Another example of autonomous system is Navya, a robotically driven electric shuttle which operates at a maximum speed of 25 kilometers per hour.
+Made by Induct Technology, France, it can accommodate 15 passengers.
+It uses four LIDAR units and stereoscopic optical cameras, and it does not
+require any road modifications. Its LIDAR unit and
+optical cameras help in generating a real-time three dimensional map of the surroundings.
+It is being successfully tested at various universities across Switzerland, England and Singapore \cite{Zhang2014}.
+
+\begin{figure}[!h]
+	\centering
+	\includegraphics[width=0.6\textwidth]{../figure/veiculos5.png}
+	\caption{Navya Shuttle developted in 2016 by Navya Group in France.}
+	\label{fig:veiculos5}
+\end{figure}
+
+\section{Context of the Problem and Proposed Approach}\label{sec:context}
+Dynamic environments pose several added difficulties to the motion planning problem.
+The dynamics of the ATLASCAR2 must be taken into account, and there are limitations due to the sensors range and uncertainty in measurements, that must be reflected on the motion plan.
+Besides it, a motion plan must incorporate time restrictions, meaning the vehicle will require a certain amount of time to accomplish a task.
+For example, when crossing a road, the ATLASCAR2 must do it fast enough to avoid incoming cars.
+The proposed algorithms were studied for the ATLASCAR2 project in which the group for Robotics and Automation at the University of Aveiro has setup and adapted a common commercial electric vehicle to provide a versatile  framework  to  develop  studies  and  research \cite{vsantos2010} \cite{vsantos2019}.
+The fact that the vehicle is electric allows to use the energy stored in the batteries, making it easier to power the sensors installed.
+In fact, the ATLACAR2 is equipped with sensors, such as lidar, that measure the distance to obstacles in front and around the vehicle.
+The obstacles can be static, such as a large pothole, or moving, such as a moving vehicle on the same or a nearby lane.
+The most common maneuver from the driver is to temporarily move to another lane, drive past the obstacle, and move back to the original lane afterward.
+In this case, we want to design an obstacle avoidance system that moves the ATLASCAR2 around a moving obstacle in the lane using throttle and steering angle.
+This system uses an adaptive Model Predictive Controller that updates both the predictive model and the mixed input/output constraints at each control interval.
+Moreover we want to develop a lane-keeping assist system for the vehicle: it has a sensor, such as camera or laser, that measures the lateral deviation and relative yaw angle between the centerline of a lane and the ATLASCAR2; it also measures the current lane curvature and its derivative.
+Depending on the curve length that the sensor can view, the curvature in front of the vehicle can be calculated from the current curvature and its derivative.
+This system keeps the autonomous car travelling along the centerline of the lanes on the road by adjusting the front steering angle.
+The goal for lane keeping control is to drive both lateral deviation and relative yaw angle close to zero.
+
+\section{Thesis Outline}\label{sec:outline}
+
+In this section, we outline the thesis organization:
+
+Chapter 1 is used to introduce the thesis focus areas of autonomous vehicle technology.
+In particular the ATLAS project and examples of autonomous navigation projects are presented.
+Moreover the context of the problem and the objectives to be achieved are carried out.
+
+Chapter 2

### 2019-03-09 Thesis_Latex/Thesis/Chapter3/Chapter3.tex
update thesis

@@
 Finally, the set $\mathbb{X}_f\subseteq\mathbb{X}$ defines the terminal constraint on the state.
-If we consider a regulation problem, the system \ref{eqn:MPC_plant_discrete} should be steered to the origin and the cost function $J(\vec{x}(k), \textbf{u})$ could be in a quadratic form as follows:
+If we consider a regulation problem, the system (\ref{eqn:MPC_plant_discrete}) should be steered to the origin and the cost function $J(\vec{x}(k), \textbf{u})$ could be in a quadratic form as follows:
 \begin{equation}
@@
 	\end{algorithmic}
-	\label{alg:rightOvertaking}
+	\label{alg:MPCloop}
 \end{algorithm}

### 2019-03-09 Thesis_Latex/Thesis/Chapter4/Chapter4.tex
update thesis

@@
 \section{Problem Formulation}
+The collision avoidance problem is very dependent on the vehicle modeling since it is a requirement for  adaptive MPC law design.
+Figure \ref{fig:obstacleAvoidance} illustrates a typical scenario of overtaking of a moving obstacle.
 % COLLISION AVOIDANCE FIGURE
@@
 \end{figure}
+
+The model used in this report should take into account the kinematic and dynamic aspects of the vehicle.
+Here, we present a non linear mathematical model of a vehicle used for the development of a collision avoidance system.
+The model has four states and two inputs:
+\begin{equation*} 
+\vec{x}=\begin{bmatrix}
+x&y&\theta&v 
+\end{bmatrix}^\intercal
+,\qquad 
+\vec{u}=\begin{bmatrix}
+T&\delta 
+\end{bmatrix}^\intercal
+\end{equation*}
+where $(x,y)$ are the global coordinates of the contact point between the rear wheel and the ground, $\theta$ is the heading angle of the car body with respect to the $x$-axis and $v$ is the linear speed of the car (positive).
+The manipulated variables are $T$ the throttle (positive when accelerating/negative when braking) and $\delta$ the steering angle of the front wheel with respect to the vehicle ($0$ when aligned with car, counterclockwise positive).
+Figure \ref{fig:car_model} illustrates the applied nonlinear bicycle model and the related parameters.
 % BICYCLE MODEL
@@
 \end{figure}
-\section{Design of Adaptive MPC}
+
+The ATLASCAR2 can be modeled using the non-linear kinematic bicycle model described by the following equations of motion \cite{safety} \cite{swarms}:
+\begin{equation*}
+\label{eqn:dynamics_model_obstacle_avoidance}
+\left \{ \begin{array}{llll}
+\dot{x} = v\cos(\theta)\\
+\dot{y} = v\sin(\theta)\\
+\dot{\theta} =\dfrac{v}{C_L}\tan(\delta)\\
+\dot{v} =0.5 \cdot T
+\end{array} 
+\right .
+\Longrightarrow 
+\begin{array}{llll}
+\dot{\vec{x}} = \vec{f}(\vec{x},\vec{u})\\
+\vec{y} = \vec{g}(\vec{x},\vec{u})
+\end{array}
+\end{equation*}
+where $C_L$ is the car length.
+In order to simplify the model, it is assumed that only the front wheel can be steered.
+Moreover, in this paper it is assumed that the ATLASCAR2 does not slip, so any slippage is thus considered as an external disturbance.
+Under this assumption, the slip angle is zero, meaning that the velocity is directed along the heading of the vehicle.
+In order to use MPC, the state space model needs to be linearized with a first order approximation and also re-written in a more compact form:
+\begin{equation}
+\label{eqn:dynamics_model_non_linear}
+\begin{array}{llll}
+\dot{\vec{x}} = \vec{f}(\vec{x},\vec{u})\\
+\vec{y} = \vec{g}(\vec{x},\vec{u})
+\end{array} \Longrightarrow
+\begin{array}{ll}
+\dot{\vec{x}} =\vec{A}_c \vec{x}+ \vec{B}_c \vec{u}\\
+\vec{y} =\vec{C}_c \vec{x} + \vec{D}_c \vec{u}
+\end{array}
+\end{equation}
+where the matrices $\vec{A}_c$, $\vec{B}_c$, $\vec{C}_c$ and $\vec{D}_c$ are obtained as follows:
+\[ 
+\vec{A}_c=\frac{\partial \vec{f}(\vec{x},\vec{u})}{\partial \vec{x}}=\begin{bmatrix}
+0&0&-v\sin(\theta)&\cos(\theta)\\
+0&0&v\cos(\theta)&\sin(\theta)\\
+0&0&0&\tan(\delta)/C_L\\
+0&0&0&0
+\end{bmatrix},
+\]
+\[
+\vec{B}_c=\frac{\partial \vec{f}(\vec{x},\vec{u})}{\partial \vec{u}}=\begin{bmatrix}
+0&0\\
+0&0\\
+0&\dfrac{v}{C_L}\big(\tan(\delta)^2+1\big)\\
+0.5&0
+\end{bmatrix},
+\]
+\[
+\vec{C}_c=\frac{\partial \vec{g}(\vec{x},\vec{u})}{\partial \vec{u}} = \mathbf{I}_4, 
+\qquad
+\vec{D}_c=\frac{\partial \vec{g}(\vec{x},\vec{u})}{\partial \vec{u}}=\mathbf{0}_{4\times2}. 
+\]
+The simple linearized approximation of the system to describe the dynamics of the ATLASCAR2 will be evaluated at the operating conditions.
+Note also that the system we are considering is a linear state-space model whose dynamics vary as a function of certain time-varying parameters.
+The system to be controlled is usually modeled by a discrete state-space model in the MPC literature.
+Therefore, (\ref{eqn:dynamics_model_non_linear})
+is transformed into a discrete state-space model to be used by the Model Predictive Controller:
+\begin{equation*}
+\label{eqn:dynamics_ss_obstacle_avoidance_dis}
+\begin{array}{ll}
+\dot{\vec{x}} =\vec{A}_c \vec{x}+ \vec{B}_c \vec{u}\\
+\vec{y} =\vec{C}_c \vec{x} + \vec{D}_c \vec{u}
+\end{array}
+\Rightarrow
+\begin{array}{rr}
+{\vec{x}}(k+1) =\vec{A}_d \vec{x}(k)+ \vec{B}_d \vec{u}(k)\\
+\vec{y}(k) =\vec{C}_d \vec{x}(k) + \vec{D}_d \vec{u}(k)
+\end{array}
+\end{equation*}
+
+where $\vec{A}_d$ and $\vec{B}_d$ are the state and control matrices for the discrete state-space equation, respectively, which can be calculated with the Euler method as
+\begin{equation*}
+\vec{A}_d = e^{\vec{A}_cT_s},\qquad \vec{B}_d = \int_{kT_s}^{(k+1)T_s} e^{\vec{A}_c[(k+1)T_s-\eta]}\vec{B}_c d\eta
+\end{equation*}
+
+where $T_s$ is the sampling interval for the discrete state-space model.
+The matrices $\vec{C}_d$ and $\vec{D}_d$ are equivalent to those in the continuous case.
+For simplicity, we assume that all the states are measurable and the ATLASCAR2 drives east with a constant speed at the nominal operating point.
+In the scenario that we are going to consider, the road is straight and our vehicle stays in the middle of the center lane when not passing.
+Without losing generality, the ATLASCAR2 passes an obstacle both to the right and to the left lane depending on where it is placed on the road.
+We create also a safe zone around the obstacles so that the vehicle does not get too close to the obstacle when passing it.
+
+\section{Design of Adaptive Model Predictive Control}
+We designed a Model Predictive Controller that can make the ATLASCAR2 maintain a desired velocity and stay in the middle of center lane.
+We used an Adaptive MPC controller because it handles the nonlinear vehicle dynamics more effectively than a traditional MPC controller; in fact, the latter uses a constant plant model but the former allows us to provide a new plant model at each control interval.
+Because the new model describes the plant dynamics more accurately at the new operating condition, an adaptive MPC controller performs better than a traditional MPC controller.
+In practice, at each control interval, the adaptive MPC controller updates the plant model and the nominal conditions.
+Once updated, the model and the conditions remain constant over the prediction horizon.
+In motion planning that uses adaptive MPC, it is common to formulate the constrained control problem as a real-time optimization problem subject to hard constraints on plant variables and soft constraints on outputs; at the beginning, we specified the constraints for the manipulated variables: to prevent the ATLASCAR2 from accelerating or decelerating too quickly, we added an hard constraint on the throttle rate of change and another one on the steering angle rate of change.
+We used an approach that takes advantage of the ability of MPC to handle constraint explicitly.
+Figure \ref{fig:flowchart} shows a conditional state machine designed for higher-level behavior planning.
+
 % FLOWCHART
@@
 \end{figure}
+
+When an obstacle is detected, it defines an area on the road (in terms of constraints) that the ATLASCAR2 must not enter during the prediction horizon.
+At the next control interval the area is redefined based on the new positions of the vehicle and the obstacle until passing is completed.
+To define the area to avoid, we used the following mixed Input/Output constraints:
+\begin{equation*}
+\label{eqn:mixed_IO_constraints}
+\vec{E}\vec{u}+\vec{F}\vec{y}\leq \vec{G}
+\end{equation*}
+where $\vec{u}$ and $\vec{y}$ are respectively the manipulated variable vector and the output variable vector, while $\vec{E},\vec{F},\vec{G}$ are the constraint matrices that can be updated when the controller is running.
+Five constraints were defined:
+\begin{enumerate}
+	\item upper bound on the $y$-coordinate (left boundary of the road);
+	\item lower bound on the $y$-coordinate (right boundary of the road);
+	\item constraint for obstacle avoidance; although no obstacle is considered in the nominal condition, we must add this virtual constraint here because we cannot change the dimensions of the constraint matrices at run time;
+	\item upper bound on the $x$-coordinate (position of the closest obstacle);
+	\item lower bound on the $x$-coordinate (position of the ATLASCAR2).
+\end{enumerate}
+The matrices for the above inequality are the following:
+\[
+\vec{E}= 
+\begin{bmatrix}
+0&0\\
+0&0\\
+0&0\\
+0&0\\
+0&0
+\end{bmatrix},
+\;
+\vec{F}=\begin{bmatrix}
+0&1&0&0\\
+0&-1&0&0\\
+cS&-1&0&0\\
+1&0&0&0\\
+-1&0&0&0\\
+\end{bmatrix},\;
+\vec{G}=
+\begin{bmatrix}
+W/2\\W/2\\-cI\\x_{\max}\\x_{\min}
+\end{bmatrix}
+\]
+where $W$ is the width of the road, $cI$ and $cS$ are the required parameters such that the ATLASCAR2 must be above the line formed from the vehicle to safe zone corner for left/right passing and finally $x_{\max}$ represents the position of the closest obstacle in the case there is not free space for the overtaking (otherwise $x_{\max}=+\infty$) while $x_{\min}$ depicts the location of our vehicle.
+Figure \ref{fig:constraint} illustrates the constraints that are computed at each $T_s$ in the case of a left overtaking.
 % FIGURE CONSTRAINT
@@
 \section{Simulation Results}
+The performances of the proposed adaptive MPC based vehicle control method are demonstrated in three simulation examples.
+We tried to choose parameters that were as close as possible to a real situation: the sampling time used in the discretization of the system is $T_s=\SI{0.02}{s}$ while the values of the prediction and the control horizon are respectively $p_H=25$ and $c_H=5$.
+In all simulations, the distance between the front and rear axles is $C_L=\SI{5}{m}$ and the width of the vehicle is $C_W=\SI{2}{m}$.
+The saturation ranges of the control inputs are: the steering angle lies in $\big[-\frac{\pi}{30}, +\frac{\pi}{30}\big]$ rad/s while in order to prevent the ATLASCAR2 from accelerating or decelerating too quickly, we impose an hard constraint of \SI{2.5}{m/s^2} on the throttle rate of change.
+Moreover we are using a constant reference signal for the velocity of $v=\SI{20}{m/s}$ ($\approx\SI{72}{km/h}$).
+Blue paths in Figures \ref{fig:obstacleAvoidance_one_obstacle}, \ref{fig:obstacleAvoidance_random}, \ref{fig:braking} are known only at the end of the simulations.
+
+\subsection{One Moving Obstacle - Right Overtaking}
+In this first simulation
+(Fig.
+\ref{fig:obstacleAvoidance_one_obstacle}) the ATLASCAR2 drives in the middle of the center lane while the road is completely free and when there is an obstacle, the vehicle passes it only using the right lane (the same simulation can be launched so that the car goes over to the left fast lane).
+In other words if the ATLASCAR2 is already in the adjacent lane, it uses the safety zone as the constraint, otherwise the vehicle must be above the line formed from the ATLASCAR2 to safe zone corner for right passing.
+If the vehicle is parallel to the obstacle, it  uses the safety zone as the constraint and finally if it has passed the obstacle, it uses the inactive constraint to go back to the center lane.
+Algorithm \ref{alg:rightOvertaking} summarizes the main steps to compute custom constraints for the obstacle; when the vehicle detects the obstacle, the constraints are computed.
+In this simulation only the first three constraints are necessary because there is space for the overtaking without braking (the fourth and fifth constraints don't change).
+
 % ONE MOVING OBSTACLE
@@
 \end{figure}
+
 % ALGORITHM FOR RIGHT OVERTAKING OF ONE MOVING OBSTACLE
@@
 \end{algorithm}
+
 % OVERALL SCHEME ONE MOVING OBSTACLE
@@
 \end{figure}
+%
+\subsection{Multiple Moving Obstacles}
+For a second test, additional obstacles were added to make the scenario more complex (Fig. \ref{fig:obstacleAvoidance_random}).
 % MULTIPLE MOVING OBSTACLE
@@
 \end{figure}
+
+The vehicle is capable of overtaking the obstacles on the right or left depending on their positions with respect to the road.
+If the $y$-coordinate of the closest obstacle is greater than 0, then the vehicle overtakes to the right, otherwise the overtaking takes place on the left lane.
+We also hypothesized that the obstacles move at different speeds but that they are initially at a common distance; they can have a uniform motion or a uniformely accelerated motion.
+In case two obstacles are too close during the simulation and their distance is less than the detection range, which is \SI{30}{m}, the ATLASCAR2 perceives the objects as a single entity and adapts to the situation.
+The same test can be done with the obstacles that drive in the same direction as the vehicle but to better assess and demonstrate results we decided to show a very unusual scenario.
+
+\subsection{Vehicle Braking and Obstacles Overtaking}
+Finally we have improved the code related to the mixed Input/Output constraints so that in the case there are 3 obstacles that block the road and drive at a lower speed than the ATLASCAR2, the velocity of the vehicle decreases in order to prevent the collision.
+Figure \ref{fig:braking} depicts a simulation in which there are 3 obstacles at the same $x$-coordinate.
+Two obstacles have a constant speed of \SI{8}{m/s} while the one on the left lane of \SI{15}{m/s}.
+In this particular case it is essential to consider the fourth and the fifth restriction in order to allow the ATLASCAR2 to slow down without colliding with the cars in front.
+The fifth constraint is simply the position of the ATLASCAR2 that updates at each interval, while the fourth constraint, until there is a free lane, is the position of the closest obstacle (both the positions are with respect to the global reference frame).
+In the calculation of the fourth constraint is necessary  to consider the speed at which the vehicle and the obstacle are moving in order to keep a safe distance.
+In particular three parameters have been identified as the key
+factors computing the safe distance between cars:
+\begin{itemize}
+	\item detection range of the ATLASCAR2;
+	\item velocities of the vehicle and the obstacle;
+	\item distance between the cars.
+\end{itemize}
 
@@
 \end{figure}
+
+At the beginning, the vehicle moves with the reference velocity of $v=\SI{20}{m/s}$.
+When the ATLASCAR2 detects all the other cars on the road, checks if there is a free lane.
+In the first part of the simulation, the ATLASCAR2 brakes because there is not enough space for overtaking the cars as shown in Fig.
+\ref{fig:velocity_braking}.
+A collision would happen if the vehicle continues to follow the initially planned path with the reference velocity.
+It is possible to notice that the speed decreases because the applied throttle is negative, so a consistent deceleration is set after $\approx\SI{1.5}{s}$ as depicted in Fig.
+\ref{fig:throttle_braking}.
+The velocity of the ATLASCAR2 for $\approx\SI{2}{s}$ adapts to that of the closest obstacle.
+After a few seconds the fastest car moves and makes available the left lane for overtaking.
+Dramatic changes of steering angle in early stage are observed in Fig.
+\ref{fig:delta_braking} and consequently also on the heading angle in Fig.
+\ref{fig:theta_braking}.
+Then, the ATLASCAR2 returns to the reference velocity during the overtaking of the two obstacles (the applied throttle after $\approx\SI{5}{s}$ is positive).
+It is seen that the ATLASCAR2 avoids the obstacles and returns to the road center line with a low overshoot.
+
 % RESULTS BRAKING THREE OBSTACLES
@@
 		\includegraphics[width=\textwidth]{./figure/three_obstacles_no_overtaking/VelocityVsTime.pdf}
-		\vspace{-17pt}
 		\subcaption{}\label{fig:velocity_braking}
@@
 		\includegraphics[width=\textwidth]{./figure/three_obstacles_no_overtaking/ThrottleVsTime.pdf}
-		\vspace{-17pt}
 		\subcaption{}\label{fig:throttle_braking}
@@
 		\includegraphics[width=\textwidth]{./figure/three_obstacles_no_overtaking/SteeringAngleVsTime.pdf}
-		\vspace{-17pt}
 		\subcaption{}\label{fig:delta_braking}
@@
 		\includegraphics[width=\textwidth]{./figure/three_obstacles_no_overtaking/HeadingAngleVsTime.pdf}
-		\vspace{-17pt}
 		\subcaption{}\label{fig:theta_braking}

### 2019-03-09 Thesis_Latex/Thesis/Chapter5/Chapter5.tex
update thesis

@@
 \chapter{Lane Following}
-\section{Problem Formulation}
+\section{Lane Following System}
+\subsection{Problem Formulation}
+A lane-following system is a control system that keeps the vehicle traveling along the centerline of a highway lane, while maintaining a user-set velocity.
+Figure \ref{fig:laneFollowing} illustrates a typical lane following scenario.
 \begin{figure}[!h]
@@
 \end{figure}
-\section{Design of Adaptive MPC}
-\section{Simulation Results}
+In a classic lane keeping assist, it is assumed that the longitudinal velocity is constant \cite{borelli3}.
+This restriction is relaxed in this model because the longitudinal acceleration varies in this MIMO control system.
+This lane-following system manipulates both the longitudinal acceleration and the front steering angle of the vehicle to keep the lateral deviation and the relative yaw angle small and the longitudinal velocity close to a driver set velocity.
+If these two goals cannot be met at the same moment, the system tries to balance them.
+The model that we are considering contains many parameters.
+The first fundamental block describes the vehicle dynamics: we have applied the bicycle model of lateral vehicle dynamics and approximate the longitudinal dynamics using a time constant obtaining  a linear model.
+\subsubsection{Longitudinal dynamics}
+We can use the following state space to describe the longitudinal model:
+\begin{equation}
+\label{eqn:longi_dynamics_simple_model_ss}
+\begin{array}{ll}
+\dot{\vec{x}}_{\text{lon}} =\vec{A}_m \vec{x}_{\text{lon}}+ \vec{B_m}\vec{u}_{\text{lon}}\\
+\vec{y}_{\text{lon}} =\vec{C_m} \vec{x}_{\text{lon}} + \vec{D_m} \vec{u}_{\text{lon}}
+\end{array}
+\end{equation}
+where the input is the acceleration and the states are the longitudinal velocity and the actual acceleration which is also the only output of this system.
+\begin{equation}
+\vec{x}_{\text{lon}} = \begin{bmatrix}
+\dot{V}_x\\V_x
+\end{bmatrix},
+\qquad
+\vec{u}_{\text{lon}} = a
+\end{equation}
+and
+\begin{equation}
+\begin{array}{cc}
+\vec{A_m}=\begin{bmatrix}
+-\frac{1}{\tau}&0\\1&0
+\end{bmatrix},
+\qquad
+\vec{B_m}=\begin{bmatrix}
+\frac{1}{\tau}\\
+0
+\end{bmatrix},\\\\
+\vec{C_m}=\begin{bmatrix}
+1&0
+\end{bmatrix}, 
+\qquad
+\vec{D_m}=0.
+\end{array}
+\end{equation}
+where $\tau$ is a time constant \cite{long_tf}; in practice we are considering a second order transfer function like in \cite{longitudinal}.
+\subsubsection{Lateral dynamics}
+Local function: we have a continuous vehicle lateral model from parameters obtained by simplifying the one in \cite{rathai}: 
+\begin{equation}
+\label{eqn:lateral_dynamics_simple_model}
+\begin{array}{ll}
+\dot{\vec{x}}_{\text{lat}} =\vec{A}_g \vec{x}_{\text{lat}}+ \vec{B}_g \vec{u}_{\text{lat}}\\
+\vec{y}_{\text{lat}} =\vec{C}_g \vec{x}_{\text{lat}} + \vec{D}_g \vec{u}_{\text{lat}}
+\end{array}
+\end{equation}
+where the input is the steering angle in radians, and the outputs are the lateral velocity in meters per second and yaw angle rate in radians per second:
+\begin{equation}
+\vec{x}_{\text{lat}} = \begin{bmatrix}
+V_y\\\dot{\psi}
+\end{bmatrix}
+\qquad
+\vec{u}_{\text{lat}} = \delta
+\end{equation}
+and
+\begin{equation}
+\begin{array}{cc}
+\vec{A}_g=
+\begin{bmatrix}
+\displaystyle -\frac{2C_F+2C_R}{mV_x}&\displaystyle -\frac{2C_Fl_F-2C_Rl_R}{mV_x} - V_x\\
+\displaystyle -\frac{2C_Fl_F-2C_Rl_R}{I_ZV_x}&\displaystyle -\frac{2C_Fl_F^2+2C_Rl_R^2}{I_ZV_x}
+\end{bmatrix},
+\\\\
+\vec{B}_g=\begin{bmatrix}
+2C_F/m\\2C_Fl_F/I_Z
+\end{bmatrix},
+\qquad
+\vec{C}_g=\begin{bmatrix}
+1&0\\0&1
+\end{bmatrix}=
+\vec{I}_2, 
+\qquad
+\vec{D}_g=\begin{bmatrix}
+0\\0
+\end{bmatrix}=
+\vec{0}_{2\times1}.
+\end{array}
+\end{equation}
+The parameters in the previous matrices are:
+\begin{itemize}
+	\item $V_x$ is the longitudinal velocity of the car;	
+	\item $m$ is the total mass parameter; 
+	\item $I_Z$ is the yaw moment of inertia parameter;
+	\item $l_F$ and $l_R$ are the longitudinal distances from center of gravity to front and rear tires parameters;
+	\item $C_F$ and $C_R$ are the cornering stiffnesses of front and rear tires parameters.
+\end{itemize}
+The goal for the driver steering model is to keep the vehicle in its lane and follow the curved road by controlling the front steering angle .
+This goal is achieved by driving the yaw angle error $e_2 = \psi -\psi_{\text{des}}$ and lateral displacement error $e_1$ to zero ($\dot{e}_1 = V_xe_2+V_y$).
+We can incorporate these two paramenters in the augmented model:
+\begin{equation}
+\label{eqn:lateral_dynamics_augmented_model}
+\begin{array}{ll}
+\dot{\vec{x}}_{\text{aug}} =\vec{A}_a \vec{x}_{\text{aug}}+ \vec{B}_a \vec{u}_{\text{aug}}\\
+\vec{y}_{\text{aug}} = \vec{C}_a \vec{x}_{\text{aug}} + \vec{D}_a \vec{u}_{\text{aug}}
+\end{array}
+\end{equation}
+where
+\begin{equation}
+\vec{x}_{\text{aug}} = \begin{bmatrix}
+V_y\\\dot{\psi}\\e_1\\e_2
+\end{bmatrix},
+\qquad
+\vec{u}_{\text{aug}} = 
+\begin{bmatrix}
+\delta\\\dot{\psi}_{\text{des}}
+\end{bmatrix}
+\end{equation}
+and
+\begin{equation}
+\begin{array}{cc} 
+\vec{A}_a=\begin{bmatrix}
+\vec{A}_g&\vec{0}_{2\times2}\\
+\vec{I}_2&\begin{matrix}
+0&V_x\\
+0&0
+\end{matrix}
+\end{bmatrix},
+\qquad
+\vec{B}_a=\begin{bmatrix}
+\vec{B}_g&\vec{0}_{2\times1}\\
+0&0\\
+0&-1
+\end{bmatrix},
+\\\\
+\vec{C}_a=\begin{bmatrix}
+\vec{0}_{2\times2}&\vec{I}_2
+\end{bmatrix}, 
+\qquad
+\vec{D}_a=
+\vec{0}_{2\times2}. 
+\end{array}
+\end{equation}
+
+Combining (\ref{eqn:longi_dynamics_simple_model_ss}) with (\ref{eqn:lateral_dynamics_augmented_model}) yields the state-space model that characterizes the Model Predictive Controller:
+\begin{equation}
+\label{eqn:full_dynamics_model}
+\begin{array}{ll}
+\dot{\vec{x}}_{\text{tot}} = \vec{A}_f \vec{x}_{\text{tot}}+ \vec{B}_f \vec{u}_{\text{tot}}\\
+\vec{y}_{\text{tot}} = \vec{C}_f \vec{x}_{\text{tot}} + \vec{D}_f \vec{u}_{\text{tot}}
+\end{array}
+\end{equation}
+where
+\begin{equation}
+\vec{x}_{\text{tot}} = \begin{bmatrix}
+\vec{x}_{\text{lon}}\\\vec{x}_{\text{aug}}
+\end{bmatrix} = \begin{bmatrix}
+\dot{V}_x\\V_x\\V_y\\\dot{\psi}\\e_1\\e_2
+\end{bmatrix},
+\qquad
+\vec{u}_{\text{tot}} = \begin{bmatrix}
+\vec{u}_{\text{lon}}\\\vec{u}_{\text{aug}}
+\end{bmatrix}  =
+\begin{bmatrix}
+a\\\delta\\\dot{\psi}_{\text{des}}
+\end{bmatrix}
+\end{equation}
+and
+\begin{equation}
+\begin{array}{cc}
+\vec{A}_f=\begin{bmatrix}
+\vec{A}_m&\vec{0}_{2\times4}\\
+\vec{0}_{4\times2}&\vec{A}_a
+\end{bmatrix},
+\qquad
+\vec{B}_f=\begin{bmatrix}
+\vec{B}_m&\vec{0}_{2\times2}\\
+\vec{0}_{4\times1}&\vec{B}_a
+\end{bmatrix},
+\\\\
+\vec{C}_f=\begin{bmatrix}
+\vec{C}_m&\vec{0}_{1\times4}\\
+\vec{0}_{2\times2}&\vec{C}_a
+\end{bmatrix}, 
+\qquad
+\vec{D}_f=\vec{0}_{3\times3}. 
+\end{array}
+\end{equation}
+
+However the system to be controlled is usually modeled by a linear discrete state-space model:
+\begin{equation}
+\label{eqn:full_dynamics_model_disc}
+\begin{array}{rr}
+{\vec{x}}_{\text{tot}}(k+1) =\vec{A} \vec{x}_{\text{tot}}(k)+ \vec{B} \vec{u}_{\text{tot}}(k)\\
+\vec{y}_{\text{tot}}(k) = \vec{C}\vec{x}_{\text{tot}}(k) + \vec{D} \vec{u}_{\text{tot}}(k)
+\end{array}
+\end{equation}
+where $\vec{A}$ and $\vec{B}$ are the state and control matrices for the discrete state-space equation, respectively, which can be calculated, also in this case, with the Euler method as:
+\[
+\vec{A} = e^{\vec{A}_fT_s},\qquad \vec{B} = \int_{kT_s}^{(k+1)T_s} e^{\vec{A}_f[(k+1)T_s-\eta]}\vec{B}_f d\eta
+\]
+where $T_s$ is the sampling interval for the discrete state-space model. The matrices $\vec{C}$ and $\vec{D}$ are equivalent to those in the continuous case.
+
+\subsection{Design of Adaptive Model Predictive Control}
+We created an Adaptive MPC controller with a prediction model that has six states, three outputs (longitudinal velocity, lateral deviation, relative yaw angle), and two manipulated signals (acceleration and steering).
+The objective of the trajectory planning along specified path can be described as follows: given a path which the vehicle is expected to follow design a trajectory of a car-vehicle configuration.
+In order to do this, according with \cite{curvature} it is possible to derive the road curvature and its derivative.
+The product of the road curvature and the longitudinal velocity is modeled as a measured disturbance.
+We have set the constraints for manipulated variables and the scale factors.
+Moreover we have specified the weights in the standard MPC cost function.
+The third output, yaw angle, is allowed to float because there are only two manipulated variables to make it a square system.
+In this controller, there is no steady-state error in the yaw angle as long as the second output, lateral deviation, reaches 0 at steady state.
+Finally we have also penalized acceleration change more for smooth driving experience.
+This controller uses a linear model for the vehicle dynamics and updates the model online as the longitudinal velocity varies.
+
+\subsection{Simulation Results}
+The proposed adaptive MPC algorithm is designed in the MATLAB/Simulink and validated through simulation.
+The objective of this test is to evaluate the behavior of the proposed control strategy in critical situations.
+Table 3 shows the parameters used in the lane following simulation.
 \begin{table}[!h]
@@
 
+Figures \ref{fig:reference_laneFollowing} and \ref{fig:curvature_laneFollowing} show the desired path that the car must follow and its curvature, where the former is described in terms of the lateral position $Y_{\text{ref}}$ as function of the longitudinal position $X_{\text{ref}}$ and the latter is derived according with \cite{curvature}.
+The ATLASCAR2 is controlled to follow a sinusoidal trajectory which is given as follows:
+\begin{equation*}
+X_\text{ref}=V_x\cdot t, \quad Y_\text{ref}=5\sin(X_\text{ref}/20)\quad \text{with}\quad t\in[0,20]\SI{}{s}
+\end{equation*}
 \begin{figure}[!t]
@@
 		\includegraphics[width=\textwidth]{../../MATLAB/lane_following/figure/Reference.pdf}
-		\vspace{-17pt}
 		\subcaption{}
@@
 		\includegraphics[width=\textwidth]{../../MATLAB/lane_following/figure/Curvature.pdf}
-		\vspace{-17pt}
 		\subcaption{}
@@
 	\label{fig:laneFollowing_desired}
-	\vspace{-30pt}
 \end{figure}
 
-\begin{figure}[!t]
+Moreover the following figures show the trend of the main parameters confirming that the control strategy used allows the vehicle to follow the path.
+In particular we simulated also a small error in the sensor dynamics in order to make the simulation more realistic: we added a 3 percent error to the longitudinal velocity and this is evident from the small noise in the graphs of the steering angle (Fig.\ref{fig:steering_laneFollowing}) and the lateral deviation (Fig.\ref{fig:lateral_deviation_laneFollowing}).
+Figure {\ref{fig:longitudinal_velocity_laneFollowing}} shows the evolution of the vehicle longitudinal velocity.
+At the start of the simulation, this velocity is equal to the initial condition for longitudinal velocity parameter $V_0$.
+At run time, we can note that $V_x$ reaches the predefined value of \SI{20}{m/s} meters for second and then it stabilizes near the cruising speed because it continues to vary the steering angle to adapt to the path to be followed.
+Finally we presents the overall scheme for the lane following developted in Simulink depicted in Figure \ref{fig:scheme_lane_following}.
+\begin{figure}[!h]
 	\centering
@@
 	\centering
-	\includegraphics[width=1\textwidth]{../figure/lane_following_AMPC.pdf}
+	\includegraphics[width=\textwidth]{../figure/lane_following_AMPC.pdf}
 	\caption{Overall procedure scheme lane following.}
@@
 \end{figure}
+
+%%%CIAOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOO

### 2019-03-09 Thesis_Latex/Thesis/Conclusions/Conclusions.tex
update thesis

@@
 \addcontentsline{toc}{chapter}{Conclusions and Future Work}
+This thesis proposes two advanced methods for short term motion planning of an autonomous car based on adaptive Model Predictive Control.
+The first component is an obstacle avoidance system that moves the vehicle around different moving obstacles in the lane using throttle and steering angle.
+This system updates both the predictive model and the mixed input/output constraints at each control interval.
+The vehicle is also able to brake in order to prevent collisions against closest obstacles.
+Instead, in the second scheme  we have developed a lane following system that keeps the ATLASCAR2 traveling along the centerline of the lanes on the road by adjusting the front steering angle of the car.
+The flexibility of the concepts used in the algorithms allows a multitude of refinements and extensions to this work.
+The future work includes the combination of these two control strategies in a way that they can operate simultaneously.
+In order to achieve this objective we have started to simulate a trajectory tracking framework using a slight modification of the linearized tracking error model in \cite{error_model}.
+Next expected steps include the migration to ROS-Gazebo simulation environment and, later on, the usage of real data collected on board the ATLASCAR2 and, ultimately, test it in a real autonomous driving scenario.

### 2019-03-11 Thesis_Latex/Thesis/Chapter4/Chapter4.tex
update thesis

@@
 The model has four states and two inputs:
-\begin{equation*} 
+\begin{equation}
+\begin{array}{cc}
 \vec{x}=\begin{bmatrix}
-x&y&\theta&v 
-\end{bmatrix}^\intercal
-,\qquad 
+x\\y\\\theta\\v 
+\end{bmatrix},\qquad 
 \vec{u}=\begin{bmatrix}
-T&\delta 
-\end{bmatrix}^\intercal
-\end{equation*}
+T\\\delta 
+\end{bmatrix}
+\end{array} 
+\end{equation}
 where $(x,y)$ are the global coordinates of the contact point between the rear wheel and the ground, $\theta$ is the heading angle of the car body with respect to the $x$-axis and $v$ is the linear speed of the car (positive).
@@
 	\includegraphics[width=0.80\textwidth]{../figure/car_model.pdf}
-	\caption{Bicycle model of a car, (adapted from \cite{siciliano}).}
+	\caption{Bicycle model of a car (adapted from \cite{siciliano}).}
 	\label{fig:car_model}
@@
 The ATLASCAR2 can be modeled using the non-linear kinematic bicycle model described by the following equations of motion \cite{safety} \cite{swarms}:
-\begin{equation*}
+\begin{equation}
 \label{eqn:dynamics_model_obstacle_avoidance}
@@
 \end{array}
-\end{equation*}
+\end{equation}
 where $C_L$ is the car length.
@@
 where the matrices $\vec{A}_c$, $\vec{B}_c$, $\vec{C}_c$ and $\vec{D}_c$ are obtained as follows:
-\[ 
-\vec{A}_c=\frac{\partial \vec{f}(\vec{x},\vec{u})}{\partial \vec{x}}=\begin{bmatrix}
+\begin{equation}
+\begin{array}{ccc}
+\vec{A}_c=\displaystyle\frac{\partial \vec{f}(\vec{x},\vec{u})}{\partial \vec{x}}=\begin{bmatrix}
 0&0&-v\sin(\theta)&\cos(\theta)\\
@@
 \end{bmatrix},
-\]
-\[
-\vec{B}_c=\frac{\partial \vec{f}(\vec{x},\vec{u})}{\partial \vec{u}}=\begin{bmatrix}
+\\\\
+\vec{B}_c=\displaystyle\frac{\partial \vec{f}(\vec{x},\vec{u})}{\partial \vec{u}}=\begin{bmatrix}
 0&0\\
@@
 \end{bmatrix},
-\]
-\[
-\vec{C}_c=\frac{\partial \vec{g}(\vec{x},\vec{u})}{\partial \vec{u}} = \mathbf{I}_4, 
+\\\\
+\vec{C}_c=\displaystyle\frac{\partial \vec{g}(\vec{x},\vec{u})}{\partial \vec{u}} = \mathbf{I}_4, 
 \qquad
 \vec{D}_c=\frac{\partial \vec{g}(\vec{x},\vec{u})}{\partial \vec{u}}=\mathbf{0}_{4\times2}.
-\]
+\end{array}
+\end{equation} 
 The simple linearized approximation of the system to describe the dynamics of the ATLASCAR2 will be evaluated at the operating conditions.
@@
 is transformed into a discrete state-space model to be used by the Model Predictive Controller:
-\begin{equation*}
+\begin{equation}
 \label{eqn:dynamics_ss_obstacle_avoidance_dis}
@@
 \end{array}
-\Rightarrow
+\Longrightarrow
 \begin{array}{rr}
@@
 \end{array}
-\end{equation*}
+\end{equation}
 
 where $\vec{A}_d$ and $\vec{B}_d$ are the state and control matrices for the discrete state-space equation, respectively, which can be calculated with the Euler method as
-\begin{equation*}
+\begin{equation}
 \vec{A}_d = e^{\vec{A}_cT_s},\qquad \vec{B}_d = \int_{kT_s}^{(k+1)T_s} e^{\vec{A}_c[(k+1)T_s-\eta]}\vec{B}_c d\eta
-\end{equation*}
+\end{equation}
 
@@
 To define the area to avoid, we used the following mixed Input/Output constraints:
-\begin{equation*}
+\begin{equation}
 \label{eqn:mixed_IO_constraints}
 \vec{E}\vec{u}+\vec{F}\vec{y}\leq \vec{G}
-\end{equation*}
+\end{equation}
 where $\vec{u}$ and $\vec{y}$ are respectively the manipulated variable vector and the output variable vector, while $\vec{E},\vec{F},\vec{G}$ are the constraint matrices that can be updated when the controller is running.
@@
 The matrices for the above inequality are the following:
-\[
+\begin{equation}
 \vec{E}= 
@@
 \end{bmatrix},
-\;
+\qquad
 \vec{F}=\begin{bmatrix}
@@
 -1&0&0&0\\
-\end{bmatrix},\;
+\end{bmatrix},
+\qquad
 \vec{G}=
@@
 \end{bmatrix}
-\]
+\end{equation}
+
 where $W$ is the width of the road, $cI$ and $cS$ are the required parameters such that the ATLASCAR2 must be above the line formed from the vehicle to safe zone corner for left/right passing and finally $x_{\max}$ represents the position of the closest obstacle in the case there is not free space for the overtaking (otherwise $x_{\max}=+\infty$) while $x_{\min}$ depicts the location of our vehicle.
@@
 In this first simulation
-(Fig.
-\ref{fig:obstacleAvoidance_one_obstacle}) the ATLASCAR2 drives in the middle of the center lane while the road is completely free and when there is an obstacle, the vehicle passes it only using the right lane (the same simulation can be launched so that the car goes over to the left fast lane).
+(Figure \ref{fig:obstacleAvoidance_one_obstacle}) the ATLASCAR2 drives in the middle of the center lane while the road is completely free and when there is an obstacle, the vehicle passes it only using the right lane (the same simulation can be launched so that the car goes over to the left fast lane).
 In other words if the ATLASCAR2 is already in the adjacent lane, it uses the safety zone as the constraint, otherwise the vehicle must be above the line formed from the ATLASCAR2 to safe zone corner for right passing.
@@
 \subsection{Multiple Moving Obstacles}
-For a second test, additional obstacles were added to make the scenario more complex (Fig. \ref{fig:obstacleAvoidance_random}).
+For a second test, additional obstacles were added to make the scenario more complex (Figure \ref{fig:obstacleAvoidance_random}).
 % MULTIPLE MOVING OBSTACLE
@@
 	\end{minipage}
-	\caption{Time signals of the ATLASCAR2 in the simulation of braking and overtaking in the situation illustrated in Fig. \ref{fig:braking}.}
+	\caption{Time signals of the ATLASCAR2 in the simulation of braking and overtaking in the situation illustrated in Figure \ref{fig:braking}.}
 	\label{fig:components}

### 2019-03-11 Thesis_Latex/Thesis/Chapter5/Chapter5.tex
update thesis

@@
 \chapter{Lane Following}
-\section{Lane Following System}
-\subsection{Problem Formulation}
+\section{Problem Formulation}
 A lane-following system is a control system that keeps the vehicle traveling along the centerline of a highway lane, while maintaining a user-set velocity.
@@
 \end{figure}
-In a classic lane keeping assist, it is assumed that the longitudinal velocity is constant \cite{borelli3}.
+
+In a classic lane keeping assist, it is assumed that the longitudinal velocity is constant \cite{Adaptive_Mpc_Lane_keeping_borelli}.
 This restriction is relaxed in this model because the longitudinal acceleration varies in this MIMO control system.
@@
 The first fundamental block describes the vehicle dynamics: we have applied the bicycle model of lateral vehicle dynamics and approximate the longitudinal dynamics using a time constant obtaining  a linear model.
-\subsubsection{Longitudinal dynamics}
+\subsection{Longitudinal Dynamics}
 We can use the following state space to describe the longitudinal model:
@@
 where $\tau$ is a time constant \cite{long_tf}; in practice we are considering a second order transfer function like in \cite{longitudinal}.
-\subsubsection{Lateral dynamics}
+\subsection{Lateral Dynamics}
 Local function: we have a continuous vehicle lateral model from parameters obtained by simplifying the one in \cite{rathai}: 
@@
 \end{itemize}
+\subsection{Augmented Model for Lateral Dynamics}
 The goal for the driver steering model is to keep the vehicle in its lane and follow the curved road by controlling the front steering angle .
@@
 
+\subsection{Overall Model Dynamics}
 Combining (\ref{eqn:longi_dynamics_simple_model_ss}) with (\ref{eqn:lateral_dynamics_augmented_model}) yields the state-space model that characterizes the Model Predictive Controller:
@@
 
-\subsection{Design of Adaptive Model Predictive Control}
+\section{Design of Adaptive Model Predictive Control}
 We created an Adaptive MPC controller with a prediction model that has six states, three outputs (longitudinal velocity, lateral deviation, relative yaw angle), and two manipulated signals (acceleration and steering).
@@
 
-\subsection{Simulation Results}
-The proposed adaptive MPC algorithm is designed in the MATLAB/Simulink and validated through simulation.
-The objective of this test is to evaluate the behavior of the proposed control strategy in critical situations.
-Table 3 shows the parameters used in the lane following simulation.
+\section{Simulation Results}
+The proposed adaptive MPC algorithm is designed in the MATLAB/Simulink and validated through different simulations.
+The objective of these test is to evaluate the behavior of the proposed control strategy in critical situations.
+Table 3 shows the parameters used in the lane following simulations.
 \begin{table}[!h]
@@
 
+\subsection{Sinusoidal Path}
+
 Figures \ref{fig:reference_laneFollowing} and \ref{fig:curvature_laneFollowing} show the desired path that the car must follow and its curvature, where the former is described in terms of the lateral position $Y_{\text{ref}}$ as function of the longitudinal position $X_{\text{ref}}$ and the latter is derived according with \cite{curvature}.
 The ATLASCAR2 is controlled to follow a sinusoidal trajectory which is given as follows:
-\begin{equation*}
+\begin{equation}
 X_\text{ref}=V_x\cdot t, \quad Y_\text{ref}=5\sin(X_\text{ref}/20)\quad \text{with}\quad t\in[0,20]\SI{}{s}
-\end{equation*}
+\end{equation}
+%LANE FOLLOWING SINUSOIDAL PATH - PATH/CURVATURE
 \begin{figure}[!t]
@@
 	\end{minipage}
-	\begin{minipage}[t]{0.5\textwidth}
+	\begin{minipage}[t]{0.49\textwidth}
 		\includegraphics[width=\textwidth]{../../MATLAB/lane_following/figure/Curvature.pdf}
@@
 	\end{minipage}
-	\caption{Desired path and curvature of the ATLASCAR2 in a simulation of \SI{20}{s}}
+	\caption{Desired path and curvature of the ATLASCAR2 in a simulation of \SI{20}{s}.}
 	\label{fig:laneFollowing_desired}
@@
 Moreover the following figures show the trend of the main parameters confirming that the control strategy used allows the vehicle to follow the path.
-In particular we simulated also a small error in the sensor dynamics in order to make the simulation more realistic: we added a 3 percent error to the longitudinal velocity and this is evident from the small noise in the graphs of the steering angle (Fig.\ref{fig:steering_laneFollowing}) and the lateral deviation (Fig.\ref{fig:lateral_deviation_laneFollowing}).
+In particular we simulated also a small error in the sensor dynamics in order to make the simulation more realistic: we added a 3 percent error to the longitudinal velocity and this is evident from the small noise in the graphs of the steering angle (Figure \ref{fig:steering_laneFollowing}) and the lateral deviation (Figure \ref{fig:lateral_deviation_laneFollowing}).
 Figure {\ref{fig:longitudinal_velocity_laneFollowing}} shows the evolution of the vehicle longitudinal velocity.
@@
 Finally we presents the overall scheme for the lane following developted in Simulink depicted in Figure \ref{fig:scheme_lane_following}.
+%LANE FOLLOWING SINUSOIDAL PATH - SIGNALS
 \begin{figure}[!h]
@@
 		\includegraphics[width=\textwidth]{../../MATLAB/lane_following/figure/LongitudinalVelocityVsTime.pdf}
-		\subcaption{Longitudinal velocity $V_x$ with respect to time.}
+		\subcaption{Longitudinal velocity $V_x$ w.r.t. time.}
 		\label{fig:longitudinal_velocity_laneFollowing}
@@
 		\includegraphics[width=\textwidth]{../../MATLAB/lane_following/figure/AccelerationVsTime.pdf}
-		\subcaption{Acceleration $u_1$ with respect to time.}
+		\subcaption{Acceleration $u_1$ w.r.t. time.}
 		\label{fig:acceleration_laneFollowing}
@@
 		\includegraphics[width=\textwidth]{../../MATLAB/lane_following/figure/SteeringAngleVsTime.pdf}
-		\subcaption{Steering angle $u_2$ with respect to time.}
+		\subcaption{Steering angle $u_2$ w.r.t. time.}
 		\label{fig:steering_laneFollowing}
@@
 	%	\includegraphics[width=\columnwidth]{../../MATLAB/lane_following/figure/RelativeYawAngleVsTime.pdf}
-	%	\subcaption{Relative yaw angle $e_2$ with respect to time.}
+	%	\subcaption{Relative yaw angle $e_2$ w.r.t. time.}
 	%	\label{fig:relative_yaw_angle_laneFollowing}
@@
 		\includegraphics[width=\textwidth]{../../MATLAB/lane_following/figure/LateralDeviationVsTime.pdf}
-		\subcaption{Lateral deviation $e_1$ with respect to time.}
+		\subcaption{Lateral deviation $e_1$ w.r.t. time.}
 		\label{fig:lateral_deviation_laneFollowing}
@@
 
+%OVERALL SCHEME LANE FOLLOWING
 \begin{figure}[!h]
@@
 
+%SENSOR DYNAMICS
+\begin{figure}[!h]
+	\centering
+	\includegraphics[width=\textwidth]{../figure/lane_following_AMPC_sensor_dynamics.pdf}
+	\caption{Sensor Dynamics of the overall scheme lane following.}
+	\label{fig:scheme_lane_following_sensor_dynamics}
+\end{figure}
+
+\subsection{Simple Curve Path}
+
+%LANE FOLLOWING SIMPLE CURVE - PATH/CURVATURE
+\begin{figure}[!t]
+	\centering
+	\begin{minipage}[t]{0.49\textwidth}
+		\includegraphics[width=\textwidth]{../../MATLAB/lane_following_curve/figure/Reference_curve.pdf}
+		\subcaption{}
+		\label{fig:reference_laneFollowing_curve}
+	\end{minipage}
+	\begin{minipage}[t]{0.49\textwidth}
+		\includegraphics[width=\textwidth]{../../MATLAB/lane_following_curve/figure/Curvature_curve.pdf}
+		\subcaption{}
+		\label{fig:curvature_laneFollowing_curve}
+	\end{minipage}
+	\caption{Desired path and curvature of the ATLASCAR2 in a simulation of \SI{10}{s}.}
+	\label{fig:laneFollowing_desired_curve}
+\end{figure}
+
+%LANE FOLLOWING SIMPLE CURVE - PATH/CURVATURE
+\begin{figure}[!h]
+	\centering
+	\begin{minipage}[t]{0.49\textwidth}
+		\includegraphics[width=\textwidth]{../../MATLAB/lane_following_curve/figure/LongitudinalVelocityVsTime_curve.pdf}
+		\subcaption{Longitudinal velocity $V_x$ w.r.t. time.}
+		\label{fig:longitudinal_velocity_laneFollowing_curve}
+	\end{minipage}
+	\begin{minipage}[t]{0.49\textwidth}
+		\includegraphics[width=\textwidth]{../../MATLAB/lane_following_curve/figure/AccelerationVsTime_curve.pdf}
+		\subcaption{Acceleration $u_1$ w.r.t. time.}
+		\label{fig:acceleration_laneFollowing_curve}
+	\end{minipage}
+	\begin{minipage}[t]{0.49\textwidth}
+		\includegraphics[width=\textwidth]{../../MATLAB/lane_following_curve/figure/SteeringAngleVsTime_curve.pdf}
+		\subcaption{Steering angle $u_2$ w.r.t. time.}
+		\label{fig:steering_laneFollowing_curve}
+	\end{minipage}
+	%\begin{minipage}[t]{\columnwidth}
+	%	\includegraphics[width=\columnwidth]{../../MATLAB/lane_following_curve/figure/RelativeYawAngleVsTime_curve.pdf}
+	%	\subcaption{Relative yaw angle $e_2$ w.r.t. time.}
+	%	\label{fig:relative_yaw_angle_laneFollowing_curve}
+	%\end{minipage}
+	\begin{minipage}[t]{0.49\textwidth}
+		\includegraphics[width=\textwidth]{../../MATLAB/lane_following_curve/figure/LateralDeviationVsTime_curve.pdf}
+		\subcaption{Lateral deviation $e_1$ w.r.t. time.}
+		\label{fig:lateral_deviation_laneFollowing_curve}
+	\end{minipage}
+	\caption{Time signals of the ATLASCAR2 in the simulation with a curve path.}
+	\label{fig:laneFollowing_signals_curve}
+\end{figure}
+
 %%%CIAOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOOO

### 2019-03-11 MATLAB/lane_following_curve/LaneFollowingGetCurvature.m

@@ -14,17 +14,17 @@ Xref = Vx*time;
 z1 = (2.4/50)*(Xref-27.19)-1.2;
 z2 = (2.4/43.9)*(Xref-56.46)-1.2;
 Yref = 8.1/2*(1+tanh(z1)) - 8.4/2*(1+tanh(z2));
-h = figure ('Position',[100, 100, 340, 230], 'PaperPositionMode','auto');
+h0 = figure ('Position',[100, 100, 340, 230], 'PaperPositionMode','auto');
 plot(Xref,Yref)
 hold on
 grid on
 grid minor
-title('\textbf{Desired Path}','Interpreter','latex');
+%title('\textbf{Desired Path}','Interpreter','latex');
 xlabel('X-coordinate [m]','Interpreter','latex');
 ylabel('Y-coordinate [m]','Interpreter','latex');
-pos = get(h,'Position');
-set(h,'PaperPositionMode','Auto','PaperUnits','Points','PaperSize',[pos(3)*0.8, pos(4)-40])
-print(h,'figure\Reference_curve','-dpdf','-r0')
+pos0 = get(h0,'Position');
+set(h0,'PaperPositionMode','Auto','PaperUnits','Points','PaperSize',[pos0(3)*0.8, pos0(4)-40])
+print(h0,'figure\Reference_curve','-dpdf','-r0')
 hold off
 
 % Desired curvature
@@ -42,10 +42,10 @@ plot(rho.time,rho.signals.values)
 hold on
 grid on
 grid minor
-title('\textbf{Curvature}','Interpreter','latex');
+%title('\textbf{Curvature}','Interpreter','latex');
 xlabel('Time [s]','Interpreter','latex');
-ylabel('Curvature [m]','Interpreter','latex');
-pos = get(hcurv,'Position');
-set(hcurv,'PaperPositionMode','Auto','PaperUnits','Points','PaperSize',[pos(3)*0.8, pos(4)-40])
+ylabel('Curvature','Interpreter','latex');
+poscurv = get(hcurv,'Position');
+set(hcurv,'PaperPositionMode','Auto','PaperUnits','Points','PaperSize',[poscurv(3)*0.8, poscurv(4)-40])
 print(hcurv,'figure\Curvature_curve','-dpdf','-r0')
 hold off

### 2019-03-11 MATLAB/lane_following_curve/LaneFollowingResults.m

@@ -8,75 +8,75 @@ function LaneFollowingResults(logsout,Yref)
 %% Steering Angle vs Time
 
 h1 = figure ('Position',[100, 100, 340, 230], 'PaperPositionMode','auto');
+plot(delta_ampc.Values.time,delta_ampc.Values.Data);
 hold on;
 grid on;
 grid minor;
-plot(delta_ampc.Values.time,delta_ampc.Values.Data);
-title('\textbf{Steering Angle (u$_2$) vs Time}','Interpreter','latex');
+%title('\textbf{Steering Angle (u$_2$) vs Time}','Interpreter','latex');
 xlabel('Time [s]','Interpreter','latex');
 ylabel('Steering angle [rad]','Interpreter','latex');
-pos = get(h1,'Position');
-set(h1,'PaperPositionMode','Auto','PaperUnits','Points','PaperSize',[pos(3), pos(4)-40])
+pos1 = get(h1,'Position');
+set(h1,'PaperPositionMode','Auto','PaperUnits','Points','PaperSize',[pos1(3)*0.8, pos1(4)-40])
 print(h1,'figure\SteeringAngleVsTime_curve','-dpdf','-r0')
 hold off
 pause(2)
 %% Lateral deviation vs Time
 
 h2 = figure ('Position',[100, 100, 340, 230], 'PaperPositionMode','auto');
+plot(e1_ampc.Values.time,e1_ampc.Values.Data);
 hold on;
 grid on;
 grid minor;
-plot(e1_ampc.Values.time,e1_ampc.Values.Data);
-title('\textbf{Lateral Deviation (e$_1$) vs Time}','Interpreter','latex');
+%title('\textbf{Lateral Deviation (e$_1$) vs Time}','Interpreter','latex');
 xlabel('Time [s]','Interpreter','latex');
 ylabel('Lateral Deviation [m]','Interpreter','latex');
-pos = get(h2,'Position');
-set(h2,'PaperPositionMode','Auto','PaperUnits','Points','PaperSize',[pos(3), pos(4)-41])
+pos2 = get(h2,'Position');
+set(h2,'PaperPositionMode','Auto','PaperUnits','Points','PaperSize',[pos2(3)*0.8, pos2(4)-41])
 print(h2,'figure\LateralDeviationVsTime_curve','-dpdf','-r0')
 hold off
 pause(2)
 %% Relative Yaw Angle vs Time
 
[…]

### 2019-03-11 MATLAB/lane_following_curve/main_lane_following_curve.m

@@ -43,3 +43,6 @@ logsout1 = logsout;
 LaneFollowingResults(logsout1,Yref)
 print -slane_following_AMPC -dpdf lane_following_AMPC.pdf
 movefile('lane_following_AMPC.pdf','figure')
+
+print -slane_following_AMPC/Sensor_Dynamics -dpdf lane_following_AMPC_sensor_dynamics.pdf
+movefile('lane_following_AMPC_sensor_dynamics.pdf','figure')

### 2019-03-11 Thesis_Latex/Thesis/Chapter4/Chapter4.tex
update thesis

@@
 \chapter{Moving Obstacle Avoidance}
+In this chapter we present an Obstacle Avoidance alghorithm based on Adaptive Model Predictive Control.
+First we introduced the case-study model, then we designed the controller and the method of decision-making.
+Finally we verified the proposed strategy in different scenarios.
 
@@
 Figure \ref{fig:obstacleAvoidance} illustrates a typical scenario of overtaking of a moving obstacle.
+The maneuver from the driver is to temporarily move to another lane, drive past the obstacle, and move back to the original lane afterward.
 % COLLISION AVOIDANCE FIGURE
@@
 
-The model used in this report should take into account the kinematic and dynamic aspects of the vehicle.
+This is possible if and only if there is a free lane or  sufficient space for overtaking the obstacle.
+In the case the road is busy with vehicles, the ATLASCAR2 must slow down and adapts its speed to that of the closest obstacle until the scenario changes.
+
+\subsection{Car-like Model}
+The model used in this part of the thesis should take into account the kinematic and dynamic aspects of the vehicle.
 Here, we present a non linear mathematical model of a vehicle used for the development of a collision avoidance system.
+
 The model has four states and two inputs:
@@
 \end{equation}
-where $C_L$ is the car length.
+
+where $C_L$ is the car length. When the velocity is zero then the rate of change of heading angle is zero, that is, it is not possible to change the vehicle's orientation
+when it is not moving.
+If the front wheel is orthogonal to the back wheel, i.e.
+the steering angle is $\frac{\pi}{2}$, the ATLASCAR2 cannot move forward and the model enters an undefined region.
 In order to simplify the model, it is assumed that only the front wheel can be steered.
@@
 Under this assumption, the slip angle is zero, meaning that the velocity is directed along the heading of the vehicle.
-In order to use MPC, the state space model needs to be linearized with a first order approximation and also re-written in a more compact form:
+In particular the rate of change of heading angle is referred to as turn rate which can be evaluated with a gyroscope.
+This yaw rate can also be deduced from the angular velocity of the wheels on the left- and right-hand sides of the vehicle which therefore rotate at different speeds because follow arcs of different radius.
+We can write the non-holonomic constraint which is an expression for velocity in the vehicle's $y$-direction in the world coordinate frame as follows:
+\begin{equation}
+	\dot{y}\cos\theta-\dot{x}\cos\theta=0
+\end{equation}
+This equation cannot be integrated to form a
+relationship between $x,y$ and $\theta$.
+
+In order to use an MPC controller, the state space model needs to be linearized with a first order approximation and also re-written in a more compact form:
 \begin{equation}

### 2019-03-11 Thesis_Latex/Thesis/Chapter5/Chapter5.tex
update thesis

@@
 At the start of the simulation, this velocity is equal to the initial condition for longitudinal velocity parameter $V_0$.
-At run time, we can note that $V_x$ reaches the predefined value of \SI{20}{m/s} meters for second and then it stabilizes near the cruising speed because it continues to vary the steering angle to adapt to the path to be followed.
+At run time, we can note that $V_x$ reaches the predefined value of \SI{20}{m/s} and then it stabilizes near the cruising speed because it continues to vary the steering angle to adapt to the path to be followed.
 Finally we presents the overall scheme for the lane following developted in Simulink depicted in Figure \ref{fig:scheme_lane_following}.
@@
 	\end{minipage}
-	%\begin{minipage}[t]{\columnwidth}
-	%	\includegraphics[width=\columnwidth]{../../MATLAB/lane_following/figure/RelativeYawAngleVsTime.pdf}
-	%	\subcaption{Relative yaw angle $e_2$ w.r.t. time.}
-	%	\label{fig:relative_yaw_angle_laneFollowing}
-	%\end{minipage}
+	\begin{minipage}[t]{0.49\textwidth}
+		\includegraphics[width=\textwidth]{../../MATLAB/lane_following/figure/RelativeYawAngleVsTime.pdf}
+		\subcaption{Relative yaw angle $e_2$ w.r.t. time.}
+		\label{fig:relative_yaw_angle_laneFollowing}
+	\end{minipage}
 	\begin{minipage}[t]{0.49\textwidth}
@@
 		\label{fig:lateral_deviation_laneFollowing}
+	\end{minipage}
+	\begin{minipage}[t]{0.49\textwidth}
+		\includegraphics[width=\textwidth]{../../MATLAB/lane_following/figure/LateralVelocityVsTime.pdf}
+		\subcaption{Lateral velocity $V_y$ w.r.t. time.}
+		\label{fig:lateral_velocity_laneFollowing}
 	\end{minipage}
@@
 	\end{minipage}
-	%\begin{minipage}[t]{\columnwidth}
-	%	\includegraphics[width=\columnwidth]{../../MATLAB/lane_following_curve/figure/RelativeYawAngleVsTime_curve.pdf}
-	%	\subcaption{Relative yaw angle $e_2$ w.r.t. time.}
-	%	\label{fig:relative_yaw_angle_laneFollowing_curve}
-	%\end{minipage}
+	\begin{minipage}[t]{0.49\textwidth}
+		\includegraphics[width=\textwidth]{../../MATLAB/lane_following_curve/figure/RelativeYawAngleVsTime_curve.pdf}
+	\subcaption{Relative yaw angle $e_2$ w.r.t. time.}
+		\label{fig:relative_yaw_angle_laneFollowing_curve}
+	\end{minipage}
 	\begin{minipage}[t]{0.49\textwidth}
@@
 		\label{fig:lateral_deviation_laneFollowing_curve}
+	\end{minipage}
+	\begin{minipage}[t]{0.49\textwidth}
+		\includegraphics[width=\textwidth]{../../MATLAB/lane_following_curve/figure/LateralVelocityVsTime_curve.pdf}
+		\subcaption{Lateral velocity $V_y$ w.r.t. time.}
+		\label{fig:lateral_velocity_laneFollowing_curve}
 	\end{minipage}

### 2019-03-11 Thesis_Latex/Thesis/Introduction/Introduction.tex
update thesis

@@
 The most common maneuver from the driver is to temporarily move to another lane, drive past the obstacle, and move back to the original lane afterward.
-In this case, we want to design an obstacle avoidance system that moves the ATLASCAR2 around a moving obstacle in the lane using throttle and steering angle.
+In this case, we want to design an obstacle avoidance system that moves the ATLASCAR2 around  moving obstacles in the lane using throttle and steering angle.
 This system uses an adaptive Model Predictive Controller that updates both the predictive model and the mixed input/output constraints at each control interval.

### 2019-03-11 MATLAB/lane_following/LaneFollowingResults.m

@@ -79,8 +79,24 @@ pos5 = get(h5,'Position');
 set(h5,'PaperPositionMode','Auto','PaperUnits','Points','PaperSize',[pos5(3)*0.8, pos5(4)-40])
 print(h5,'figure\LongitudinalVelocityVsTime','-dpdf','-r0')
 hold off
+
+
+%% Lateral Velocity
+
+hpp = figure ('Position',[100, 100, 340, 230], 'PaperPositionMode','auto');
+plot(vy_ampc.Values.Time,vy_ampc.Values.Data);
+hold on;
+grid on;
+grid minor;
+%title('\textbf{Velocity (V$_x$) vs Time}','Interpreter','latex');
+xlabel('Time [s]','Interpreter','latex');
+ylabel('Velocity [m/s]','Interpreter','latex');
+pospp = get(hpp,'Position');
+set(hpp,'PaperPositionMode','Auto','PaperUnits','Points','PaperSize',[pospp(3)*0.8, pospp(4)-40])
+print(hpp,'figure\LateralVelocityVsTime','-dpdf','-r0')
+hold off
 %% Local function: Get data from simulation
-function [e1,e2,delta,accel,vx,vy,xp,yp] = getData(logsout)
+function [e1,e2,delta,accel,vx,vy] = getData(logsout)
 e1 = logsout.getElement('Lateral Deviation');    % lateral deviation
 e2 = logsout.getElement('Relative Yaw Angle');   % relative yaw angle
 delta = logsout.getElement('Steering');          % steering angle

### 2019-03-11 MATLAB/lane_following_curve/LaneFollowingResults.m

@@ -79,7 +79,21 @@ pos5 = get(h5,'Position');
 set(h5,'PaperPositionMode','Auto','PaperUnits','Points','PaperSize',[pos5(3)*0.8, pos5(4)-40])
 print(h5,'figure\LongitudinalVelocityVsTime_curve','-dpdf','-r0')
 hold off
+pause(2)
+%% Lateral Velocity
 
+h6 = figure ('Position',[100, 100, 340, 230], 'PaperPositionMode','auto');
+plot(vy_ampc.Values.Time,vy_ampc.Values.Data);
+hold on;
+grid on;
+grid minor;
+%title('\textbf{Velocity (V$_x$) vs Time}','Interpreter','latex');
+xlabel('Time [s]','Interpreter','latex');
+ylabel('Velocity [m/s]','Interpreter','latex');
+pos6 = get(h6,'Position');
+set(h6,'PaperPositionMode','Auto','PaperUnits','Points','PaperSize',[pos6(3)*0.8, pos6(4)-40])
+print(h6,'figure\LateralVelocityVsTime_curve','-dpdf','-r0')
+hold off
 %% Local function: Get data from simulation
 function [e1,e2,delta,accel,vx,vy] = getData(logsout)
 e1 = logsout.getElement('Lateral Deviation');    % lateral deviation

### 2019-03-11 MATLAB/lane_following_curve/main_lane_following_curve.m

@@ -40,7 +40,7 @@ LaneFollowingGenerateAMPC;
 % function |LaneFollowingResults|
 sim(mdl)
 logsout1 = logsout;
-LaneFollowingResults(logsout1,Yref)
+closLaneFollowingResults(logsout1,Yref)
 print -slane_following_AMPC -dpdf lane_following_AMPC.pdf
 movefile('lane_following_AMPC.pdf','figure')
 

### 2019-03-15 Thesis_Latex/Thesis/Chapter4/Chapter4.tex
update thesis

@@
 In order to simplify the model, it is assumed that only the front wheel can be steered.
-Moreover, in this paper it is assumed that the ATLASCAR2 does not slip, so any slippage is thus considered as an external disturbance.
+Moreover, in this chapter it is assumed that the ATLASCAR2 does not slip, so any slippage is thus considered as an external disturbance.
 Under this assumption, the slip angle is zero, meaning that the velocity is directed along the heading of the vehicle.
@@
 \begin{equation}
-	\dot{y}\cos\theta-\dot{x}\cos\theta=0
+	\dot{y}\cos\theta-\dot{x}\cos\theta=0.
 \end{equation}
+
 This equation cannot be integrated to form a
@@
 
+% RESULTS ONE MOVING OBSTACLE
+\begin{figure}[!t] %vs changes to t instead of b
+	\begin{minipage}[t]{0.5\textwidth}
+		\includegraphics[width=\textwidth]{../../MATLAB/one_obstacle_right_overtaking/figure/LongitudinalPositionVsTime.pdf}
+		\subcaption{}\label{fig:longitudinal_one_moving}
+	\end{minipage}
+	\begin{minipage}[t]{0.5\textwidth}
+		\includegraphics[width=\textwidth]{../../MATLAB/one_obstacle_right_overtaking/figure/LateralPositionVsTime.pdf}
+		\subcaption{}\label{fig:lateral_one_moving}
+	\end{minipage}
+	\begin{minipage}[t]{0.5\textwidth}
+		\includegraphics[width=\textwidth]{../../MATLAB/one_obstacle_right_overtaking/figure/VelocityVsTime.pdf}
+		\subcaption{}\label{fig:velocity_one_moving}
+	\end{minipage}
+	\begin{minipage}[t]{0.5\textwidth}
+		\includegraphics[width=\textwidth]{../../MATLAB/one_obstacle_right_overtaking/figure/ThrottleVsTime.pdf}
+		\subcaption{}\label{fig:throttle_one_moving}
+	\end{minipage}
+	\begin{minipage}[t]{0.5\textwidth}
+		\includegraphics[width=\textwidth]{../../MATLAB/one_obstacle_right_overtaking/figure/SteeringAngleVsTime.pdf}
+		\subcaption{}\label{fig:delta_one_moving}
+	\end{minipage}
+	\begin{minipage}[t]{0.5\textwidth}
+		\includegraphics[width=\textwidth]{../../MATLAB/one_obstacle_right_overtaking/figure/HeadingAngleVsTime.pdf}
+		\subcaption{}\label{fig:theta_one_moving}
+	\end{minipage}
+	\caption{Time signals of the ATLASCAR2 in the simulation of right overtaking of one moving obstacle illustrated in Figure \ref{fig:obstacleAvoidance_one_obstacle}.}
+	\label{fig:components_one_moving_obstacle}
+\end{figure}
+
 % ALGORITHM FOR RIGHT OVERTAKING OF ONE MOVING OBSTACLE
@@
 The same test can be done with the obstacles that drive in the same direction as the vehicle but to better assess and demonstrate results we decided to show a very unusual scenario.
+
+% SIX MOVING OBSTACLES
+\begin{figure}[h!]
+	\centering
+	\begin{minipage}[t]{\textwidth}
+		\includegraphics[width=\textwidth]{../figure/6_obstacles/6_obstacles_1.pdf}
+	\end{minipage}
+	\begin{minipage}[t]{\textwidth}
+		\includegraphics[width=\textwidth]{../figure/6_obstacles/6_obstacles_2.pdf}
+	\end{minipage}
+	\begin{minipage}[t]{\textwidth}
+		\includegraphics[width=\textwidth]{../figure/6_obstacles/6_obstacles_3.pdf}
+	\end{minipage}
+	\begin{minipage}[t]{\textwidth}
+		\includegraphics[width=\textwidth]{../figure/6_obstacles/6_obstacles_4.pdf}
+	\end{minipage}
+	\begin{minipage}[t]{\textwidth}
+		\includegraphics[width=\textwidth]{../figure/6_obstacles/6_obstacles_5.pdf}
+	\end{minipage}
+	\begin{minipage}[t]{\textwidth}
+		\includegraphics[width=\textwidth]{../figure/6_obstacles/6_obstacles_6.pdf}
+	\end{minipage}
+	\caption{Simulation of overtaking with six moving obstacles that moves in the opposite direction with respect the vehicle.}
+	\label{fig:obstacleAvoidance_six_obstacles}
+\end{figure}
+
+% RESULTS SIX MOVING OBSTACLES
+\begin{figure}[!t] %vs changes to t instead of b
+	\begin{minipage}[t]{0.5\textwidth}
+		\includegraphics[width=\textwidth]{../../MATLAB/6_obstacles/figure/LongitudinalPositionVsTime.pdf}
+		\subcaption{}\label{fig:longitudinal_six_moving}
+	\end{minipage}
+	\begin{minipage}[t]{0.5\textwidth}
+		\includegraphics[width=\textwidth]{../../MATLAB/6_obstacles/figure/LateralPositionVsTime.pdf}
+		\subcaption{}\label{fig:lateral_six_moving}
+	\end{minipage}
+	\begin{minipage}[t]{0.5\textwidth}
+		\includegraphics[width=\textwidth]{../../MATLAB/6_obstacles/figure/VelocityVsTime.pdf}
+		\subcaption{}\label{fig:velocity_six_moving}
+	\end{minipage}
+	\begin{minipage}[t]{0.5\textwidth}
+		\includegraphics[width=\textwidth]{../../MATLAB/6_obstacles/figure/ThrottleVsTime.pdf}
+		\subcaption{}\label{fig:throttle_six_moving}
+	\end{minipage}
+	\begin{minipage}[t]{0.5\textwidth}
+		\includegraphics[width=\textwidth]{../../MATLAB/6_obstacles/figure/SteeringAngleVsTime.pdf}
+		\subcaption{}\label{fig:delta_six_moving}
+	\end{minipage}
+	\begin{minipage}[t]{0.5\textwidth}
+		\includegraphics[width=\textwidth]{../../MATLAB/6_obstacles/figure/HeadingAngleVsTime.pdf}
+		\subcaption{}\label{fig:theta_six_moving}
+	\end{minipage}
+	\caption{Time signals of the ATLASCAR2 in the simulation of overtaking with six moving obstacles illustrated in Figure \ref{fig:obstacleAvoidance_six_obstacles}.}
+	\label{fig:components_six_moving_obstacles}
+\end{figure}
+
+\subsection{No Overtaking}
+%NO OVERTAKING
+\begin{figure}[h!]
+	\centering
+	\begin{minipage}[t]{\textwidth}
+		\includegraphics[width=\textwidth]{../figure/no_overtaking/no_overtaking_1.pdf}
+	\end{minipage}
+	\begin{minipage}[t]{\textwidth}
+		\includegraphics[width=\textwidth]{../figure/no_overtaking/no_overtaking_1_5.pdf}
+	\end{minipage}
+	\begin{minipage}[t]{\textwidth}
+		\includegraphics[width=\textwidth]{../figure/no_overtaking/no_overtaking_2.pdf}
+	\end{minipage}
+	\begin{minipage}[t]{\textwidth}
+		\includegraphics[width=\textwidth]{../figure/no_overtaking/no_overtaking_3.pdf}
+	\end{minipage}
+	\begin{minipage}[t]{\textwidth}
+		\includegraphics[width=\textwidth]{../figure/no_overtaking/no_overtaking_4.pdf}
+	\end{minipage}
+	\caption{Simulation of no overtaking with three moving obstacles that move in the same direction as the vehicle.}
+	\label{fig:obstacleAvoidance_no_overtaking}
+\end{figure}
+
+% RESULTS NO OVERTAKING
+\begin{figure}[!t] %vs changes to t instead of b
+	\begin{minipage}[t]{0.5\textwidth}
+		\includegraphics[width=\textwidth]{../../MATLAB/no_overtaking/figure/LongitudinalPositionVsTime.pdf}
+		\subcaption{}\label{fig:longitudinal_no_overtaking}
+	\end{minipage}
+	\begin{minipage}[t]{0.5\textwidth}
+		\includegraphics[width=\textwidth]{../../MATLAB/no_overtaking/figure/LateralPositionVsTime.pdf}
+		\subcaption{}\label{fig:lateral_no_overtaking}
+	\end{minipage}
+	\begin{minipage}[t]{0.5\textwidth}
+		\includegraphics[width=\textwidth]{../../MATLAB/no_overtaking/figure/VelocityVsTime.pdf}
+		\subcaption{}\label{fig:velocity_no_overtaking}
+	\end{minipage}
+	\begin{minipage}[t]{0.5\textwidth}
+		\includegraphics[width=\textwidth]{../../MATLAB/no_overtaking/figure/ThrottleVsTime.pdf}
+		\subcaption{}\label{fig:throttle_no_overtaking}
+	\end{minipage}
+	\begin{minipage}[t]{0.5\textwidth}
+		\includegraphics[width=\textwidth]{../../MATLAB/no_overtaking/figure/SteeringAngleVsTime.pdf}
+		\subcaption{}\label{fig:delta_no_overtaking}
+	\end{minipage}
+	\begin{minipage}[t]{0.5\textwidth}
+		\includegraphics[width=\textwidth]{../../MATLAB/no_overtaking/figure/HeadingAngleVsTime.pdf}
+		\subcaption{}\label{fig:theta_no_overtaking}
+	\end{minipage}
+	\caption{Time signals of the ATLASCAR2 in the simulation of no overtaking with three moving obstacles illustrated in Figure \ref{fig:obstacleAvoidance_no_overtaking}.}
+	\label{fig:components_no_overtaking}
+\end{figure}
 
@@
 	\begin{minipage}[t]{0.5\textwidth}
+		\includegraphics[width=\textwidth]{./figure/three_obstacles_no_overtaking/LongitudinalPositionVsTime.pdf}
+		\subcaption{}\label{fig:longitudinal_braking}
+	\end{minipage}
+	\begin{minipage}[t]{0.5\textwidth}
+		\includegraphics[width=\textwidth]{./figure/three_obstacles_no_overtaking/LateralPositionVsTime.pdf}
+		\subcaption{}\label{fig:lateral_braking}
+	\end{minipage}
+	\begin{minipage}[t]{0.5\textwidth}
 		\includegraphics[width=\textwidth]{./figure/three_obstacles_no_overtaking/VelocityVsTime.pdf}

### 2019-03-15 Thesis_Latex/Thesis/Chapter5/Chapter5.tex
update thesis

@@
 The first fundamental block describes the vehicle dynamics: we have applied the bicycle model of lateral vehicle dynamics and approximate the longitudinal dynamics using a time constant obtaining  a linear model.
+
 \subsection{Longitudinal Dynamics}
+Dynamics of the powertrain are commonly modeled using a first-order transfer function, called the generalized vehicle longitudinal dynamic system in \cite{longitudinal_paper}:
+\begin{equation}
+\label{eqn:longitudinal_transfer_function}
+\dot{V_x} = \frac{K}{\tau s+1}a
+\end{equation}
+
+with the system gain usually $K = 1$ and a time constant $\tau = 0.2$.
+This type of model was used in \cite{longitudinal_paper} for a predictive multi-objective vehicular ACC and in \cite{longitudinal_paper2} for model predictive control of transitional maneuvers for adaptive
+vehicle cruise control. Moreover a similar modeling approach
+was applied in \cite{longitudinal} to address trajectory tracking for autonomous vehicles, with the goal of developing a racing controller.
+
 We can use the following state space to describe the longitudinal model:
@@
 \begin{array}{ll}
-\dot{\vec{x}}_{\text{lon}} =\vec{A}_m \vec{x}_{\text{lon}}+ \vec{B_m}\vec{u}_{\text{lon}}\\
-\vec{y}_{\text{lon}} =\vec{C_m} \vec{x}_{\text{lon}} + \vec{D_m} \vec{u}_{\text{lon}}
+\dot{\vec{x}}_{\text{lon}} =\vec{A}_m \vec{x}_{\text{lon}}+ \vec{B}_m\vec{u}_{\text{lon}}\\
+\vec{y}_{\text{lon}} =\vec{C}_m \vec{x}_{\text{lon}} + \vec{D}_m \vec{u}_{\text{lon}}
 \end{array}
 \end{equation}
-where the input is the acceleration and the states are the longitudinal velocity and the actual acceleration which is also the only output of this system.
+where the input is the desired acceleration and the states are the longitudinal velocity and the actual acceleration which is also the only output of this system:
 \begin{equation}
@@
 \qquad
-\vec{u}_{\text{lon}} = a
+\vec{u}_{\text{lon}} = a,
 \end{equation}
-and
+while the matrices $\vec{A}_m$,$\vec{B}_m$,$\vec{C}_m$ and $\vec{D}_m$ are the following:
 \begin{equation}
 \begin{array}{cc}
-\vec{A_m}=\begin{bmatrix}
+\vec{A}_m=\begin{bmatrix}
 -\frac{1}{\tau}&0\\1&0
@@
 \qquad
-\vec{B_m}=\begin{bmatrix}
+\vec{B}_m=\begin{bmatrix}
 \frac{1}{\tau}\\
@@
 \end{bmatrix},\\\\
-\vec{C_m}=\begin{bmatrix}
+\vec{C}_m=\begin{bmatrix}
 1&0
@@
 \qquad
-\vec{D_m}=0.
+\vec{D}_m=0,
 \end{array}
 \end{equation}
-where $\tau$ is a time constant \cite{long_tf}; in practice we are considering a second order transfer function like in \cite{longitudinal}.
+where $\tau$ is time constant described above.
+
 \subsection{Lateral Dynamics}
-Local function: we have a continuous vehicle lateral model from parameters obtained by simplifying the one in \cite{rathai}: 
+
+The vehicle is modelled at each axis through a bicycle model in which the two wheels are lumped into a single wheel.
+It will be assumed that a simple linear tire model can be used due to the considered speeds.
+It is also assumed that the small angles approximation can be used.
+The equations describing the yaw and lateral motion are:
+\begin{equation}
+	\label{eqn:yaw_lateral_motion}
+	\begin{array}{ll}
+	m\dot{V_y}=F_{yf}+F_{yr}\\
+	I_Z\ddot{\psi}=l_FF_{yf}-l_RF_{yr}
+	\end{array}
+\end{equation}
+where $F_{yf}$ and $F_{yr}$ are the tire forces at the front and rear axles of the vehicle, which are a function of the cornering stifness of the tires $C_F$ and $C_R$, the steering angle $\delta$ and the vehicle states.
+The ATLASCAR2 travels with a longitudinal velocity $V_x$ and a lateral velocity $V_y$.
+These two velocities can be used to form a vector describing the resultant velocity and its direction.
+In this case it is also possible to find the slip angles, the difference between the actual travelling direction of the and where it is pointed (in the previous chapter we assumed that the ATLASCAR2 does not slip, so any slippage is thus considered as an external disturbance):
+\begin{equation}
+	\label{eqn:alpha_f_alpha_r}
+	\begin{array}{ll}
+	\alpha_f = \delta-\theta_{vf}\\
+	\alpha_r = -\theta_{vr}
+	\end{array}
+\end{equation}
+
+where $\theta_{vf}$ and $\theta_{vr}$ represent the angles of the velocity vectors for the rear and front tires evaluated as follows:
+
+\begin{equation}
+\label{eqn:theta_vf}
+\theta_{vf}=\text{atan}\Bigg(\frac{V_y+l_F\dot{\psi}}{V_x}\Bigg)
+\end{equation}
+\begin{equation}
+\label{eqn:theta_vr}
+\theta_{vr}=\text{atan}\Bigg(\frac{V_y-l_R\dot{\psi}}{V_x}\Bigg)
+\end{equation}
+
+Finally the lateral tire forces acting on the wheels, $F_{yf}$ and $F_{yr}$, are proportional to the slip angle, for small angles; so they can be written as:
+
+\begin{equation}
+	\label{eqn:lateral_tire_forces}
+	\begin{array}{ll}
+	F_{yf} = 2C_F(\delta-\theta_{vf})\\
+	F_{yr} = -2C_R\theta_{vr}
+	\end{array}
+\end{equation}
+
+Combining (\ref{eqn:yaw_lateral_motion}) and (\ref{eqn:lateral_tire_forces}) gives the following vehicle lateral model from parameters: 
 \begin{equation}
@@
 \end{equation}
-and
+while the matrices $\vec{A}_g$,$\vec{B}_g$,$\vec{C}_g$ and $\vec{D}_g$ are the following:
 \begin{equation}
@@
 \end{equation}
-The parameters in the previous matrices are:
+Recapping the parameters in the previous matrices are:
 \begin{itemize}
@@
 \subsection{Augmented Model for Lateral Dynamics}
-The goal for the driver steering model is to keep the vehicle in its lane and follow the curved road by controlling the front steering angle .
+The goal for the driver steering model is to keep the vehicle in its lane and follow the curved road by controlling the front steering angle.
+Denote by $e_1$ the offset to the center line and $e_2$, the relative angle to the center line.
 This goal is achieved by driving the yaw angle error $e_2 = \psi -\psi_{\text{des}}$ and lateral displacement error $e_1$ to zero ($\dot{e}_1 = V_xe_2+V_y$).
@@
 \end{equation}
-where
+where the states and the inputs are:
 \begin{equation}
@@
 \end{equation}
-and
+while the matrices $\vec{A}_a$,$\vec{B}_a$,$\vec{C}_a$ and $\vec{D}_a$ are the following:
 \begin{equation}
@@
 \subsection{Overall Model Dynamics}
-Combining (\ref{eqn:longi_dynamics_simple_model_ss}) with (\ref{eqn:lateral_dynamics_augmented_model}) yields the state-space model that characterizes the Model Predictive Controller:
+Combining (\ref{eqn:longi_dynamics_simple_model_ss}) with (\ref{eqn:lateral_dynamics_augmented_model}) yields the state-space model that characterizes the Model Predictive Control problem:
 \begin{equation}
@@
 \end{equation}
-and
+while the matrices $\vec{A}_f$,$\vec{B}_f$,$\vec{C}_f$ and $\vec{D}_f$ are the following:
 \begin{equation}
@@
 \end{equation}
-
 However the system to be controlled is usually modeled by a linear discrete state-space model:
@@
 where $\vec{A}$ and $\vec{B}$ are the state and control matrices for the discrete state-space equation, respectively, which can be calculated, also in this case, with the Euler method as:
-\[
+\begin{equation}
 	\vec{A} = e^{\vec{A}_fT_s},\qquad \vec{B} = \int_{kT_s}^{(k+1)T_s} e^{\vec{A}_f[(k+1)T_s-\eta]}\vec{B}_f d\eta
-\]
+\end{equation}
 where $T_s$ is the sampling interval for the discrete state-space model. The matrices $\vec{C}$ and $\vec{D}$ are equivalent to those in the continuous case.
@@
 \section{Design of Adaptive Model Predictive Control}
-We created an Adaptive MPC controller with a prediction model that has six states, three outputs (longitudinal velocity, lateral deviation, relative yaw angle), and two manipulated signals (acceleration and steering).
+Before talking about the design of the controller, it is necessary to highlight which are all the elements that make up our control scheme.
+The overall framework for a lane keeping assist is depicted in the Figure \ref{fig:scheme_lane_following}.
+%OVERALL SCHEME LANE FOLLOWING
+\begin{figure}[!h]
+	\centering
+	\includegraphics[width=\textwidth]{../figure/lane_following_AMPC.pdf}
+	\caption{Overall procedure scheme lane following.}
+	\label{fig:scheme_lane_following}
+\end{figure}
+
+This control scheme is composed by four different blocks that are the Sensor Dynamics, the Vehicle Dynamics, the Adaptive MPC controller and the Curvature Previewer.
+Summarizing, the Vehicle Dynamics applies the bicycle model of lateral vehicle dynamics and approximate the longitudinal dynamics using a time constant according to what was seen previously; the Sensor Dynamics approximates a sensor, such as a camera or a laser, to calculate the lateral deviation and relative yaw angle; the Curvature Previewer detects the curvature at the current time step and the curvature sequence over the prediction horizon of the MPC controller and finally Adaptive MPC generates the optimal control inputs for a lane following system.
 The objective of the trajectory planning along specified path can be described as follows: given a path which the vehicle is expected to follow design a trajectory of a car-vehicle configuration.
-In order to do this, according with \cite{curvature} it is possible to derive the road curvature and its derivative.
-The product of the road curvature and the longitudinal velocity is modeled as a measured disturbance.
-We have set the constraints for manipulated variables and the scale factors.
+In order to do this it is possible to derive the road curvature and its derivative.
+For a plane curve given parametrically in Cartesian coordinates as $\gamma(t)=(x(t),y(t))$, the signed curvature is 
+\begin{equation}
+\label{eqn:curvature}
+\kappa=\frac{x'y''-x''y'}{(x'^2+y'^2)^\frac{3}{2}}
+\end{equation}
+where primes refer to derivatives $\frac{d}{dt}$ with respect to the parameter $t$.
+The resulting curvature (\ref{eqn:curvature}) is a rational function, continuous except at the roots of the denominator, which is always nonzero provided that the interpolated positions do not contain subsequent duplicate values and that the points are spaced sufficiently \cite{longitudinal}.
+The vehicle dynamics is represented by a Simulink model in Figure \ref{fig:scheme_lane_following_vehicle_dynamics}  where on the upper part we find the longitudinal dynamics while on the lower part we can see the lateral dynamics highlighted by the gains that are the components of the linear discrete state-space model (\ref{eqn:lateral_dynamics_simple_model}).
+
+%VEHICLE DYNAMICS
+\begin{figure}[!h]
+	\centering
+	\includegraphics[width=\textwidth]{../figure/lane_following_AMPC_vehicle_dynamics.pdf}
+	\caption{Vehicle Dynamics of the overall scheme lane following.}
+	\label{fig:scheme_lane_following_vehicle_dynamics}
+\end{figure}
+We created an Adaptive MPC controller with a prediction model that has six states, three outputs (longitudinal velocity, lateral deviation, relative yaw angle), two manipulated signals (acceleration and steering) and one measured disturbance (desired yaw rate).
+
+In order to design a valid lane keeping algorithm based on MPC we have set the constraints for manipulated variables and the scale factors. In particular the control
+variables are constrained as follows:
+\begin{equation}
+\label{eqn:constraint_LKA}
+\begin{array}{cc}
+	\SI{-3}{m/s}\leq a\leq\SI{3}{m/s}\;,\\\\
+	\SI{-1.13}{rad}\leq \delta \leq \SI{1.13}{rad}\;,
+\end{array}
+\end{equation}
+
 Moreover we have specified the weights in the standard MPC cost function.
@@
 This controller uses a linear model for the vehicle dynamics and updates the model online as the longitudinal velocity varies.
+The dynamics of the sensors (Figure \ref{fig:scheme_lane_following_sensor_dynamics}) allows us to calculate two fundamental parameters to reach the goal of keeping the vehicle in its lane and following the curved road by controlling the front steering angle:
+\begin{itemize}
+	\item $e_1$ which is the offset to the center line,
+	\item $e_2$ which is the relative angle to the center line.
+\end{itemize}
+where we want to drive the yaw angle error and the lateral displacement error to zero to achieve our goal.
+The product of the road curvature and the longitudinal velocity is modeled as a measured disturbance.
+%SENSOR DYNAMICS
+\begin{figure}[!h]
+	\centering
+	\includegraphics[width=\textwidth]{../figure/lane_following_AMPC_sensor_dynamics.pdf}
+	\caption{Sensor Dynamics of the overall scheme lane following.}
+	\label{fig:scheme_lane_following_sensor_dynamics}
+\end{figure}
 
 \section{Simulation Results}
-The proposed adaptive MPC algorithm is designed in the MATLAB/Simulink and validated through different simulations.
-The objective of these test is to evaluate the behavior of the proposed control strategy in critical situations.
-Table 3 shows the parameters used in the lane following simulations.
+The proposed adaptive MPC algorithm is designed in the MATLAB/Simulink and validated through simulations considering different paths.
+The objective of these tests is to evaluate the behavior of the proposed control strategy in critical situations.
+The parameters used in the lane following simulations are summarized in table \ref{tab:params}:
 \begin{table}[!h]
 	\centering
-	\begin{tabular}{|c|c|}
+	\begin{tabular}{|c|c|c|}
 		\hline
-		Parameters          & Values      \\
+		\bfseries Parameters          & \bfseries Values   & \bfseries Description   \\
 		\hline
-		$m$          & \SI{1575}{kg}              \\
-		$I_z$         & \SI{2875}{kgm^2}               \\
-		$l_F$           & \SI{1.2}{m}               \\
-		$l_R$         & \SI{1.6}{m}               \\
-		$C_F$          & \SI{19000}{\newton/rad}      \\
-		$C_R$           & \SI{33000}{\newton/rad}  \\
-		$\tau$             & 0.2                \\
-		$V_0$           & \SI{15}{m/s}       \\
-		$V_{\text{set}}$          & \SI{20}{m/s}   \\
-		$T_s$         & \SI{0.02}{s}          \\
+		$m$          & \SI{1575}{kg}  & Mass of the vehicle            \\
+		$I_z$         & \SI{2875}{kgm^2}   & Inertia Moment            \\
+		$l_F$           & \SI{1.2}{m}     & Distance from COG to front axle         \\
+		$l_R$         & \SI{1.6}{m}    & Distance from COG to rear axle           \\
+		$C_F$          & \SI{19000}{\newton/rad}&Front cornering stiffness      \\
+		$C_R$           & \SI{33000}{\newton/rad}&Rear cornering stiffness  \\
+		$\tau$             & 0.2    & Time constant            \\
+		$V_0$           & \SI{15}{m/s} & Initial Velocity      \\
+		$V_{\text{set}}$          & \SI{20}{m/s} & Driver-set Velocity  \\
+		$T_s$         & \SI{0.02}{s} & Sampling Time
+		         \\
 		\hline
 	\end{tabular}
+	\caption{Parameters of Vehicle Dynamics and Road Curvature.}
+	\label{tab:params}
 \end{table}
 
+The paths considered for the evaluation of the proposed control strategy are:
+\begin{itemize}
+	\item a \textit{double lane change} curve (useful when a vehicle has to pass an obstacle), 
+	\item a \textit{sinusoidal} path (slalom cones scenario),
+	\item a \textit{circular/elliptic} path (NASCAR race tracks).
+\end{itemize}
+
+\subsection{Double Lane Change Path}
+In the first simulation the desired path is described in terms of the lateral position $Y_\text{ref}$ as function of the
+longitudinal position $X_\text{ref}$. The equations (\ref{eqn:double_lane_change}) describe a double lane change that have
+been employed in different tests for different scenarios i.e. \cite{Falcone2007a} \cite{Falcone2007b} \cite{Falcone2006} as follow :
+\begin{equation}
+\label{eqn:double_lane_change}
+\begin{array}{cccc}
+X_\text{ref}=V_x\cdot t, \quad\text{with}\quad t\in[0,10]\SI{}{s} \\\\
+z_1 = \displaystyle
+\frac{2.4}{50}(X_\text{ref}-27.19)-1.2;\quad
+z_2=\displaystyle\frac{2.4}{43.9}(X_\text{ref}-56.46)-1.2;\\\\
+Y_\text{ref}=\displaystyle\frac{8.1}{2}(1+\tanh(z_1)) - \frac{8.4}{2}(1+\tanh(z_2)).
+\end{array}
+\end{equation}
+Figures \ref{fig:reference_laneFollowing_curve} and \ref{fig:curvature_laneFollowing_curve} represent the first trajectory that the vehicle must perform and the curvature calculated with the previous formula \ref{eqn:curvature}.
+
+%LANE FOLLOWING SIMPLE CURVE - PATH/CURVATURE
+\begin{figure}[!h]
+	\centering
+	\begin{minipage}[t]{0.49\textwidth}
+		\includegraphics[width=\textwidth]{../../MATLAB/lane_following_curve/figure/Reference_curve.pdf}
+		\subcaption{}
+		\label{fig:reference_laneFollowing_curve}
+	\end{minipage}
+	\begin{minipage}[t]{0.49\textwidth}
+		\includegraphics[width=\textwidth]{../../MATLAB/lane_following_curve/figure/Curvature_curve.pdf}
+		\subcaption{}
+		\label{fig:curvature_laneFollowing_curve}
+	\end{minipage}
+	\caption{Desired path and curvature of the ATLASCAR2 in a simulation of \SI{10}{s}.}
+	\label{fig:laneFollowing_desired_curve}
+\end{figure}
+From the following figures, on the other hand, it can be deduced that the control system we have created allows the ATLASCAR2 to respect the imposed constraints and to reach the set objectives.
+The longitudinal and lateral components of the velocity are represented in figures \ref{fig:longitudinal_velocity_laneFollowing_curve} and \ref{fig:lateral_velocity_laneFollowing_curve}.
+In the first few seconds of the simulation $V_x$ increases thanks to a constant acceleration imposed by the first input (Figure \ref{fig:acceleration_laneFollowing_curve}).
+Later this acceleration decreases converging to zero so that at run time, we can note that $V_x$ reaches the predefined value of \SI{20}{m/s} and then it stabilizes near the driver set velocity because it continues to vary the steering angle to adapt to the path to be followed (Figure \ref{fig:steering_laneFollowing_curve}).
+The lateral component $V_y$, on the other hand, only affects during the steering phase when we are forcing a change of direction.
+%LANE FOLLOWING SIMPLE CURVE - PATH/CURVATURE
+\begin{figure}[!h]
+	\centering
+	\begin{minipage}[t]{0.49\textwidth}
+		\includegraphics[width=\textwidth]{../../MATLAB/lane_following_curve/figure/LongitudinalVelocityVsTime_curve.pdf}
+		\subcaption{Longitudinal velocity $V_x$ w.r.t. time.}
+		\label{fig:longitudinal_velocity_laneFollowing_curve}
+	\end{minipage}
+	\begin{minipage}[t]{0.49\textwidth}
+		\includegraphics[width=\textwidth]{../../MATLAB/lane_following_curve/figure/LateralVelocityVsTime_curve.pdf}
+		\subcaption{Lateral velocity $V_y$ w.r.t. time.}
+		\label{fig:lateral_velocity_laneFollowing_curve}
+	\end{minipage}
+	\begin{minipage}[t]{0.49\textwidth}
+		\includegraphics[width=\textwidth]{../../MATLAB/lane_following_curve/figure/AccelerationVsTime_curve.pdf}
+		\subcaption{Acceleration $u_1$ w.r.t. time.}
+		\label{fig:acceleration_laneFollowing_curve}
+	\end{minipage}
+	\begin{minipage}[t]{0.49\textwidth}
+		\includegraphics[width=\textwidth]{../../MATLAB/lane_following_curve/figure/SteeringAngleVsTime_curve.pdf}
+		\subcaption{Steering angle $u_2$ w.r.t. time.}
+		\label{fig:steering_laneFollowing_curve}
+	\end{minipage}
+	\begin{minipage}[t]{0.49\textwidth}
+		\includegraphics[width=\textwidth]{../../MATLAB/lane_following_curve/figure/RelativeYawAngleVsTime_curve.pdf}
+		\subcaption{Relative yaw angle $e_2$ w.r.t. time.}
+		\label{fig:relative_yaw_angle_laneFollowing_curve}
+	\end{minipage}
+	\begin{minipage}[t]{0.49\textwidth}
+		\includegraphics[width=\textwidth]{../../MATLAB/lane_following_curve/figure/LateralDeviationVsTime_curve.pdf}
+		\subcaption{Lateral deviation $e_1$ w.r.t. time.}
+		\label{fig:lateral_deviation_laneFollowing_curve}
+	\end{minipage}
+	\caption{Time signals of the ATLASCAR2 in the simulation with a curve path.}
+	\label{fig:laneFollowing_signals_curve}
+\end{figure}
+From Figures \ref{fig:lateral_deviation_laneFollowing_curve} and \ref{fig:relative_yaw_angle_laneFollowing_curve} we can notice that the lateral deviation and the relative yaw angle both converge to zero.
+That is, the ATLASCAR2 follows the road closely based on the previewed curvature.
 \subsection{Sinusoidal Path}
-
-Figures \ref{fig:reference_laneFollowing} and \ref{fig:curvature_laneFollowing} show the desired path that the car must follow and its curvature, where the former is described in terms of the lateral position $Y_{\text{ref}}$ as function of the longitudinal position $X_{\text{ref}}$ and the latter is derived according with \cite{curvature}.
+In the second simulation we assumed that the car must follow a sinusoidal path.
+We have extended the simulation time to 20 seconds in order to better understand the progress of the various signals.
+Figures \ref{fig:reference_laneFollowing} and \ref{fig:curvature_laneFollowing} show the desired path and its curvature, where the former is described in terms of the lateral position $Y_{\text{ref}}$ as function of the longitudinal position $X_{\text{ref}}$ and the latter is derived according with \cite{curvature}.
 The ATLASCAR2 is controlled to follow a sinusoidal trajectory which is given as follows:
 \begin{equation}
-X_\text{ref}=V_x\cdot t, \quad Y_\text{ref}=5\sin(X_\text{ref}/20)\quad \text{with}\quad t\in[0,20]\SI{}{s}
+X_\text{ref}=V_x\cdot t, \quad Y_\text{ref}=\displaystyle 5\sin\Big(\frac{X_\text{ref}}{20}\Big)\quad \text{with}\quad t\in[0,20]\SI{}{s}
 \end{equation}
 %LANE FOLLOWING SINUSOIDAL PATH - PATH/CURVATURE
-\begin{figure}[!t]
+\begin{figure}[!h]
 	\centering
@@
 
+In practice this type of route can be followed by the vehicle when it has to make a slalom between cones or it must go up some hairpin bends in the mountains.
 Moreover the following figures show the trend of the main parameters confirming that the control strategy used allows the vehicle to follow the path.
@@
 Figure {\ref{fig:longitudinal_velocity_laneFollowing}} shows the evolution of the vehicle longitudinal velocity.
-At the start of the simulation, this velocity is equal to the initial condition for longitudinal velocity parameter $V_0$.
+Also in this simulation the velocity is equal to the initial condition for longitudinal velocity parameter $V_0$.
 At run time, we can note that $V_x$ reaches the predefined value of \SI{20}{m/s} and then it stabilizes near the cruising speed because it continues to vary the steering angle to adapt to the path to be followed.
-Finally we presents the overall scheme for the lane following developted in Simulink depicted in Figure \ref{fig:scheme_lane_following}.
+In this scenario the lateral deviation and the relative angle yaw do not converge to zero but oscillate.
+We can however assert that this type of oscillation is due to the type of path we are following.
+Furthermore the limits of this oscillation are very small indeed: in particular the lateral deviation is less than \SI{1.5}{cm} while the maximum relative yaw angle is \SI{0.04}{rad}.
+We can therefore state that even in this case the vehicle correctly follows the lane.
 %LANE FOLLOWING SINUSOIDAL PATH - SIGNALS
@@
 		\label{fig:longitudinal_velocity_laneFollowing}
+	\end{minipage}
+	\begin{minipage}[t]{0.49\textwidth}
+			\includegraphics[width=\textwidth]{../../MATLAB/lane_following/figure/LateralVelocityVsTime.pdf}
+			\subcaption{Lateral velocity $V_y$ w.r.t. time.}
+			\label{fig:lateral_velocity_laneFollowing}
 	\end{minipage}
@@
 	\end{minipage}
-	\begin{minipage}[t]{0.49\textwidth}
-		\includegraphics[width=\textwidth]{../../MATLAB/lane_following/figure/LateralVelocityVsTime.pdf}
-		\subcaption{Lateral velocity $V_y$ w.r.t. time.}
-		\label{fig:lateral_velocity_laneFollowing}
-	\end{minipage}
 	\caption{Time signals of the ATLASCAR2 in the simulation with a sinusoidal path.}
@@
 
-%OVERALL SCHEME LANE FOLLOWING
-\begin{figure}[!h]
-	\centering
-	\includegraphics[width=\textwidth]{../figure/lane_following_AMPC.pdf}
-	\caption{Overall procedure scheme lane following.}
-	\label{fig:scheme_lane_following}
-\end{figure}
+\subsection{Circular/Elliptic Path}
+% ELLIPTIC PATH
 
-%SENSOR DYNAMICS
-\begin{figure}[!h]
-	\centering
-	\includegraphics[width=\textwidth]{../figure/lane_following_AMPC_sensor_dynamics.pdf}
-	\caption{Sensor Dynamics of the overall scheme lane following.}
-	\label{fig:scheme_lane_following_sensor_dynamics}
-\end{figure}
-
-\subsection{Simple Curve Path}
-
-%LANE FOLLOWING SIMPLE CURVE - PATH/CURVATURE
 \begin{figure}[!t]
@@
 	\begin{minipage}[t]{0.49\textwidth}
-		\includegraphics[width=\textwidth]{../../MATLAB/lane_following_curve/figure/Reference_curve.pdf}
+		\includegraphics[width=\textwidth]{../../MATLAB/lane_following_circular_path/figure/Reference_circular.pdf}
 		\subcaption{}
-		\label{fig:reference_laneFollowing_curve}
+		\label{fig:reference_laneFollowing_circular}
 	\end{minipage}
 	\begin{minipage}[t]{0.49\textwidth}
-		\includegraphics[width=\textwidth]{../../MATLAB/lane_following_curve/figure/Curvature_curve.pdf}
+		\includegraphics[width=\textwidth]{../../MATLAB/lane_following_circular_path/figure/Curvature_circular.pdf}
 		\subcaption{}
-		\label{fig:curvature_laneFollowing_curve}
+		\label{fig:curvature_laneFollowing_circular}
 	\end{minipage}
 	\caption{Desired path and curvature of the ATLASCAR2 in a simulation of \SI{10}{s}.}
-	\label{fig:laneFollowing_desired_curve}
+	\label{fig:laneFollowing_desired_circular}
 \end{figure}
 
-%LANE FOLLOWING SIMPLE CURVE - PATH/CURVATURE
+%LANE FOLLOWING ELLIPTIC - PATH/CURVATURE
 \begin{figure}[!h]
@@
 	\begin{minipage}[t]{0.49\textwidth}
-		\includegraphics[width=\textwidth]{../../MATLAB/lane_following_curve/figure/LongitudinalVelocityVsTime_curve.pdf}
+		\includegraphics[width=\textwidth]{../../MATLAB/lane_following_circular_path/figure/LongitudinalVelocityVsTime_circular.pdf}
 		\subcaption{Longitudinal velocity $V_x$ w.r.t. time.}
-		\label{fig:longitudinal_velocity_laneFollowing_curve}
+		\label{fig:longitudinal_velocity_laneFollowing_circular}
 	\end{minipage}
 	\begin{minipage}[t]{0.49\textwidth}
-		\includegraphics[width=\textwidth]{../../MATLAB/lane_following_curve/figure/AccelerationVsTime_curve.pdf}
-		\subcaption{Acceleration $u_1$ w.r.t. time.}
-		\label{fig:acceleration_laneFollowing_curve}
+		\includegraphics[width=\textwidth]{../../MATLAB/lane_following_circular_path/figure/LateralVelocityVsTime_circular.pdf}
+		\subcaption{Lateral velocity $V_y$ w.r.t. time.}
+		\label{fig:lateral_velocity_laneFollowing_circular}
 	\end{minipage}
 	\begin{minipage}[t]{0.49\textwidth}
-		\includegraphics[width=\textwidth]{../../MATLAB/lane_following_curve/figure/SteeringAngleVsTime_curve.pdf}
-		\subcaption{Steering angle $u_2$ w.r.t. time.}
-		\label{fig:steering_laneFollowing_curve}
+		\includegraphics[width=\textwidth]{../../MATLAB/lane_following_circular_path/figure/AccelerationVsTime_circular.pdf}
+		\subcaption{Acceleration $u_1$ w.r.t. time.}
+		\label{fig:acceleration_laneFollowing_circular}
 	\end{minipage}
 	\begin{minipage}[t]{0.49\textwidth}
-		\includegraphics[width=\textwidth]{../../MATLAB/lane_following_curve/figure/RelativeYawAngleVsTime_curve.pdf}
-	\subcaption{Relative yaw angle $e_2$ w.r.t. time.}
-		\label{fig:relative_yaw_angle_laneFollowing_curve}
+		\includegraphics[width=\textwidth]{../../MATLAB/lane_following_circular_path/figure/SteeringAngleVsTime_circular.pdf}
+		\subcaption{Steering angle $u_2$ w.r.t. time.}
+		\label{fig:steering_laneFollowing_circular}
 	\end{minipage}
 	\begin{minipage}[t]{0.49\textwidth}
-		\includegraphics[width=\textwidth]{../../MATLAB/lane_following_curve/figure/LateralDeviationVsTime_curve.pdf}
-		\subcaption{Lateral deviation $e_1$ w.r.t. time.}
-		\label{fig:lateral_deviation_laneFollowing_curve}
+		\includegraphics[width=\textwidth]{../../MATLAB/lane_following_circular_path/figure/RelativeYawAngleVsTime_circular.pdf}
+		\subcaption{Relative yaw angle $e_2$ w.r.t. time.}
+		\label{fig:relative_yaw_angle_laneFollowing_circular}
 	\end{minipage}
 	\begin{minipage}[t]{0.49\textwidth}
-		\includegraphics[width=\textwidth]{../../MATLAB/lane_following_curve/figure/LateralVelocityVsTime_curve.pdf}
-		\subcaption{Lateral velocity $V_y$ w.r.t. time.}
-		\label{fig:lateral_velocity_laneFollowing_curve}
+		\includegraphics[width=\textwidth]{../../MATLAB/lane_following_circular_path/figure/LateralDeviationVsTime_circular.pdf}
+		\subcaption{Lateral deviation $e_1$ w.r.t. time.}
+		\label{fig:lateral_deviation_laneFollowing_circular}
 	\end{minipage}
-	\caption{Time signals of the ATLASCAR2 in the simulation with a curve path.}
-	\label{fig:laneFollowing_signals_curve}
+	\caption{Time signals of the ATLASCAR2 in the simulation with an elliptic path.}
+	\label{fig:laneFollowing_signals_circular}
 \end{figure}

### 2019-03-15 Thesis_Latex/Thesis/Conclusions/Conclusions.tex
update thesis

@@
-\chapter*{Conclusions and Future Work}
-\addcontentsline{toc}{chapter}{Conclusions and Future Work}
+\chapter{Conclusions and Future Work}
+%\addcontentsline{toc}{chapter}{Conclusions and Future Work}
 This thesis proposes two advanced methods for short term motion planning of an autonomous car based on adaptive Model Predictive Control.

### 2019-03-15 MATLAB/6_obstacles/main_6_obstacles.m

@@ -1,0 +1,256 @@
+clear all
+close all
+clc
+
+%% ATLASCAR2 - Moving Obstacle Avoidance based on MPC
+
+car = struct;
+road = struct;
+obstacle = struct;
+
+%% Vehicle model
+
+% Parameters definition
+car.length = 5;                 % Length of the ATLASCAR2
+car.width = 2;                  % Witdh of the ATLASCAR2
+car.V = 20;                     % Constant speed of the ATLASCAR2
+car.x0 = [0; 0; 0; car.V];      % Initial conditions
+car.u0 = [0; 0];
+Ts = 0.02;                      % Sampling time
+
+% Obtain a linear plant model at the nominal operating point and convert it
+% into a discrete-time model to be used by the model predictive controller.
+[Ad,Bd,Cd,Dd,U,Y,X,DX] = ATLASCAR2ModelDT(Ts,car.x0,car.u0);
+
+dsys = ss(Ad,Bd,Cd,Dd,'Ts',Ts);          % State space
+dsys.InputName = {'Throttle','Delta'};   % Input u
+dsys.StateName = {'X','Y','Theta','V'};  % State x
+dsys.OutputName = dsys.StateName;        % Output y   
+
+%% Road and Obstacles Information
+
+road.lanes = 3;            % The road is straight and has 3 lanes.
+road.laneWidth = 4;        % Each lane is |4| meters wide.
+
+N = 6;          % Random number of obstacles (1,2,3,4,5,6)
+road.length = 150;         % length of the street
+car.minimum_dist=40;       % minimum distance between 2 cars
+  
+obstacle_random_X=obstacleRandomGenerationX(road.length,car.minimum_dist,N);
+obstacle_cresc_X=sort(obstacle_random_X);
+
+for i=1:N
+    obstacle(i).length = 5;     % The obstacles in this example are moving cars 
+    obstacle(i).width = 2;      % with the same size and shape of the ATLASCAR2
+
+    %obstacle(i).X = obstacle_cresc_X(i);         % Initial positions of the N obstacles   
+    %obstacle(i).Y = randi([-(road.laneWidth*road.lanes)/4 (road.laneWidth*road.lanes)/4],1,1);   
+   
+    obstacle(1).X = 28;
+    obstacle(2).X = 56;
+    obstacle(3).X = 94;
+    obstacle(4).X = 122; 
[…]

### 2019-03-15 MATLAB/6_obstacles/obstacleComputeCustomConstraint.m

@@ -1,0 +1,99 @@
+function [E,F,G,constraintSlope,constraintIntercept] = obstacleComputeCustomConstraint(x,detection,obstacle,laneWidth,lanes,N,m)
+%% Compute custom constraints for the obstacle.
+
+carX = x(1);
+carY = x(2);
+% Compute constraints only if an obstacle is detected. Otherwise, set
+% constraint to lower road boundary (the inactive constraint).
+if(obstacle(m).Y(end)<=0)
+   for i=1:N 
+   slope(i) = ( (obstacle(i).rlSafeY - carY)/(obstacle(i).rlSafeX - carX) );    
+   pop(i) = ( (obstacle(i).rrSafeY - carY)/(obstacle(i).rrSafeX - carX) );
+   if detection(:,m)
+    % If the ATLASCAR2 is to the left of the obstacle
+    if (carX<=obstacle(i).rlSafeX)
+        % if the ATLASCAR2 is already in the adjacent lane, use the safety
+        % zone as the constraint.
+        if (carY>obstacle(i).rlSafeY)
+            constraintSlope(i) = 0;
+            constraintIntercept(i) = obstacle(i).rlSafeY;
+        else
+            % The ATLASCAR2 must be above the line formed from the ATLASCAR2 to
+            % safe zone corner for left passing.
+            constraintSlope(i) = tan(atan2(slope(i),1));
+            constraintIntercept(i) = obstacle(i).rlSafeY - constraintSlope(i)*obstacle(i).rlSafeX;
+        end
+    % If the ATLASCAR2 is parallel to the obstacle, use the safety zone as
+    % the constraint.
+    elseif  ((carX>obstacle(i).rlSafeX) && (carX<=obstacle(i).flX))
+        constraintSlope(i) = 0;
+        constraintIntercept(i) = obstacle(i).rlSafeY; 
+    % If the ATLASCAR2 has passed the obstacle, use the inactive constraint
+    % to go back to the center lane.
+    else 
+        constraintSlope(i) = 0;
+        constraintIntercept(i) = obstacle(i).rlSafeY; %-laneWidth*lanes/2;
+    end
+    % If there is another obstacles in the detection zone se the safety zone as
+    % the constraint. Otherwise use the inactive constraint
+    % to go back to the center lane.
+    elseif(detection(:,:)==zeros(1,N))
[…]

### 2019-03-15 MATLAB/6_obstacles/obstacleDetect.m

@@ -1,0 +1,42 @@
+function [detection m]= obstacleDetect(x,obstacle,laneWidth,N)
+% Detect when the vehicle sees an obstacle.
+
+carX = x(1);
+carY = x(2);
+
+% Compute the distance between each obstacles and the ATLASCAR2
+for i=1:N
+    dist2Obstacle(i)= sqrt( (obstacle(i).X(end)- carX)^2 + (obstacle(i).Y(end) - carY)^2 );    
+end
+mindist2Obstacle = min(dist2Obstacle);
+
+% Choose the obstacle closest to the ATLASCAR2  
+index=0;
+for i=1:length(dist2Obstacle)
+    if (dist2Obstacle(i)==mindist2Obstacle)
+    index=i;
+    end
+end
+m=index; % represents the index of the closest obstacle 
+
+if(carX>=obstacle(m).flX)
+    if (m~=N)    
+        m=m+1;
+    else
+        m=m;
+    end
+end
+
+
+for i=1:N
+    flagCloseEnough(i) = (dist2Obstacle(i) < obstacle(i).DetectionDistance);
+    flagInLane(i)    = ( abs(obstacle(i).Y(end) - carY) < 2*laneWidth );
+    detection(i) = ( flagCloseEnough(i) && (carX < obstacle(i).frSafeX) && flagInLane(i));
+end
+end
+        
+  
+
+
+
+

### 2019-03-15 MATLAB/6_obstacles/obstaclePlotInitialCondition.m

@@ -1,0 +1,47 @@
+function f = obstaclePlotInitialCondition(car,obstacle,road,N)
+
+% Create figure
+
+f = figure;
+
+% Starting position of the ATLASCAR2 ('green cross')
+X0 = car.x0(1);
+Y0 = car.x0(2);
+plot(X0,Y0,'gx');
+hold on 
+grid on
+grid minor
+axis equal
+
+% ATLASCAR2 initialization
+p = patch([X0-car.length/2 X0-car.length/2 X0+car.length/2 X0+car.length/2], [Y0-car.width/2, Y0+car.width/2, Y0+car.width/2, Y0-car.width/2], [0 1 0]); 
+
+% Obstacles initialization with their safe zones
+for i=1:N
+    o(i) = patch([obstacle(i).X-obstacle(i).length/2 obstacle(i).X-obstacle(i).length/2 obstacle(i).X+obstacle(i).length/2 obstacle(i).X+obstacle(i).length/2], [obstacle(i).Y-obstacle(i).width/2 obstacle(i).Y+obstacle(i).width/2 obstacle(i).Y+obstacle(i).width/2 obstacle(i).Y-obstacle(i).width/2], [1 0 0]);
+    safe(i) = patch([obstacle(i).flSafeX obstacle(i).frSafeX obstacle(i).rlSafeX obstacle(i).rrSafeX],[obstacle(i).flSafeY obstacle(i).frSafeY obstacle(i).rrSafeY obstacle(i).rlSafeY],'--');
+    safe(i).FaceColor='none';
+    safe(i).EdgeColor='[1 0 0]';
+    safe(i).LineStyle='--';
+end
+
+% For the animation remove the initializations
+delete(p)
+    for i=1:N
+        delete(o(i))
+        delete(safe(i))
+    end
+
+% Plot the lanes.
+X = [X0-car.length;50;obstacle(end).X+obstacle(end).length];
+Y = [2;2;2];
+line(X,Y,'LineStyle','--','Color','k');
+X = [X0-car.length;50;obstacle(end).X+obstacle(end).length];
+Y = [-2;-2;-2];
+line(X,Y,'LineStyle','--','Color','k');
+
+% Reset the axis.
+axis([X0-car.length 120 -road.laneWidth*road.lanes/2 road.laneWidth*road.lanes/2]);
+xlabel('X');
+ylabel('Y');
+%title('ATLASCAR2 Moving Obstacle Avoidance');

### 2019-03-15 MATLAB/6_obstacles/obstacleRandomGenerationX.m

@@ -1,0 +1,25 @@
+function obstacle_random_X = obstacleRandomGenerationX(length,distance,N)
+
+% This function creates random positions in the x coordinate for the obstacles 
+% where the parameters are the length of the street, the minimum distance between two
+% consecutive obstacles and the number of the cars. 
+
+E=length-(N-1)*distance;  % excess space for points
+
+% generate N+1 random values; 
+
+Ro=rand(N+1,1);     % random vector
+
+% normalize so that the extra space is consumed
+% extra value is the amount of extra space "unused"
+
+Rn=E*Ro(1:N)/sum(Ro); % normalize
+
+% spacing of points
+
+S=distance*ones(N,1)+Rn;  
+
+% location of points, adjusted to "start" at 0
+obstacle_random_X=cumsum(S)-1;
+
+end

### 2019-03-15 MATLAB/6_obstacles/obstacles6Results.m

@@ -1,0 +1,91 @@
+%% Plot results for adaptive MPC
+
+% Velocity vs Time
+h1 = figure ('Position',[100, 100, 340, 230], 'PaperPositionMode','auto');
+plot(T,ympc(:,4));
+hold on;
+grid on;
+grid minor;
+%title('\textbf{Velocity ($v$) vs Time}','Interpreter','latex');
+xlabel('Time [s]','Interpreter','latex');
+ylabel('Velocity [m/s]','Interpreter','latex');
+pos1 = get(h1,'Position');
+set(h1,'PaperPositionMode','Auto','PaperUnits','Points','PaperSize',[pos1(3)*0.8, pos1(4)-40])
+print(h1,'figure\VelocityVsTime','-dpdf','-r0')
+hold off
+pause(2)
+
+% LateralPosition vs Time
+h2 = figure ('Position',[100, 100, 340, 230], 'PaperPositionMode','auto');
+plot(T,ympc(:,2));
+hold on;
+grid on;
+grid minor;
+%title('\textbf{Lateral Position ($y$) vs Time}','Interpreter','latex');
+xlabel('Time [s]','Interpreter','latex');
+ylabel('Lateral Position [m]','Interpreter','latex');
+pos2 = get(h2,'Position');
+set(h2,'PaperPositionMode','Auto','PaperUnits','Points','PaperSize',[pos2(3)*0.8, pos2(4)-40])
+print(h2,'figure\LateralPositionVsTime','-dpdf','-r0')
+hold off
+pause(2)
+
+% Theta vs Time
+h3 = figure ('Position',[100, 100, 340, 230], 'PaperPositionMode','auto');
+plot(T,ympc(:,3));
+hold on;
+grid on;
+grid minor;
+%title('\textbf{Heading Angle($\theta$) vs Time}','Interpreter','latex');
+xlabel('Time [s]','Interpreter','latex');
+ylabel('Heading Angle [rad]','Interpreter','latex');
+pos3 = get(h3,'Position');
+set(h3,'PaperPositionMode','Auto','PaperUnits','Points','PaperSize',[pos3(3)*0.8, pos3(4)-40])
+print(h3,'figure\HeadingAngleVsTime','-dpdf','-r0')
+hold off
+pause(2)
+
+% Throttle vs Time
+h5 = figure ('Position',[100, 100, 340, 230], 'PaperPositionMode','auto');
+plot(T,umpc(:,1));
+hold on;
[…]

### 2019-03-15 MATLAB/lane_following/LaneFollowingGetCurvature.m

@@ -35,6 +35,7 @@ pos1 = get(h1,'Position');
 set(h1,'PaperPositionMode','Auto','PaperUnits','Points','PaperSize',[pos1(3)*0.8, pos1(4)-40])
 print(h1,'figure\Reference','-dpdf','-r0')
 hold off
+pause(2)
 
 % Desired curvature
 DX = gradient(Xref,0.1);
@@ -53,8 +54,9 @@ grid on
 grid minor
 %title('\textbf{Curvature}','Interpreter','latex');
 xlabel('Time [s]','Interpreter','latex');
-ylabel('Curvature [m]','Interpreter','latex');
-pos2 = get(hcurv,'Position');
-set(hcurv,'PaperPositionMode','Auto','PaperUnits','Points','PaperSize',[pos2(3)*0.8, pos2(4)-40])
+ylabel('Curvature','Interpreter','latex');
+poscurv = get(hcurv,'Position');
+set(hcurv,'PaperPositionMode','Auto','PaperUnits','Points','PaperSize',[poscurv(3)*0.8, poscurv(4)-40])
 print(hcurv,'figure\Curvature','-dpdf','-r0')
 hold off
+pause(2)

### 2019-03-15 MATLAB/lane_following/LaneFollowingResults.m

@@ -79,7 +79,7 @@ pos5 = get(h5,'Position');
 set(h5,'PaperPositionMode','Auto','PaperUnits','Points','PaperSize',[pos5(3)*0.8, pos5(4)-40])
 print(h5,'figure\LongitudinalVelocityVsTime','-dpdf','-r0')
 hold off
-
+pause(2)
 
 %% Lateral Velocity
 
@@ -95,6 +95,8 @@ pospp = get(hpp,'Position');
 set(hpp,'PaperPositionMode','Auto','PaperUnits','Points','PaperSize',[pospp(3)*0.8, pospp(4)-40])
 print(hpp,'figure\LateralVelocityVsTime','-dpdf','-r0')
 hold off
+pause(2)
+
 %% Local function: Get data from simulation
 function [e1,e2,delta,accel,vx,vy] = getData(logsout)
 e1 = logsout.getElement('Lateral Deviation');    % lateral deviation

### 2019-03-15 MATLAB/lane_following_circular_path/LaneFollowingGetCurvature.m

@@ -7,9 +7,9 @@ function rho = LaneFollowingGetCurvature(Vx,time)
 %
 % Outputs:
 %   rho: previewed curvature
-
-Xref=200*cos(Vx*time/60);
-Yref=200*sin(Vx*time/60);
+Ts = 0.02;
+Xref=15*cos(Vx*time/60);
+Yref=30*sin(Vx*time/60);
 % Xref = Vx*time;
 % 
 % % Desired Y position
@@ -22,19 +22,21 @@ hold on
 grid on
 grid minor
 axis equal
-title('\textbf{Desired Path}','Interpreter','latex');
+%title('\textbf{Desired Path}','Interpreter','latex');
 xlabel('X-coordinate [m]','Interpreter','latex');
 ylabel('Y-coordinate [m]','Interpreter','latex');
 pos = get(h,'Position');
 set(h,'PaperPositionMode','Auto','PaperUnits','Points','PaperSize',[pos(3)*0.8, pos(4)-40])
 print(h,'figure\Reference_circular','-dpdf','-r0')
 hold off
+pause(2)
 
 % Desired curvature
-DX = gradient(Xref,0.1);
-DY = gradient(Yref,0.1);
-D2Y = gradient(DY,0.1);
-curvature = DX.*D2Y./(DX.^2+DY.^2).^(3/2);
+DX = gradient(Xref,Ts);
+DY = gradient(Yref,Ts);
+D2X = gradient(DX,Ts);
+D2Y = gradient(DY,Ts);
+curvature = (DX.*D2Y-D2X.*DY)./(DX.^2+DY.^2).^(3/2);
 
 % Stored curvature (as input for LKA)
 rho.time = time;
@@ -45,10 +47,11 @@ plot(rho.time,rho.signals.values)
 hold on
 grid on
 grid minor
-title('\textbf{Curvature}','Interpreter','latex');
+%title('\textbf{Curvature}','Interpreter','latex');
 xlabel('Time [s]','Interpreter','latex');
-ylabel('Curvature [m]','Interpreter','latex');
-pos = get(hcurv,'Position');
-set(hcurv,'PaperPositionMode','Auto','PaperUnits','Points','PaperSize',[pos(3)*0.8, pos(4)-40])
+ylabel('Curvature','Interpreter','latex');
+poscurv = get(hcurv,'Position');
[…]

### 2019-03-15 MATLAB/lane_following_circular_path/LaneFollowingResults.m

@@ -8,77 +8,95 @@ function LaneFollowingResults(logsout)
 %% Steering Angle vs Time
 
 h1 = figure ('Position',[100, 100, 340, 230], 'PaperPositionMode','auto');
+plot(delta_ampc.Values.time,delta_ampc.Values.Data);
 hold on;
 grid on;
 grid minor;
-plot(delta_ampc.Values.time,delta_ampc.Values.Data);
-title('\textbf{Steering Angle (u$_2$) vs Time}','Interpreter','latex');
+%title('\textbf{Steering Angle (u$_2$) vs Time}','Interpreter','latex');
 xlabel('Time [s]','Interpreter','latex');
 ylabel('Steering angle [rad]','Interpreter','latex');
-pos = get(h1,'Position');
-set(h1,'PaperPositionMode','Auto','PaperUnits','Points','PaperSize',[pos(3), pos(4)-40])
+pos1 = get(h1,'Position');
+set(h1,'PaperPositionMode','Auto','PaperUnits','Points','PaperSize',[pos1(3)*0.8, pos1(4)-40])
 print(h1,'figure\SteeringAngleVsTime_circular','-dpdf','-r0')
 hold off
 pause(2)
 %% Lateral deviation vs Time
 
 h2 = figure ('Position',[100, 100, 340, 230], 'PaperPositionMode','auto');
+plot(e1_ampc.Values.time,e1_ampc.Values.Data);
 hold on;
 grid on;
 grid minor;
-plot(e1_ampc.Values.time,e1_ampc.Values.Data);
-title('\textbf{Lateral Deviation (e$_1$) vs Time}','Interpreter','latex');
+%title('\textbf{Lateral Deviation (e$_1$) vs Time}','Interpreter','latex');
 xlabel('Time [s]','Interpreter','latex');
 ylabel('Lateral Deviation [m]','Interpreter','latex');
-pos = get(h2,'Position');
-set(h2,'PaperPositionMode','Auto','PaperUnits','Points','PaperSize',[pos(3), pos(4)-41])
+pos2 = get(h2,'Position');
+set(h2,'PaperPositionMode','Auto','PaperUnits','Points','PaperSize',[pos2(3)*0.8, pos2(4)-40])
 print(h2,'figure\LateralDeviationVsTime_circular','-dpdf','-r0')
 hold off
 pause(2)
+
 %% Relative Yaw Angle vs Time
 
[…]

### 2019-03-15 MATLAB/lane_following_curve/LaneFollowingGetCurvature.m

@@ -26,6 +26,7 @@ pos0 = get(h0,'Position');
 set(h0,'PaperPositionMode','Auto','PaperUnits','Points','PaperSize',[pos0(3)*0.8, pos0(4)-40])
 print(h0,'figure\Reference_curve','-dpdf','-r0')
 hold off
+pause(2)
 
 % Desired curvature
 DX = gradient(Xref,0.1);
@@ -49,3 +50,4 @@ poscurv = get(hcurv,'Position');
 set(hcurv,'PaperPositionMode','Auto','PaperUnits','Points','PaperSize',[poscurv(3)*0.8, poscurv(4)-40])
 print(hcurv,'figure\Curvature_curve','-dpdf','-r0')
 hold off
+pause(2)

### 2019-03-15 MATLAB/lane_following_curve/LaneFollowingResults.m

@@ -94,6 +94,7 @@ pos6 = get(h6,'Position');
 set(h6,'PaperPositionMode','Auto','PaperUnits','Points','PaperSize',[pos6(3)*0.8, pos6(4)-40])
 print(h6,'figure\LateralVelocityVsTime_curve','-dpdf','-r0')
 hold off
+pause(2)
 %% Local function: Get data from simulation
 function [e1,e2,delta,accel,vx,vy] = getData(logsout)
 e1 = logsout.getElement('Lateral Deviation');    % lateral deviation

### 2019-03-15 MATLAB/lane_following_curve/main_lane_following_curve.m

@@ -40,9 +40,12 @@ LaneFollowingGenerateAMPC;
 % function |LaneFollowingResults|
 sim(mdl)
 logsout1 = logsout;
-closLaneFollowingResults(logsout1,Yref)
+LaneFollowingResults(logsout1,Yref)
 print -slane_following_AMPC -dpdf lane_following_AMPC.pdf
 movefile('lane_following_AMPC.pdf','figure')
 
 print -slane_following_AMPC/Sensor_Dynamics -dpdf lane_following_AMPC_sensor_dynamics.pdf
 movefile('lane_following_AMPC_sensor_dynamics.pdf','figure')
+
+print -slane_following_AMPC/Vehicle_Dynamics -dpdf lane_following_AMPC_vehicle_dynamics.pdf
+movefile('lane_following_AMPC_vehicle_dynamics.pdf','figure')

### 2019-03-15 MATLAB/no_overtaking/main_no_overtaking.m

@@ -1,0 +1,248 @@
+clear all
+close all
+clc
+
+%% ATLASCAR2 - Moving Obstacle Avoidance based on MPC
+
+car = struct;
+road = struct;
+obstacle = struct;
+
+%% Vehicle model
+
+% Parameters definition
+car.length = 5;                 % Length of the ATLASCAR2
+car.width = 2;                  % Witdh of the ATLASCAR2
+car.V = 20;                     % Constant speed of the ATLASCAR2
+car.x0 = [0; 0; 0; car.V];      % Initial conditions
+car.u0 = [0; 0];
+Ts = 0.02;                      % Sampling time
+
+% Obtain a linear plant model at the nominal operating point and convert it
+% into a discrete-time model to be used by the model predictive controller.
+[Ad,Bd,Cd,Dd,U,Y,X,DX] = ATLASCAR2ModelDT(Ts,car.x0,car.u0);
+
+dsys = ss(Ad,Bd,Cd,Dd,'Ts',Ts);          % State space
+dsys.InputName = {'Throttle','Delta'};   % Input u
+dsys.StateName = {'X','Y','Theta','V'};  % State x
+dsys.OutputName = dsys.StateName;        % Output y   
+
+%% Road and Obstacles Information
+
+road.lanes = 3;            % The road is straight and has 3 lanes.
+road.laneWidth = 4;        % Each lane is |4| meters wide.
+road.length = 130;
+N = 3;                     % Number of obstacles
+
+for i=1:N
+    obstacle(i).length = 5;    % The obstacles in this example are moving cars 
+    obstacle(i).width = 2;     % with the same size and shape of the ATLASCAR2
+
+    obstacle(i).X = 33+3;      % Initial positions of the N obstacles   
+    obstacle(i).Y =-10+5*i; % (in this example the obstacles are DYNAMIC)    
+    
+    obstacle(i).safeDistanceX = obstacle(i).length;    % Length equal to two car lengths
+    obstacle(i).safeDistanceY = road.laneWidth;        % Width equal to two lane widths
+    
+    obstacle(i).space = 0.16;                
+    obstacle(i).velocity = obstacle(i).space/Ts;      % Velocity of the obstacle 8 m/s (0.16/Ts)         
+    
[…]

### 2019-03-15 MATLAB/no_overtaking/no_overtaking_Results.m

@@ -1,0 +1,95 @@
+%% Plot results for adaptive MPC
+
+% Velocity vs Time
+h1 = figure ('Position',[100, 100, 340, 230], 'PaperPositionMode','auto');
+plot(T,ympc(:,4));
+hold on;
+grid on;
+grid minor;
+%title('\textbf{Velocity ($v$) vs Time}','Interpreter','latex');
+xlabel('Time [s]','Interpreter','latex');
+ylabel('Velocity [m/s]','Interpreter','latex');
+axis([0 10 6.5 20.5])
+pos1 = get(h1,'Position');
+set(h1,'PaperPositionMode','Auto','PaperUnits','Points','PaperSize',[pos1(3)*0.8, pos1(4)-40])
+print(h1,'figure\VelocityVsTime','-dpdf','-r0')
+hold off
+pause(2)
+
+% Y_mpc vs Time
+h2 = figure ('Position',[100, 100, 340, 230], 'PaperPositionMode','auto');
+plot(T,ympc(:,2));
+hold on;
+grid on;
+grid minor;
+%title('\textbf{Lateral Position ($y$) vs Time}','Interpreter','latex');
+xlabel('Time [s]','Interpreter','latex');
+ylabel('Lateral Position [m]','Interpreter','latex');
+axis([0 10 -3 3])
+pos2 = get(h2,'Position');
+set(h2,'PaperPositionMode','Auto','PaperUnits','Points','PaperSize',[pos2(3)*0.8, pos2(4)-40])
+print(h2,'figure\LateralPositionVsTime','-dpdf','-r0')
+hold off
+pause(2)
+
+% Theta vs Time
+h3 = figure ('Position',[100, 100, 340, 230], 'PaperPositionMode','auto');
+plot(T,ympc(:,3));
+hold on;
+grid on;
+grid minor;
+%title('\textbf{Heading Angle ($\theta$) vs Time}','Interpreter','latex');
+xlabel('Time [s]','Interpreter','latex');
+ylabel('Heading Angle [rad]','Interpreter','latex');
+axis([0 10 -0.00005 0.00005])
+pos3 = get(h3,'Position');
+set(h3,'PaperPositionMode','Auto','PaperUnits','Points','PaperSize',[pos3(3)*0.8, pos3(4)-40])
+print(h3,'figure\HeadingAngleVsTime','-dpdf','-r0')
+hold off
+pause(2)
+
+% Throttle vs Time
[…]

### 2019-03-15 MATLAB/no_overtaking/obstacleComputeCustomConstraint.m

@@ -1,0 +1,241 @@
+function [E,F,G,constraintSlope,constraintIntercept] = obstacleComputeCustomConstraint(x,detection,obstacle,laneWidth,lanes,N,m)
+%% Compute custom constraints for the obstacle.
+
+carX = x(1);
+carY = x(2);
+
+% Compute constraints only if an obstacle is detected. Otherwise, set
+% constraint to lower road boundary (the inactive constraint).
+% If the street is full of obstacles the ATLASCAR2 must adapt its speed to 
+% that of the nearest obstacle; otherwise it can overcome the obstacles.
+
+% Compute the distance between the obstacles
+for i=1:N    
+    distObs(i)=sqrt((obstacle(m).X(end)-obstacle(i).X(end))^2 +(obstacle(m).Y(end)-obstacle(i).Y(end))^2);
+end
+maxObs = max(distObs);
+n = find(distObs==maxObs);
+distObs(m)=[]; % remove the distance of the obstacle m with itself.
+
+if (distObs>30)
+    x_max = obstacle(m).X(end)+1000;
+    x_min = carX;
+    % LEFT OVERTAKING
+    if(obstacle(m).Y(end)<=0)
+        for i=1:N 
+   slope(i) = ( (obstacle(i).rlSafeY - carY)/(obstacle(i).rlSafeX - carX) );    
+   pop(i) = ( (obstacle(i).rrSafeY - carY)/(obstacle(i).rrSafeX - carX) );
+   if detection(:,m)
+    % If the ATLASCAR2 is to the left of the obstacle
+    if (carX<=obstacle(i).rlSafeX)
+        % if the ATLASCAR2 is already in the adjacent lane, use the safety
+        % zone as the constraint.
+        if (carY>obstacle(i).rlSafeY)
+            constraintSlope(i) = 0;
+            constraintIntercept(i) = obstacle(i).rlSafeY;
+        else
+            % The ATLASCAR2 must be above the line formed from the ATLASCAR2 to
+            % safe zone corner for left passing.
+            constraintSlope(i) = tan(atan2(slope(i),1));
+            constraintIntercept(i) = obstacle(i).rlSafeY - constraintSlope(i)*obstacle(i).rlSafeX;
+        end
+    % If the ATLASCAR2 is parallel to the obstacle, use the safety zone as
+    % the constraint.
[…]

### 2019-03-15 MATLAB/no_overtaking/obstaclePlotInitialCondition.m

@@ -1,0 +1,49 @@
+function f = obstaclePlotInitialCondition(car,obstacle,road,N)
+
+% Create figure
+
+f = figure;
+
+% Starting position of the ATLASCAR2 ('green cross')
+X0 = car.x0(1);
+Y0 = car.x0(2);
+plot(X0,Y0,'gx');
+hold on 
+grid on
+%grid minor
+axis equal
+
+% ATLASCAR2 initialization
+p = patch([X0-car.length/2 X0-car.length/2 X0+car.length/2 X0+car.length/2], [Y0-car.width/2, Y0+car.width/2, Y0+car.width/2, Y0-car.width/2], [0 1 0]); 
+
+% Obstacles initialization with their safe zones
+for i=1:N
+    o(i) = patch([obstacle(i).X-obstacle(i).length/2 obstacle(i).X-obstacle(i).length/2 obstacle(i).X+obstacle(i).length/2 obstacle(i).X+obstacle(i).length/2], [obstacle(i).Y-obstacle(i).width/2 obstacle(i).Y+obstacle(i).width/2 obstacle(i).Y+obstacle(i).width/2 obstacle(i).Y-obstacle(i).width/2], [1 0 0]);
+    safe(i) = patch([obstacle(i).flSafeX obstacle(i).frSafeX obstacle(i).rlSafeX obstacle(i).rrSafeX],[obstacle(i).flSafeY obstacle(i).frSafeY obstacle(i).rrSafeY obstacle(i).rlSafeY],'--');
+    safe(i).FaceColor='none';
+    safe(i).EdgeColor='[1 0 0]';
+    safe(i).LineStyle='--';
+end
+
+% For the animation remove the initializations
+delete(p)
+    for i=1:N
+        delete(o(i))
+        delete(safe(i))
+    end
+
+% Plot the lanes.
+X = [X0-car.length; 50; road.length];
+Y = [2;2;2];
+line(X,Y,'LineStyle','--','Color','k');
+X = [X0-car.length; 50; road.length];
+Y = [-2;-2;-2];
+line(X,Y,'LineStyle','--','Color','k');
+
+% Reset the axis.
+axis([X0-car.length 100 -road.laneWidth*road.lanes/2 road.laneWidth*road.lanes/2]);
+xlabel('X');
+ylabel('Y');
+title('ATLASCAR2 Moving Obstacle Avoidance');
+
+

### 2019-03-15 MATLAB/one_obstacle_right_overtaking/plot_one_moving_obstacle_right.m

@@ -1,0 +1,91 @@
+%% Plot results for one moving obstacles
+
+% Velocity vs Time
+h1 = figure ('Position',[100, 100, 340, 230], 'PaperPositionMode','auto');
+plot(T,ympc(:,4));
+hold on;
+grid on;
+grid minor;
+%title('\textbf{Velocity ($v$) vs Time}','Interpreter','latex');
+xlabel('Time [s]','Interpreter','latex');
+ylabel('Velocity [m/s]','Interpreter','latex');
+pos1 = get(h1,'Position');
+set(h1,'PaperPositionMode','Auto','PaperUnits','Points','PaperSize',[pos1(3)*0.8, pos1(4)-40])
+print(h1,'figure\VelocityVsTime','-dpdf','-r0')
+hold off
+pause(2)
+
+% Y_mpc vs Time
+h2 = figure ('Position',[100, 100, 340, 230], 'PaperPositionMode','auto');
+plot(T,ympc(:,2));
+hold on;
+grid on;
+grid minor;
+%title('\textbf{Lateral Position ($y$) vs Time}','Interpreter','latex');
+xlabel('Time [s]','Interpreter','latex');
+ylabel('Lateral Position [m]','Interpreter','latex');
+pos2 = get(h2,'Position');
+set(h2,'PaperPositionMode','Auto','PaperUnits','Points','PaperSize',[pos2(3)*0.8, pos2(4)-40])
+print(h2,'figure\LateralPositionVsTime','-dpdf','-r0')
+hold off
+pause(2)
+
+% Theta vs Time
+h3 = figure ('Position',[100, 100, 340, 230], 'PaperPositionMode','auto');
+plot(T,ympc(:,3));
+hold on;
+grid on;
+grid minor;
+%title('\textbf{Heading Angle ($\theta$) vs Time}','Interpreter','latex');
+xlabel('Time [s]','Interpreter','latex');
+ylabel('Heading Angle [rad]','Interpreter','latex');
+pos3 = get(h3,'Position');
+set(h3,'PaperPositionMode','Auto','PaperUnits','Points','PaperSize',[pos3(3)*0.8, pos3(4)-40])
+print(h3,'figure\HeadingAngleVsTime','-dpdf','-r0')
+hold off
+pause(2)
+
+% Throttle vs Time
+h4 = figure ('Position',[100, 100, 340, 230], 'PaperPositionMode','auto');
+plot(T,umpc(:,1));
+hold on;
[…]

### 2019-03-15 MATLAB/three_obstacles_no_overtaking/three_obstaclesResults.m

@@ -13,7 +13,8 @@ axis([0 10 6.5 20.5])
 pos1 = get(h1,'Position');
 set(h1,'PaperPositionMode','Auto','PaperUnits','Points','PaperSize',[pos1(3)*0.8, pos1(4)-40])
 print(h1,'figure\VelocityVsTime','-dpdf','-r0')
-
+hold off
+pause(2)
 
 % Y_mpc vs Time
 h2 = figure ('Position',[100, 100, 340, 230], 'PaperPositionMode','auto');
@@ -27,7 +28,8 @@ ylabel('Lateral Position [m]','Interpreter','latex');
 pos2 = get(h2,'Position');
 set(h2,'PaperPositionMode','Auto','PaperUnits','Points','PaperSize',[pos2(3)*0.8, pos2(4)-40])
 print(h2,'figure\LateralPositionVsTime','-dpdf','-r0')
-
+hold off
+pause(2)
 
 % Theta vs Time
 h3 = figure ('Position',[100, 100, 340, 230], 'PaperPositionMode','auto');
@@ -42,6 +44,7 @@ pos3 = get(h3,'Position');
 set(h3,'PaperPositionMode','Auto','PaperUnits','Points','PaperSize',[pos3(3)*0.8, pos3(4)-40])
 print(h3,'figure\HeadingAngleVsTime','-dpdf','-r0')
 hold off
+pause(2)
 
 % Throttle vs Time
 h4 = figure ('Position',[100, 100, 340, 230], 'PaperPositionMode','auto');
@@ -56,6 +59,7 @@ pos4 = get(h4,'Position');
 set(h4,'PaperPositionMode','Auto','PaperUnits','Points','PaperSize',[pos4(3)*0.8, pos4(4)-40])
 print(h4,'figure\ThrottleVsTime','-dpdf','-r0')
 hold off
+pause(2)
 
 % Steering Angle vs Time
 h5 = figure ('Position',[100, 100, 340, 230], 'PaperPositionMode','auto');
@@ -70,3 +74,19 @@ pos5 = get(h5,'Position');
 set(h5,'PaperPositionMode','Auto','PaperUnits','Points','PaperSize',[pos5(3)*0.8, pos5(4)-40])
 print(h5,'figure\SteeringAngleVsTime','-dpdf','-r0')
 hold off
+pause(2)
+
+% x_mpc vs Time
+hx = figure ('Position',[100, 100, 340, 230], 'PaperPositionMode','auto');
+plot(T,ympc(:,1));
[…]

### 2019-03-25 Thesis_Latex/Thesis/Chapter4/Chapter4.tex
update thesis

@@
 Figure \ref{fig:flowchart} shows a conditional state machine designed for higher-level behavior planning.
-
 % FLOWCHART
-\begin{figure}[!h]
+\begin{figure}[!b]
 	\centering
@@
 \section{Simulation Results}
-The performances of the proposed adaptive MPC based vehicle control method are demonstrated in three simulation examples.
+The performances of the proposed adaptive MPC based vehicle control method are demonstrated in four simulation examples.
 We tried to choose parameters that were as close as possible to a real situation: the sampling time used in the discretization of the system is $T_s=\SI{0.02}{s}$ while the values of the prediction and the control horizon are respectively $p_H=25$ and $c_H=5$.
 In all simulations, the distance between the front and rear axles is $C_L=\SI{5}{m}$ and the width of the vehicle is $C_W=\SI{2}{m}$.
-The saturation ranges of the control inputs are: the steering angle lies in $\big[-\frac{\pi}{30}, +\frac{\pi}{30}\big]$ rad/s while in order to prevent the ATLASCAR2 from accelerating or decelerating too quickly, we impose an hard constraint of \SI{2.5}{m/s^2} on the throttle rate of change.
+The saturation ranges of the control inputs are: the steering angle rate of change lies in $\big[-\frac{\pi}{30}, +\frac{\pi}{30}\big]$ rad/s while in order to prevent the ATLASCAR2 from accelerating or decelerating too quickly, we impose an hard constraint of \SI{2.5}{m/s^2} on the throttle rate of change.
 Moreover we are using a constant reference signal for the velocity of $v=\SI{20}{m/s}$ ($\approx\SI{72}{km/h}$).
-Blue paths in Figures \ref{fig:obstacleAvoidance_one_obstacle}, \ref{fig:obstacleAvoidance_random}, \ref{fig:braking} are known only at the end of the simulations.
+Note that the blue paths in Figures \ref{fig:obstacleAvoidance_one_obstacle}, \ref{fig:obstacleAvoidance_random}, 	\ref{fig:obstacleAvoidance_six_obstacles}, \ref{fig:obstacleAvoidance_no_overtaking} and \ref{fig:braking} are known only at the end of the simulations but we have decided to report the entire trajectory that the vehicle will perform in every frame.
+The overall framework for a multiple moving obstacle avoidance is depicted in the Figure \ref{fig:MovingObstacleAvoidance}.
+% OVERALL SCHEME ONE MOVING OBSTACLE
+\begin{figure}[!h]
+	\centering
+	\includegraphics[width=\textwidth]{../figure/MovingObstacleAvoidance.pdf}
+	\caption{Overall procedure scheme moving obstacle avoidance.}
+	\label{fig:MovingObstacleAvoidance}
+\end{figure}
+
+All the simulations are done in MATLAB and Simulink.
+MATLAB is used for loop-shaping.
+Simulink is used as a testing environment.
+Moreover, the MATLAB Model Predictive Toolbox is used.
+The controller will be tested in the same Simulink environment as the classical controller.
+Note that all these blocks have been implemented through the S-functions (types of dynamically linked subroutines for Simulink).
 
@@
 (Figure \ref{fig:obstacleAvoidance_one_obstacle}) the ATLASCAR2 drives in the middle of the center lane while the road is completely free and when there is an obstacle, the vehicle passes it only using the right lane (the same simulation can be launched so that the car goes over to the left fast lane).
-In other words if the ATLASCAR2 is already in the adjacent lane, it uses the safety zone as the constraint, otherwise the vehicle must be above the line formed from the ATLASCAR2 to safe zone corner for right passing.
-If the vehicle is parallel to the obstacle, it  uses the safety zone as the constraint and finally if it has passed the obstacle, it uses the inactive constraint to go back to the center lane.
-Algorithm \ref{alg:rightOvertaking} summarizes the main steps to compute custom constraints for the obstacle; when the vehicle detects the obstacle, the constraints are computed.
-In this simulation only the first three constraints are necessary because there is space for the overtaking without braking (the fourth and fifth constraints don't change).
-
+In this example the obstacle has a constant speed of \SI{8}{m/s} and moves in the same direction as the ATLASCAR2.
+We assume that the LIDAR sensor can detect an obstacle \SI{30}{m} in front of the vehicle.
+The red dashed block around the obstacle represents a safe zone used to evaluate the restrictions so that, even if there is a small margin of error in the manuever, there is always a safe distance between the ATLASCAR2 and the nearby vehicle.
 % ONE MOVING OBSTACLE
@@
 
+Algorithm \ref{alg:rightOvertaking} summarizes the main steps to compute custom constraints for the obstacle; when the vehicle detects the obstacle, the constraints are computed.
+% ALGORITHM FOR RIGHT OVERTAKING OF ONE MOVING OBSTACLE
+\begin{algorithm}[!h]
+	\caption{Right Overtaking if an obstacle is detected}
+	\small
+	\begin{algorithmic}[1]
+		\Function{RightOvertaking}{car, obstacle, road}
+		\State $x_\text{min} \gets \text{car}X $,  $x_\text{max} \gets +\infty$;
+		\State obsYrr = Obstacle.RearRightSafeY;
+		\State obsXrr = Obstacle.RearRightSafeX;
+		\If{ATLASCAR2 is behind the obstacle} 
+		\If{ATLASCAR2 is in the adjacent lane}
+		\State $cS \gets 0$; $cI \gets \text{obsYrr}$; \label{line:safety_zone}
+		\Else
+		\State $cS \gets \text{tan}(\text{atan2}(\frac{\text{obsYrr}-\text{ carY}}{\text{obsXrr}-\text{carX}},1))$; \label{line:corner1}
+		\State $cI \gets \text{obsYrr}-cS*\text{obsXrr}$;\label{line:corner2}
+		\EndIf
+		\Else
+		\If{ATLASCAR2 is parallel to the obstacle}
+		\State $cS \gets 0$; $cI \gets \text{obsYrr}$;\label{line:safety_zone_parallel}
+		\Else
+		\State $cS \gets 0$; $cI \gets W/2$;\label{line:inactive}
+		\EndIf
+		\EndIf
+		\State \Return $x_\text{min}$, $x_\text{max}$, $cI$, $cS$
+		\State \text{Update matrices $\vec{E},\vec{F}$ and $\vec{G}$}
+		\EndFunction
+	\end{algorithmic}
+	\label{alg:rightOvertaking}
+\end{algorithm}
+
+In other words the constraints are evaluated as follows:
+\begin{itemize}
+	\item if the ATLASCAR2 is already in the adjacent lane, it uses the safety zone as the constraint (line \ref{line:safety_zone});
+	\item otherwise the vehicle must be above the line formed from the ATLASCAR2 to safe zone corner for right passing (lines \ref{line:corner1} and \ref{line:corner2});
+	\item if the vehicle is parallel to the obstacle (line \ref{line:safety_zone_parallel}), it  uses the safety zone as the constraint;
+	\item finally if it has passed the obstacle, it uses the inactive constraint to go back to the center lane (line \ref{line:inactive}).
+\end{itemize}
+
+In this simulation only the first three constraints are necessary because there is enough space for the overtaking without braking (the fourth and fifth constraints don't change).
+The first two constraints are constant and represent the left and right boundary of the road (upper and lower bound on the $y$-coordinate).
+The third constraint is useful to define a region where the vehicle can navigate; it consists of two parameters ($cS$ and $cI$) that are calculated in the algorithm depending on where the vehicle is located with respect to the obstacle.
+After calculating these parameters, the matrices $\vec{E}$, $\vec{F}$ and $\vec{G}$ are updated so that the MPC can process the new optimal input.
+
+Finally we can analyze time signals of the ATLASCAR2 in the simulation of right overtaking of one moving obstacle.
+Figures \ref{fig:longitudinal_one_moving} and \ref{fig:lateral_one_moving} illustrate the longitudinal and lateral position of the vehicle with respect to time, showing a constant trend with respect to the $x$ component, while a shift from 0 can be noted regarding the $y$ coordinate due to the overcoming of the obstacle.
+To confirm a uniform trend, the speed of the ATLASCAR2 remains fairly constant.
+Obviously it is possible to note from Figure \ref{fig:velocity_one_moving} that the velocity decreases very little during the first part of the overtaking phase, and then come back to the cruising speed in the second part.
+Instead from the remaining Figures \ref{fig:throttle_one_moving}, \ref{fig:delta_one_moving} and \ref{fig:theta_one_moving} we can observe that the throttle $T$ and the steering angle $\delta$ respect the limits we imposed while the heading angle $\theta$ is used to describe the direction the ATLASCAR2 is pointing.
 % RESULTS ONE MOVING OBSTACLE
@@
 
-% ALGORITHM FOR RIGHT OVERTAKING OF ONE MOVING OBSTACLE
-\begin{algorithm}%[b]
-	\caption{Right Overtaking if an obstacle is detected}
-	\small
-	\begin{algorithmic}[1]
-		\Function{RightOvertaking}{car, obstacle, road}
-		\State $x_\text{min} \gets \text{car}X $,  $x_\text{max} \gets +\infty$;
-		\State obsYrr = obstacle.RearRightSafeY;
-		\State obsXrr = obstacle.RearRightSafeX;
-		\If{ATLASCAR2 is behind the obstacle} 
-		\If{ATLASCAR2 is in the adjacent lane}
-		\State $cS \gets 0$; $cI \gets \text{obsYrr}$;
-		\Else
-		\State $cS \gets \text{tan}(\text{atan2}(\frac{\text{obsYrr}-\text{ carY}}{\text{obsXrr}-\text{carX}},1))$;
-		\State $cI \gets \text{obsYrr}-cS*\text{obsXrr}$;
-		\EndIf
-		\Else
-		\If{ATLASCAR2 is parallel to the obstacle}
-		\State $cS \gets 0$; $cI \gets \text{obsYrr}$;
-		\Else
-		\State $cS \gets 0$; $cI \gets W/2$;
-		\EndIf
-		\EndIf
-		\State \Return $x_\text{min}$, $x_\text{max}$, $cI$, $cS$
-		\EndFunction
-	\end{algorithmic}
-	\label{alg:rightOvertaking}
-\end{algorithm}
-
-% OVERALL SCHEME ONE MOVING OBSTACLE
-\begin{figure}[!h]
-	\centering
-	\includegraphics[width=\textwidth]{../figure/MovingObstacleAvoidance.pdf}
-	\caption{Overall procedure scheme moving obstacle avoidance.}
-	\label{fig:MovingObstacleAvoidance}
-\end{figure}
 %
 \subsection{Multiple Moving Obstacles}
-For a second test, additional obstacles were added to make the scenario more complex (Figure \ref{fig:obstacleAvoidance_random}).
+For a second test, additional obstacles were added to make the scenario more complex like in a real highway.
+
+Initially we assumed that the obstacles were located at a distance greater than the LIDAR detection range which is \SI{30}{m}.
+In this way every time the vehicle overtakes a car, it applies the inactive constraints to go back to the center lane.
+
+This situation is represented in Figure \ref{fig:obstacleAvoidance_random}
+where there are three different scenarios with $N = 2,3 \text{ and } 4$ moving obstacles that drive with a constant velocity of \SI{8}{m/s} in the opposite direction with respect to the ATLASCAR2.
+The vehicle is capable of overtaking the obstacles on the right or left depending on their positions with respect to the road.
+If the $y$-coordinate of the closest obstacle is greater than 0, then the vehicle overtakes to the right, otherwise the overtaking takes place on the left lane.
 % MULTIPLE MOVING OBSTACLE
@@
 
-The vehicle is capable of overtaking the obstacles on the right or left depending on their positions with respect to the road.
-If the $y$-coordinate of the closest obstacle is greater than 0, then the vehicle overtakes to the right, otherwise the overtaking takes place on the left lane.
-We also hypothesized that the obstacles move at different speeds but that they are initially at a common distance; they can have a uniform motion or a uniformely accelerated motion.
-In case two obstacles are too close during the simulation and their distance is less than the detection range, which is \SI{30}{m}, the ATLASCAR2 perceives the objects as a single entity and adapts to the situation.
+In the Figure \ref{fig:obstacleAvoidance_six_obstacles} we also hypothesized there are six moving obstacles that can drive at different speeds but initially they are at a common distance; they can have a uniform motion or a uniformely accelerated motion.
+We also improved the code infact in case two obstacles are too close during the simulation and their distance is less than the detection range, which is \SI{30}{m}, the ATLASCAR2 perceives the objects as a single entity and adapts to the situation.
 The same test can be done with the obstacles that drive in the same direction as the vehicle but to better assess and demonstrate results we decided to show a very unusual scenario.
-
 % SIX MOVING OBSTACLES
@@
 
+Also in this case we reported time signals of the ATLASCAR2 in the simulation with six moving obstacles (Figure \ref{fig:components_six_moving_obstacles}).
+The most articulated scenario makes the signals more complex with respect to time.
+However, we can see that the speed is just under \SI{20}{m/s} while the inputs continue to respect the imposed boundaries.
+Note that the vehicle manages to overcome all the obstacles without encountering any difficulty since there is always an empty lane.
 % RESULTS SIX MOVING OBSTACLES
@@
 \subsection{No Overtaking}
+We have seen that as long as there is always a free lane, the obstacle avoidance algorithm works correctly.
+In the case that there are too many obstacles on the road, which do not allow overtaking, the vehicle must adapt to the situation and it must slow down in order not to collide.
+In the algorithm that we have developed it is possible to calculate two other restrictions which permit this deceleration in the case that it is strictly necessary.
+To better understand how these restrictions change the speed and deceleration of the ATLASCAR2, we simulated a scenario (Figure \ref{fig:obstacleAvoidance_no_overtaking}) in which there are 3 obstacles at an initial distance of \SI{35}{m} occupying the 3 different lanes, all with the same $x$-coordinate and the same velocity of \SI{8}{m/s}.
+When these obstacles enter in the vehicle's detection range, it checks whether there is enough space to perform the overtaking maneuver by calculating the distance between the obstacles.
+Noting that it is not possible to overtake, our vehicle must decelerate in order not to crash into the nearest car.
+To do this, the MPC must take into account the position of the vehicle $x_\text{min}$ and the position of the closest obstacle $x_\text{max}$.
 %NO OVERTAKING
@@
 
+Also in this simulation the reference speed of the car is \SI{20}{m/s}, but after $\simeq$\SI{1,5}{s}, the obstacles enter in the detection range and as we can see from the Figure \ref{fig:velocity_no_overtaking} the velocity decreases rapidly to adapt to that of the nearest vehicle.
+It is possible to observe that this decrease in speed, which subsequently remains constant at \SI{8}{m/s}, is due to a strong negative throttle impulse (Figure \ref{fig:throttle_no_overtaking}).
+Finally, we note that the steering angle $\delta$ and heading angle $\theta$ remain at zero: there is only a very small oscillatory trend due to measurement errors as the vehicle always requires a minimum change of direction.
+Finally we imposed a safety distance that must always be respected between two vehicles so that if the obstacle brakes sharply the ATLASCAR2 can avoid the impact.
+It is very difficult to achieve reliable calculations of the braking distance as road conditions and the tyres' grip can vary greatly.
+An easy formula to calculate the braking distance is the following one:
+\begin{equation}
+	d = \frac{v^2}{250\times f}
+\end{equation}
+where:
+\begin{itemize}
+	\item $d$ is the braking distance in metres (to be calculated).
+	\item $v$ is the speed in \SI{}{km/h};
+	\item 250 is the fixed figure which is always used;
+	\item $f$ is the coefficient of friction, approx. 0.8 on dry asphalt and 0.1 on ice.
+\end{itemize}
 % RESULTS NO OVERTAKING
@@
 \subsection{Vehicle Braking and Obstacles Overtaking}
-Finally we have improved the code related to the mixed Input/Output constraints so that in the case there are 3 obstacles that block the road and drive at a lower speed than the ATLASCAR2, the velocity of the vehicle decreases in order to prevent the collision.
+Finally we have improved the code related to the mixed Input/Output constraints.
 Figure \ref{fig:braking} depicts a simulation in which there are 3 obstacles at the same $x$-coordinate.
 Two obstacles have a constant speed of \SI{8}{m/s} while the one on the left lane of \SI{15}{m/s}.
-In this particular case it is essential to consider the fourth and the fifth restriction in order to allow the ATLASCAR2 to slow down without colliding with the cars in front.
-The fifth constraint is simply the position of the ATLASCAR2 that updates at each interval, while the fourth constraint, until there is a free lane, is the position of the closest obstacle (both the positions are with respect to the global reference frame).
-In the calculation of the fourth constraint is necessary  to consider the speed at which the vehicle and the obstacle are moving in order to keep a safe distance.
-In particular three parameters have been identified as the key
-factors computing the safe distance between cars:
-\begin{itemize}
-	\item detection range of the ATLASCAR2;
-	\item velocities of the vehicle and the obstacle;
-	\item distance between the cars.
-\end{itemize}
-
 % BRAKING THREE OBSTACLE
@@
 
+In this particular case it is essential to consider the fourth and the fifth restriction in order to allow the ATLASCAR2 to slow down without colliding with the cars in front.
+The fifth constraint is simply the position of the ATLASCAR2 that updates at each interval, while the fourth constraint, until there is a free lane, is the position of the closest obstacle (both the positions are with respect to the global reference frame).
+In the calculation of the fourth constraint is necessary  to consider the speed at which the vehicle and the obstacle are moving in order to keep a safe distance.
 At the beginning, the vehicle moves with the reference velocity of $v=\SI{20}{m/s}$.
@@
 % RESULTS BRAKING THREE OBSTACLES
-\begin{figure}[!t] %vs changes to t instead of b
+\begin{figure}[!h] %vs changes to t instead of b
 	\begin{minipage}[t]{0.5\textwidth}

### 2019-03-25 Thesis_Latex/Thesis/Chapter5/Chapter5.tex
update thesis

@@
 \chapter{Lane Following}
+In this chapter we present a Lane Following alghorithm based on Adaptive Model Predictive Control.
+First we introduced the case-study model, then we designed the controller and the overall procedure scheme.
+Finally we verified the proposed strategy in different scenarios.
 \section{Problem Formulation}
@@
 \begin{array}{cc}
-	\SI{-3}{m/s}\leq a\leq\SI{3}{m/s}\;,\\\\
+	\SI{-3}{m/s^2}\leq a\leq\SI{3}{m/s^2}\;,\\\\
 	\SI{-1.13}{rad}\leq \delta \leq \SI{1.13}{rad}\;,
@@
 \begin{figure}[!h]
-	\centering
-	\begin{minipage}[t]{0.49\textwidth}
+	\begin{minipage}[t]{0.5\textwidth}
 		\includegraphics[width=\textwidth]{../../MATLAB/lane_following_curve/figure/Reference_curve.pdf}
@@
 	\end{minipage}
-	\begin{minipage}[t]{0.49\textwidth}
+	\begin{minipage}[t]{0.5\textwidth}
 		\includegraphics[width=\textwidth]{../../MATLAB/lane_following_curve/figure/Curvature_curve.pdf}
@@
 	\end{minipage}
-	\caption{Desired path and curvature of the ATLASCAR2 in a simulation of \SI{10}{s}.}
+	\caption{Desired double lane change path and its curvature of the ATLASCAR2 in a simulation of \SI{10}{s} with initial position in $(0,0)$.}
 	\label{fig:laneFollowing_desired_curve}
@@
 \begin{figure}[!h]
-	\centering
-	\begin{minipage}[t]{0.49\textwidth}
+	\begin{minipage}[t]{0.5\textwidth}
 		\includegraphics[width=\textwidth]{../../MATLAB/lane_following_curve/figure/LongitudinalVelocityVsTime_curve.pdf}
@@
 	\end{minipage}
-	\begin{minipage}[t]{0.49\textwidth}
+	\begin{minipage}[t]{0.5\textwidth}
 		\includegraphics[width=\textwidth]{../../MATLAB/lane_following_curve/figure/LateralVelocityVsTime_curve.pdf}
@@
 	\end{minipage}
-	\begin{minipage}[t]{0.49\textwidth}
+	\begin{minipage}[t]{0.5\textwidth}
 		\includegraphics[width=\textwidth]{../../MATLAB/lane_following_curve/figure/AccelerationVsTime_curve.pdf}
@@
 	\end{minipage}
-	\begin{minipage}[t]{0.49\textwidth}
+	\begin{minipage}[t]{0.5\textwidth}
 		\includegraphics[width=\textwidth]{../../MATLAB/lane_following_curve/figure/SteeringAngleVsTime_curve.pdf}
@@
 	\end{minipage}
-	\begin{minipage}[t]{0.49\textwidth}
+	\begin{minipage}[t]{0.5\textwidth}
 		\includegraphics[width=\textwidth]{../../MATLAB/lane_following_curve/figure/RelativeYawAngleVsTime_curve.pdf}
@@
 	\end{minipage}
-	\begin{minipage}[t]{0.49\textwidth}
+	\begin{minipage}[t]{0.5\textwidth}
 		\includegraphics[width=\textwidth]{../../MATLAB/lane_following_curve/figure/LateralDeviationVsTime_curve.pdf}
@@
 	\end{minipage}
-	\caption{Time signals of the ATLASCAR2 in the simulation with a curve path.}
+	\caption{Time signals of the ATLASCAR2 in the simulation with a double lane change
+		 path.}
 	\label{fig:laneFollowing_signals_curve}
@@
 That is, the ATLASCAR2 follows the road closely based on the previewed curvature.
+\newpage
 \subsection{Sinusoidal Path}
@@
 \begin{equation}
-X_\text{ref}=V_x\cdot t, \quad Y_\text{ref}=\displaystyle 5\sin\Big(\frac{X_\text{ref}}{20}\Big)\quad \text{with}\quad t\in[0,20]\SI{}{s}
+\begin{aligned}
+X_\text{ref}&=V_x\cdot t,\quad \text{with}\quad t\in[0,20]\SI{}{s}\\
+Y_\text{ref}&=\displaystyle 5\sin\Big(\frac{X_\text{ref}}{20}\Big) 
+\end{aligned}
 \end{equation}
@@
 \begin{figure}[!h]
-	\centering
-	\begin{minipage}[t]{0.49\textwidth}
+	\begin{minipage}[t]{0.5\textwidth}
 		\includegraphics[width=\textwidth]{../../MATLAB/lane_following/figure/Reference.pdf}
@@
 	\end{minipage}
-	\begin{minipage}[t]{0.49\textwidth}
+	\begin{minipage}[t]{0.5\textwidth}
 		\includegraphics[width=\textwidth]{../../MATLAB/lane_following/figure/Curvature.pdf}
@@
 	\end{minipage}
-	\caption{Desired path and curvature of the ATLASCAR2 in a simulation of \SI{20}{s}.}
+	\caption{Desired sinusoidal path and its curvature of the ATLASCAR2 in a simulation of \SI{20}{s} with initial position in $(0,0)$.}
 	\label{fig:laneFollowing_desired}
@@
 \begin{figure}[!h]
-	\centering
-	\begin{minipage}[t]{0.49\textwidth}
+	\begin{minipage}[t]{0.5\textwidth}
 		\includegraphics[width=\textwidth]{../../MATLAB/lane_following/figure/LongitudinalVelocityVsTime.pdf}
@@
 	\end{minipage}
-	\begin{minipage}[t]{0.49\textwidth}
+	\begin{minipage}[t]{0.5\textwidth}
 			\includegraphics[width=\textwidth]{../../MATLAB/lane_following/figure/LateralVelocityVsTime.pdf}
@@
 	\end{minipage}
-	\begin{minipage}[t]{0.49\textwidth}
+	\begin{minipage}[t]{0.5\textwidth}
 		\includegraphics[width=\textwidth]{../../MATLAB/lane_following/figure/AccelerationVsTime.pdf}
@@
 	\end{minipage}
-	\begin{minipage}[t]{0.49\textwidth}
+	\begin{minipage}[t]{0.5\textwidth}
 		\includegraphics[width=\textwidth]{../../MATLAB/lane_following/figure/SteeringAngleVsTime.pdf}
@@
 	\end{minipage}
-	\begin{minipage}[t]{0.49\textwidth}
+	\begin{minipage}[t]{0.5\textwidth}
 		\includegraphics[width=\textwidth]{../../MATLAB/lane_following/figure/RelativeYawAngleVsTime.pdf}
@@
 	\end{minipage}
-	\begin{minipage}[t]{0.49\textwidth}
+	\begin{minipage}[t]{0.5\textwidth}
 		\includegraphics[width=\textwidth]{../../MATLAB/lane_following/figure/LateralDeviationVsTime.pdf}
@@
 \end{figure}
-
+\newpage
 \subsection{Circular/Elliptic Path}
+In the last simulation we considered that the vehicle must follow an elliptic path with a semi-major axis of \SI{30}{m} and semi-minor axis of \SI{15}{m} depicted in Figure \ref{fig:reference_laneFollowing_circular}.
+Also in this case the simulation time is \SI{20}{s}.
+To describe the elliptic path and to evaluate its curvature, depicted in Figure \ref{fig:curvature_laneFollowing_circular}, the equations are the follows:
+\begin{equation}
+	\begin{aligned}
+	X_\text{ref}&=\displaystyle 15\cos\Big(\frac{V_x\cdot t}{60}\Big)\\
+	Y_\text{ref}&=\displaystyle 30\sin\Big(\frac{V_x\cdot t}{60}\Big)  
+	\end{aligned} \quad\text{with}\quad t\in[0,20]\SI{}{s}
+\end{equation}
 % ELLIPTIC PATH
-
 \begin{figure}[!t]
-	\centering
-	\begin{minipage}[t]{0.49\textwidth}
+	\begin{minipage}[t]{0.5\textwidth}
 		\includegraphics[width=\textwidth]{../../MATLAB/lane_following_circular_path/figure/Reference_circular.pdf}
@@
 	\end{minipage}
-	\begin{minipage}[t]{0.49\textwidth}
+	\begin{minipage}[t]{0.5\textwidth}
 		\includegraphics[width=\textwidth]{../../MATLAB/lane_following_circular_path/figure/Curvature_circular.pdf}
@@
 	\end{minipage}
-	\caption{Desired path and curvature of the ATLASCAR2 in a simulation of \SI{10}{s}.}
+	\caption{Desired elliptic path and its curvature of the ATLASCAR2 in a simulation of \SI{20}{s} with initial position in $(0,30)$.}
 	\label{fig:laneFollowing_desired_circular}
@@
 \begin{figure}[!h]
-	\centering
-	\begin{minipage}[t]{0.49\textwidth}
+	\begin{minipage}[t]{0.5\textwidth}
 		\includegraphics[width=\textwidth]{../../MATLAB/lane_following_circular_path/figure/LongitudinalVelocityVsTime_circular.pdf}
@@
 	\end{minipage}
-	\begin{minipage}[t]{0.49\textwidth}
+	\begin{minipage}[t]{0.5\textwidth}
 		\includegraphics[width=\textwidth]{../../MATLAB/lane_following_circular_path/figure/LateralVelocityVsTime_circular.pdf}
@@
 	\end{minipage}
-	\begin{minipage}[t]{0.49\textwidth}
+	\begin{minipage}[t]{0.5\textwidth}
 		\includegraphics[width=\textwidth]{../../MATLAB/lane_following_circular_path/figure/AccelerationVsTime_circular.pdf}
@@
 	\end{minipage}
-	\begin{minipage}[t]{0.49\textwidth}
+	\begin{minipage}[t]{0.5\textwidth}
 		\includegraphics[width=\textwidth]{../../MATLAB/lane_following_circular_path/figure/SteeringAngleVsTime_circular.pdf}
@@
 	\end{minipage}
-	\begin{minipage}[t]{0.49\textwidth}
+	\begin{minipage}[t]{0.5\textwidth}
 		\includegraphics[width=\textwidth]{../../MATLAB/lane_following_circular_path/figure/RelativeYawAngleVsTime_circular.pdf}
@@
 	\end{minipage}
-	\begin{minipage}[t]{0.49\textwidth}
+	\begin{minipage}[t]{0.5\textwidth}
 		\includegraphics[width=\textwidth]{../../MATLAB/lane_following_circular_path/figure/LateralDeviationVsTime_circular.pdf}

### 2019-03-25 MATLAB/6_obstacles/main_6_obstacles.m

@@ -217,9 +217,9 @@ figure(f)
 plot(ympc(:,1),ympc(:,2),'-b');
 
 %% Animation
-% writerObj = VideoWriter('animation.avi'); % Name it.
-% writerObj.FrameRate = 1/Ts; % How many frames per second.
-% open(writerObj);
+ %writerObj = VideoWriter('animation.avi'); % Name it.
+ %writerObj.FrameRate = 1/Ts; % How many frames per second.
+ %open(writerObj);
 
 for k = 1:length(saveSlope) 
     hold on 
@@ -239,8 +239,8 @@ for k = 1:length(saveSlope)
         safe(i).LineStyle='--';
     end
     
-%     frame = getframe(gcf);
-%     writeVideo(writerObj, frame);
+  %   frame = getframe(gcf);
+ %    writeVideo(writerObj, frame);
 %     print('figure\6_obstacles_2','-dpdf','-r0')
     pause(80/car.V/length(T))
     delete(p)

### 2019-03-25 MATLAB/6_obstacles/obstaclePlotInitialCondition.m

@@ -2,7 +2,8 @@ function f = obstaclePlotInitialCondition(car,obstacle,road,N)
 
 % Create figure
 
-f = figure;
+f = figure ('Position',[100, 100, 700, 110], 'PaperPositionMode','auto');
+
 
 % Starting position of the ATLASCAR2 ('green cross')
 X0 = car.x0(1);
@@ -45,3 +46,13 @@ axis([X0-car.length 120 -road.laneWidth*road.lanes/2 road.laneWidth*road.lanes/2
 xlabel('X');
 ylabel('Y');
 %title('ATLASCAR2 Moving Obstacle Avoidance');
+ax = gca;
+outerpos = ax.OuterPosition;
+ti = ax.TightInset; 
+left = outerpos(1) + ti(1);
+bottom = outerpos(2) + ti(2);
+ax_width = outerpos(3) - ti(1) - ti(3);
+ax_height = outerpos(4) - ti(2) - ti(4);
+ax.Position = [left bottom ax_width ax_height];
+pos = get(f,'Position');
+set(f,'PaperPositionMode','Auto','PaperUnits','Points','PaperSize',[pos(3), pos(4)])

### 2019-03-25 MATLAB/one_obstacle_left_overtaking/main_one_obstacle_left.m

@@ -181,24 +181,22 @@ mpcverbosity(status);
 % Plot the trajectory of the ATLASCAR2 (blue line) and the third mixed
 % I/O constraints (dashed green lines) during the obstacle avoidance
 % maneuver.
-% figure(f)
+figure(f)
 % for k = 1:length(saveSlope)
 %     X = [0;50;100];
 %     Y = saveSlope(k)*X + saveIntercept(k);
 %     line(X,Y,'LineStyle','--','Color','g' )
 % end    
-% plot(ympc(:,1),ympc(:,2),'-b');
+plot(ympc(:,1),ympc(:,2),'-b');
 % axis([0 ympc(end,1) -road.laneWidth*road.lanes/2 road.laneWidth*road.lanes/2]) % reset axis
 
 %% Animation
-% writerObj = VideoWriter('animation.avi');
-% writerObj.FrameRate = 1/Ts; 
-% open(writerObj);
+ %writerObj = VideoWriter('animation.avi');
+ %writerObj.FrameRate = 1/Ts; 
+ %open(writerObj);
 
 for k = 1:length(saveSlope) 
     hold on 
-    grid on
-    grid minor
     
     % ATLASCAR2 green rectangle
     p = patch([ympc(k,1)-car.length/2 ympc(k,1)-car.length/2 ympc(k,1)+car.length/2 ympc(k,1)+car.length/2], [ympc(k,2)-car.width/2, ympc(k,2)+car.width/2, ympc(k,2)+car.width/2, ympc(k,2)-car.width/2], [0 1 0]);
@@ -211,8 +209,8 @@ for k = 1:length(saveSlope)
     safe.EdgeColor='[1 0 0]';
     safe.LineStyle='--';
 
-%     frame = getframe(gcf); 
-%     writeVideo(writerObj, frame);
+  %   frame = getframe(gcf); 
+ %    writeVideo(writerObj, frame);
     
     pause(80/car.V/length(T))
     delete(p)

### 2019-03-25 MATLAB/one_obstacle_left_overtaking/obstaclePlotInitialCondition.m

@@ -2,7 +2,7 @@ function f = obstaclePlotInitialCondition(car,obstacle,road)
 
 % Create figure
 
-f = figure;
+f = figure ('Position',[100, 100, 700, 100], 'PaperPositionMode','auto');
 
 % Plot the ATLASCAR2
 
@@ -46,6 +46,17 @@ line(X,Y,'LineStyle','--','Color','k' );
 axis([X0-car.length 90 -road.laneWidth*road.lanes/2 road.laneWidth*road.lanes/2]);
 xlabel('X');
 ylabel('Y');
-title('ATLASCAR2 Moving Obstacle Avoidance');
+xlabel('X');
+ylabel('Y');
+ax = gca;
+outerpos = ax.OuterPosition;
+ti = ax.TightInset; 
+left = outerpos(1) + ti(1);
+bottom = outerpos(2) + ti(2);
+ax_width = outerpos(3) - ti(1) - ti(3);
+ax_height = outerpos(4) - ti(2) - ti(4);
+ax.Position = [left bottom ax_width ax_height];
+pos = get(f,'Position');
+set(f,'PaperPositionMode','Auto','PaperUnits','Points','PaperSize',[pos(3), pos(4)])
 
 

### 2019-03-25 MATLAB/three_obstacles_no_overtaking/main_three_obstacles_no_overtaking.m

@@ -212,15 +212,14 @@ figure(f)
 plot(ympc(:,1),ympc(:,2),'-b');
 
 %% Animation
-% writerObj = VideoWriter('animation3.avi'); % Name it.
-% writerObj.FrameRate = 1/Ts; % How many frames per second.
-% open(writerObj);
+ %writerObj = VideoWriter('animation_nowhite.avi'); % Name it.
+ %writerObj.FrameRate = 1/Ts; % How many frames per second.
+ %open(writerObj);
 
 for k = 1:length(saveSlope) 
     hold on 
-    grid on
+    %grid on
     %grid minor
-    
     % ATLASCAR2 green rectangle
     p = patch([ympc(k,1)-car.length/2 ympc(k,1)-car.length/2 ympc(k,1)+car.length/2 ympc(k,1)+car.length/2], [ympc(k,2)-car.width/2, ympc(k,2)+car.width/2, ympc(k,2)+car.width/2, ympc(k,2)-car.width/2], [0 1 0]);
     rotate(p, [0 0 1], rad2deg(asin(ympc(k,3))), [ympc(k,1)-car.length/2 ympc(k,2)-car.width/2 0]);
@@ -234,8 +233,8 @@ for k = 1:length(saveSlope)
         safe(i).LineStyle='--';
     end
     
-   %  frame = getframe(gcf);
-   %  writeVideo(writerObj, frame);
+     %frame = getframe(gcf);
+     %writeVideo(writerObj, frame);
       % print('figure\braking_4','-dpdf','-r0')
     pause(80/car.V/length(T))
     delete(p)

### 2019-03-25 MATLAB/three_obstacles_no_overtaking/obstaclePlotInitialCondition.m

@@ -2,7 +2,7 @@ function f = obstaclePlotInitialCondition(car,obstacle,road,N)
 
 % Create figure
 
-f = figure;
+f = figure ('Position',[100, 100, 800, 110], 'PaperPositionMode','auto');
 
 % Starting position of the ATLASCAR2 ('green cross')
 X0 = car.x0(1);
@@ -10,9 +10,8 @@ Y0 = car.x0(2);
 plot(X0,Y0,'gx');
 hold on 
 grid on
-%grid minor
+grid minor
 axis equal
-
 % ATLASCAR2 initialization
 p = patch([X0-car.length/2 X0-car.length/2 X0+car.length/2 X0+car.length/2], [Y0-car.width/2, Y0+car.width/2, Y0+car.width/2, Y0-car.width/2], [0 1 0]); 
 
@@ -44,6 +43,13 @@ line(X,Y,'LineStyle','--','Color','k');
 axis([X0-car.length road.length -road.laneWidth*road.lanes/2 road.laneWidth*road.lanes/2]);
 xlabel('X');
 ylabel('Y');
-title('ATLASCAR2 Moving Obstacle Avoidance');
-
-
+ax = gca;
+outerpos = ax.OuterPosition;
+ti = ax.TightInset; 
+left = outerpos(1) + ti(1);
+bottom = outerpos(2) + ti(2);
+ax_width = outerpos(3) - ti(1) - ti(3);
+ax_height = outerpos(4) - ti(2) - ti(4);
+ax.Position = [left bottom ax_width ax_height];
+pos = get(f,'Position');
+set(f,'PaperPositionMode','Auto','PaperUnits','Points','PaperSize',[pos(3), pos(4)])

### 2019-03-29 Thesis_Latex/Thesis/Chapter2/Chapter2.tex
update thesis

@@
 \chapter{Literature Review}
+In this chapter we introduce the literature survey of the various algorithms used for robot navigation.
+The navigation methods are divided into two kinds of control: global path planning and local motion control.
+First we analyze these two types of strategies and then we describe the current situation of Model Prediction which is the control method that we have adopted.
+\section{Global Path Searching Method}
+Global path planning uses information about a priori model or a map of the enviroment to evaluate the shortest path that allows the motion from a starting point to the goal position.
+There are a lot of path planning algorithms, like cell decomposition, road map or potential field, where the calculation of a complete trajectory from a start position to one or more goal positions can be computed off-line.
+However they produce a reliable path if and only if the map of the enviroment is already available.
+So, this prior knowledge of the space where the robot can move, must be accessible.
+The most famous method developed for global navigation is the Dijkstra algorithm \cite{Dijkstra:1959}.
+In recent years, an evolution of this method called A* is one of the most used \cite{Hart:1968}: this algorithm gives a complete and optimal global path in static enviroments.
+However, it was upgraded in D* \cite{Stentz93optimaland} for efficient online searching of a dynamic enviroment, which gives sequences of path points in the known or partially known space.
+The basic idea of these two methods is the following: minimizing their cost functions, these strategies have the capability of a quickly  redesign when the condistions of the space change, to guarantee an optimal solution of the trajectory from the starting point to the goal location.
+\subsection{The A* Algorithm}
+\subsection{The D* Algorithm}
+\section{Local Motion Control}
+Local Motion Control is related to the real-time motion of the robot inside in unknown enviroment, where monitoring with the sensors, it can detect where are the obstacles and generate a motion to avoid the collision with them.
+\subsection{Potential Field Method}
+\subsection{Dynamic Window Approach}
+\subsection{VFF Approach for Obstacle Avoidance}
+\section{MPC in Autonomous Driving}
 \cite{4651075}

### 2019-03-29 Thesis_Latex/Thesis/Chapter4/Chapter4.tex
update thesis

@@
 
-In this particular case it is essential to consider the fourth and the fifth restriction in order to allow the ATLASCAR2 to slow down without colliding with the cars in front.
+In this particular case it is essential to consider the fourth and the fifth restrictions in order to allow the ATLASCAR2 to slow down without colliding with the cars in front.
 The fifth constraint is simply the position of the ATLASCAR2 that updates at each interval, while the fourth constraint, until there is a free lane, is the position of the closest obstacle (both the positions are with respect to the global reference frame).

### 2019-03-29 Thesis_Latex/Thesis/Chapter5/Chapter5.tex
update thesis

@@
 We can therefore state that even in this case the vehicle correctly follows the lane.
+\newpage
 %LANE FOLLOWING SINUSOIDAL PATH - SIGNALS
@@
 	\end{minipage}
-	\begin{minipage}[t]{0.5\textwidth}
+	\begin{minipage}[t]{0.49\textwidth}
 		\includegraphics[width=\textwidth]{../../MATLAB/lane_following/figure/AccelerationVsTime.pdf}
@@
 	\end{minipage}
-	\begin{minipage}[t]{0.5\textwidth}
+	\begin{minipage}[t]{0.49\textwidth}
 		\includegraphics[width=\textwidth]{../../MATLAB/lane_following/figure/SteeringAngleVsTime.pdf}
@@
 	\end{minipage}
-	\begin{minipage}[t]{0.5\textwidth}
+	\begin{minipage}[t]{0.49\textwidth}
 		\includegraphics[width=\textwidth]{../../MATLAB/lane_following/figure/RelativeYawAngleVsTime.pdf}
@@
 	\end{minipage}
-	\begin{minipage}[t]{0.5\textwidth}
+	\begin{minipage}[t]{0.49\textwidth}
 		\includegraphics[width=\textwidth]{../../MATLAB/lane_following/figure/LateralDeviationVsTime.pdf}
@@
 Also in this case the simulation time is \SI{20}{s}.
-To describe the elliptic path and to evaluate its curvature, depicted in Figure \ref{fig:curvature_laneFollowing_circular}, the equations are the follows:
+To describe the elliptic path and to evaluate its curvature, depicted in Figure \ref{fig:curvature_laneFollowing_circular}, the equations are as follows:
 \begin{equation}
 	\begin{aligned}
-	X_\text{ref}&=\displaystyle 15\cos\Big(\frac{V_x\cdot t}{60}\Big)\\
-	Y_\text{ref}&=\displaystyle 30\sin\Big(\frac{V_x\cdot t}{60}\Big)  
+	X_\text{ref}&=\displaystyle 15\cos\Bigg(\frac{V_x\cdot t}{60}\Bigg)\\
+	Y_\text{ref}&=\displaystyle 30\sin\Bigg(\frac{V_x\cdot t}{60}\Bigg)  
 	\end{aligned} \quad\text{with}\quad t\in[0,20]\SI{}{s}
@@
 % ELLIPTIC PATH
-\begin{figure}[!t]
+\begin{figure}[!h]
 	\begin{minipage}[t]{0.5\textwidth}
@@
 
+In particular in Figure \ref{fig:laneFollowing_signals_circular} are represented the time signals of the ATLASCAR2 in the simulation with the elliptic path.
+It is possible to notice that also in this case the vehicle follows the path with a minimal lateral deviation described in the Figure \ref{fig:lateral_deviation_laneFollowing_circular}.
+
+However, the minimum lateral displacement is at the expense of the costant cruise velocity; infact Figure \ref{fig:longitudinal_velocity_laneFollowing_circular} and \ref{fig:lateral_velocity_laneFollowing_circular} show an oscillatory pattern of both longitudinal speed and lateral velocity caused by the continuous change of direction of the road and the length of the latter.
+
+Also in this situation we simulated a small error in the sensor dynamics in order to make the scenario more realistic: we added a 2 percent error to the longitudinal velocity and this is evident from the small noise in the graphs of the steering angle (Figure \ref{fig:steering_laneFollowing_circular}) and the lateral deviation (Figure \ref{fig:lateral_deviation_laneFollowing_circular}).
+
+As previously stated, the vehicle follows the lane and allows us to state that the control system we have designed is efficient and robust.
 %LANE FOLLOWING ELLIPTIC - PATH/CURVATURE

### 2019-03-29 Thesis_Latex/Thesis/Introduction/Introduction.tex
update thesis

@@
 
-Chapter 2
+Chapter 2 focuses on some of the more theoretical aspects of this dissertation with a brief introduction to path planning, a literature review related to local navigation algorithms with a special section centred on MPC control strategy for obstacle avoidance and tracking.
+
+In Chapter 3, the theory of Model Predictive Control is discussed in detail to highlight working principle and its characteristics (tuning parameters, stability and robustness).
+In particular for this work we used an advanced control strategy based on this paradigm called Adaptive MPC that uses a fixed model structure, but allows the model parameters to evolve with the time.
+
+Chapter 4 is used to present the Obstacle Avoidance method that we have developted.
+First we introduced the case-study model, then we designed the decision making alghorithm and the controller.
+Finally we verified the control strategy in different scenarios.
+
+Chapter 5 focuses on the Lane Following alghoritm based on Adaptive Model Predictive Control.
+We considered a different model in which we have applied the bicycle model of lateral vehicle dynamics and approximated the longitudinal dynamics using a first order transfer function.
+Then we developed the overall control scheme considering different paths to follow.

### 2019-03-29 Thesis_Presentation/Presentazione/Presentation.tex
update thesis

--- 2019-03-06 Thesis_Presentation/template_beamer_padova/example.tex
@@
 \documentclass{beamer}
-
 \usetheme{Padova}
-
+\usepackage{movie15}
+\usepackage{media9}
 \title{Local Path Planning with Moving Obstacle Avoidance based on Adaptive MPC in ATLASCAR2}
-\author{Alberto Franco 1156523}
-\date{15 Aprile 2019}
+\subtitle{\itshape Tesi di Laurea in Ingegneria dell'Automazione}
+\author{Relatore: Prof. Angelo Cenedese\qquad\quad Laureando: Alberto Franco Correlatore: Prof. Vitor Santos}
+\date{\vspace{0.4cm}15 Aprile 2019}
 
@@
 	\begin{frame}{First section}
-		\begin{block}{Normal block}
-			Fusce luctus venenatis felis quis semper
-		\end{block}
+		\includemedia[
+		label=myVidPlayer,
+		width=6cm,height=6cm,
+		activate=pageopen,
+		addresource=./videos/animation_6_obstacles.avi,
+		flashvars={
+			source=./videos/animation_6_obstacles.avi %video to be shown at first
+			&autoPlay=true
+			&scaleMode=letterbox %useful, if videos are of different aspect ratio
+		}
+		]{}{VPlayer.swf}
 
-		\begin{alertblock}{Alert block}
-			$$ E = (x_1 \vee \neg x_2 \vee \neg x_3) \wedge (x_1 \vee x_2 \vee x_4) $$
-		\end{alertblock}
-
-		\begin{exampleblock}{Example block}
-			Proin tincidunt, neque at tincidunt mollis
-		\end{exampleblock}
+		\mediabutton[mediacommand=myVidPlayer:setSource [(./videos/animation_6_obstacles.avi)]]{animation.avi}
 	\end{frame}

### 2019-04-03 Thesis_Latex/Thesis/Chapter2/Chapter2.tex
update final thesis

@@
 The basic idea of these two methods is the following: minimizing their cost functions, these strategies have the capability of a quickly  redesign when the condistions of the space change, to guarantee an optimal solution of the trajectory from the starting point to the goal location.
+
 \subsection{The A* Algorithm}
@@
 \section{Local Motion Control}
-Local Motion Control is related to the real-time motion of the robot inside in unknown enviroment, where monitoring with the sensors, it can detect where are the obstacles and generate a motion to avoid the collision with them.
+Local Motion Control is related to the real-time motion of the robot inside in unknown enviroment, where monitoring with the sensors, it can detect where are the obstacles and create a motion to avoid the collision with them.
+One of the advantages of the local navigation systems is the ability of generating a new path every time the space changes, for example when multiple moving obstacles are identified thanks to the sensors that captured the information in the enviroments.
+These methods can be divided into directional and velocity space-based approaches.
+
+The most famous directional approaches (generate a direction for the robot/vehicle) are:
+\begin{itemize}
+	\item Potential field method \cite{Khatib1986}, where the robot is represented as a particle and it is subject to forces that are produced by the surrounding environment;
+	\item Virtual Force Field which expands to Vector Field Histogram \cite{Borenstein1991}, where it utilizes a statistical representation of the vehicle's space through the so-called histogram grid;
+	\item Nearness Diagram algorithm \cite{Montano2000}, which  performs a high level information extraction and interpretation of the environment, used to generate the motion commands;
+\end{itemize}
+while the velocity space approaches, that manage the robot/vehicle considering translation and rotation velocities, are:
+\begin{itemize}
+	\item Curvature Velocity method \cite{Simmons1996} which formulates the problem as one of constrained optimization in velocity space;
+	\item Dynamic Window method \cite{Fox1997} which is divided in two main phases; in first one, it generates a valid search space while in the second one it selects an optimal solution in the search space;
+\end{itemize}
+.
 \subsection{Potential Field Method}

### 2019-04-03 Thesis_Latex/ThesisFinal/Chapter2/Chapter2.tex
update final thesis

\chapter{Literature Review}
In this chapter we introduce the literature survey of the various algorithms used for robot navigation. The navigation methods are divided into two kinds of control: global path planning and local motion control. First we analyze these two types of strategies and then we describe the current situation of Model Prediction which is the control method that we have adopted.
\section{Global Path Searching Method}
Global path planning uses information about a priori model or a map of the enviroment to evaluate the shortest path that allows the motion from a starting point to the goal position.
There are a lot of path planning algorithms, like cell decomposition, road map or potential field, where the calculation of a complete trajectory from a start position to one or more goal positions can be computed off-line. However they produce a reliable path if and only if the map of the enviroment is already available. So, this prior knowledge of the space where the robot can move, must be accessible.
The most famous method developed for global navigation is the Dijkstra algorithm \cite{Dijkstra:1959}. In recent years, an evolution of this method called A* is one of the most used \cite{Hart:1968}: this algorithm gives a complete and optimal global path in static enviroments. However, it was upgraded in D* \cite{Stentz93optimaland} for efficient online searching of a dynamic enviroment, which gives sequences of path points in the known or partially known space. The basic idea of these two methods is the following: minimizing their cost functions, these strategies have the capability of a quickly  redesign when the conditions of the space change, to guarantee an optimal solution of the trajectory from the starting point to the goal location. Moreover it has been shown that the D* algorithm is much more efficent than the A* method. Now we will analyze the general structure of these two algorithms and the practical operation based on a representation of an environment grid around the vehicle. However these methods are not sufficient to create a complete robot system navigation. We will see later that if the information of the map is not yet available, the system has to use onboard sensors to define a path and avoid obstacles.

\subsection{The A* Algorithm}
The algorithm A*, based on a graph representation, examines, step by step, the nodes that have the best score. A* uses the following data structures to keep track of the execution status: the first one is a list of nodes already visited while the second one is a priority queue containing the nodes to be visited. During execution, each node is associated with multiple values: gScore, hScore, fScore. In mathematical terms, given the current node $n$, the starting node $p$ and the solution node $s$, we define the values:
\begin{itemize}
	\item $gScore = g(p,n)$ that evaluates the actual cost of the path that separates the $p$ (start) and $n$ (current) nodes.
	\item $hScore = h(s,n)$ that calculates an estimate of the cost of the path between the $s$ (solution) and $n$ (current) nodes; this is also called Euristic function because it is associated to an Euristic algorithm that allows A* to find rapidly a solution.
	\item $fScore = gScore + hScore$ which is the total cost. 
\end{itemize}

The structure of the A* method can be summarized in 8 steps as follows:
\begin{enumerate}
	\item Insertion in the queue of the starting node with priority equal to the fScore;
	\item If the queue is empty, the algorithm returns that the solution cannot be found;
	\item Extraction of the best node to visit (priority with lower value);
	\item If the extracted node has zero $hScore$, the algorithm terminates: solution found;
	\item Creation of child nodes;
	\item Deletion of child nodes already visited and suboptimal;
	\item Inserting the remaining nodes in the queue with priority equal to the fScore;
	\item Return to step 2.
\end{enumerate}
Finally it is possible to state that the major limitation of this algorithm is in the absence of constraints on the search depth.
\subsection{The D* Algorithm}
Before describing how the D* algorithm works, we have to introduce how the nodes are marked (infact also this method mantains a list of nodes):
\begin{itemize}
	\item NEW, it has never been placed on the list;
	\item OPEN, it is currently on the list;
	\item CLOSED, it is no longer on the list;
	\item RAISE/LOWER, its cost is higher/lower than the last time it was on the list;
\end{itemize}

This method works by iteratively choosing a node from the list and evaluating it; then the node's changes are propagated to all of the neighboring nodes and they are placed on the list. This first process is called expansion. In particular we can emphasize that the D* algorithm begins by searching backwards from the goal node. After being expanded, each node has a backpointer which refers to next node leading to the target where the exact cost is known by each node.
When an obstacle is detected along the path, all the points that are thwarted, are again placed on the list marked as RAISED. Hence, the method examines RAISED's neighbors to try to reduce the node's cost; otherwise it increases the cost of the RAISED node. If not, the nodes' descendants, which have backpointers, are marked as RAISE. These nodes are calculated and the RAISE state is propagated forming a wave. If it is possible to reduce a RAISED node, its backpointer is updated and the LOWER state is passed to its neighbors. These two waves cannot touch other points so the algorithm worked only on the nodes that are affected by the cost change.

\section{Local Motion Control}
Local Motion Control is related to the real-time motion of the robot inside in unknown enviroment, where monitoring with the sensors, it can detect where are the obstacles and create a motion to avoid the collision with them. One of the advantages of the local navigation systems is the ability of generating a new path every time the space changes, for example when multiple moving obstacles are identified thanks to the sensors that captured the information in the enviroments. These methods can be divided into directional and velocity space-based approaches.

The most famous directional approaches (generate a direction for the robot/vehicle) are:
\begin{itemize}
	\item Potential field method \cite{Khatib1986}, where the robot is represented as a particle and it is subject to forces that are produced by the surrounding environment;
	\item Virtual Force Field which expands to Vector Field Histogram \cite{Borenstein1991}, where it utilizes a statistical representation of the vehicle's space through the so-called histogram grid;
	\item Nearness Diagram algorithm \cite{Montano2000}, which  performs a high level information extraction and interpretation of the environment, used to generate the motion commands;
\end{itemize}
while the velocity space approaches, that manage the robot/vehicle considering translation and rotation velocities, are:
\begin{itemize}
	\item Curvature Velocity method \cite{Simmons1996} which formulates the problem as one of constrained optimization in velocity space;
	\item Dynamic Window method \cite{Fox1997} which is divided in two main phases; in first one, it generates a valid search space while in the second one it selects an optimal solution in the search space.
\end{itemize}
Now we will analyze the general structure of some of these algorithms. In particular it is important to underline that to create a complete navigation system it is necessary that there are both local algorithms and global methods such as those seen previously.

\subsection{Potential Field Method}
The first local method that we analyzed is the Potential Field; in this strategy the robot/vehicle is represented as a particle that moves in the workspace and it is affected by attractive and repulsive forces that are generated by the surrounding environment. In particular the target propagates an attractive force while the obstacles transmit a repulsive forces. The latter can be evaluated considering only the distance from the obstacles and the instantaneous vehicle velocity and accelerations. Combining these two forces it is possible to compute the trajectory of the robot at every time instant. The total force can be used as input to control the trajectory of the vehicle.
\subsection{Curvature Velocity Method}
Another obstacle avoidance problem can be solved applying the
Curvature Velocity Method where the problem becomes a constrained optimization in the velocity space of a syncro-drive steered robot. This strategy tries to maximize
the following function:
\begin{equation}
\label{eqn:CVM}
	f(tv,rv)=\alpha_1\text{speed}(tv)+\alpha_2\text{dist}(tv,rv)+\alpha_3\text{head}(rv)
\end{equation}
where $tv$ and $rv$ are respectively the robot’s translational and rotational velocities while $\text{speed}(tv)$ represents the speed of the vehicle, $\text{head}(rv)$ is the heading of the robot and $\text{dist}(tv,rv)$ is distance to a set of obstacles within a given limit. These last three terms can be expressed as follows:
\begin{equation}
	\text{speed}(tv) = \frac{tv}{tv_{\text{max}}}\qquad 
	\text{head}(tv) = 1-\frac{\theta_g-rvT_c}{\pi}\qquad
	\text{dist}(tv,rv)=\frac{D_{\text{limit}}(tv,rv,OBS)}{\text{limit}}.
\end{equation}
At each sampling time $T_c$, the constrained optimization problem is solved choosing the transational and rotational velocities to adjuste $\alpha_1,\alpha_2$ and $\alpha_3$ values. In order to limit the search space of possible curvatures of the vehicle in velocity space, the value $D_\text{limit}$ is bounded and discretized. Finally we can classify these intervals in disjoint, contained by, contains or overlapping and they are fundamentals to compute optimal values for the distance function and consequently for the equation (\ref{eqn:CVM}).

\subsection{Dynamic Window method}
The last obstacle avoidance method that we have analyzed is called Dynamic Window approach; this is a velocity-based local planner that evaluates the optimal speed for a robot rquired to reach the target without colliding. In this algorithm the cartesian goal is translated into a velocity command for a vehicle. First, we can evaluate the desired velocity to the target based on our current position, and the destination; then we select the ammissible linear and angular velocities given the robots dynamics. From all the allowable velocities we determine the closest obstacle for the proposed vehicle velocity. If the distance to the nearest obstacle is within the robots breaking distance and the vehicle is not able to stop in time, we will reject this proposed robot speed.
Otherwise, we can evaluate the required values for the cost function. If the calculated cost is better than anything else so far, then we set this as our best option. Finally, the desired trajectory is set to the best proposed velocity.
Hence, this method calculate a valid velocity search space and select the best speed that maximizes the robots clearance and obtains the closest heading to the target.

\section{MPC in Autonomous Driving}
The algorithms we have developed in this project have a different approach than those mentioned above. In this section we have reported some algorithms based on the MPC used in the field of autonomous navigation. This literature review was fundamental to understand what methods exist and the strategies adopted to solve certain problems.
In \cite{Frasch2013} the authors addressed the problem of real-time obstacle avoidance on low-friction road surfaces using spatial Nonlinear Model Predictive Control (NMPC). They considered a nonlinear four wheel vehicle dynamics model that includes load transfer and they also used the ACADO Code Generation tool to generate NMPC algorithms based on the real-time iteration scheme for dynamic optimization. An obstacle avoidance problem solved with an MPC approach that integrates the artificial potential field method is discussed in \cite{Manzoor2015} where the controller is combined with the feedback linearization in order to manage the control problem of a single robot with unicycle kinematics and collision avoidance function. However in many traffic emergency situations a collision cannot be prevented by braking alone. This is the reason why in \cite{Werling2012} the authors proposed an obstacle avoidance method based on the NMPC paradigm that simultaneously optimizes steering and braking. In \cite{Multi2017} a path planning and tracking framework is considered to maintain a collision-free path for autonomous vehicles. In particular to track the planned
trajectory, the proposed controller formulated the tracking task as a multiconstrained model predictive control (MMPC) problem and evaluated the steering angle to prevent the robot  from colliding with a moving obstacle vehicle. Finally we considered another driver assistance method for obstacle avoidance based on constrained model predictive control. The algorithm also in this case was reduced to a convex quadratic programming problem. \cite{Wada2017}. All these methods, based on the MPC paradigm, allowed us to define two different situations where the use this type of controller is required. The first situation we have faced is a collision avoidance problem considering moving obstacles. In the second scenario we have instead built a system that allows tracking of the lane. These two approaches, faced earlier, have been solved through a new type of MPC called Adaptive MPC.

### 2019-04-03 Thesis_Latex/ThesisFinal/Chapter3/Chapter3.tex
update final thesis

--- 2019-03-09 Thesis_Latex/Thesis/Chapter3/Chapter3.tex
@@
 The control effort is included in the objective function in most
-cases. An explicit solution can be obtained if the criterion is quadratic, the model is linear, and there are no constraints; otherwise an iterative
-optimization method has to be used.
+cases. 
+\begin{figure}[!h]
+	\centering
+	\includegraphics[width=\textwidth]{./figure/mpc_theory.png}
+	\caption{A discrete Model Predictive Control scheme adapted from \cite{mpctoolbox}.}
+	\label{fig:mpc_theory}
+\end{figure}
+
+An explicit solution can be obtained if the criterion is quadratic, the model is linear, and there are no constraints; otherwise an iterative optimization method has to be used.
 Some assumptions about the structure of the future control law are also made in some cases, such as that it will be constant from a given instant.
@@
 Thus the predicted control input is then calculated using the receding horizon concept.
-\begin{figure}[!h]
-	\centering
-	\includegraphics[width=\textwidth]{../figure/mpc_theory.png}
-	\caption{A discrete Model Predictive Control scheme adapted from \cite{mpctoolbox}.}
-	\label{fig:mpc_theory}
-\end{figure}
 
-MPC is typically formulated in the state space. For a given discrete linear time-invariant (LTI) system:
+MPC is typically formulated in the state space form. For a given discrete linear time-invariant (LTI) system:
 \begin{equation}
@@
 \label{eqn:MPC_cost_function_regulation}
-	J(\vec{x}(k), \textbf{u}) = \vec{x}^\intercal_{k+N}\vec{P}_f\vec{x}_{k+N}+\sum_{i=1}^{N}\vec{x}^\intercal_{k+i}\vec{Q}\vec{x}_{k+i}+\vec{u}_{k+i}^\intercal\vec{R}\vec{u}_{k+i}
+	J(\vec{x}(k), \textbf{u}) = \vec{x}^\intercal_{k+N}\vec{P}_f\vec{x}_{k+N}+\sum_{i=1}^{N}\Big(\vec{x}^\intercal_{k+i}\vec{Q}\vec{x}_{k+i}+\vec{u}_{k+i}^\intercal\vec{R}\vec{u}_{k+i}\Big)
 \end{equation}
@@
 J(\vec{x}(k), \textbf{u})=& (\vec{x}_{k+N}-\vec{x}^\text{ref}_{k+N})^\intercal\vec{P}_f(\vec{x}_{k+N}-\vec{x}^\text{ref}_{k+N})\\
-&+\sum_{i=1}^{N}(\vec{x}_{k+i}-\vec{x}^\text{ref}_{k+i})^\intercal\vec{Q}(\vec{x}_{k+i}-\vec{x}^\text{ref}_{k+i})+\vec{u}_{k+i}^\intercal\vec{R}\vec{u}_{k+i}
+&+\sum_{i=1}^{N}\Big((\vec{x}_{k+i}-\vec{x}^\text{ref}_{k+i})^\intercal\vec{Q}(\vec{x}_{k+i}-\vec{x}^\text{ref}_{k+i})+\vec{u}_{k+i}^\intercal\vec{R}\vec{u}_{k+i}\Big)
 \end{aligned}
 \end{equation}
-where $\vec{x}^\text{ref}_{k+i}$, $\vec{x}^\text{ref}_{k+N}$ describe the reference trajectory. The standard MPC algorithm can be summarized by the following steps:
+where $\vec{x}^\text{ref}_{k+i}$, $\vec{x}^\text{ref}_{k+N}$ describe the reference trajectory. 
+The standard MPC algorithm can be summarized by the following steps:
 \begin{algorithm}%[b]
@@
 		\State Measure the current state $\vec{x}(k)$;
-		\State Solve the optimization problem \ref{eqn:MPC_optimization} with $\vec{x}(k)$ as initial state, where $\vec{u}(k)$ is calculated;
+		\State Solve the optimization problem (\ref{eqn:MPC_optimization}) with $\vec{x}(k)$ as initial state, where $\vec{u}(k)$ is calculated;
 		\State Apply the first control of the optimal control sequence;
@@
 Also mathematical convexity is an important part of the resulting problem formulation of an MPC.
-In fact there exists efficient solvers for convex optimization problems but it is therefore desirable that the MPC problem \ref{eqn:MPC_optimization} is convex which is ensured if:
+In fact there exists efficient solvers for convex optimization problems but it is therefore desirable that the MPC problem (\ref{eqn:MPC_optimization}) is convex which is ensured if:
 \begin{enumerate}

### 2019-04-03 Thesis_Latex/ThesisFinal/Chapter4/Chapter4.tex
update final thesis

--- 2019-03-29 Thesis_Latex/Thesis/Chapter4/Chapter4.tex
@@
 	\centering
-	\includegraphics[width=\textwidth]{../figure/obstacleAvoidance/obstacleAvoidance.pdf}
+	\includegraphics[width=\textwidth]{./figure/obstacleAvoidance/obstacleAvoidance.pdf}
 	\caption{Problem description of collision avoidance on a road with only two lanes.}
@@
 Here, we present a non linear mathematical model of a vehicle used for the development of a collision avoidance system.
-
 The model has four states and two inputs:
@@
 \end{equation}
+
 where $(x,y)$ are the global coordinates of the contact point between the rear wheel and the ground, $\theta$ is the heading angle of the car body with respect to the $x$-axis and $v$ is the linear speed of the car (positive).
@@
 	\centering
-	\includegraphics[width=0.80\textwidth]{../figure/car_model.pdf}
+	\includegraphics[width=0.65\textwidth]{./figure/car_model.pdf}
 	\caption{Bicycle model of a car (adapted from \cite{siciliano}).}
@@
 This equation cannot be integrated to form a
-relationship between $x,y$ and $\theta$.
-
-In order to use an MPC controller, the state space model needs to be linearized with a first order approximation and also re-written in a more compact form:
+relationship between $x,y$ and $\theta$. In order to use an MPC controller, the state space model needs to be linearized with a first order approximation and also re-written in a more compact form:
 \begin{equation}
@@
 For simplicity, we assume that all the states are measurable and the ATLASCAR2 drives east with a constant speed at the nominal operating point.
+
 In the scenario that we are going to consider, the road is straight and our vehicle stays in the middle of the center lane when not passing.
@@
 Because the new model describes the plant dynamics more accurately at the new operating condition, an adaptive MPC controller performs better than a traditional MPC controller.
+
 In practice, at each control interval, the adaptive MPC controller updates the plant model and the nominal conditions.
@@
 % FLOWCHART
-\begin{figure}[!b]
+\begin{figure}[!t]
 	\centering
-	\includegraphics[width=\textwidth]{../figure/flowchart/flowchart.pdf}
+	\includegraphics[width=0.90\textwidth]{./figure/flowchart/flowchart.pdf}
 	\caption{Behaviour planning conditional flowchart.}
@@
 At the next control interval the area is redefined based on the new positions of the vehicle and the obstacle until passing is completed.
+
 To define the area to avoid, we used the following mixed Input/Output constraints:
@@
 where $\vec{u}$ and $\vec{y}$ are respectively the manipulated variable vector and the output variable vector, while $\vec{E},\vec{F},\vec{G}$ are the constraint matrices that can be updated when the controller is running.
+
 Five constraints were defined:
@@
 	\centering
-	\includegraphics[width=\textwidth]{../figure/constraint/constraint.pdf}
+	\includegraphics[width=\textwidth]{./figure/constraint/constraint.pdf}
 	\caption{Constraints in the case of left overtaking.}
@@
 We tried to choose parameters that were as close as possible to a real situation: the sampling time used in the discretization of the system is $T_s=\SI{0.02}{s}$ while the values of the prediction and the control horizon are respectively $p_H=25$ and $c_H=5$.
+
 In all simulations, the distance between the front and rear axles is $C_L=\SI{5}{m}$ and the width of the vehicle is $C_W=\SI{2}{m}$.
 The saturation ranges of the control inputs are: the steering angle rate of change lies in $\big[-\frac{\pi}{30}, +\frac{\pi}{30}\big]$ rad/s while in order to prevent the ATLASCAR2 from accelerating or decelerating too quickly, we impose an hard constraint of \SI{2.5}{m/s^2} on the throttle rate of change.
+
 Moreover we are using a constant reference signal for the velocity of $v=\SI{20}{m/s}$ ($\approx\SI{72}{km/h}$).
@@
 	\centering
-	\includegraphics[width=\textwidth]{../figure/MovingObstacleAvoidance.pdf}
+	\includegraphics[width=\textwidth]{./figure/MovingObstacleAvoidance.pdf}
 	\caption{Overall procedure scheme moving obstacle avoidance.}
@@
 	\begin{minipage}[t]{\textwidth}
-		\includegraphics[width=\textwidth]{../figure/one_obstacle_right_overtaking/overtaking_start.pdf}
+		\includegraphics[width=\textwidth]{./figure/one_obstacle_right_overtaking/overtaking_start.pdf}
 	\end{minipage}
 	\begin{minipage}[t]{\textwidth}
-		\includegraphics[width=\textwidth]{../figure/one_obstacle_right_overtaking/overtaking_middle.pdf}
+		\includegraphics[width=\textwidth]{./figure/one_obstacle_right_overtaking/overtaking_middle.pdf}
 	\end{minipage}
 	\begin{minipage}[t]{\textwidth}
-		\includegraphics[width=\textwidth]{../figure/one_obstacle_right_overtaking/overtaking_middle_end.pdf}
+		\includegraphics[width=\textwidth]{./figure/one_obstacle_right_overtaking/overtaking_middle_end.pdf}
 	\end{minipage}
 	\begin{minipage}[t]{\textwidth}
-		\includegraphics[width=\textwidth]{../figure/one_obstacle_right_overtaking/overtaking_end.pdf}
+		\includegraphics[width=\textwidth]{./figure/one_obstacle_right_overtaking/overtaking_end.pdf}
 	\end{minipage}
@@
 Algorithm \ref{alg:rightOvertaking} summarizes the main steps to compute custom constraints for the obstacle; when the vehicle detects the obstacle, the constraints are computed.
+
+In other words the constraints are evaluated as follows:
+\begin{itemize}
+	\item if the ATLASCAR2 is already in the adjacent lane, it uses the safety zone as the constraint (line \ref{line:safety_zone});
+	\item otherwise the vehicle must be above the line formed from the ATLASCAR2 to safe zone corner for right passing (lines \ref{line:corner1} and \ref{line:corner2});
+	\item if the vehicle is parallel to the obstacle (line \ref{line:safety_zone_parallel}), it  uses the safety zone as the constraint;
+	\item finally if it has passed the obstacle, it uses the inactive constraint to go back to the center lane (line \ref{line:inactive}).
+\end{itemize}
+
 % ALGORITHM FOR RIGHT OVERTAKING OF ONE MOVING OBSTACLE
@@
 \end{algorithm}
-
-In other words the constraints are evaluated as follows:
-\begin{itemize}
-	\item if the ATLASCAR2 is already in the adjacent lane, it uses the safety zone as the constraint (line \ref{line:safety_zone});
-	\item otherwise the vehicle must be above the line formed from the ATLASCAR2 to safe zone corner for right passing (lines \ref{line:corner1} and \ref{line:corner2});
-	\item if the vehicle is parallel to the obstacle (line \ref{line:safety_zone_parallel}), it  uses the safety zone as the constraint;
-	\item finally if it has passed the obstacle, it uses the inactive constraint to go back to the center lane (line \ref{line:inactive}).
-\end{itemize}
 
@@
 % SIX MOVING OBSTACLES
-\begin{figure}[h!]
+\begin{figure}[b!]
 	\centering
 	\begin{minipage}[t]{\textwidth}
-		\includegraphics[width=\textwidth]{../figure/6_obstacles/6_obstacles_1.pdf}
+		\includegraphics[width=\textwidth]{./figure/6_obstacles/6_obstacles_1.pdf}
 	\end{minipage}
 	\begin{minipage}[t]{\textwidth}
-		\includegraphics[width=\textwidth]{../figure/6_obstacles/6_obstacles_2.pdf}
+		\includegraphics[width=\textwidth]{./figure/6_obstacles/6_obstacles_2.pdf}
 	\end{minipage}
 	\begin{minipage}[t]{\textwidth}
-		\includegraphics[width=\textwidth]{../figure/6_obstacles/6_obstacles_3.pdf}
+		\includegraphics[width=\textwidth]{./figure/6_obstacles/6_obstacles_3.pdf}
 	\end{minipage}
 	\begin{minipage}[t]{\textwidth}
-		\includegraphics[width=\textwidth]{../figure/6_obstacles/6_obstacles_4.pdf}
+		\includegraphics[width=\textwidth]{./figure/6_obstacles/6_obstacles_4.pdf}
 	\end{minipage}
 	\begin{minipage}[t]{\textwidth}
-		\includegraphics[width=\textwidth]{../figure/6_obstacles/6_obstacles_5.pdf}
+		\includegraphics[width=\textwidth]{./figure/6_obstacles/6_obstacles_5.pdf}
 	\end{minipage}
 	\begin{minipage}[t]{\textwidth}
-		\includegraphics[width=\textwidth]{../figure/6_obstacles/6_obstacles_6.pdf}
+		\includegraphics[width=\textwidth]{./figure/6_obstacles/6_obstacles_6.pdf}
 	\end{minipage}
@@
 	\begin{minipage}[t]{\textwidth}
-		\includegraphics[width=\textwidth]{../figure/no_overtaking/no_overtaking_1.pdf}
+		\includegraphics[width=\textwidth]{./figure/no_overtaking/no_overtaking_1.pdf}
 	\end{minipage}
 	\begin{minipage}[t]{\textwidth}
-		\includegraphics[width=\textwidth]{../figure/no_overtaking/no_overtaking_1_5.pdf}
+		\includegraphics[width=\textwidth]{./figure/no_overtaking/no_overtaking_1_5.pdf}
 	\end{minipage}
 	\begin{minipage}[t]{\textwidth}
-		\includegraphics[width=\textwidth]{../figure/no_overtaking/no_overtaking_2.pdf}
+		\includegraphics[width=\textwidth]{./figure/no_overtaking/no_overtaking_2.pdf}
 	\end{minipage}
 	\begin{minipage}[t]{\textwidth}
-		\includegraphics[width=\textwidth]{../figure/no_overtaking/no_overtaking_3.pdf}
+		\includegraphics[width=\textwidth]{./figure/no_overtaking/no_overtaking_3.pdf}
 	\end{minipage}
 	\begin{minipage}[t]{\textwidth}
-		\includegraphics[width=\textwidth]{../figure/no_overtaking/no_overtaking_4.pdf}
+		\includegraphics[width=\textwidth]{./figure/no_overtaking/no_overtaking_4.pdf}
 	\end{minipage}
@@
 \end{equation}
-where:
-\begin{itemize}
-	\item $d$ is the braking distance in metres (to be calculated).
-	\item $v$ is the speed in \SI{}{km/h};
-	\item 250 is the fixed figure which is always used;
-	\item $f$ is the coefficient of friction, approx. 0.8 on dry asphalt and 0.1 on ice.
-\end{itemize}
+where $d$ is the braking distance in metres, $v$ is the speed in \SI{}{km/h}, $250$ is the fixed figure which is always used and $f$ is the coefficient of friction, approx.
+0.8 on dry asphalt and 0.1 on ice.
 % RESULTS NO OVERTAKING

### 2019-04-03 Thesis_Latex/ThesisFinal/Chapter5/Chapter5.tex
update final thesis

--- 2019-03-29 Thesis_Latex/Thesis/Chapter5/Chapter5.tex
@@
 First we introduced the case-study model, then we designed the controller and the overall procedure scheme.
-Finally we verified the proposed strategy in different scenarios.
+Finally we verified the proposed strategy in different scenarios considering a double lane change, sinusoidal and elliptic/circular paths.
 \section{Problem Formulation}
@@
 	\centering
-	\includegraphics[width=0.75\textwidth]{../figure/laneFollowing/laneFollowing.pdf}
+	\includegraphics[width=0.75\textwidth]{./figure/laneFollowing/laneFollowing.pdf}
 	\caption{Problem description of a lane following system.}
@@
 \begin{equation}
-	\label{eqn:alpha_f_alpha_r}
-	\begin{array}{ll}
-	\alpha_f = \delta-\theta_{vf}\\
+	\label{eqn:alphas}
+	\alpha_f = \delta-\theta_{vf},\qquad\quad
 	\alpha_r = -\theta_{vr}
-	\end{array}
 \end{equation}
@@
 \begin{equation}
-\label{eqn:theta_vf}
-\theta_{vf}=\text{atan}\Bigg(\frac{V_y+l_F\dot{\psi}}{V_x}\Bigg)
-\end{equation}
-\begin{equation}
-\label{eqn:theta_vr}
+\label{eqn:theta_v}
+\theta_{vf}=\text{atan}\Bigg(\frac{V_y+l_F\dot{\psi}}{V_x}\Bigg),
+\qquad \quad
 \theta_{vr}=\text{atan}\Bigg(\frac{V_y-l_R\dot{\psi}}{V_x}\Bigg)
@@
 	\label{eqn:lateral_tire_forces}
-	\begin{array}{ll}
-	F_{yf} = 2C_F(\delta-\theta_{vf})\\
+	F_{yf} = 2C_F(\delta-\theta_{vf}),\qquad\quad
 	F_{yr} = -2C_R\theta_{vr}
-	\end{array}
 \end{equation}
@@
 	\item $I_Z$ is the yaw moment of inertia parameter;
-	\item $l_F$ and $l_R$ are the longitudinal distances from center of gravity to front and rear tires parameters;
-	\item $C_F$ and $C_R$ are the cornering stiffnesses of front and rear tires parameters.
+	\item $l_F$ is the longitudinal distances from center of gravity to front tire parameter;
+	\item $l_R$ is the longitudinal distances from center of gravity to rear tire parameter;
+	\item $C_F$ is the cornering stiffnesses of front tire parameter;
+	\item $C_R$ is the cornering stiffnesses of rear tire parameter;
 \end{itemize}
@@
 	\centering
-	\includegraphics[width=\textwidth]{../figure/lane_following_AMPC.pdf}
+	\includegraphics[width=\textwidth]{./figure/lane_following_AMPC.pdf}
 	\caption{Overall procedure scheme lane following.}
@@
 	\centering
-	\includegraphics[width=\textwidth]{../figure/lane_following_AMPC_vehicle_dynamics.pdf}
+	\includegraphics[width=\textwidth]{./figure/lane_following_AMPC_vehicle_dynamics.pdf}
 	\caption{Vehicle Dynamics of the overall scheme lane following.}
@@
 \begin{array}{cc}
-	\SI{-3}{m/s^2}\leq a\leq\SI{3}{m/s^2}\;,\\\\
+	\SI{-3}{m/s^2}\leq a\leq\SI{3}{m/s^2}\qquad\quad
 	\SI{-1.13}{rad}\leq \delta \leq \SI{1.13}{rad}\;,
@@
 	\centering
-	\includegraphics[width=\textwidth]{../figure/lane_following_AMPC_sensor_dynamics.pdf}
+	\includegraphics[width=\textwidth]{./figure/lane_following_AMPC_sensor_dynamics.pdf}
 	\caption{Sensor Dynamics of the overall scheme lane following.}
@@
 		$C_R$           & \SI{33000}{\newton/rad}&Rear cornering stiffness  \\
-		$\tau$             & 0.2    & Time constant            \\
+		$\tau$             & \SI{0.2}    & Time constant            \\
 		$V_0$           & \SI{15}{m/s} & Initial Velocity      \\
@@
 	\end{minipage}
-	\caption{Desired sinusoidal path and its curvature of the ATLASCAR2 in a simulation of \SI{20}{s} with initial position in $(0,0)$.}
+	\caption{Desired sinusoidal path and its curvature of the ATLASCAR2 in a simulation of \SI{20}{s}.}
 	\label{fig:laneFollowing_desired}
@@
 We can therefore state that even in this case the vehicle correctly follows the lane.
-\newpage
 %LANE FOLLOWING SINUSOIDAL PATH - SIGNALS
@@
 \end{figure}
-\newpage
+
 \subsection{Circular/Elliptic Path}
@@
 \begin{equation}
-	\begin{aligned}
-	X_\text{ref}&=\displaystyle 15\cos\Bigg(\frac{V_x\cdot t}{60}\Bigg)\\
-	Y_\text{ref}&=\displaystyle 30\sin\Bigg(\frac{V_x\cdot t}{60}\Bigg)  
-	\end{aligned} \quad\text{with}\quad t\in[0,20]\SI{}{s}
+	X_\text{ref}=\displaystyle 15\cos\Bigg(\frac{V_x\cdot t}{60}\Bigg) \qquad
+	Y_\text{ref}=\displaystyle 30\sin\Bigg(\frac{V_x\cdot t}{60}\Bigg)  
+ \quad\text{with}\quad t\in[0,20]\SI{}{s}
 \end{equation}

### 2019-04-03 Thesis_Latex/ThesisFinal/Introduction/Introduction.tex
update final thesis

--- 2019-03-29 Thesis_Latex/Thesis/Introduction/Introduction.tex
@@
+\begin{savequote}[75mm]
+	``Self-driving cars are the natural extension of active safety and obviously something we thing we should do."
+	\qauthor{Elon Musk}
+\end{savequote}
+
 \chapter{Introduction}
@@
 Moreover, the paths can be also defined in terms of specifications; for example, short or smooth paths are usually more desirable than long and curved ones in every dynamic environments.
-
 Beyond the path planning, the navigation problem also involves reacting to changes of the environment model.
 Robots are required to move towards the target in a short time and avoid either static or dynamic obstacles observed by their sensors, which involves efficient path planning and valid obstacle avoidance.
-
 Research and development of Unmanned Ground Vehicles has been dominated by DARPA (Defense Advanced Research Projects Agency) and NASA (National Aeronautics and Space Administration).
@@
 Recent UGV design and development has been enhanced to build UGVs capable of operating in Intelligent Vehicle Highway Systems \cite{Bai2015}.
-
 Over the last decades, the development of Advanced Driver Assistance Systems has become a critical endeavor to attain different objectives: safety enhancement, mobility improvement, energy optimization and comfort \cite{Gruyer2017}.
@@
 Algorithms for autonomous navigation are increasingly robust and reliable and are starting to handle complex situations and decision problems.
-
 According to Katrakazas \cite{Katrakazas2015}, local navigation is responsible for guiding the vehicle, that is, for the planning of the direction and speed to be taken, in a space close to the current position based on information exclusively obtained by the sensors on board.
 The guiding must be planned in such a way as to guarantee the displacement, from the current state to the objective, without collisions.
-
 The algorithms we have developed at the LAR, follow a new and different approach for an advanced control strategy for autonomous navigation.
@@
 		\begin{minipage}[t]{0.32\textwidth}
-			\includegraphics[width=\textwidth]{../figure/modelosatlas1.pdf}
+			\includegraphics[width=\textwidth]{./figure/modelosatlas1.pdf}
 			\subcaption{First ATLAS prototype.}
@@
 		\begin{minipage}[t]{0.32\textwidth}
-			\includegraphics[width=\textwidth]{../figure/modelosatlas2.pdf}
+			\includegraphics[width=\textwidth]{./figure/modelosatlas2.pdf}
 			\subcaption{ATLAS 2000.}
@@
 		\begin{minipage}[t]{0.32\textwidth}
-			\includegraphics[width=\textwidth]{../figure/modelosatlas3.pdf}
+			\includegraphics[width=\textwidth]{./figure/modelosatlas3.pdf}
 			\subcaption{ATLAS MV.}
@@
 	\centering
-	\includegraphics[width=\textwidth]{../figure/atlascar1.jpg}
+	\includegraphics[width=0.9\textwidth]{./figure/atlascar1.jpg}
 	\caption{The car used in ATLASCAR, based on Ford Escort Station Wagon of 1998 (adapted from \cite{Pereira2012}).}
@@
 	\centering
-	\includegraphics[width=\textwidth]{../figure/atlascar2.jpg}
+	\includegraphics[width=0.85\textwidth]{./figure/atlascar2.jpg}
 	\caption{The vehicle used in ATLASCAR2, based on an electric car, a Mitsubishi iMiEV of 2015 (adapted from \cite{Ricardo:Thesis:2018}).}
@@
 \section{Autonomous Cars}\label{sec:autonomous_examples}
-The legal definition of autonomous vehicle in the District of Columbia code is:
+The legal definition of autonomous vehicle in the District of Columbia code \cite{DColumbia} is:
 \begin{quotation}
@@
 	\centering
-	\begin{minipage}[t]{0.65\textwidth}
-		\includegraphics[width=\textwidth]{../figure/veiculos0.png}
+	\begin{minipage}[t]{0.45\textwidth}
+		\includegraphics[width=\textwidth]{./figure/veiculos0.png}
 		\subcaption{Google's Firefly self-driving prototype in 2015 (adapted from \cite{waymoh}).}
@@
 	\end{minipage}
-	\begin{minipage}[t]{0.65\textwidth}
-		\includegraphics[width=\textwidth]{../figure/veiculos1.png}
+	\begin{minipage}[t]{0.45\textwidth}
+		\includegraphics[width=\textwidth]{./figure/veiculos1.png}
 		\subcaption{Waymo Chrysler Pacifica Hybrid self-driving prototype in 2017 (adapted from \cite{waymoh}).}
@@
 	\centering
-	\includegraphics[width=0.65\textwidth]{../figure/veiculos4.png}
+	\includegraphics[width=0.65\textwidth]{./figure/veiculos4.png}
 	\caption{BRAiVE prototype developted by VisLab, based on a Hyundai Sonata (adapted from \cite{Broggi2013}).}
@@
 	\centering
-	\includegraphics[width=0.6\textwidth]{../figure/veiculos5.png}
+	\includegraphics[width=0.6\textwidth]{./figure/veiculos5.png}
 	\caption{Navya Shuttle developted in 2016 by Navya Group in France.}

### 2019-04-03 Thesis_Latex/ThesisFinal/frontmatter/abstract.tex
update final thesis

--- 2019-03-08 Thesis_Latex/Thesis/Abstract/Abstract.tex
@@
-\chapter*{Abstract}
-\thispagestyle{empty}
-Inserted in the ATLASCAR2 project this work aims to develop a short-term path planning algorithm
-for driver assistance in dynamic environments.
-In order to achieve this objective, it was made a preliminary study of the existing local path planning methods and the projects that have already been developed in this field, their advantages and disadvantages were weighed
-and the most successful approaches applied to local navigation in real autonomous driving projects were taken into account.
+%!TEX root = ../dissertation.tex
+% the abstract
+Inserted in the ATLASCAR2 project this work aims to develop a short-term path planning framework for driver assistance in dynamic environments.
+In order to achieve this objective, it was made a preliminary study of the existing local path planning methods and the projects that have already been developed in this field, their advantages and disadvantages were weighed and the most successful approaches applied to local navigation in real autonomous driving projects were taken into account.
 This thesis presents two different strategies for a self-driving car short-term path planning among multiple moving obstacles.

### 2019-04-03 Thesis_Presentation/Presentazione/Presentazione.tex
update final thesis

\documentclass{beamer}
\usepackage[italian]{babel}
\usepackage[utf8]{inputenc}
\usepackage{default}
\usepackage{subcaption}
\usepackage{afterpage}
\usepackage{xcolor}
\usepackage{wrapfig}
\usepackage{caption}
\usepackage{bbm}
\usepackage{multimedia}

\newsavebox{\tempbox}
\usetheme{Padova}
\title{Local Path Planning with Moving Obstacle Avoidance based on Adaptive MPC in ATLASCAR2}
\subtitle{\itshape Tesi di Laurea in Ingegneria dell'Automazione}
\author{Relatore: Prof. Angelo Cenedese\qquad\quad Laureando: Alberto Franco Correlatore: Prof. Vitor Santos}
\date{\vspace{0.4cm}15 Aprile 2019}

\AtBeginSection[]{

	\begin{frame}{}
		\nonumber
		\pagecolor{rossoPantano}\afterpage{\nopagecolor}
		\usebeamerfont{title}\vfill\centering
		\usebeamercolor[fg]{title}\insertsectionhead\par%
		\vfill
	\end{frame}
}

\begin{document}

	\maketitle

	\begin{frame}{Progetto ATLASCAR2}

	  \begin{figure}[!t]
	  	\centering
	  	\begin{minipage}[t]{0.49\textwidth}
		  	\includegraphics[scale=0.32]{./images/logo_ua.png}
	  		\label{fig:logoua}
	  	\end{minipage}
	  	\begin{minipage}[t]{0.49\textwidth}
	  		\includegraphics[scale=0.055]{./images/atlascar2.pdf}
	  		\label{fig:atlascar2}
	  	\end{minipage}
	  	\caption{ATLASCAR2 - Mitsubishi iMiEV elettrica del 2015}
	  	\end{figure}

	\end{frame}

	\begin{frame}{Motivazione e Obiettivi della Tesi}

	\end{frame}

	\begin{frame}{Model Predictive Control}
		\begin{block}{Normal block}
			Fusce luctus venenatis felis quis semper
		\end{block}

		\begin{alertblock}{Alert block}
			$$ E = (x_1 \vee \neg x_2 \vee \neg x_3) \wedge (x_1 \vee x_2 \vee x_4) $$
		\end{alertblock}

		\begin{exampleblock}{Example block}
			Proin tincidunt, neque at tincidunt mollis
		\end{exampleblock}
	\end{frame}

	\section{Moving Obstacle Avoidance System {\itshape \large (sistema di anticollisione con ostacoli in movimento)}} % ovvero un sistema di anticollisione con ostacoli in movimento.

	\begin{frame}{Formulazione del Problema}

	\end{frame}

	\begin{frame}{Design Adaptive MPC - parte 1} % progettazione dell'algoritmo di anticollisione basato su un controllore MPC adattivo.

	\end{frame}

	\begin{frame}{Design Adaptive MPC - parte 2} % progettazione dell'algoritmo di anticollisione basato su un controllore MPC adattivo.

	\end{frame}

	\begin{frame}{Risultati Simulativi}

	\end{frame}

	\section{Lane Following System \qquad\qquad{\itshape\large(sistema di assistenza al mantenimento della corsia)}}  % ovvero un sistema di assistenza al mantenimento della corsia.

	\begin{frame}{Formulazione del Problema}

	\end{frame}

	\begin{frame}{Design Adaptive MPC} % progettazione dell'algoritmo di mantenimento della corsia basato su un controllore MPC adattivo.

	\end{frame}

	\begin{frame}{Risultati Simulativi}

	\end{frame}
	\begin{frame}{Conclusioni e Sviluppi Futuri}
		contenuto...
	\end{frame}

\end{document}

### 2019-04-05 Thesis_Latex/ThesisFinal/Chapter2/Chapter2.tex
update final thesis

@@
 \chapter{Literature Review}
-In this chapter we introduce the literature survey of the various algorithms used for robot navigation.
+In this chapter we introduce the literature review of the various algorithms used for robot navigation.
 The navigation methods are divided into two kinds of control: global path planning and local motion control.
@@
 \end{itemize}
-while the velocity space approaches, that manage the robot/vehicle considering translation and rotation velocities, are:
+while velocity space approaches, that manage the robot/vehicle considering translation and rotation velocities, are:
 \begin{itemize}
@@
 Another obstacle avoidance problem can be solved applying the
-Curvature Velocity Method where the problem becomes a constrained optimization in the velocity space of a syncro-drive steered robot. This strategy tries to maximize
+Curvature Velocity Method where the problem becomes a constrained optimization in the velocity space of a syncro-drive steered robot \cite{CVM2003}. This strategy tries to maximize
 the following function:
@@
 \cite{Wada2017}.
-All these methods, based on the MPC paradigm, allowed us to define two different situations where the use this type of controller is required.
+All these methods, based on the MPC paradigm, allowed us to define two different situations where the use of this type of controller is required.
 The first situation we have faced is a collision avoidance problem considering moving obstacles.

### 2019-04-05 Thesis_Latex/ThesisFinal/Chapter3/Chapter3.tex
update final thesis

@@
 control inputs that are calculated at each sampling instance $k$, using the current state as initial
-conditions to solve a finite optimal control problem. Some of the advantages of using MPC are:
+conditions to solve a finite optimal control problem.\\
+Some of the advantages of using MPC, reported in \cite{camacho2004}, are:
 \begin{itemize}
@@
 This criterion usually takes the form of a quadratic function of the errors between the predicted output signal and the predicted reference trajectory.
-The control effort is included in the objective function in most
-cases. 
+The control effort is included in the objective function in most cases \cite{camacho2013model}.
 \begin{figure}[!h]
@@
 & & \vec{x}_{k+i+1} = \vec{A}\vec{x}_{k+i}+ \vec{B} \vec{u}_{k+i}\quad\forall i=0,\dots N-1;\\
-& & & \vec{x}_{k+i}\in \mathbb{X}\quad\forall i=0,\dots N-1;\\
-& & & \vec{u}_{k+i}\in \mathbb{U}\quad\forall i=0,\dots N-1;\\  
-& & & \vec{x}_{k+N}\in \mathbb{X}_f;\quad\vec{x}_k = \vec{x}(k).
+& & & \vec{x}_{k+i}\in \mathcal{X}\quad\forall i=0,\dots N-1;\\
+& & & \vec{u}_{k+i}\in \mathcal{U}\quad\forall i=0,\dots N-1;\\  
+& & & \vec{x}_{k+N}\in \mathcal{X}_f;\quad\vec{x}_k = \vec{x}(k).
 \end{aligned}
@@
 where $\textbf{u}=(\vec{u}_k,\dots,\vec{u}_{k+N-1})$ is a sequence of control inputs, $\vec{x}_{k+i}$ is the state at time $k+i$ as predicted at time $k$, and $N$ is the prediction horizon.
-The sets $\mathbb{X}\in\mathbb{R}^n$ and $\mathbb{U}\in\mathbb{R}^m$ define the constraints on the state and the input, respectively.
-Finally, the set $\mathbb{X}_f\subseteq\mathbb{X}$ defines the terminal constraint on the state.
+The sets $\mathcal{X}\in\mathbb{R}^n$ and $\mathcal{U}\in\mathbb{R}^m$ define the constraints on the state and the input, respectively.
+Finally, the set $\mathcal{X}_f\subseteq\mathcal{X}$ defines the terminal constraint on the state.
 If we consider a regulation problem, the system (\ref{eqn:MPC_plant_discrete}) should be steered to the origin and the cost function $J(\vec{x}(k), \textbf{u})$ could be in a quadratic form as follows:
@@
 \item the prediction model is linear;
-\item the constraint sets $\mathbb{X}, \mathbb{U}$ are convex.	
+\item the constraint sets $\mathcal{X}, \mathcal{U}$ are convex.	
 \end{enumerate}
+
 The optimization handles actuator constraints and state constraints naturally in the optimization which allows for

### 2019-04-05 Thesis_Latex/ThesisFinal/Chapter4/Chapter4.tex
update final thesis

@@
-\chapter{Moving Obstacle Avoidance}
+\chapter{Moving Obstacle Avoidance System}
 In this chapter we present an Obstacle Avoidance alghorithm based on Adaptive Model Predictive Control.
@@
 
-This is possible if and only if there is a free lane or  sufficient space for overtaking the obstacle.
-In the case the road is busy with vehicles, the ATLASCAR2 must slow down and adapts its speed to that of the closest obstacle until the scenario changes.
+This is possible if and only if there is a free lane or enough space to overcome the obstacle.
+If the road is occupied by vehicles, the ATLASCAR2 must slow down and adjust its speed to that of the nearest obstacle until the scenario changes.
 
@@
 This yaw rate can also be deduced from the angular velocity of the wheels on the left- and right-hand sides of the vehicle which therefore rotate at different speeds because follow arcs of different radius.
-We can write the non-holonomic constraint which is an expression for velocity in the vehicle's $y$-direction in the world coordinate frame as follows:
+We can write the non-holonomic constraint which is an expression for velocity in the ATLASCAR2's $y$-direction in the world coordinate frame as follows:
 \begin{equation}
@@
 Finally we can analyze time signals of the ATLASCAR2 in the simulation of right overtaking of one moving obstacle.
-Figures \ref{fig:longitudinal_one_moving} and \ref{fig:lateral_one_moving} illustrate the longitudinal and lateral position of the vehicle with respect to time, showing a constant trend with respect to the $x$ component, while a shift from 0 can be noted regarding the $y$ coordinate due to the overcoming of the obstacle.
+Figures \ref{fig:longitudinal_one_moving} and \ref{fig:lateral_one_moving} illustrate the longitudinal and lateral positions of the vehicle with respect to time, showing a constant trend with respect to the $x$ component, while a shift from $0$ can be noted regarding the $y$ coordinate due to the overcoming of the obstacle.
 To confirm a uniform trend, the speed of the ATLASCAR2 remains fairly constant.
-Obviously it is possible to note from Figure \ref{fig:velocity_one_moving} that the velocity decreases very little during the first part of the overtaking phase, and then come back to the cruising speed in the second part.
+Obviously it is possible to note from Figure \ref{fig:velocity_one_moving} that the velocity decreases very little during the first part of the overtaking phase, and then comes back to the cruising speed in the second part.
 Instead from the remaining Figures \ref{fig:throttle_one_moving}, \ref{fig:delta_one_moving} and \ref{fig:theta_one_moving} we can observe that the throttle $T$ and the steering angle $\delta$ respect the limits we imposed while the heading angle $\theta$ is used to describe the direction the ATLASCAR2 is pointing.
@@
 The vehicle is capable of overtaking the obstacles on the right or left depending on their positions with respect to the road.
-If the $y$-coordinate of the closest obstacle is greater than 0, then the vehicle overtakes to the right, otherwise the overtaking takes place on the left lane.
+If the $y$-coordinate of the closest obstacle is greater than $0$, then the vehicle overtakes to the right, otherwise the overtaking takes place on the left lane.
 % MULTIPLE MOVING OBSTACLE
@@
 
-In the Figure \ref{fig:obstacleAvoidance_six_obstacles} we also hypothesized there are six moving obstacles that can drive at different speeds but initially they are at a common distance; they can have a uniform motion or a uniformely accelerated motion.
+In Figure \ref{fig:obstacleAvoidance_six_obstacles} we also hypothesized there are six moving obstacles that can drive at different speeds but initially they are at a common distance; they can have a uniform motion or a uniformely accelerated motion.
 We also improved the code infact in case two obstacles are too close during the simulation and their distance is less than the detection range, which is \SI{30}{m}, the ATLASCAR2 perceives the objects as a single entity and adapts to the situation.

### 2019-04-05 Thesis_Latex/ThesisFinal/Chapter5/Chapter5.tex
update final thesis

@@
-\chapter{Lane Following}
+\chapter{Lane Following System}
 In this chapter we present a Lane Following alghorithm based on Adaptive Model Predictive Control.
@@
 These two velocities can be used to form a vector describing the resultant velocity and its direction.
-In this case it is also possible to find the slip angles, the difference between the actual travelling direction of the and where it is pointed (in the previous chapter we assumed that the ATLASCAR2 does not slip, so any slippage is thus considered as an external disturbance):
+In this case it is also possible to find the slip angles, the difference between the actual travelling direction of the wheel and where it is pointed \cite{Nilsson2015} (in the previous chapter we assumed that the ATLASCAR2 does not slip, so any slippage is thus considered as an external disturbance):
 \begin{equation}
@@
 \end{equation}
-
 Combining (\ref{eqn:yaw_lateral_motion}) and (\ref{eqn:lateral_tire_forces}) gives the following vehicle lateral model from parameters: 
@@
 The third output, yaw angle, is allowed to float because there are only two manipulated variables to make it a square system.
-In this controller, there is no steady-state error in the yaw angle as long as the second output, lateral deviation, reaches 0 at steady state.
+In this controller, there is no steady-state error in the yaw angle as long as the second output, lateral deviation, reaches $0$ at steady state.
 Finally we have also penalized acceleration change more for smooth driving experience.
@@
 \end{equation}
-Figures \ref{fig:reference_laneFollowing_curve} and \ref{fig:curvature_laneFollowing_curve} represent the first trajectory that the vehicle must perform and the curvature calculated with the previous formula \ref{eqn:curvature}.
+Figures \ref{fig:reference_laneFollowing_curve} and \ref{fig:curvature_laneFollowing_curve} represent the first trajectory that the vehicle must perform and the curvature calculated with the previous formula (\ref{eqn:curvature}).
 
@@
 At run time, we can note that $V_x$ reaches the predefined value of \SI{20}{m/s} and then it stabilizes near the cruising speed because it continues to vary the steering angle to adapt to the path to be followed.
-In this scenario the lateral deviation and the relative angle yaw do not converge to zero but oscillate.
+In this scenario the lateral deviation and the relative yaw angle do not converge to zero but oscillate.
 We can however assert that this type of oscillation is due to the type of path we are following.
 Furthermore the limits of this oscillation are very small indeed: in particular the lateral deviation is less than \SI{1.5}{cm} while the maximum relative yaw angle is \SI{0.04}{rad}.
-We can therefore state that even in this case the vehicle correctly follows the lane.
+We can therefore state that, even in this case, the vehicle correctly follows the lane.
 %LANE FOLLOWING SINUSOIDAL PATH - SIGNALS
@@
 
-As previously stated, the vehicle follows the lane and allows us to state that the control system we have designed is efficient and robust.
+As previously stated, the vehicle follows the lane and allows us to affirm that the control system we have designed is efficient and robust.
 %LANE FOLLOWING ELLIPTIC - PATH/CURVATURE

### 2019-04-05 Thesis_Latex/ThesisFinal/Introduction/Introduction.tex
update final thesis

@@
 In this introductory chapter, the ATLAS project is presented in more detail in section \ref{sec:ATLAS}, while examples of autonomous navigation projects are discussed later (section \ref{sec:autonomous_examples}).
-The context of the problem and the proposed solution of this thesis are carried out in section \ref{sec:context} while the organization of the document is discussed in section \ref{sec:outline}.
+The context of the problem and the proposed solution of this thesis are carried out in section \ref{sec:context} while the organization of the document is presented in section \ref{sec:outline}.
 \section{ATLAS Project}\label{sec:ATLAS}
@@
 In particular the ATLAS project and examples of autonomous navigation projects are presented.
-Moreover the context of the problem and the objectives to be achieved are carried out.
+Moreover the context of the problem and the objectives to be achieved are reported.
 

### 2019-04-05 Thesis_Latex/ThesisFinal/frontmatter/thanks.tex
update final thesis

--- 2019-03-06 Thesis_Latex/Thesis/Acknowledgements/Acknowledgements.tex
@@
-\chapter*{Ringraziamenti/Acknowledgements}
-\thispagestyle{empty}
-dedica a parenti e amici
+%!TEX root = ../dissertation.tex
+% the acknowledgments section
+Dedico questa tesi ai miei genitori, che mi hanno permesso  di percorrere e concludere questo cammino.
+Il loro sostegno e incoraggiamento nei momenti difficili son stati fondamentali per il raggiungimento di questo traguardo.
+\vspace{3em}
+
+Ringrazio i miei nonni, zii e mio cugino Andrea per l'affetto che non mi hanno mai fatto mancare.
+Roberta per aver sempre creduto in me ed essere stata al mio fianco in tutto questo percorso aiutandomi quando più ne avevo bisogno.
+Nicola, Federico, Giulia, Matteo e tutti gli amici di Montegrotto per essere cresciuti assieme.
+I compagni dell'Università, in particolare Nicola e Marta per aver reso questi anni di Automazione indimenticabili, Nicola e Laura per l'amicizia nata tra i banchi del DEI.
+Alberto, Jacopo e i Germofobici per aver condiviso con me un'esperienza incredibile.
+\vspace{3em}
 
 The research work for this thesis was carried out at the Laboratory for Automation and Robotics (LAR) in the Department of Mechanical Engineering of Aveiro (Portugal), during a period of 5 months as an exchange student.
-\begin{figure}[!h]
-	\centering
-	\includegraphics[width=0.50\textwidth]{../figure/logo_ua.png}
-	\label{fig:logo_ua}
-\end{figure}
-
-I would like to express my gratitude to Professor Vitor Santos, for welcoming me at the Laboratory for Automation and Robotics and making possible my experience of study at the University of Aveiro.
+I would like to express my gratitude to Professor Vitor Santos.
 His help has been invaluable both personally and academically.

### 2019-04-05 Thesis_Presentation/Presentazione/Presentazione.tex
update final thesis

@@
 \usepackage{default}
-\usepackage{subcaption}
 \usepackage{afterpage}
@@
 \usepackage{wrapfig}
-\usepackage{caption}
+\usepackage{caption,subcaption}
+\usepackage[font={small,it}]{caption}
 \usepackage{bbm}
-\usepackage{multimedia}
-
-\newsavebox{\tempbox}
+%\usepackage{movie15}
+%\usepackage{multimedia} 
+%\newsavebox{\tempbox}
 \usetheme{Padova}
+\setbeamertemplate{caption}[numbered]
 \title{Local Path Planning with Moving Obstacle Avoidance based on Adaptive MPC in ATLASCAR2}
@@
 	\begin{frame}{Formulazione del Problema} 
-
+		\begin{columns}[onlytextwidth,T]
+			\begin{column}[c]{0.35\textwidth}
+				\begin{figure}
+					\centering
+					\includegraphics[width=
+					\textwidth]{./images/car_model.pdf}
+					\caption{Bicycle model.}
+					\label{fig:car_model}
+				\end{figure}
+			\end{column}			
+			\begin{column}[c]{0.6\textwidth}
+					 Quality of \textbf{reconstruction} is related to the number
+					of cameras from which the target is visible.
+					We assume that such number is more likely to be
+					higher if the field-of-views are overlapped.
+			\end{column}
+		\end{columns}
 	\end{frame}
@@
 	\begin{frame}{Design Adaptive MPC - parte 1} % progettazione dell'algoritmo di anticollisione basato su un controllore MPC adattivo.
-
+	\begin{columns}[onlytextwidth,T]
+		\begin{column}[c]{0.72\textwidth}
+		\begin{figure}[!h]
+			\vspace{-2.3em}
+			\centering
+			\includegraphics[width=
+			\textwidth]{./images/flowchart/flowchart.pdf}
+			\captionsetup{singlelinecheck = false, format= hang, justification=raggedright,}
+			\caption{Algoritmo decisionale.}
+			\label{fig:flowchart}
+		\end{figure}
+		\end{column}	
+		\vspace{-1.1em}		
+		\begin{column}[c]{0.27\textwidth}
+			Quality of \textbf{reconstruction} is related to the number
+			of cameras from which the target is visible.
+			We assume that such number is more likely to be
+			higher if the field-of-views are overlapped.
+		\end{column}
+	\end{columns}
 	\end{frame}
@@
 	\begin{frame}{Risultati Simulativi}
-
+		\begin{figure}								
+		\href{run:./video/animation_one_obstacle_left_overtaking.avi}{\includegraphics[width=\textwidth]{./images/one_obstacle_right_overtaking/overtaking_pres.pdf}}
+		\caption{\href{run:./video/animation_one_obstacle_left_overtaking.avi}{Sorpasso a sinistra di un ostacolo in movimento (animazione).}}
+		\label{fig:un_ostacolo}
+		\vspace{-1.5em}
+		\end{figure}
+		\begin{figure}
+		\href{run:./video/animation_6_obstacles.avi}{\includegraphics[width=\textwidth]{./images/6_obstacles/6_obstacles_pres.pdf}}
+		\caption{\href{run:./video/animation_6_obstacles.avi}{Sorpasso di 6 ostacoli in movimento (animazione).}}
+		\label{fig:sei_ostacoli}
+		\vspace{-1.5em}
+		\end{figure}
+		\begin{figure}
+		\href{run:./video/animation_braking_overtaking.avi}{\includegraphics[width=\textwidth]{./images/three_obstacles_no_overtaking/braking_pres.pdf}}
+		\caption{\href{./video/animation_braking_overtaking.avi}{Frenata e sorpasso di 3 ostacoli in movimento (animazione).}}
+		\label{fig:frenata}
+		\end{figure}
 	\end{frame}

### 2019-04-05 Thesis_Presentation/Presentazione/images/flowchart/flowchart.tex
update final thesis

--- 2019-02-13 Thesis_Latex/FinalReport/figure/flowchart/flowchart.tex
@@
 	\pagestyle{empty}	
-
 	% Define block styles
@@
 	% Place nodes
-	\node [decision] (detection) {Obstacle 
-		detected?}; 
-	\node [cloud,left of=detection] (start) {Start};
-	\node [decision,below of=detection] (multiObstacles) {Multiple Obstacles detected?};
-	\node [block,right of=detection] (reference) {Follow Path: stick to the lane};
-	\node [block,left of=multiObstacles] (distance) {Obtain distance to closest obstacle};
-	\node [block,right of=multiObstacles] (distances) {Obtain distance between the obstacles};
-	\node [decision,below of=distances](space) {Free Space for Overtaking?};
-	\node [block,right of=space,node distance=3.3cm](braking){Braking/ Ostacle Velocity};
-	\node [block,below of=space](free){Overtaking on free lane};
-	\node [decision,below of=distance,node distance=2.5cm] (decisionOvertaking) {Left w.r.t vehicle?};
-	\node [block, below of=decisionOvertaking,node distance=2.5cm] (rightOver) {Right Overtaking};     
-	\node [block, right of=decisionOvertaking] (leftOver) {Left Overtaking};
+	\node [decision] (detection) {Rilevato Ostacolo?}; 
+	\node [cloud,left of=detection] (start) {Inizio};
+	\node [decision,below of=detection] (multiObstacles) {Rilevati Multipli Ostacoli?};
+	\node [block,right of=detection] (reference) {Seguire il percorso: attenersi alla corsia};
+	\node [block,left of=multiObstacles] (distance) {Calcola la distanza da quello più vicino};
+	\node [block,right of=multiObstacles] (distances) {Calcola la distanza tra gli ostacoli};
+	\node [decision,below of=distances](space) {Spazio libero per sorpassare?};
+	\node [block,right of=space,node distance=3.3cm](braking){Frenata/ Velocità Ostacolo};
+	\node [block,below of=space](free){Sorpasso nella corsia libera};
+	\node [decision,below of=distance,node distance=2.5cm] (decisionOvertaking) {A sinistra rispetto al veicolo?};
+	\node [block, below of=decisionOvertaking,node distance=2.5cm] (rightOver) {Sorpasso a Destra};     
+	\node [block, right of=decisionOvertaking] (leftOver) {Sorpasso a Sinistra};
 
@@
 	\path [line] (start) -- (detection);
-	\path [line] (detection) -- node {yes} (multiObstacles);
+	\path [line] (detection) -- node {si} (multiObstacles);
 	\path [line] (detection) -- node {no} (reference);
 	\path [line] (multiObstacles) -- node {no} (distance);
-	\path [line] (multiObstacles) -- node {yes} (distances);
+	\path [line] (multiObstacles) -- node {si} (distances);
 	\path [line] (distances)--(space);
 	\path [line] (space) -- node{no}(braking);
-	\path [line] (space) -- node{yes} (free);
+	\path [line] (space) -- node{si} (free);
 	\path [line] (braking) |- (distances);
 	\path [line] (distance) -- (decisionOvertaking);
-	\path[line] (decisionOvertaking) -- node {no}(leftOver);
-	\path[line] (decisionOvertaking) -- node{yes} (rightOver);
+	\path [line] (decisionOvertaking) -- node {no}(leftOver);
+	\path [line] (decisionOvertaking) -- node{si} (rightOver);
 	\end{tikzpicture}
-
 \end{document}

### 2019-04-05 MATLAB/6_obstacles/main_6_obstacles.m

@@ -241,7 +241,7 @@ for k = 1:length(saveSlope)
     
   %   frame = getframe(gcf);
  %    writeVideo(writerObj, frame);
-%     print('figure\6_obstacles_2','-dpdf','-r0')
+  %   print('figure\6_obstacles_pres','-dpdf','-r0')
     pause(80/car.V/length(T))
     delete(p)
     for i=1:N
@@ -249,8 +249,8 @@ for k = 1:length(saveSlope)
         delete(safe(i))
     end
 end
-% hold off
-% close(writerObj); % Saves the movie.
+ %hold off
+ %close(writerObj); % Saves the movie.
 %close(f);
 
 %obstacles6Results;

### 2019-04-05 MATLAB/one_obstacle_left_overtaking/main_one_obstacle_left.m

@@ -211,7 +211,7 @@ for k = 1:length(saveSlope)
 
   %   frame = getframe(gcf); 
  %    writeVideo(writerObj, frame);
-    
+  %  print('overtaking_pres','-dpdf','-r0'); 
     pause(80/car.V/length(T))
     delete(p)
     delete(o)

### 2019-04-05 MATLAB/three_obstacles_no_overtaking/main_three_obstacles_no_overtaking.m

@@ -235,7 +235,7 @@ for k = 1:length(saveSlope)
     
      %frame = getframe(gcf);
      %writeVideo(writerObj, frame);
-      % print('figure\braking_4','-dpdf','-r0')
+      % print('figure\braking_pres','-dpdf','-r0')
     pause(80/car.V/length(T))
     delete(p)
     for i=1:N

### 2019-04-07 Thesis_Presentation/Presentazione/Presentazione.tex
update final thesis

@@
 \usepackage[font={small,it}]{caption}
+\usepackage[font={scriptsize,it}]{subcaption}
 \usepackage{bbm}
+\usepackage{siunitx}
 %\usepackage{movie15}
@@
 %\newsavebox{\tempbox}
+\renewcommand{\vec}[1]{\ensuremath{\boldsymbol{\mathit{#1}}}}
 \usetheme{Padova}
@@
 
-	\begin{frame}{Progetto ATLASCAR2}
+	\begin{frame}{Progetto ATLAS}
+	  \begin{columns}[onlytextwidth,T]
+	\begin{column}[c]{0.65\textwidth}
+		Questo lavoro di tesi è stato sviluppato all'interno del progetto ATLAS:
+		\begin{itemize}
+			\item Creato dal gruppo di Automazione e Robotica dell'Università di Aveiro
 
-	  \begin{figure}[!t]
+			\item L'obiettivo è sviluppare sistemi per la navigazione autonoma delle automobili %L'obiettivo è studiare e sviluppare sensori avanzati e sistemi attivi per promuovere il controllo autonomo di auto e altre piattaforme
+
+			\item 2003 - 2010 Modelli piccola scala\\
+			2010 - 2019 Automobili 
+			\item 3 LIDAR, 1 Telecamera, 1  Sensore inclinometrico, 1 Unità GNSS
+		\end{itemize}
+	\end{column}
+	\begin{column}[c]{0.33\textwidth}
+		\begin{figure}
+			\vspace{-3em}
 			\centering
-	  	\begin{minipage}[t]{0.49\textwidth}
-		  	\includegraphics[scale=0.32]{./images/logo_ua.png}
-	  		\label{fig:logoua}
-	  	\end{minipage}
-	  	\begin{minipage}[t]{0.49\textwidth}
-	  		\includegraphics[scale=0.055]{./images/atlascar2.pdf}
-	  		\label{fig:atlascar2}
-	  	\end{minipage}
-	  	\caption{ATLASCAR2 - Mitsubishi iMiEV elettrica del 2015}
+			\includegraphics[scale=0.25]{./images/logo_ua.png}
 		\end{figure}
-
+		\begin{figure}
+			\vspace{-2em}
+			\captionsetup{justification=raggedleft}
+			\centering
+			\includegraphics[scale=0.048]{./images/atlascar2.pdf}
+			\caption{ATLASCAR2 Mitsubishi iMiEV elettrica del 2015}
+		\end{figure}
+	\end{column}			
+\end{columns}
 	\end{frame}
@@
 	\begin{frame}{Motivazione e Obiettivi della Tesi}
-
+	Motivazioni:
+		\begin{itemize}
+			\item Sono stati sviluppati sistemi di navigazione globali
+			\item Sistema di pianificazione locale in ambiente statico
+		\end{itemize}
+	Obiettivi:
+		\begin{itemize}
+			\item Sistema di anticollisione con ostacoli in movimento
+			\item Sistema di assistenza al mantenimento della corsia
+		\end{itemize}
+	$\Longrightarrow$ Algoritmi basati su ottimizzazione matematica.
 	\end{frame}
@@
 	\begin{frame}{Model Predictive Control}
-		\begin{block}{Normal block}
-			Fusce luctus venenatis felis quis semper
-		\end{block}
-
-		\begin{alertblock}{Alert block}
-			$$ E = (x_1 \vee \neg x_2 \vee \neg x_3) \wedge (x_1 \vee x_2 \vee x_4) $$
-		\end{alertblock}
-
-		\begin{exampleblock}{Example block}
-			Proin tincidunt, neque at tincidunt mollis
-		\end{exampleblock}
+		Model Predictive Control:
+		\begin{itemize}
+			\item tecnica avanzata basata su ottimizzazione matematica
+			\item prevede il comportamento futuro utilizzando un modello dinamico LTI
+			\item predizioni non esatte - insensibile agli errori di predizione - performance inaccettabili
+		\end{itemize}
+		$\Longrightarrow$ Tecnica adottata: {\bfseries Adaptive Model Predictive Control}
+		\begin{itemize}
+			\item adatta il modello di predizione per cambiare le condizioni operative
+			\item struttura di modello fissa, ma consente ai parametri del modello di evolvere nel tempo
+		\end{itemize}
 	\end{frame}
@@
 	\begin{frame}{Formulazione del Problema} 
+		Il modello utilizzato è il seguente:
+			\begin{equation*}
+			\label{eqn:dynamics_model_obstacle_avoidance}
+			\left \{ \begin{array}{llll}
+			\dot{x} = v\cos(\theta)\\
+			\dot{y} = v\sin(\theta)\\
+			\dot{\theta} =\dfrac{v}{C_L}\tan(\delta)\\
+			\dot{v} =0.5 \cdot T
+			\end{array} 
+			\right .
+			\Longrightarrow 
+			\begin{array}{llll}
+			\dot{\vec{x}} = \vec{f}(\vec{x},\vec{u})\\
+			\vec{y} = \vec{g}(\vec{x},\vec{u})
+			\end{array}
+			\quad \text{where} \quad 
+			\begin{array}{ll}
+			\vec{x}=\begin{bmatrix}
+			x&y&\theta&v 
+			\end{bmatrix}^\intercal
+			\\\\
+			\vec{u}=\begin{bmatrix}
+			T&\delta 
+			\end{bmatrix}^\intercal
+			\end{array}
+			\end{equation*}
+			\vspace{-1.5em}
 		\begin{columns}[onlytextwidth,T]
@@
 					\textwidth]{./images/car_model.pdf}
-					\caption{Bicycle model.}
+					\caption{Bicycle model}
 					\label{fig:car_model}
@@
 			\begin{column}[c]{0.6\textwidth} 
-					 Quality of \textbf{reconstruction} is related to the number
-					of cameras from which the target is visible.
-					We assume that such number is more likely to be
-					higher if the field-of-views are overlapped.
+				Per usare l'MPC, il sistema è stato:
+				\begin{itemize}
+					\item linearizzato con un'approssimazione del primo ordine
+					\item discretizzato con il metodo di Eulero (tempo campionamento $T_s$)
+				\end{itemize}
+				$\Rightarrow$ Ipotesi: tutti gli stati sono misurabili
 			\end{column}
@@
 	\begin{frame}{Design Adaptive MPC - parte 1} % progettazione dell'algoritmo di anticollisione basato su un controllore MPC adattivo.
+	\vspace{-1.3em}
 	\begin{columns}[onlytextwidth,T]
+		\hspace{-2.4em}
 		\begin{column}[c]{0.72\textwidth}
 		\begin{figure}[!h]
-			\vspace{-2.3em}
 			\centering
@@
 			\captionsetup{singlelinecheck = false, format= hang, justification=raggedright,}
-			\caption{Algoritmo decisionale.}
+			\caption{Algoritmo decisionale}
 			\label{fig:flowchart}
@@
 		\end{column}	
-		\vspace{-1.1em}		
-		\begin{column}[c]{0.27\textwidth}
-			Quality of \textbf{reconstruction} is related to the number
-			of cameras from which the target is visible.
-			We assume that such number is more likely to be
-			higher if the field-of-views are overlapped.
+		\hspace{1em}		
+		\begin{column}[c]{0.4\textwidth}
+		L'ATLASCAR2 deve:
+		\begin{itemize}
+		\item seguire una velocità di riferimento
+		\item rimanere nel mezzo della corsia centrale
+		\end{itemize}
+		\vspace{1.4em}
+		Per definire l'area del sorpasso usiamo i seguenti vincoli di ingresso/uscita:
+		\begin{equation*}
+		\label{eqn:mixed_IO_constraints}
+		\vec{E}\vec{u}+\vec{F}\vec{y}\leq \vec{G}
+		\end{equation*}
+		dove $\vec{E},\vec{F}$ e $\vec{G}$ sono aggiornate ogni $T_s$
 		\end{column}
@@
 	\begin{frame}{Design Adaptive MPC - parte 2} % progettazione dell'algoritmo di anticollisione basato su un controllore MPC adattivo.
-
+		\hspace{-2em}
+		{\vspace{5em} L'area del sorpasso è definita come $\vec{E}\vec{u}+\vec{F}\vec{y}\leq \vec{G}$ dove: $\quad\Rightarrow\vec{E}=\vec{0}_{5\times2}$}
+		\begin{columns}[onlytextwidth,T]
+			\hspace{-1.5em}
+			\begin{column}[c]{0.73\textwidth}
+				\vspace{-5.6em}
+				\begin{figure}[!t]
+					\centering
+					\includegraphics[width=0.9\columnwidth]{./images/constraint/constraint.pdf}
+					\caption{Vincoli nel sorpasso a sinistra.}
+					\label{fig:constraint}
+				\end{figure}
+				\vspace{-0.8em}
+				\hspace{-0.5em} Sono stati definiti i seguenti vincoli:
+				\begin{enumerate}
+				\item limite superiore coordinata $y$
+				\item limite inferiore coordinata $y$
+				\item linea veicolo-angolo della zona di sicurezza
+				\item limite destro coordinata $x$
+				\item limite sinistro coordinata $x$
+				\end{enumerate}
+			\end{column}
+			\begin{column}[c]{0.34\textwidth}
+				\vspace{-6em}
+				\begin{equation*}
+				\begin{array}{lll}
+				\hspace{-0.5em}\Rightarrow\vec{F}=\begin{bmatrix}
+				0&1&0&0\\
+				0&-1&0&0\\
+				cS&-1&0&0\\
+				1&0&0&0\\
+				-1&0&0&0\\
+				\end{bmatrix}\\\\
+				\quad\Rightarrow\vec{G}=
+				\begin{bmatrix}
+				W/2\\W/2\\-cI\\x_{\max}\\x_{\min}
+				\end{bmatrix}
+				\end{array}
+				\end{equation*}
+			\end{column}
+		\end{columns}
 	\end{frame}
@@
 		\href{run:./video/animation_one_obstacle_left_overtaking.avi}{\includegraphics[width=\textwidth]{./images/one_obstacle_right_overtaking/overtaking_pres.pdf}}
-		\caption{\href{run:./video/animation_one_obstacle_left_overtaking.avi}{Sorpasso a sinistra di un ostacolo in movimento (animazione).}}
+		\caption{\href{run:./video/animation_one_obstacle_left_overtaking.avi}{Sorpasso a sinistra di un ostacolo in movimento (animazione)}}
 		\label{fig:un_ostacolo}
@@
 		\href{run:./video/animation_6_obstacles.avi}{\includegraphics[width=\textwidth]{./images/6_obstacles/6_obstacles_pres.pdf}}
-		\caption{\href{run:./video/animation_6_obstacles.avi}{Sorpasso di 6 ostacoli in movimento (animazione).}}
+		\caption{\href{run:./video/animation_6_obstacles.avi}{Sorpasso di 6 ostacoli in movimento (animazione)}}
 		\label{fig:sei_ostacoli}
@@
 		\href{run:./video/animation_braking_overtaking.avi}{\includegraphics[width=\textwidth]{./images/three_obstacles_no_overtaking/braking_pres.pdf}}
-		\caption{\href{./video/animation_braking_overtaking.avi}{Frenata e sorpasso di 3 ostacoli in movimento (animazione).}}
+		\caption{\href{./video/animation_braking_overtaking.avi}{Frenata e sorpasso di 3 ostacoli in movimento (animazione)}}
 		\label{fig:frenata}
@@
 	\begin{frame}{Formulazione del Problema}
+		\vspace{-2.5em}
+		\begin{columns}[onlytextwidth,T]
+			\hspace{-2.5em}
+			\begin{column}[c]{0.5\textwidth}
+			\begin{figure}[!h]
+			\centering
+			\includegraphics[width=\columnwidth]{./images/laneFollowing/laneFollowingPres.pdf}
+		\end{figure}
+		\centering
+		\textbf{Dinamica dei Sensori\\}
+		$e_1$ = Deviazione Laterale\\
+		$e_2$ = Tasso di imbardata relativo\\
+		$\big\Downarrow$\\
+		Devono essere guidati a zero
+			\end{column}
+			\begin{column}[c]{0.65\textwidth}
+				\textbf{Obiettivo}: il veicolo deve seguire la linea centrale, con una velocità di riferimento.\\
+				\vspace{2em}
+				\textbf{Dinamica del veicolo}:
+				\begin{itemize}
+					\item Longitudinale $\rightarrow$ Funzione di trasferimento del primo ordine.
+					\item Laterale $\rightarrow$ Bicycle model parametrizzato
+				\end{itemize}
+				\vspace{2em}
+				\centering
+				\textbf{Modello complessivo}: viene discretizzato secondo Eulero, tiene conto dell' intera dinamica e degli errori.
+			\end{column}
+		\end{columns}
 
@@
 	\begin{frame}{Design Adaptive MPC} % progettazione dell'algoritmo di mantenimento della corsia basato su un controllore MPC adattivo.
-
+		\begin{figure}[!h]
+			\includegraphics[width=\textwidth]{./images/lane_following_AMPC.pdf}
+			\caption{Schema di controllo per il mantenimento della corsia}
+			\label{fig:scheme_lane_following}
+		\end{figure}
+		\textbf{Adaptive MPC:} modello predittivo con 6 stati, 3 output, 2 variabili indipendenti. Abbiamo vincolato l'accelerazione e l'angolo di sterzata per una guida più confortevole.
 	\end{frame}
 
-	\begin{frame}{Risultati Simulativi}
+	\begin{frame}{Risultati Simulativi - parte 1}
+		\vspace{-1.4em}
+		\begin{columns}[onlytextwidth,T]	
+			\begin{column}[c]{0.5\columnwidth}
+				\begin{figure}[!h]
+					\includegraphics[width=0.92\columnwidth]{../../MATLAB/lane_following/figure/Reference.pdf}
+					\vspace{-0.5em}
+					\caption{Traiettoria Sinusoidale}	
+				\end{figure}
+				\begin{figure}[!h]
+					\vspace{-2.4em}
+					\includegraphics[width=0.92\columnwidth]{../../MATLAB/lane_following/figure/Curvature.pdf}
+					\vspace{-0.5em}
+					\caption{Curvatura}
+				\end{figure}
+			\end{column}
+			\begin{column}[c]{0.55\columnwidth}
+				Esempio: \textbf{Percorso Sinusoidale}
+				\begin{equation*}
+				\begin{array}{ll}
+				X_\text{ref}=V_x\cdot t,\quad t\in[0,20]\SI{}{s}\\ Y_\text{ref}=5\sin(X_\text{ref}/20) 
+				\end{array}
+				\end{equation*}
+				Ipotesi:\\
+				{\hspace{1em}
+				$\rightarrow$ Velocità iniziale \SI{15}{m/s}\\
+				\hspace{1em} $\rightarrow$ Velocità di crociera \SI{20}{m/s}\\}
+				\vspace{1.5em}
+				Calcoliamo la \textbf{Curvatura}:
+				\begin{equation*}
+				\label{eqn:curvature}
+				\kappa=\frac{x'y''-x''y'}{(x'^2+y'^2)^\frac{3}{2}}
+				\end{equation*}
+				che sarà il riferimento da inseguire
+			\end{column}	
+		\end{columns}		
+	\end{frame}
 
+	\begin{frame}{Risultati Simulativi - parte 2}	
+		\vspace{-2.4em}
+		\begin{columns}[onlytextwidth,T]
+			\begin{column}[c]{0.5\columnwidth}
+				\begin{figure}[!h]
+				\includegraphics[width=0.92\columnwidth]{../../MATLAB/lane_following/figure/LongitudinalVelocityVsTime.pdf}
+				%\captionsetup{font=scriptsize}
+				\vspace{-0.5em}
+				\subcaption*{Velocità Longitudinale $V_x$}
+				\end{figure}
+				\begin{figure}[!h]
+				\vspace{-3em}
+				\includegraphics[width=0.92\columnwidth]{../../MATLAB/lane_following/figure/SteeringAngleVsTime.pdf}
+				%\captionsetup{font=scriptsize}
+				\vspace{-0.5em}
+				\subcaption*{Angolo di Sterzata $u_2$}
+				\end{figure}	
+			\end{column}		
+			\begin{column}[c]{0.5\columnwidth}
+				\begin{figure}[!h]
+				\includegraphics[width=0.92\columnwidth]{../../MATLAB/lane_following/figure/AccelerationVsTime.pdf}
+				%\captionsetup{font=scriptsize}
+				\vspace{-0.5em}
+				\subcaption*{Accelerazione $u_1$}	
+				\end{figure}
+				\begin{figure}[!h]
+				\vspace{-3em}	
+				\includegraphics[width=0.92\columnwidth]{../../MATLAB/lane_following/figure/LateralDeviationVsTime.pdf}
+				%\captionsetup{font=scriptsize}
+				\vspace{-0.5em}
+				\subcaption*{Deviazione Laterale $e_1$}
+				\end{figure}
+			\end{column}
+		\end{columns}		
 	\end{frame}
+
 	\begin{frame}{Conclusioni e Sviluppi Futuri}
-		contenuto...
+		\begin{columns}[onlytextwidth,T]
+			\begin{column}[c]{0.75\textwidth}
+				\textbf{Conclusioni}:			\begin{itemize}
+					\item Sistema di anticollisione in ambiente dinamico (ostacoli in movimento)
+					\item Sistema di assistenza al mantenimento della corsia (Lane Keeping Assist)
+				\end{itemize}
+				\textbf{Sviluppi futuri}:
+				\begin{itemize}
+					\item Combinazione dei due metodi in un unico schema di controllo
+					\item Implementazione in ambiente ROS-Gazebo
+					\item Uso di dati reali collezionati dai sensori dell'ATLASCAR2 per testare gli algoritmi sviluppati
+				\end{itemize}
+			\end{column}
+			\begin{column}[c]{0.20\textwidth}
+				\begin{figure}
+					\vspace{-3em}
+					\includegraphics[width=
+					\textwidth]{./images/GAZEBO.png}
+				\end{figure}
+				\begin{figure}
+					\vspace{-3em}
+					\includegraphics[width=
+					\textwidth]{./images/ROS.png}
+				\end{figure}
+			\end{column}			
+		\end{columns}
 	\end{frame}

### 2019-04-19 Thesis_Latex/ThesisFinal/Chapter3/Chapter3.tex
update final thesis

@@
 If the plant is strongly nonlinear or its characteristics vary dramatically with time, MPC performance might become unacceptable because LTI prediction accuracy degrade \cite{mpctoolbox}.
+
 A method that can address this degradation by adapting the prediction model for changing operating conditions is called Adaptive MPC: this control strategy uses a fixed model structure, but allows the model parameters to evolve with time.
@@
 most updated value) \cite{mpctoolbox}.
+
 In adaptive MPC, as time evolves it should update the nominal operating point to be consistent with the updated plant model.

### 2019-04-19 Thesis_Presentation/Presentazione/Presentazione.tex
update final thesis

@@
 \usepackage{siunitx}
+\usepackage{amsmath,amssymb}
 %\usepackage{movie15}
@@
 
-	\begin{frame}{Model Predictive Control}
+	\begin{frame}{Model Predictive Control - parte 1}
 		Model Predictive Control:
@@
 		\end{itemize}
+	\end{frame}
+
+	\begin{frame}{Model Predictive Control - parte 2}
+		Dato un sistema discreto LTI:
+		\begin{equation*}
+		\label{eqn:MPC_plant_discrete}
+		\vec{x}(k+1)=\vec{A}\vec{x}(k)+ \vec{B} \vec{u}(k)
+		\end{equation*}
+		%dove $\vec{x}(k)\in\mathbb{R}^n$, $\vec{u}(k)\in\mathbb{R}^m$.
+		L'idea è quella di minimizzare la funzione obiettivo assicurando che i vincoli siano rispettati:
+		\begin{equation*}
+		\label{eqn:MPC_optimization}
+		\begin{aligned}
+		& \underset{\textbf{u}}{\text{minimizzare}}
+		& & {\text{\itshape
+				\bfseries J}}(\vec{x}(k), \textbf{u}) \\
+		& \text{soggetto a}
+		& & \vec{x}_{k+i+1} = \vec{A}\vec{x}_{k+i}+ \vec{B} \vec{u}_{k+i}\quad\forall i=0,\dots N-1;\\
+		& & & \vec{x}_{k+i}\in \mathcal{X}\quad\forall i=0,\dots N-1;\\
+		& & & \vec{u}_{k+i}\in \mathcal{U}\quad\forall i=0,\dots N-1;\\  
+		& & & \vec{x}_{k+N}\in \mathcal{X}_f;\quad\vec{x}_k = \vec{x}(k).
+		\end{aligned}
+		\end{equation*}
+		%dove $\textbf{u}=(\vec{u}_k,\dots,\vec{u}_{k+N-1})$ sono una sequenza di ingressi di controllo, $\vec{x}_{k+i}$ è lo stato al tempo $k+i$ come predetto al tempo $k$, $N$ è l'orizzonte di predizione.
+Gli insiemi $\mathbb{X}\in\mathbb{R}^n$ e $\mathbb{U}\in\mathbb{R}^m$ definiscono i vincoli sullo stato e sull'ingresso.Infine l'insieme $\mathbb{X}_f\subseteq\mathbb{X}$ definisce il vincolo finale sullo stato.
 	\end{frame}
@@
 		\begin{columns}[onlytextwidth,T]
-			\begin{column}[c]{0.75\textwidth}
+			\begin{column}[c]{0.79\textwidth}
 				\textbf{Conclusioni}:			\begin{itemize}
-					\item Sistema di anticollisione in ambiente dinamico (ostacoli in movimento)
-					\item Sistema di assistenza al mantenimento della corsia (Lane Keeping Assist)
+					\item Sistema di anticollisione in ambiente dinamico
+					\item Sistema Lane Keeping Assist
 				\end{itemize}
@@
 				\begin{itemize}
-					\item Combinazione dei due metodi in un unico schema di controllo
+					\item Combinazione in un unico schema di controllo
 					\item Implementazione in ambiente ROS-Gazebo
-					\item Uso di dati reali collezionati dai sensori dell'ATLASCAR2 per testare gli algoritmi sviluppati
+					\item Dati reali collezionati dai sensori dell'ATLASCAR2 per testare gli algoritmi
 				\end{itemize}
@@
 		\end{columns}
+		\vspace{1em}
+		$\Longrightarrow$ A. Franco, 
+		V. Santos, {\itshape ``Short-term Path Planning with Multiple Moving Obstacle Avoidance based on Adaptive MPC''}, IEEE ICARSC 2019, Porto, April 24-26
 	\end{frame}
 
+	\section{Grazie per l'attenzione! \qquad\qquad{\itshape\large(Obrigado)}}
 \end{document}
